### 2024-11-20 wp/method and results.tex
dfd

%l !Rnw weave = knitr

\documentclass[11pt]{article}

\usepackage[]{graphicx} % omit 'demo' option in real doc.
\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\usepackage{epstopdf}
\usepackage{float}
\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage{hyperref}
\hypersetup{
        colorlinks=true,
        breaklinks,
        allcolors=[RGB]{128,0,0}
}

\let\oldFootnote\footnote
\newcommand\nextToken\relax

\renewcommand\footnote[1]{%
    \oldFootnote{#1}\futurelet\nextToken\isFootnote}

\newcommand\isFootnote{%
    \ifx\footnote\nextToken\textsuperscript{,}\fi}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{crimson}

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}

\usepackage{bbding} % checkmark symbol
\usepackage{comment} % checkmark symbol

\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\floatpagefraction}{0.75}

%Bibliography
\usepackage{natbib}
%\usepackage[autostyle]{csquotes}
%\usepackage[backend=bibtex, style=authoryear, natbib=true]{biblatex}
%\addbibresource{CCH.bib}

%%For Hypotheses and Subhypotheses
%\usepackage{ntheorem}
\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp}
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
}
\makeatother
%%%

\setcounter{MaxMatrixCols}{10}

\theoremstyle{plain}
\newtheorem{prop}{\protect\propositionname}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\makeatother
\providecommand{\examplename}{Example}
\providecommand{\propositionname}{Proposition}
\providecommand{\theoremname}{Theorem}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bb}{\begin{block}}
\newcommand{\eb}{\end{block}}
\newcommand{\bmath}{\begin{eqnarray}}
\newcommand{\emath}{\end{eqnarray}}
\newcommand{\bmathnn}{\begin{eqnarray*}}
\newcommand{\emathnn}{\end{eqnarray*}}
\newtheorem{theorem}{{Theorem}}%[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{prediction}{Prediction}
\newtheorem{open_question}{Open question}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{claim}[theorem]{{Claim}}
\newtheorem{example}[theorem]{{Example}}
\newtheorem{corollary}[theorem]{{Corollary}}
\newtheorem{remark}[theorem]{{Remark}}
\newtheorem{assumptions}[theorem]{{Assumptions}}
\newtheorem*{thm1star}{{Theorem $\mathbf{1^*}$}}
\newtheorem*{thm2star}{{Theorem $\mathbf{2^*}$}}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}

%For nice tables
\usepackage{booktabs}
\usepackage{array}
\usepackage{threeparttable}
\usepackage{tabulary}
\newcolumntype{M}[1]{{\centering\arraybackslash}m{#1}}

%Expectation opperator
\newcommand{\Expect}{{\rm I\kern-.3em E}}

%Significance commands
\newcommand*{\SuperScriptSameStyle}[1]{%
  \ensuremath{%
    \mathchoice
      {{}^{\displaystyle #1}}%
      {{}^{\textstyle #1}}%
      {{}^{\scriptstyle #1}}%
      {{}^{\scriptscriptstyle #1}}%
  }%
}

\newcommand*{\oneS}{\SuperScriptSameStyle{*}}
\newcommand*{\twoS}{\SuperScriptSameStyle{**}}
\newcommand*{\threeS}{\SuperScriptSameStyle{*{*}*}}
\newcommand{\vh}[1]{\textcolor{red}{(VH: #1)}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\title{Mobile Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

\vspace{1cm}

\author{
\textbf{Illan Barriola} \\ CRED -- Paris II \\
\and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
}

\date{ \today}

\maketitle
\section*{Data}
We use Afrobarometer surveys to leverage geocoded information on public opinion, information-gathering and demographic characteristics across African countries at the individual level.\footnote{All Afrobarometer surveys were conducted via-in-person, face-to-face interviews. The method did not change to computer-assisted interviews, thereby avoiding potential bias toward areas with mobile internet coverage.} We rely on rounds 5 to 8, covering the period from 2011 to 2021, to construct our sample of 98,235 individual respondents across 20 Sub-Saharan African countries.\footnote{Our sample includes: Benin, Burkina Faso, Botswana, Cameroon, Ivory Coast, 
Ghana, Guinea, Kenya, Liberia, Mali, Malawi, Mozambique, Namibia, Niger, Nigeria, Sierra Leone, Tanzania, Uganda, Zambia, Zimbabwe.}\footnote{We exclude islands, countries with multiple capitals, and Northern African countries. We also exclude Burundi, Gabon, Gambia, and Senegal due to missing data on mobile internet coverage.}
We measure political accountability by focusing on two key sets of variables from the Afrobarometer.
First, we measure trust in institutions through the following questions:
\textit{‘‘How much do you trust each of the following: the president, the parliament/national assembly?’’}.
Each question is measured on a scale from 0 ('Not at all') to 3 ('A lot'). We construct our main dependent variable \textit{Institutional Trust} by averaging the responses to these two questions.\footnote{In Table X we report the results of the replication using the variables analyzed individually.}
Second, we measure the willingness to sanction the ruling party through the following question:
\textit{‘‘If [presidential elections] were held tomorrow, which [party’s candidate] would you vote for?’’}.
We create a binary variable that equals 1 if the respondent indicates they would vote for any party other than the ruling party, and 0 if they would vote for the ruling party.\\

The geographic spread of our sample, ranging from urban centers to remote rural areas, allows us to effectively examine how the impact of mobile internet on political accountability varies with distance from political centers.
We leverage the precise geocoding of Afrobarometer survey enumeration areas to calculate the distance of each survey respondent from their country's capital city. Similar to Michalopoulos and Papaioannou (2014), to account for varying country sizes in our sample, we construct a relative distance measure as our main independent variable instead of using absolute distance from the capital city. For each respondent, we calculate the relative distance by dividing the respondent's distance from the capital by the maximum distance to the capital within the country.
This standardization allows for meaningful comparisons across countries of different sizes. The resulting values range from 0 (at the capital) to 1 (at the furthest point from the capital), providing an intuitive scale of remoteness that is comparable across all countries in our sample.\\

We combine Afrobarometer geocoded individual level data with detailed digital maps of mobile internet coverage provided by the Global System for Mobile Communications Association (GSMA). These maps compile coverage data from mobile network providers to measure coverage availability at a reliable signal strength with a 1x1-kilometer grid cell resolution.
To integrate mobile network coverage data with the Afrobarometer surveys, we calculate regional mobile internet coverage for each region and year. This process involves overlaying the mobile internet coverage map with population density data at the grid-cell level. We then compute a weighted average of mobile internet availability for each region, using population density as weights. These weights are normalized to sum to one, ensuring comparability across regions of different sizes and population distributions.

\section*{IV method}

Specifically, our main treatment of interest is the interaction between internet coverage at the regional level and distance from the capital city. This approach allows us to capture potential heterogeneity in the effect of internet news exposure across different geographic contexts.\\

Several econometric challenges necessitate an instrumental variable (IV) approach. Reverse causality is a concern, as trust in political institutions may influence internet news consumption patterns, creating a bidirectional relationship that complicates causal inference. Omitted variable bias poses a threat, as unobservable factors such as political interest, media literacy, or cultural attitudes may affect both news consumption and institutional trust, potentially biasing our estimates. Furthermore, measurement error in self-reported internet news consumption could lead to attenuation bias. These issues are compounded when considering the interaction term, as any endogeneity in the component variables carries over and potentially amplifies in the interaction.\\

To address these challenges, we propose using the interaction between mobile internet coverage and distance from the capital city as our instrument. This choice is motivated by several factors. Higher mobile internet coverage directly increases the potential for internet news consumption, ensuring relevance. The rollout of internet infrastructure is primarily driven by commercial and technical factors rather than political considerations, enhancing the likelihood of satisfying the exclusion restriction. Moreover, mobile internet coverage and its impact likely vary with distance from the capital city, providing a strong first-stage relationship with our treatment of interest.
The interaction term in our instrument captures how the availability of mobile internet coverage changes with distance from the capital city, which in turn affects the likelihood of internet news consumption across different regions. This approach allows us to estimate how the influence of internet news consumption on trust varies depending on geographic proximity to the center of political power, using only the variation in news consumption driven by exogenous factors related to internet infrastructure development.\\

While our instrument choice is theoretically justified, we acknowledge potential criticisms. In some contexts, governments may influence internet infrastructure deployment for political reasons, potentially violating the exclusion restriction. Additionally, uneven internet development could reflect broader patterns of regional inequality, which might independently affect trust in institutions. The interaction with distance from the capital could exacerbate these concerns if there are systematic differences in how mobile internet infrastructure is rolled out about proximity to the political center.\\

To address these concerns, we argue that economic and technical determinants are the primary drivers of the expansion of mobile internet coverage, rather than political incentives. Investment decisions made by telecom providers — often international firms – are made on the basis of their economic viability and expected returns. This emphasis on financial incentives diminishes the probability of politically motivated deployment strategies. Additionally, variations in mobile internet coverage across regions often arise due to technical and geographical limitations. Terrain, population density and the availability of supporting infrastructure all define the feasibility and cost of network deployment. These technical considerations often override any potential political motivation in infrastructure development decisions. We capture the nuanced interplay of these economic and technical factors across diverse geographic contexts by using an instrument that interacts mobile internet coverage and distance to the capital.\\

\end{document}

### 2024-11-20 wp/tables.tex
dfd

%l !Rnw weave = knitr

\documentclass[11pt]{article}

\usepackage[]{graphicx} % omit 'demo' option in real doc.
\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\usepackage{epstopdf}
\usepackage{float}
\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage{hyperref}
\hypersetup{
        colorlinks=true,
        breaklinks,
        allcolors=[RGB]{128,0,0}
}

\let\oldFootnote\footnote
\newcommand\nextToken\relax

\renewcommand\footnote[1]{%
    \oldFootnote{#1}\futurelet\nextToken\isFootnote}

\newcommand\isFootnote{%
    \ifx\footnote\nextToken\textsuperscript{,}\fi}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{crimson}

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{rotating}

\usepackage{bbding} % checkmark symbol
\usepackage{comment} % checkmark symbol

\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\floatpagefraction}{0.75}

%Bibliography
\usepackage{natbib}
%\usepackage[autostyle]{csquotes}
%\usepackage[backend=bibtex, style=authoryear, natbib=true]{biblatex}
%\addbibresource{CCH.bib}

%%For Hypotheses and Subhypotheses
%\usepackage{ntheorem}
\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp}
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
}
\makeatother
%%%

\setcounter{MaxMatrixCols}{10}

\theoremstyle{plain}
\newtheorem{prop}{\protect\propositionname}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\makeatother
\providecommand{\examplename}{Example}
\providecommand{\propositionname}{Proposition}
\providecommand{\theoremname}{Theorem}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bb}{\begin{block}}
\newcommand{\eb}{\end{block}}
\newcommand{\bmath}{\begin{eqnarray}}
\newcommand{\emath}{\end{eqnarray}}
\newcommand{\bmathnn}{\begin{eqnarray*}}
\newcommand{\emathnn}{\end{eqnarray*}}
\newtheorem{theorem}{{Theorem}}%[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{prediction}{Prediction}
\newtheorem{open_question}{Open question}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{claim}[theorem]{{Claim}}
\newtheorem{example}[theorem]{{Example}}
\newtheorem{corollary}[theorem]{{Corollary}}
\newtheorem{remark}[theorem]{{Remark}}
\newtheorem{assumptions}[theorem]{{Assumptions}}
\newtheorem*{thm1star}{{Theorem $\mathbf{1^*}$}}
\newtheorem*{thm2star}{{Theorem $\mathbf{2^*}$}}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}

%For nice tables
\usepackage{booktabs}
\usepackage{array}
\usepackage{threeparttable}
\usepackage{tabulary}
\newcolumntype{M}[1]{{\centering\arraybackslash}m{#1}}

%Expectation opperator
\newcommand{\Expect}{{\rm I\kern-.3em E}}

%Significance commands
\newcommand*{\SuperScriptSameStyle}[1]{%
  \ensuremath{%
    \mathchoice
      {{}^{\displaystyle #1}}%
      {{}^{\textstyle #1}}%
      {{}^{\scriptstyle #1}}%
      {{}^{\scriptscriptstyle #1}}%
  }%
}

\newcommand*{\oneS}{\SuperScriptSameStyle{*}}
\newcommand*{\twoS}{\SuperScriptSameStyle{**}}
\newcommand*{\threeS}{\SuperScriptSameStyle{*{*}*}}
\newcommand{\vh}[1]{\textcolor{red}{(VH: #1)}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\title{Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

\vspace{1cm}

\author{
\textbf{Illan Barriola} \\ CRED -- Paris II \\
\and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
}

\date{ \today}

\maketitle

\begin{table}[H]
    \sffamily
    \caption{{Effect of distance from the capital on political trust}}
    \centering
    %\footnotesize
    \resizebox{12cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
    &  \multicolumn{4}{c}{{OLS}}  \\
    \cmidrule(r){2-5}
    &  \multicolumn{4}{c}{{Political trust}}  \\
    \cmidrule(r){2-5}
    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
     \midrule

     Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
     \medskip
     &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
     \midrule
     \smallskip
    Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
    \smallskip
    Country controls & Yes& No& Yes& No\\
    \smallskip
    Round FE & Yes & No& Yes & No\\
    \smallskip
    Country X Round FE       & No & Yes& No & Yes\\
    \smallskip
    Ethnic homeland FE & No & No & Yes& Yes\\
    \smallskip
    Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
    Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\

                          \bottomrule
    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}
    }
    \end{table}

    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{17cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance from the capital &0.463***&&&& 1.361***\\      
    \smallskip
    &      (0.05)   &&&&     (0.49)   \\
    Internet coverage     &       0.029   &&&&       1.470**  \\
    \smallskip
    & (0.06)   &&&&      (0.64)    \\ 
    \smallskip
    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
    \smallskip  &       (0.10)   &&&               &      (1.09) \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-&-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{27cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}

        \begin{table}[H]
            \sffamily
            \caption{{Other outcomes}}
            \centering
            %\footnotesize
            \resizebox{18cm}{!}{
            \begin{tabular}{@{\extracolsep{5pt}} l c c}
            \\
            \toprule
            \toprule
            & \multicolumn{2}{c}{2SLS}\\
            \cmidrule(r){2-3}
            &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
                \cmidrule(r){2-2}
                \cmidrule(r){3-3}
                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
             \midrule

             Distance from the capital&   -1.306***&       1.560***\\
             \smallskip
             &      (0.40)   &      (0.52)   \\
             Internet coverage     &      -1.370***&       1.565**  \\
             \smallskip
             &      (0.47)   &      (0.62)   \\
             Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
             \medskip
             &       (0.92)   &      (1.16)   \\
             \midrule
             \smallskip
            Individual \& regional controls  & Yes & Yes\\
            \smallskip
            Country X Round FE       & Yes& Yes\\
            \smallskip
            Observations      &       99,414   &       98,512  \\            \bottomrule
            \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
            includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
            \end{tabular}
            }
            \end{table}

            \begin{table}[H]
              \sffamily
              \caption{{Media and institutions freedom}}
              \centering
              %\footnotesize
              \resizebox{16cm}{!}{
              \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
              \\
              \toprule
              \toprule
              & \multicolumn{4}{c}{2SLS: Political trust}\\
              \cmidrule(r){2-5}
              & \multicolumn{4}{c}{{Base sample}}\\
              \cmidrule(r){2-5}
              &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
              \cmidrule(r){2-3}
                  \cmidrule(r){4-5}
                  & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
                  \cmidrule(r){2-2}
                  \cmidrule(r){3-3}
                  \cmidrule(r){4-4}
                  \cmidrule(r){5-5}
                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
               \midrule

               Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
               \smallskip
               &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
               Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
               \smallskip
               &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
            Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
            \medskip
            &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\

               \midrule
               \smallskip
              Individual \& regional controls  & Yes & Yes & Yes & Yes\\
              \smallskip
              Country X Round FE       & Yes& Yes & Yes& Yes\\
              \smallskip
              Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
              \bottomrule
              \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
              \end{tabular}
              }
              \end{table}

              \begin{table}[H]
                \sffamily
                \caption{{Individual heterogeneity}}
                \centering
                %\footnotesize
                \resizebox{16cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
                \\
                \toprule
                \toprule
                & \multicolumn{8}{c}{2SLS: Political trust}\\
                \cmidrule(r){2-9}
                & \multicolumn{8}{c}{{Base sample}}\\
                \cmidrule(r){2-9}
                &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}&  \multicolumn{4}{c}{{Age}}\\
                \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    \cmidrule(r){6-9}
                    & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}} & \multicolumn{1}{c}{{18-25}}& \multicolumn{1}{c}{{26-35}}& \multicolumn{1}{c}{{36-44}}& \multicolumn{1}{c}{{45+}}\\
                    \cmidrule(r){2-2}
                    \cmidrule(r){3-3}
                    \cmidrule(r){4-4}
                    \cmidrule(r){5-5}
                    \cmidrule(r){6-6}
                    \cmidrule(r){7-7}
                    \cmidrule(r){8-8}
                    \cmidrule(r){9-9}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
                 \midrule

                 Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961***&       1.295** &       0.965   &       1.438** &       1.723*** \\
                 \smallskip
                 &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)   &      (0.57)   &      (0.63)   &      (0.56)   &      (0.59)   \\
                 Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***&       1.439*  &       0.982   &       1.236*  &       2.540***\\
                 \smallskip
                 &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   &      (0.74)   &      (0.76)   &      (0.72)   &      (0.87)   \\
                   Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447*  &      -1.994   &      -1.477   &      -2.577** &      -3.103**  \\
                   \medskip
                   &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)   &      (1.24)   &      (1.38)   &      (1.28)   &      (1.39)   \\
                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes\\
                \smallskip
                Country X Round FE       & Yes& Yes & Yes& Yes & Yes& Yes & Yes& Yes\\
                \smallskip
                Observations         &       36,389   &       62,039   &       37,348   &       60,887   &       25,442   &       29,913   &       20,074   &       23,246   \\
                \bottomrule
                \multicolumn{9}{p{24cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

            \begin{table}[H]
              \sffamily
              \caption{{Generalized trust}}
              \centering
              %\footnotesize
              \resizebox{16cm}{!}{
              \begin{tabular}{@{\extracolsep{5pt}} l c c}
              \\
              \toprule
              \toprule
              & \multicolumn{2}{c}{2SLS}\\
              \cmidrule(r){2-3}
              & \multicolumn{2}{c}{{Base sample: rounds 5 $\&$ 8}}\\
              \cmidrule(r){2-3}
                  & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Generalized trust}}\\
                  \cmidrule(r){2-2}
                  \cmidrule(r){3-3}
                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
               \midrule
               Distance from the capital&       1.358** &      -0.157   \\
               \smallskip
               &      (0.62)   &      (0.17)    \\
               Internet coverage    &       1.508   &      -0.101    \\
               \smallskip
               &      (0.94)   &      (0.23)   \\
               Distance from the capital $\times$ Internet coverage&      -2.161*  &       0.542   \\
               \medskip
               &      (1.22)   &      (0.33)   \\

               \midrule
               \smallskip
              Individual \& regional controls  & Yes & Yes\\
              \smallskip
              Country X Round FE       & Yes& Yes\\
              \smallskip
              Observations         &     49,404   &       49,362\\
              \bottomrule
              \multicolumn{3}{p{14cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
              \end{tabular}
              }
              \end{table}

              \begin{table}[H]
                \sffamily
                \caption{{Effect of distance from the capital on institutional trust (President, Parliament, Electoral commission)}}
                \centering
                %\footnotesize
                \resizebox{16cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                \\
                \toprule
                \toprule
                &  \multicolumn{6}{c}{{Trust in institutions (President, Parliament, Electoral commission)}}  \\
                \cmidrule(r){2-7}
                &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                \cmidrule(r){2-6}
                \cmidrule(r){7-7}
                & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                    \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    \cmidrule(r){6-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                 \midrule

                 Distance from the capital&    0.295***&       0.301***&       0.563***&       0.306 &       0.483***&       1.738***\\
                 \smallskip
                 &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20) &      (0.05)   &      (0.58) \\
                 Internet coverage &&&&&       0.016   &       2.035*** \\
                 \smallskip

                 &&&&&      (0.06)   &      (0.71)\\
                 Distance from the capital $\times$ Internet coverage &&&&&      -0.458***&-2.992**\\
                 \medskip
                 &&&&&      (0.10) & (1.32)\\
                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                \smallskip
                Country controls & Yes& No& Yes& No& No& No\\
                \smallskip
                Round FE & Yes & No& Yes & No& No& No\\
                \smallskip
                Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                \smallskip
                Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                \smallskip
                Observations           &   98,499   &       98,499   &        4,202   &        4,202   & 98,499   &       98,499 \\
                Adjusted-R$^2$        &        0.164   &       0.198   &       0.148   &       0.184  & 0.200   &       - \\

                                      \bottomrule
                \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

                \begin{table}[H]
                  \sffamily
                  \caption{{Effect of distance from the capital on trust in president}}
                  \centering
                  %\footnotesize
                  \resizebox{16cm}{!}{
                  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                  \\
                  \toprule
                  \toprule
                  &  \multicolumn{6}{c}{{Trust in president}}  \\
                  \cmidrule(r){2-7}
                  &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                  \cmidrule(r){2-6}
                  \cmidrule(r){7-7}
                  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                      \cmidrule(r){2-3}
                      \cmidrule(r){4-5}
                      \cmidrule(r){6-6}
                      \cmidrule(r){7-7}
                      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                   \midrule

                   Distance from the capital&       0.287***&       0.262***&       0.799***&       0.343   &       0.473***&       1.517**\\
                   \smallskip
                   &      (0.05)   &      (0.03)   &      (0.19)   &      (0.25)   &      (0.06)   &      (0.63) \\
                   Internet coverage &&&&       &       0.047   &       1.659**  \\
                   \smallskip
                   &&&&    &      (0.07)   &      (0.81) \\
                   Distance from the capital $\times$ Internet coverage &&&&&      -0.521***&-2.654*\\
                   \medskip
                   &&&&&      (0.12)  & (1.41) \\
                   \midrule
                   \smallskip
                  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                  \smallskip
                  Country controls & Yes& No& Yes& No& No& No\\
                  \smallskip
                  Round FE & Yes & No& Yes & No& No& No\\
                  \smallskip
                  Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                  \smallskip
                  Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                  \smallskip
                  Observations            &       97,261   &       97,261   &        4,149   &        4,149   &       97,261   &       97,261  \\
                  Adjusted-R$^2$        &       0.137   &       0.180   &       0.180   &       0.215   &       0.182    &       - \\

                                        \bottomrule
                  \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                  \end{tabular}
                  }
                  \end{table}

                  \begin{table}[H]
                    \sffamily
                    \caption{{Effect of distance from the capital on trust in parliament}}
                    \centering
                    %\footnotesize
                    \resizebox{16cm}{!}{
                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                    \\
                    \toprule
                    \toprule
                    &  \multicolumn{6}{c}{{Trust in parliament}}  \\
                    \cmidrule(r){2-7}
                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                    \cmidrule(r){2-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                        \cmidrule(r){2-3}
                        \cmidrule(r){4-5}
                        \cmidrule(r){6-6}
                        \cmidrule(r){7-7}
                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                     \midrule

                     Distance from the capital&       0.282***&       0.279***&       0.560***&       0.471** &       0.453***&       1.124***\\
                     \smallskip
                     &      (0.04)   &      (0.03)   &      (0.17)   &      (0.21)   &      (0.05)   &      (0.39) \\
                     Internet coverage &&&&       &        0.007   &       1.169**  \\
                     \smallskip
                     &&&&    &      (0.06)   &      (0.52)   \\
                     Distance from the capital $\times$ Internet coverage &&&&&      -0.442***& -1.776**\\
                     \medskip
                     &&&&&     (0.10)   &  (0.89) \\
                     \midrule
                     \smallskip
                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                    \smallskip
                    Country controls & Yes& No& Yes& No& No& No\\
                    \smallskip
                    Round FE & Yes & No& Yes & No& No& No\\
                    \smallskip
                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                    \smallskip
                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                    \smallskip
                    Observations            &      96,182   &       96,182   &        4,111   &        4,111   &       96,182   &       96,182  \\
                    Adjusted-R$^2$        &        0.130   &       0.160   &       0.102   &       0.127   &       0.161   &       - \\

                                          \bottomrule
                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                    \end{tabular}
                    }
                    \end{table}

                  \begin{table}[H]
                    \sffamily
                    \caption{{Effect of distance from the capital on trust in electoral commission}}
                    \centering
                    %\footnotesize
                    \resizebox{16cm}{!}{
                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
                    \\
                    \toprule
                    \toprule
                    &  \multicolumn{6}{c}{{Trust in electoral commission}}  \\
                    \cmidrule(r){2-7}
                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
                    \cmidrule(r){2-6}
                    \cmidrule(r){7-7}
                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
                        \cmidrule(r){2-3}
                        \cmidrule(r){4-5}
                        \cmidrule(r){6-6}
                        \cmidrule(r){7-7}
                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
                     \midrule

                     Distance from the capital&       0.319***&       0.365***&       0.366*  &       0.206   &       0.529***&       2.588***\\
                     \smallskip
                     &     (0.04)   &      (0.03)   &      (0.19)   &      (0.23)   &      (0.06)   &      (0.84) \\
                     Internet coverage &&&&       &        0.003   &       3.252***  \\
                     \smallskip
                     &&&&    &      (0.07)   &      (0.95)   \\
                     Distance from the capital $\times$ Internet coverage &&&&&     -0.418***&  -4.606**\\
                     \medskip
                     &&&&&      (0.11)    &  (1.93) \\
                     \midrule
                     \smallskip
                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
                    \smallskip
                    Country controls & Yes& No& Yes& No& No& No\\
                    \smallskip
                    Round FE & Yes & No& Yes & No& No& No\\
                    \smallskip
                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
                    \smallskip
                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
                    \smallskip
                    Observations            &      94,926   &       94,926   &        4,035   &        4,035   &       94,926   &       94,926   \\
                    Adjusted-R$^2$        &         0.118   &       0.144   &       0.094   &       0.137   &       0.145   &       - \\

                                          \bottomrule
                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                    \end{tabular}
                    }
                    \end{table}

\begin{table}[H]
  \sffamily
  \caption{{Effect of distance from the capital on political trust}}
  \centering
  %\footnotesize
  \resizebox{12cm}{!}{
  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
  \\
  \toprule
  \toprule
  &  \multicolumn{8}{c}{{OLS}}  \\
  \cmidrule(r){2-9}
  &  \multicolumn{4}{c}{{Vote against ruling party}}&  \multicolumn{4}{c}{{Country performance}}  \\
  \cmidrule(r){2-5}
  \cmidrule(r){6-9}
  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
      \cmidrule(r){2-3}
      \cmidrule(r){4-5}
      \cmidrule(r){6-7}
      \cmidrule(r){8-9}
      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}&  \multicolumn{1}{c}{{(7)}}&  \multicolumn{1}{c}{{(8)}}\\
      \midrule

   Distance from the capital&      -0.164***&      -0.101***&      -0.462***&      -0.334***&       0.183***&       0.153***&       0.272*  &      -0.034   \\
   \medskip
   &      (0.02)   &      (0.02)   &      (0.09)   &      (0.09)   &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20)   \\
   \midrule
   \smallskip
  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes  \\
  \smallskip
  Country controls & Yes& No& Yes& No& Yes& No& Yes& No\\
  \smallskip
  Round FE & Yes & No& Yes & No& Yes & No& Yes & No\\
  \smallskip
  Country X Round FE       & No & Yes& No & Yes& No & Yes& No & Yes\\
  \smallskip
  Ethnic homeland FE & No & No & Yes& Yes& No & No & Yes& Yes\\
  \smallskip
  Observations           &       99,414   &       99,414   &        4,247   &        4,247   &       98,512   &       98,512   &        4,203   &        4,203   \\
  Adjusted-R$^2$         &       0.082   &       0.147   &       0.167   &       0.249   &       0.140   &       0.161   &       0.166   &       0.184   \\
                        \bottomrule
  \multicolumn{9}{p{21cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
  \end{tabular}
  }
  \end{table}

\end{document}

### 2025-02-24 script.Rmd
script 1

---
title: "Untitled"
author: "Redha Chaba"
date: "2025-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2025-02-24 script/ADM_w8.Rmd
import folders

```{r}
setwd("~/Working paper/Trust/Script")
getwd()

```

```{r}
library(dplyr)
select <- dplyr::select
library(magrittr)
library(sf)
#afro_w8 <- sf::st_sf(afro_w8)

afro_w8 <- afro_w8%>%ungroup()

afro_w8%>%
  distinct(cname,ISO,ccode)%>%
  arrange(ISO)%>%
  select(cname)%>%
  print(n=50)

```

```{r}
library(tidyverse)

# Path to the folder containing the files
folder_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw"

# List of files in the folder
files <- list.files(folder_path, full.names = TRUE)

# Extract countries and levels from file names
data <- data.frame(file = files) %>%
  mutate(country = str_extract(file, "(?<=_)[A-Z]{3}(?=_\\d)"),
         level = as.integer(str_extract(file, "(?<=_)[0-9]+(?=\\.shp$)"))) %>%
  arrange(country, desc(level)) %>%
  distinct(country, .keep_all = TRUE)

# Count the number of levels for each country
levels_per_country <- data %>%
  group_by(country) %>%
  summarise(number_of_levels = first(level))

# Print the result
print(levels_per_country)

objects <- ls()
objects <- objects[objects != "afro_w8"]

```
**Countries with 3 ADM levels**

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BEN_1.shp")

regions_valid_BEN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BEN_1))

result <- st_intersects(panel_sf, regions_valid_BEN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_BEN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 <- left_join(afro_w8, result_with_region_1, by = "id_unique")

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BEN_2.shp")

regions_valid_BEN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BEN_2))

result <- st_intersects(panel_sf, regions_valid_BEN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_BEN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 <- left_join(afro_w8, result_with_region_2, by = "id_unique")

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BEN_3.shp")

regions_valid_BEN_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BEN_3))

result <- st_intersects(panel_sf, regions_valid_BEN_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_BEN_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 <- left_join(afro_w8, result_with_region_3, by = "id_unique")

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SEN_1.shp")

regions_valid_SEN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SEN_1))

result <- st_intersects(panel_sf, regions_valid_SEN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_SEN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SEN_2.shp")

regions_valid_SEN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SEN_2))

result <- st_intersects(panel_sf, regions_valid_SEN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_SEN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SEN_3.shp")

regions_valid_SEN_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SEN_3))

result <- st_intersects(panel_sf, regions_valid_SEN_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_SEN_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BDI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BDI_1.shp")

regions_valid_BDI_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BDI_1))

result <- st_intersects(panel_sf, regions_valid_BDI_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_BDI_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BDI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BDI_2.shp")

regions_valid_BDI_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BDI_2))

result <- st_intersects(panel_sf, regions_valid_BDI_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_BDI_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BDI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BDI_3.shp")

regions_valid_BDI_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BDI_3))

result <- st_intersects(panel_sf, regions_valid_BDI_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_BDI_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BFA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BFA_1.shp")

regions_valid_BFA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BFA_1))

result <- st_intersects(panel_sf, regions_valid_BFA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_BFA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BFA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BFA_2.shp")

regions_valid_BFA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BFA_2))

result <- st_intersects(panel_sf, regions_valid_BFA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_BFA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BFA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BFA_3.shp")

regions_valid_BFA_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BFA_3))

result <- st_intersects(panel_sf, regions_valid_BFA_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_BFA_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CIV") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CIV_1.shp")

regions_valid_CIV_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CIV_1))

result <- st_intersects(panel_sf, regions_valid_CIV_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_CIV_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CIV") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CIV_2.shp")

regions_valid_CIV_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CIV_2))

result <- st_intersects(panel_sf, regions_valid_CIV_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_CIV_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CIV") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CIV_3.shp")

regions_valid_CIV_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CIV_3))

result <- st_intersects(panel_sf, regions_valid_CIV_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_CIV_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CMR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CMR_1.shp")

regions_valid_CMR_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CMR_1))

result <- st_intersects(panel_sf, regions_valid_CMR_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_CMR_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CMR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CMR_2.shp")

regions_valid_CMR_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CMR_2))

result <- st_intersects(panel_sf, regions_valid_CMR_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_CMR_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CMR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CMR_3.shp")

regions_valid_CMR_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CMR_3))

result <- st_intersects(panel_sf, regions_valid_CMR_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_CMR_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ETH") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ETH_1.shp")

regions_valid_ETH_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ETH_1))

result <- st_intersects(panel_sf, regions_valid_ETH_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_ETH_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ETH") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ETH_2.shp")

regions_valid_ETH_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ETH_2))

result <- st_intersects(panel_sf, regions_valid_ETH_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_ETH_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ETH") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ETH_3.shp")

regions_valid_ETH_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ETH_3))

result <- st_intersects(panel_sf, regions_valid_ETH_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_ETH_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GIN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GIN_1.shp")

regions_valid_GIN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GIN_1))

result <- st_intersects(panel_sf, regions_valid_GIN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_GIN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GIN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GIN_2.shp")

regions_valid_GIN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GIN_2))

result <- st_intersects(panel_sf, regions_valid_GIN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_GIN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GIN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GIN_3.shp")

regions_valid_GIN_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GIN_3))

result <- st_intersects(panel_sf, regions_valid_GIN_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_GIN_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="KEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_KEN_1.shp")

regions_valid_KEN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_KEN_1))

result <- st_intersects(panel_sf, regions_valid_KEN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_KEN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="KEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_KEN_2.shp")

regions_valid_KEN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_KEN_2))

result <- st_intersects(panel_sf, regions_valid_KEN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_KEN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="KEN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_KEN_3.shp")

regions_valid_KEN_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_KEN_3))

result <- st_intersects(panel_sf, regions_valid_KEN_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_KEN_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="LBR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_LBR_1.shp")

regions_valid_LBR_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_LBR_1))

result <- st_intersects(panel_sf, regions_valid_LBR_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_LBR_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="LBR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_LBR_2.shp")

regions_valid_LBR_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_LBR_2))

result <- st_intersects(panel_sf, regions_valid_LBR_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_LBR_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="LBR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_LBR_3.shp")

regions_valid_LBR_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_LBR_3))

result <- st_intersects(panel_sf, regions_valid_LBR_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_LBR_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MAR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MAR_1.shp")

regions_valid_MAR_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MAR_1))

result <- st_intersects(panel_sf, regions_valid_MAR_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MAR_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MAR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MAR_2.shp")

regions_valid_MAR_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MAR_2))

result <- st_intersects(panel_sf, regions_valid_MAR_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_MAR_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MAR") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MAR_3.shp")

regions_valid_MAR_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MAR_3))

result <- st_intersects(panel_sf, regions_valid_MAR_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_MAR_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MDG") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MDG_1.shp")

regions_valid_MDG_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MDG_1))

result <- st_intersects(panel_sf, regions_valid_MDG_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MDG_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MDG") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MDG_2.shp")

regions_valid_MDG_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MDG_2))

result <- st_intersects(panel_sf, regions_valid_MDG_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_MDG_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MDG") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MDG_3.shp")

regions_valid_MDG_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MDG_3))

result <- st_intersects(panel_sf, regions_valid_MDG_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_MDG_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MLI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MLI_1.shp")

regions_valid_MLI_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MLI_1))

result <- st_intersects(panel_sf, regions_valid_MLI_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MLI_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MLI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MLI_2.shp")

regions_valid_MLI_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MLI_2))

result <- st_intersects(panel_sf, regions_valid_MLI_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_MLI_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MLI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MLI_3.shp")

regions_valid_MLI_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MLI_3))

result <- st_intersects(panel_sf, regions_valid_MLI_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_MLI_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MOZ") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MOZ_1.shp")

regions_valid_MOZ_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MOZ_1))

result <- st_intersects(panel_sf, regions_valid_MOZ_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MOZ_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MOZ") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MOZ_2.shp")

regions_valid_MOZ_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MOZ_2))

result <- st_intersects(panel_sf, regions_valid_MOZ_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_MOZ_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MOZ") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MOZ_3.shp")

regions_valid_MOZ_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MOZ_3))

result <- st_intersects(panel_sf, regions_valid_MOZ_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_MOZ_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MWI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MWI_1.shp")

regions_valid_MWI_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MWI_1))

result <- st_intersects(panel_sf, regions_valid_MWI_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MWI_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MWI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MWI_2.shp")

regions_valid_MWI_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MWI_2))

result <- st_intersects(panel_sf, regions_valid_MWI_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_MWI_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MWI") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MWI_3.shp")

regions_valid_MWI_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MWI_3))

result <- st_intersects(panel_sf, regions_valid_MWI_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_MWI_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NER") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NER_1.shp")

regions_valid_NER_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NER_1))

result <- st_intersects(panel_sf, regions_valid_NER_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_NER_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NER") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NER_2.shp")

regions_valid_NER_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NER_2))

result <- st_intersects(panel_sf, regions_valid_NER_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_NER_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NER") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NER_3.shp")

regions_valid_NER_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NER_3))

result <- st_intersects(panel_sf, regions_valid_NER_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_NER_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SDN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SDN_1.shp")

regions_valid_SDN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SDN_1))

result <- st_intersects(panel_sf, regions_valid_SDN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_SDN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SDN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SDN_2.shp")

regions_valid_SDN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SDN_2))

result <- st_intersects(panel_sf, regions_valid_SDN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_SDN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SDN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SDN_3.shp")

regions_valid_SDN_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SDN_3))

result <- st_intersects(panel_sf, regions_valid_SDN_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_SDN_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SLE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SLE_1.shp")

regions_valid_SLE_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SLE_1))

result <- st_intersects(panel_sf, regions_valid_SLE_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_SLE_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SLE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SLE_2.shp")

regions_valid_SLE_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SLE_2))

result <- st_intersects(panel_sf, regions_valid_SLE_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_SLE_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SLE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SLE_3.shp")

regions_valid_SLE_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SLE_3))

result <- st_intersects(panel_sf, regions_valid_SLE_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_SLE_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TGO") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TGO_1.shp")

regions_valid_TGO_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TGO_1))

result <- st_intersects(panel_sf, regions_valid_TGO_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_TGO_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TGO") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TGO_2.shp")

regions_valid_TGO_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TGO_2))

result <- st_intersects(panel_sf, regions_valid_TGO_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_TGO_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TGO") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TGO_3.shp")

regions_valid_TGO_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TGO_3))

result <- st_intersects(panel_sf, regions_valid_TGO_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_TGO_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TZA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TZA_1.shp")

regions_valid_TZA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TZA_1))

result <- st_intersects(panel_sf, regions_valid_TZA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_TZA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TZA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TZA_2.shp")

regions_valid_TZA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TZA_2))

result <- st_intersects(panel_sf, regions_valid_TZA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_TZA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TZA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TZA_3.shp")

regions_valid_TZA_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TZA_3))

result <- st_intersects(panel_sf, regions_valid_TZA_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_TZA_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="UGA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_UGA_1.shp")

regions_valid_UGA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_UGA_1))

result <- st_intersects(panel_sf, regions_valid_UGA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_UGA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="UGA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_UGA_2.shp")

regions_valid_UGA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_UGA_2))

result <- st_intersects(panel_sf, regions_valid_UGA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_UGA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="UGA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_UGA_3.shp")

regions_valid_UGA_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_UGA_3))

result <- st_intersects(panel_sf, regions_valid_UGA_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_UGA_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZAF") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZAF_1.shp")

regions_valid_ZAF_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZAF_1))

result <- st_intersects(panel_sf, regions_valid_ZAF_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_ZAF_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZAF") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZAF_2.shp")

regions_valid_ZAF_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZAF_2))

result <- st_intersects(panel_sf, regions_valid_ZAF_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_ZAF_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZAF") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZAF_3.shp")

regions_valid_ZAF_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZAF_3))

result <- st_intersects(panel_sf, regions_valid_ZAF_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_ZAF_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZWE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZWE_1.shp")

regions_valid_ZWE_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZWE_1))

result <- st_intersects(panel_sf, regions_valid_ZWE_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_ZWE_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZWE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZWE_2.shp")

regions_valid_ZWE_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZWE_2))

result <- st_intersects(panel_sf, regions_valid_ZWE_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_ZWE_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZWE") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZWE_3.shp")

regions_valid_ZWE_3 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZWE_3))

result <- st_intersects(panel_sf, regions_valid_ZWE_3)

result_with_region_3 <- st_join(panel_sf, regions_valid_ZWE_3, join = st_intersects)

result_with_region_3 <- as.data.frame(result_with_region_3)

result_with_region_3%<>%
  select(id_unique, NAME_3)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_3, by = "id_unique")%>%
    mutate(NAME_3= if_else(!is.na(NAME_3.x), NAME_3.x, NAME_3.y))%>%
    select(-c(NAME_3.x, NAME_3.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

**Country with only 2 ADM levels**

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BWA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BWA_1.shp")

regions_valid_BWA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BWA_1))

result <- st_intersects(panel_sf, regions_valid_BWA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_BWA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="BWA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_BWA_2.shp")

regions_valid_BWA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_BWA_2))

result <- st_intersects(panel_sf, regions_valid_BWA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_BWA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="DZA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_DZA_1.shp")

regions_valid_DZA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_DZA_1))

result <- st_intersects(panel_sf, regions_valid_DZA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_DZA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="DZA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_DZA_2.shp")

regions_valid_DZA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_DZA_2))

result <- st_intersects(panel_sf, regions_valid_DZA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_DZA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="EGY") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_EGY_1.shp")

regions_valid_EGY_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_EGY_1))

result <- st_intersects(panel_sf, regions_valid_EGY_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_EGY_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="EGY") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_EGY_2.shp")

regions_valid_EGY_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_EGY_2))

result <- st_intersects(panel_sf, regions_valid_EGY_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_EGY_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GAB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GAB_1.shp")

regions_valid_GAB_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GAB_1))

result <- st_intersects(panel_sf, regions_valid_GAB_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_GAB_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GAB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GAB_2.shp")

regions_valid_GAB_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GAB_2))

result <- st_intersects(panel_sf, regions_valid_GAB_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_GAB_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GHA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GHA_1.shp")

regions_valid_GHA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GHA_1))

result <- st_intersects(panel_sf, regions_valid_GHA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_GHA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GHA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GHA_2.shp")

regions_valid_GHA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GHA_2))

result <- st_intersects(panel_sf, regions_valid_GHA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_GHA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GMB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GMB_1.shp")

regions_valid_GMB_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GMB_1))

result <- st_intersects(panel_sf, regions_valid_GMB_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_GMB_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="GMB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_GMB_2.shp")

regions_valid_GMB_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_GMB_2))

result <- st_intersects(panel_sf, regions_valid_GMB_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_GMB_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NAM") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NAM_1.shp")

regions_valid_NAM_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NAM_1))

result <- st_intersects(panel_sf, regions_valid_NAM_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_NAM_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NAM") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NAM_2.shp")

regions_valid_NAM_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NAM_2))

result <- st_intersects(panel_sf, regions_valid_NAM_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_NAM_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NGA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NGA_1.shp")

regions_valid_NGA_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NGA_1))

result <- st_intersects(panel_sf, regions_valid_NGA_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_NGA_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="NGA") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_NGA_2.shp")

regions_valid_NGA_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_NGA_2))

result <- st_intersects(panel_sf, regions_valid_NGA_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_NGA_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="STP") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_STP_1.shp")

regions_valid_STP_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_STP_1))

result <- st_intersects(panel_sf, regions_valid_STP_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_STP_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="STP") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_STP_2.shp")

regions_valid_STP_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_STP_2))

result <- st_intersects(panel_sf, regions_valid_STP_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_STP_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SWZ") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SWZ_1.shp")

regions_valid_SWZ_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SWZ_1))

result <- st_intersects(panel_sf, regions_valid_SWZ_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_SWZ_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="SWZ") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_SWZ_2.shp")

regions_valid_SWZ_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_SWZ_2))

result <- st_intersects(panel_sf, regions_valid_SWZ_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_SWZ_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TUN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TUN_1.shp")

regions_valid_TUN_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TUN_1))

result <- st_intersects(panel_sf, regions_valid_TUN_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_TUN_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="TUN") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_TUN_2.shp")

regions_valid_TUN_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_TUN_2))

result <- st_intersects(panel_sf, regions_valid_TUN_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_TUN_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZMB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZMB_1.shp")

regions_valid_ZMB_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZMB_1))

result <- st_intersects(panel_sf, regions_valid_ZMB_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_ZMB_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="ZMB") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_ZMB_2.shp")

regions_valid_ZMB_2 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_ZMB_2))

result <- st_intersects(panel_sf, regions_valid_ZMB_2)

result_with_region_2 <- st_join(panel_sf, regions_valid_ZMB_2, join = st_intersects)

result_with_region_2 <- as.data.frame(result_with_region_2)

result_with_region_2%<>%
  select(id_unique, NAME_2)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_2, by = "id_unique")%>%
    mutate(NAME_2= if_else(!is.na(NAME_2.x), NAME_2.x, NAME_2.y))%>%
    select(-c(NAME_2.x, NAME_2.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
afro_w8 %>%
  filter(is.na(NAME_2)) %>%
  group_by(ISO) %>%
  summarise(count_na = sum(is.na(NAME_2))) %>%
  View()

```

**Countries with 1 ADM level**

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="CPV") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_CPV_1.shp")

regions_valid_CPV_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_CPV_1))

result <- st_intersects(panel_sf, regions_valid_CPV_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_CPV_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="LSO") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_LSO_1.shp")

regions_valid_LSO_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_LSO_1))

result <- st_intersects(panel_sf, regions_valid_LSO_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_LSO_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
panel_sf <- afro_w8 %>%
  filter(!is.na(latitude) & !is.na(longitude)) %>%
  filter(ISO=="MUS") %>%
  select(id_unique, latitude, longitude, caplong, caplat)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/Data/Data_Raw/gadm41_MUS_1.shp")

regions_valid_MUS_1 <- st_make_valid(regions)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions_valid_MUS_1))

result <- st_intersects(panel_sf, regions_valid_MUS_1)

result_with_region_1 <- st_join(panel_sf, regions_valid_MUS_1, join = st_intersects)

result_with_region_1 <- as.data.frame(result_with_region_1)

result_with_region_1%<>%
  select(id_unique, NAME_1)

afro_w8 <- as.data.frame(afro_w8)

afro_w8 %<>% left_join(result_with_region_1, by = "id_unique")%>%
    mutate(NAME_1= if_else(!is.na(NAME_1.x), NAME_1.x, NAME_1.y))%>%
    select(-c(NAME_1.x, NAME_1.y))

objects <- ls()
objects <- objects[objects != "afro_w8"]

```

```{r}
afro_w8 %>%
  group_by(ISO) %>%
  summarise(count_na = sum(is.na(NAME_1))) %>%
  print()
```

```{r}
saveRDS(afro_w8, file="Data/Data_RDS/afro_w8.rds")

```

### 2025-02-24 script/afrobarometer.Rmd
import folders

```{r}
setwd("~/working_paper/trust/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(stringr)
library(geosphere)
library(purrr)
library(kableExtra)
library(tidyr)
```

# Read Afrobarometer data from different waves (rounds 5-8)

```{r echo=FALSE}
afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")
```

# Process Wave 5 data

```{r}
# Fix country codes: Replace MAU with MUS (Mauritius) and MRC with MAR (Morocco)

afro_w5 %<>%
  mutate(respno = case_when(
    str_starts(respno, "MAU") ~ str_replace(respno, "^MAU", "MUS"),
    TRUE ~ respno
  ))

afro_w5 %<>%
  mutate(respno = case_when(
    str_starts(respno, "MRC") ~ str_replace(respno, "^MRC", "MAR"),
    TRUE ~ respno
  ))

# Add round number and create unique identifier

afro_w5%<>%
  mutate(round=rep(5, times = length("respno")))%>%
  mutate(id_unique=paste0(respno, round))

# Rename variables to standardized names across waves

afro_w5 %<>%
  rename(
    age = q1,
    assoc = q25b,
    check_citiz = q33,
    check_parl = q36,
    commu = q26a,
    conditions_country = q3a,
    conditions_eco = q3b,
    contact_counc = q30a,
    #contact_trad
    corr_judge = q60g,
    #corr_level
    corr_local = q60d,
    corr_parl = q60b,
    corr_pres = q60a,
    #corr_trad
    disc_pol = q15,
    educ = q97,
    elec_fair = q28,
    emp = q96,
    extent = q42,
    feelnat = q85b,
    food = q8a,
    internet_news = q13d,
    internet_use = q91b,
    latitude = latitude,
    listen_counc = q62b,
    #listen_trad
    longitude = longitude,
    military_reject = q31b,
    money = q8e,
    one_man_reject = q31c,
    one_party_reject = q31a,
    paper_news = q13c,
    perf_corr = q65k,
    perf_crime = q65f,
    perf_educ = q65h,
    perf_elect = q65o,
    perf_eco = q65a,
    perf_health = q65g,
    perf_ineq = q65e,
    perf_job = q65c,
    perf_local = q71c,
    perf_parl = q71b,
    perf_poor = q65b,
    perf_pres = q71a,
    perf_price = q65d,
    perf_road = q65n,
    perf_water = q65i,
    pref_demo = q32,
    prob = q26b,
    protest = q26d,
    radio_news = q13a,
    rural = urbrur,
    satis_demo = q43,
    security = q9a,
    sex = q101,
    #sm_news
    tele_news = q13b,
    tele_pos = q90b,
    trust_elec = q59c,
    trust_gen = q87,
    trust_govpart = q59f,
    trust_local = q59e,
    trust_oppart = q59g,
    trust_parl = q59b,
    trust_pres = q59a,
    #trust_trad
    unfair_eth = q85a,
    vote = q27
  )

glimpse(afro_w5)

saveRDS(afro_w5, file="data/data_rds/afro_w5.rds")
```

# Process Wave 6 data

```{r}
# Fix country codes: Replace MAU with MUS (Mauritius) and MRC with MAR (Morocco)

afro_w6 %<>%
  mutate(respno = case_when(
    str_starts(respno, "MAU") ~ str_replace(respno, "^MAU", "MUS"),
    TRUE ~ respno
  ))

afro_w6 %<>%
  mutate(respno = case_when(
    str_starts(respno, "MOR") ~ str_replace(respno, "^MOR", "MAR"),
    TRUE ~ respno
  ))

# Add round number and create unique identifier

afro_w6%<>%
  mutate(round=rep(6, times = length("respno")))%>%
  mutate(id_unique=paste0(respno, round))

# Rename variables to standardized names across waves

afro_w6 %<>%
  rename(
    age = q1,
    assoc = q19b,
    check_citiz=q31,
    check_parl=q34,
    commu = q20a,
    conditions_country = q4a,
    conditions_eco = q4b,
    contact_counc = q24a,
    contact_trad = q24e,
    corr_judge = q53g,
    corr_level = q54,
    corr_local = q53d, 
    corr_parl = q53b,
    corr_pres = q53a, 
    corr_trad = q53h,
    disc_pol = q14,
    educ = q97,
    elec_fair = q22,
    emp = q95,
    extent = q40,
    feelnat = q88b,
    food = q8a,
    internet_news = q12d,
    internet_use = q92b,
    latitude = latitude,
    listen_counc = q59b,
    #listen_trad
    longitude = longitude,
    military_reject = q28b,
    money = q8e,
    one_man_reject = q28c,
    one_party_reject = q28a,
    paper_news = q12c,
    perf_corr=q66k,
    perf_crime=q66f,
    perf_educ=q66h,
    perf_elect=q66m,
    perf_eco = q66a,
    perf_health=q66g,
    perf_ineq=q66e,
    perf_job=q66c,
    perf_local = q68c,
    perf_parl=q68b,
    perf_poor=q66b,
    perf_pres=q68a,
    perf_price=q66d,
    perf_road=q66l,
    perf_water=q66i,
    pref_demo = q30,
    prob = q20b,
    protest = q27e,
    radio_news = q12a,
    rural = urbrur,
    satis_demo = q41,
    security = q10a,
    sex = q101,
    sm_news = q12e,
    tele_news = q12b,
    tele_pos = q91b,
    trust_elec = q52c,
    #trust_gen = 
    trust_govpart = q52f,
    trust_local = q52e,
    trust_oppart = q52g,
    trust_parl = q52b,
    trust_pres = q52a, 
    trust_trad = q52k,
    unfair_eth = q88a,
    vote = q21)

glimpse(afro_w6)

saveRDS(afro_w6, file="data/data_rds/afro_w6.rds")
```

# Process Wave 7 data

```{r}
# Fix country codes: Replace MAU with MUS (Mauritius) and MRC with MAR (Morocco)

afro_w7 %<>%
  mutate(RESPNO = case_when(
    str_starts(RESPNO, "MAU") ~ str_replace(RESPNO, "^MAU", "MUS"),
    TRUE ~ RESPNO
  ))

afro_w7 %<>%
  mutate(RESPNO = case_when(
    str_starts(RESPNO, "MOR") ~ str_replace(RESPNO, "^MOR", "MAR"),
    TRUE ~ RESPNO
  ))

# Add round number and create unique identifier

afro_w7%<>%
  mutate(respno=RESPNO)%>%
  mutate(round=rep(7, times = length("respno")))%>%
  mutate(id_unique=paste0(RESPNO, round))

# Rename variables to standardized names across waves

afro_w7 %<>%
  rename(
    age = Q1,
    assoc = Q20B,
    check_citiz=Q29,
    check_parl=Q32,
    commu = Q21A,
    conditions_country = Q4A,
    conditions_eco = Q4B,
    contact_counc = Q25A,
    contact_trad = Q25E,
    corr_judge = Q44F,
    corr_level = Q45,
    corr_local = Q44D, 
    corr_parl = Q44B,
    corr_pres = Q44A, 
    corr_trad = Q44G,
    disc_pol = Q13,
    educ = Q97,
    elec_fair = Q23,
    emp = Q94,
    extent = Q35,
    feelnat = Q85B,
    food = Q8A,
    internet_news = Q12D,
    internet_use = Q91B,
    latitude = EA_GPS_LA,
    listen_counc = Q54B,
    #listen_trad
    longitude = EA_GPS_LO,
    military_reject = Q27B,
    money = Q8E,
    one_man_reject = Q27C,
    one_party_reject = Q27A,
    paper_news = Q12C,
    perf_corr = Q56K,
    perf_crime = Q56F,
    perf_eco = Q56A,
    perf_educ = Q56H,
    perf_elect = Q56M,
    perf_health = Q56G,
    perf_ineq = Q56E,
    perf_job = Q56C,
    perf_local = Q58C,
    perf_parl = Q58B,
    perf_pres = Q58A,
    perf_price = Q56D,
    perf_road = Q56L,
    perf_trad = Q58D,
    perf_water = Q56I,
    pref_demo = Q28,
    prob = Q21B,
    protest = Q26E,
    radio_news = Q12A,
    rural = URBRUR,
    satis_demo = Q36,
    security = Q10A,
    sex = Q101,
    sm_news = Q12E,
    tele_news = Q12B,
    tele_pos = Q89B,
    trust_elec =  Q43C,
    #trust_gen = 
    trust_govpart = Q43E,
    trust_local = Q43D,
    trust_oppart = Q43F,
    trust_parl = Q43B,
    trust_pres = Q43A, 
    trust_trad = Q43J,
    unfair_eth = Q85A,
    vote = Q22)

glimpse(afro_w7)

saveRDS(afro_w7, file="data/data_rds/afro_w7.rds")
```

# Process Wave 8 data

```{r}
# Fix country codes: Replace MAU with MUS (Mauritius) and MRC with MAR (Morocco)

afro_w8 %<>%
  mutate(RESPNO = case_when(
    str_starts(RESPNO, "MAU") ~ str_replace(RESPNO, "^MAU", "MUS"),
    TRUE ~ RESPNO
  ))

afro_w8 %<>%
  mutate(RESPNO = case_when(
    str_starts(RESPNO, "MOR") ~ str_replace(RESPNO, "^MOR", "MAR"),
    TRUE ~ RESPNO
  ))

# Add round number and create unique identifier

afro_w8%<>%
  mutate(respno=RESPNO)%>%
  mutate(round=rep(8, times = length("RESPNO")))%>%
  mutate(id_unique=paste0(RESPNO, round))

# Rename variables to standardized names across waves

afro_w8 %<>%
  rename(
    age = Q1,
    #assoc = ,
    check_citiz=Q22,
    check_parl=Q29,
    commu = Q11A,
    conditions_country = Q6A,
    conditions_eco = Q4B,
    contact_counc=Q12A,
    contact_trad=Q12D,
    corr_judge = Q42F,
    corr_level = Q43A,
    corr_local = Q42D,
    corr_parl = Q42B,
    corr_pres = Q42A,
    corr_trad = Q42H,
    disc_pol = Q9,
    educ = Q97,
    elec_fair = Q14,
    emp = Q95A,
    extent = Q36,
    feelnat = Q82B,
    food = Q7A,
    internet_news = Q55D,
    internet_use = Q92I,
    latitude = EA_GPS_LA,
    listen_counc=Q38B,
    listen_trad=Q38C,
    longitude = EA_GPS_LO,
    military_reject = Q20B,
    money = Q7E,
    one_man_reject = Q20C,
    one_party_reject = Q20A,
    paper_news = Q55C,
    perf_corr = Q50J,
    perf_crime = Q50F,
    perf_eco = Q50A,
    perf_educ = Q50H,
    perf_elect = Q50L,
    perf_health = Q50G,
    perf_ineq = Q50E,
    perf_job = Q50C,
    perf_local = Q51C,
    perf_parl = Q51B,
    perf_pres = Q51A,
    perf_price = Q50D,
    perf_road = Q50K,
    perf_trad = Q51D,
    perf_water = Q50I,
    pref_demo = Q21,
    prob = Q11B,
    protest = Q11C,
    radio_news = Q55A,
    rural = URBRUR,
    satis_demo = Q37,
    security = Q8A,
    sex = Q101,
    sm_news = Q55E,
    tele_news = Q55B,
    tele_pos = Q92B,
    trust_elec = Q41C,
    trust_gen = Q83,
    trust_govpart = Q41E,
    trust_local = Q41D,
    trust_oppart = Q41F,
    trust_parl = Q41B,
    trust_pres = Q41A,
    trust_trad = Q41K,
    unfair_eth = Q84C,
    vote = Q13)

glimpse(afro_w8)

saveRDS(afro_w8, file="data/data_rds/afro_w8.rds")
```

# Define variables to keep in final dataset

```{r}
variables_to_keep <- c(
  "age", "assoc", "check_citiz", "check_parl", "commu", "conditions_country", 
  "conditions_eco", "contact_counc", "contact_trad", "corr_judge", 
  "corr_level", "corr_local", "corr_parl", "corr_pres", "corr_trad", 
  "disc_pol", "educ", "elec_fair", "emp", "extent", "feelnat", "food", 
  "internet_news", "internet_use", "latitude", "listen_counc", "listen_trad", 
  "longitude", "military_reject", "money", "one_man_reject", "one_party_reject", 
  "paper_news", "perf_corr", "perf_crime", "perf_eco", "perf_educ", "perf_elect", 
  "perf_health", "perf_ineq", "perf_job", "perf_local", "perf_parl", "perf_pres", 
  "perf_price", "perf_road", "perf_trad", "perf_water", "pref_demo", "prob", 
  "protest", "radio_news", "rural", "satis_demo", "security", "sex", "sm_news", 
  "tele_news", "tele_pos", "trust_elec", "trust_gen", "trust_govpart", "trust_local", 
  "trust_oppart", "trust_parl", "trust_pres", "trust_trad", "unfair_eth", "vote", "id_unique", "round", "respno"
)
```

# Filter all datasets to keep only selected variables

```{r}
datasets <- list(afro_w5, afro_w6, afro_w7, afro_w8)

filtered_dataset_names <- c("afro_w5_filt", "afro_w6_filt", "afro_w7_filt", "afro_w8_filt")

for (i in 1:length(datasets)) {
  filtered_dataset <- datasets[[i]] %>%
    select(any_of(variables_to_keep))

  assign(filtered_dataset_names[i], filtered_dataset)
}

rm(afro_w5, afro_w6, afro_w7, afro_w8, datasets, filtered_dataset, filtered_dataset_names, i, variables_to_keep)
```

# Stack all waves together and remove duplicates

```{r}
afro_stack <- bind_rows(afro_w5_filt, afro_w6_filt, afro_w7_filt, afro_w8_filt)

afro_stack%<>%
  filter(!duplicated(id_unique))%>%
  filter(!is.na(latitude), !is.na(longitude))

rm(afro_w5_filt, afro_w6_filt, afro_w7_filt, afro_w8_filt)
```

# Add ISO country codes and standardize them

```{r}
afro_stack%<>%
  mutate(iso = substr(id_unique, 1, 3))

# Convert non-standard country codes to ISO format

afro_stack %<>%
  mutate(iso=case_when(
    iso=="BFO"~"BFA",
    iso=="BOT"~"BWA",
    iso=="CAM"~"CMR",
    iso=="CDI"~"CIV",
    iso=="CVE"~"CPV",
    iso=="LES"~"LSO",
    iso=="LIB"~"LBR",
    iso=="MAD"~"MDG",
    iso=="SAF"~"ZAF",
    iso=="SRL"~"SLE",
    iso=="ZAM"~"ZMB",
    iso=="ZIM"~"ZWE",
    iso=="GAM"~"GMB",
    iso=="ANG"~"AGO",
    iso=="ALG"~"DZA",
    iso=="GUI"~"GIN",
    iso=="MLW"~"MWI",
    iso=="NGR"~"NER",
    iso=="NIG"~"NGA",
    iso=="SUD"~"SDN",
    iso=="TAN"~"TZA",
    iso=="TOG"~"TGO",
    TRUE ~ iso))

# Create country mapping data frame

country_mapping <- data.frame(
  ccode = 1:39,
  cname = c("algeria", "angola", "benin", "botswana", "burkina_faso", "burundi", 
            "cabo_verde", "cameroon", "egypt", "eswatini", "ethiopia", "gabon", 
            "gambia", "ghana", "guinea", "ivory_coast", "kenya", "lesotho", 
            "liberia", "madagascar", "malawi", "mali", "mauritius", "morocco", 
            "mozambique", "namibia", "niger", "nigeria", "sao_tome", "senegal", 
            "sierra_leone", "south_africa", "sudan", "tanzania", "togo", 
            "tunisia", "uganda", "zambia", "zimbabwe")
)

iso <- c(
  "algeria" = "DZA", "angola" = "AGO", "benin" = "BEN", "botswana" = "BWA",
  "burkina_faso" = "BFA", "burundi" = "BDI", "cabo_verde" = "CPV", "cameroon" = "CMR",
  "egypt" = "EGY", "eswatini" = "SWZ", "ethiopia" = "ETH", "gabon" = "GAB",
  "gambia" = "GMB", "ghana" = "GHA", "guinea" = "GIN", "ivory_coast" = "CIV",
  "kenya" = "KEN", "lesotho" = "LSO", "liberia" = "LBR", "madagascar" = "MDG",
  "malawi" = "MWI", "mali" = "MLI", "mauritius" = "MUS", "morocco" = "MAR",
  "mozambique" = "MOZ", "namibia" = "NAM", "niger" = "NER", "nigeria" = "NGA",
  "sao_tome" = "STP", "senegal" = "SEN", "sierra_leone" = "SLE",
  "south_africa" = "ZAF", "sudan" = "SDN", "tanzania" = "TZA", "togo" = "TGO",
  "tunisia" = "TUN", "uganda" = "UGA", "zambia" = "ZMB", "zimbabwe" = "ZWE"
)

country_mapping %<>%
  mutate(iso = iso[cname])

afro_stack %<>%
  left_join(country_mapping, by = "iso")

rm(country_mapping, iso)
```

# Remove geographic outliers using IQR method

```{r}
rm_out <- function(data, variable = "latitude") {
  init_n <- nrow(data)

  Q1 <- quantile(data[[variable]], 0.25, na.rm = TRUE)
  Q3 <- quantile(data[[variable]], 0.75, na.rm = TRUE)
  IQR <- Q3 - Q1
  lower_bound <- Q1 - 1.5 * IQR
  upper_bound <- Q3 + 1.5 * IQR

  data_iqr <- data %>%
    filter(!!sym(variable) >= lower_bound & !!sym(variable) <= upper_bound)

  n_rm <- init_n - nrow(data_iqr)
  pct_rm <- round(100 * n_rm / init_n, 2)

  cat("Initial observations:", init_n, "\n",
      "Observations removed:", n_rm, "\n",
      "Percentage removed:", pct_rm, "%\n",
      "Final observations:", nrow(data_iqr), "\n")

  return(data_iqr)
}

afro_stack %<>% rm_out("latitude")

saveRDS(afro_stack, file="data/data_rds/afro_stack.rds")

rm(rm_out)
```

# Create summary statistics table

```{r}
vars_sum <- c(
  "age", "assoc", "check_citiz", "check_parl", "commu", "conditions_country", 
  "conditions_eco", "contact_counc", "contact_trad", "corr_judge", 
  "corr_level", "corr_local", "corr_parl", "corr_pres", "corr_trad", 
  "disc_pol", "educ", "elec_fair", "emp", "extent", "feelnat", "food", 
  "internet_news", "internet_use", "latitude", "listen_counc", "listen_trad", 
  "longitude", "military_reject", "money", "one_man_reject", "one_party_reject", 
  "paper_news", "perf_corr", "perf_crime", "perf_eco", "perf_educ", "perf_elect", 
  "perf_health", "perf_ineq", "perf_job", "perf_local", "perf_parl", "perf_pres", 
  "perf_price", "perf_road", "perf_trad", "perf_water", "pref_demo", "prob", 
  "protest", "radio_news", "rural", "satis_demo", "security", "sex", "sm_news", 
  "tele_news", "tele_pos", "trust_elec", "trust_gen", "trust_govpart", "trust_local", 
  "trust_oppart", "trust_parl", "trust_pres", "trust_trad", "unfair_eth", "vote"
)

sum_tab <- function(data, variables_list, rounds_col = "round") {

  calc_stats <- function(var_name) {
    if (!var_name %in% names(data)) {
      return(NULL)
    }

    if (is.numeric(data[[var_name]])) {
      data %>%
        group_by(!!sym(rounds_col)) %>%
        summarise(
          Mean = mean(!!sym(var_name), na.rm = TRUE),
          Median = median(!!sym(var_name), na.rm = TRUE),
          SD = sd(!!sym(var_name), na.rm = TRUE),
          Min = min(!!sym(var_name), na.rm = TRUE),
          Max = max(!!sym(var_name), na.rm = TRUE),
          N = sum(!is.na(!!sym(var_name))),
          .groups = 'drop'
        ) %>%
        mutate(Variable = var_name)
    } else {
      data %>%
        group_by(!!sym(rounds_col)) %>%
        summarise(
          Mean = n_distinct(!!sym(var_name), na.rm = TRUE),
          Median = NA,
          SD = NA,
          Min = NA,
          Max = NA,
          N = sum(!is.na(!!sym(var_name))),
          .groups = 'drop'
        ) %>%
        mutate(Variable = var_name)
    }
  }

  all_stats <- map_df(variables_list, calc_stats)

  final_table <- all_stats %>%
    pivot_wider(
      id_cols = Variable,
      names_from = !!sym(rounds_col),
      values_from = c(Mean, Median, SD, Min, Max, N),
      names_sep = "_"
    )

  latex_table <- final_table %>%
    kbl(format = "latex",
        booktabs = TRUE,
        caption = "Summary Statistics by Round",
        digits = 2,
        align = c("l", rep("c", ncol(final_table) - 1))) %>%
    kable_styling(
      latex_options = c("striped", "hold_position", "scale_down"),
      font_size = 9
    ) %>%
    column_spec(1, bold = TRUE) %>%
    footnote(
      general = paste("Number of variables:", length(variables_list)),
      footnote_as_chunk = TRUE
    )

  return(latex_table)
}

summary_table <- sum_tab(
   data = afro_stack,
   variables_list = vars_sum,
   rounds_col = "round"
 )

print(summary_table)

writeLines(summary_table, "variables_summary.tex")

rm(vars_sum, sum_tab, summary_table)
```

### 2025-02-24 script/data_trust_final.Rmd
import folders

```{r}
setwd("~/Working paper/trust/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(lubridate)
library(geosphere)
library(readxl)
```

# **Import Databases**

```{r echo=FALSE}

afro_w7 <- read_sav("data/data_raw/R7_Merged data_34ctry_4Dec18.sav")
afro_w5 <- read.csv("data/data_raw/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afb_full_r6.csv_")
country_var <- read_excel("Data/Data_Raw/country_var.xlsx")
gdppc <- read_excel("Data/Data_Raw/gdppc.xls")
population <- read_excel("Data/Data_Raw/pop.xls")
surface <- read_excel("Data/Data_Raw/surface.xls")
corr_index <- read_excel("Data/Data_Raw/corr_index.xlsx")
gov_index <- read_excel("Data/Data_Raw/gov_index.xlsx")
polstab_index <- read_excel("Data/Data_Raw/polstab_index.xlsx")
reg_index <- read_excel("Data/Data_Raw/reg_index.xlsx")
rule_index <- read_excel("Data/Data_Raw/rule_index.xlsx")
voiceac_index <- read_excel("Data/Data_Raw/voiceac_index.xlsx")
vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")
juriglobe <- read_excel("Data/Data_Raw/FR_index.xlsx")
legal_origin <- read_excel("Data/Data_Raw/origine_legale.xlsx")
cities <- read_excel("Data/Data_Raw/cities.xlsx")

```

**Merging Afrobarometer Waves**

```{r}
afro_w7 %<>%
  mutate(ccode=COUNTRY)

country_mapping <- data.frame(
  ccode = 1:34,
  cname = c("Benin", "Botswana", "Burkina Faso", "Cabo Verde", "Cameroon", "Côte d'Ivoire", "eSwatini", "Gabon", "Gambia", "Ghana", "Guinea",
            "Kenya", "Lesotho", "Liberia", "Madagascar", "Malawi", "Mali", "Mauritius", "Morocco", "Mozambique", "Namibia", "Niger", "Nigeria",
            "São Tomé and Príncipe", "Senegal", "Sierra Leone", "South Africa", "Sudan", "Tanzania", "Togo", "Tunisia", "Uganda", "Zambia", "Zimbabwe")
)

afro_w7 %<>%
  left_join(country_mapping, by = "ccode")

rm(country_mapping)

afro_w5%<>%
  mutate(country_alpha=if_else(is.na(country_alpha),36, country_alpha))

afro_w5 %<>%
  mutate(ccode = as.numeric(case_when(
    country_alpha == 1 ~ 35,
    country_alpha == 2 ~ 1,
    country_alpha == 3 ~ 2,
    country_alpha == 4 ~ 3,
    country_alpha == 5 ~ 36,
    country_alpha == 6 ~ 5,
    country_alpha == 7 ~ 4,
    country_alpha == 8 ~ 6,
    country_alpha == 9 ~ 37,
    country_alpha == 11 ~ 10,
    country_alpha == 12 ~ 11,
    country_alpha == 13 ~ 12,
    country_alpha == 14 ~ 13,
    country_alpha == 15 ~ 14,
    country_alpha == 16 ~ 15,
    country_alpha == 17 ~ 16,
    country_alpha == 18 ~ 17,
    country_alpha == 19 ~ 18,
    country_alpha == 20 ~ 19,
    country_alpha == 21 ~ 20,
    country_alpha == 22 ~ 21,
    country_alpha == 23 ~ 22,
    country_alpha == 24 ~ 23,
    country_alpha == 25 ~ 25,
    country_alpha == 26 ~ 26,
    country_alpha == 27 ~ 27,
    country_alpha == 28 ~ 28,
    country_alpha == 29 ~ 7,
    country_alpha == 30 ~ 29,
    country_alpha == 31 ~ 30,
    country_alpha == 32 ~ 31,
    country_alpha == 33 ~ 32,
    country_alpha == 34 ~ 33,
    country_alpha == 35 ~ 34,
    country_alpha == 36 ~ 38,
    TRUE ~ NA
  )))

afro_w5 %<>%
  mutate(cname = case_when(
    ccode == 1 ~ "Benin",
    ccode == 2 ~ "Botswana",
    ccode == 3 ~ "Burkina Faso",
    ccode == 4 ~ "Cabo Verde",
    ccode == 5 ~ "Cameroon",
    ccode == 6 ~ "Côte d'Ivoire",
    ccode == 7 ~ "eSwatini",
    ccode == 8 ~ "Gabon",
    ccode == 9 ~ "Gambia",
    ccode == 10 ~ "Ghana",
    ccode == 11 ~ "Guinea",
    ccode == 12 ~ "Kenya",
    ccode == 13 ~ "Lesotho",
    ccode == 14 ~ "Liberia",
    ccode == 15 ~ "Madagascar",
    ccode == 16 ~ "Malawi",
    ccode == 17 ~ "Mali",
    ccode == 18 ~ "Mauritius",
    ccode == 19 ~ "Morocco",
    ccode == 20 ~ "Mozambique",
    ccode == 21 ~ "Namibia",
    ccode == 22 ~ "Niger",
    ccode == 23 ~ "Nigeria",
    ccode == 24 ~ "São Tomé and Príncipe",
    ccode == 25 ~ "Senegal",
    ccode == 26 ~ "Sierra Leone",
    ccode == 27 ~ "South Africa",
    ccode == 28 ~ "Sudan",
    ccode == 29 ~ "Tanzania",
    ccode == 30 ~ "Togo",
    ccode == 31 ~ "Tunisia",
    ccode == 32 ~ "Uganda",
    ccode == 33 ~ "Zambia",
    ccode == 34 ~ "Zimbabwe",
    ccode == 35 ~ "Algeria",
    ccode == 36 ~ "Burundi",
    ccode == 37 ~ "Egypt",
    ccode == 38 ~ "Ethiopia",
    TRUE ~ NA_character_
  ))

afro_w6 %<>%
  mutate(ccode = as.numeric(case_when(
    country == 1 ~ 35,
    country == 2 ~ 1,
    country == 3 ~ 2,
    country == 4 ~ 3,
    country == 5 ~ 36,
    country == 6 ~ 5,
    country == 7 ~ 4,
    country == 8 ~ 6,
    country == 9 ~ 37,
    country == 10 ~ 8,
    country == 11 ~ 10,
    country == 12 ~ 11,
    country == 13 ~ 12,
    country == 14 ~ 13,
    country == 15 ~ 14,
    country == 16 ~ 15,
    country == 17 ~ 16,
    country == 18 ~ 17,
    country == 19 ~ 18,
    country == 20 ~ 19,
    country == 21 ~ 20,
    country == 22 ~ 21,
    country == 23 ~ 22,
    country == 24 ~ 23,
    country == 25 ~ 24,
    country == 26 ~ 25,
    country == 27 ~ 26,
    country == 28 ~ 27,
    country == 29 ~ 28,
    country == 30 ~ 7,
    country == 31 ~ 29,
    country == 32 ~ 30,
    country == 33 ~ 31,
    country == 34 ~ 32,
    country == 35 ~ 33,
    country == 36 ~ 34,
    TRUE ~ NA
  )))

afro_w6 %<>%
  mutate(cname = case_when(
    ccode == 1 ~ "Benin",
    ccode == 2 ~ "Botswana",
    ccode == 3 ~ "Burkina Faso",
    ccode == 4 ~ "Cabo Verde",
    ccode == 5 ~ "Cameroon",
    ccode == 6 ~ "Côte d'Ivoire",
    ccode == 7 ~ "eSwatini",
    ccode == 8 ~ "Gabon",
    ccode == 9 ~ "Gambia",
    ccode == 10 ~ "Ghana",
    ccode == 11 ~ "Guinea",
    ccode == 12 ~ "Kenya",
    ccode == 13 ~ "Lesotho",
    ccode == 14 ~ "Liberia",
    ccode == 15 ~ "Madagascar",
    ccode == 16 ~ "Malawi",
    ccode == 17 ~ "Mali",
    ccode == 18 ~ "Mauritius",
    ccode == 19 ~ "Morocco",
    ccode == 20 ~ "Mozambique",
    ccode == 21 ~ "Namibia",
    ccode == 22 ~ "Niger",
    ccode == 23 ~ "Nigeria",
    ccode == 24 ~ "São Tomé and Príncipe",
    ccode == 25 ~ "Senegal",
    ccode == 26 ~ "Sierra Leone",
    ccode == 27 ~ "South Africa",
    ccode == 28 ~ "Sudan",
    ccode == 29 ~ "Tanzania",
    ccode == 30 ~ "Togo",
    ccode == 31 ~ "Tunisia",
    ccode == 32 ~ "Uganda",
    ccode == 33 ~ "Zambia",
    ccode == 34 ~ "Zimbabwe",
    ccode == 35 ~ "Algeria",
    ccode == 36 ~ "Burundi",
    ccode == 37 ~ "Egypt",
    TRUE ~ NA_character_
  ))

afro_w7 %<>%
  mutate(round=rep(7, times = length("RESPNO")))%<>%
  select(Q8A, Q8B, Q8C, Q8D, Q8E, Q10A, Q5, Q1, Q89B, URBRUR, Q4B, Q4A, Q97, Q101, 
         Q43G, Q43H, Q43I, Q43B, Q43D, Q43A, Q43C, Q43E, Q43F, Q44B, Q44F, Q44A, 
         Q44E, Q44D, Q12A, Q12B, Q12C, Q12D, Q36, Q21A, Q21B, Q20B, EA_GPS_LO, 
         EA_GPS_LA, Q84, Q85B, Q85A , REGION, EA_SVC_D, RESPNO, 
         round, TOWNVILL, COUNTRY_Old.order,ccode,cname, Q91B, LOCATION.LEVEL.1, Q27A, Q27B, Q27C, Q28, Q13,
         Q38A, Q38B, Q38C, Q45, Q17, Q29, Q22)

afro_w7 %<>%
  select(Q8A, Q8B, Q8C, Q8D, Q8E, Q10A, Q5, Q1, Q89B, URBRUR, Q4B, Q4A, Q97, Q101, 
         Q43G, Q43H, Q43I, Q43B, Q43D, Q43A, Q43C, Q43E, Q43F, Q44B, Q44F, Q44A, 
         Q44E, Q44D, Q12A, Q12B, Q12C, Q12D, Q36, Q21A, Q21B, Q20B, EA_GPS_LO, 
         EA_GPS_LA, Q84, Q85B, Q85A, REGION, EA_SVC_D, RESPNO, 
         round, TOWNVILL, ccode, cname, Q91B, LOCATION.LEVEL.1, Q27A, Q27B, Q27C, Q28, Q13, Q38A, Q38B, Q38C, Q45, Q17, Q29, Q22)

afro_w7%<>%
  rename(food=Q8A,
         water=Q8B,
         medical=Q8C,
         cooking=Q8D,
         money=Q8E,
         security=Q10A,
         compar=Q5,
         age=Q1,
         tele_pos=Q89B,
         rural=URBRUR,
         conditions_eco=Q4B,
         conditions_country=Q4A,
         educ=Q97,
         sex=Q101,
         conf_police=Q43G,
         conf_armee=Q43H,
         conf_court=Q43I,
         conf_parl=Q43B,
         conf_municipal=Q43D,
         conf_pres=Q43A,
         conf_elec=Q43C,
         conf_coal=Q43E,
         conf_oppo=Q43F,
         cor_dep=Q44B,
         cor_juge=Q44F,
         cor_pres=Q44A,
         cor_police=Q44E,
         cor_muni=Q44D,
         radio_news=Q12A,
         tele_news=Q12B,
         journal_news=Q12C,
         internet_news=Q12D,
         satis_demo=Q36,
         commu=Q21A,
         prob=Q21B,
         assoc=Q20B,
         longitude=EA_GPS_LO,
         latitude=EA_GPS_LA,
         ethnie=Q84,
         feeleth=Q85B,
         discri_eth=Q85A,
         region=REGION,
         gsm=EA_SVC_D,
         id=RESPNO,
         round=round,
         town=TOWNVILL,
         ccode=ccode,
         cname=cname,
         internet_use=Q91B,
         district=LOCATION.LEVEL.1,
         one_party=Q27A,
         military=Q27B,
         one_man=Q27C,
         pref_demo=Q28,
         disc_pol=Q13,
         court_decis=Q38A,
         obey_law=Q38B,
         pay_taxes=Q38C,
         level_cor=Q45,
         media_free=Q17,
         account=Q29,
         vote=Q22
         )

saveRDS(afro_w7, file="Data/Data_RDS/afro_w7.rds")

afro_w5 %<>%
  mutate(round=rep(5, times = length("country")))%<>%
  rename(food=q8a,
         water=q8b,
         medical=q8c,
         cooking=q8d,
         money=q8e,
         security=q9a,
         compar=q4,
         age=q1,
         tele_pos=q90b,
         rural=urbrur,
         conditions_eco=q3b,
         conditions_country=q3a,
         educ=q97,
         sex=q101,
         conf_police=q59h,
         conf_armee=q59i,
         conf_court=q59j,
         conf_parl=q59b,
         conf_municipal=q59e,
         conf_pres=q59a,
         conf_elec=q59c,
         conf_coal=q59f,
         conf_oppo=q59g,
         cor_dep=q60b,
         cor_juge=q60g,
         cor_pres=q60a,
         cor_police=q60e,
         cor_muni=q60d,
         radio_news=q13a,
         tele_news=q13b,
         journal_news=q13c,
         internet_news=q13d,
         satis_demo=q43,
         commu=q26a,
         prob=q26b,
         assoc=q25b,
         longitude=longitude,
         latitude=latitude,
         ethnie=q84,
         feeleth=q85b,
         discri_eth=q85a,
         region=region,
         gsm=ea_svc_d,
         id=respno,
         round=round,
         town=townvill,
         ccode=ccode,
         cname=cname,
         internet_use=q91b,
         one_party=q31a,
         military=q31b,
         one_man=q31c,
         pref_demo=q32,
         disc_pol=q15,
         court_decis=q48a,
         obey_law=q48b,
         pay_taxes=q48c,
         tax_need=q50,
         high_taxes=q51,
         avoid_taxes=q56i,
         trust_tax=q59d,
         cor_tax=q60f,
         tax_difficult=q75a,
         tax_use=q75b,
         avoid_tax_difficult=q75c,
         not_pay_services=q76a,
         not_pay_taxes=q76b,
         why_avoid_taxes=q77,
         media_cor_reveal=q53,
         media_cor_act=q38,
         media_free=q20,
         account=q33,
         vote=q27
         )

afro_w5 %<>%
  select(
         food,
         water,
         medical,
         cooking,
         money,
         security,
         compar,
         age,
         tele_pos,
         rural,
         conditions_eco,
         conditions_country,
         educ,
         sex,
         conf_police,
         conf_armee,
         conf_court,
         conf_parl,
         conf_municipal,
         conf_pres,
         conf_elec,
         conf_coal,
         conf_oppo,
         cor_dep,
         cor_juge,
         cor_pres,
         cor_police,
         cor_muni,
         radio_news,
         tele_news,
         journal_news,
         internet_news,
         satis_demo,
         commu,
         prob,
         assoc,
         longitude,
         latitude,
         ethnie,
         feeleth,
         discri_eth,
         region,
         gsm,
         id,
         round,
         town,
         ccode,
         cname,
         internet_use,
         one_party,
         military,
         one_man,
         pref_demo,
         disc_pol,
         court_decis,
         obey_law,
         pay_taxes,
         tax_need,
         high_taxes,
         avoid_taxes,
         trust_tax,
         cor_tax,
         tax_difficult,
         tax_use,
         avoid_tax_difficult,
         not_pay_services,
         not_pay_taxes,
         why_avoid_taxes,
         media_cor_reveal,
         media_cor_act,
         media_free,
         account,
         vote
         )

saveRDS(afro_w5, file="Data/Data_RDS/afro_w5.rds")

afro_w6 %<>%
  mutate(round=rep(6, times = length("country")))%<>%
  rename(food=q8a,
         water=q8b,
         medical=q8c,
         cooking=q8d,
         money=q8e,
         security=q10a,
         compar=q5,
         age=q1,
         tele_pos=q91b,
         rural=urbrur,
         conditions_eco=q4b,
         conditions_country=q4a,
         educ=q97,
         sex=q101,
         conf_police=q52h,
         conf_armee=q52i,
         conf_court=q52j,
         conf_parl=q52b,
         conf_municipal=q52e,
         conf_pres=q52a,
         conf_elec=q52c,
         conf_coal=q52f,
         conf_oppo=q52g,
         cor_dep=q53b,
         cor_juge=q53g,
         cor_pres=q53a,
         cor_police=q53e,
         cor_muni=q53d,
         radio_news=q12a,
         tele_news=q12b,
         journal_news=q12c,
         internet_news=q12d,
         satis_demo=q41,
         commu=q20a,
         prob=q20b,
         assoc=q19b,
         longitude=longitude,
         latitude=latitude,
         ethnie=q87,
         feeleth=q88b,
         discri_eth=q88a,
         region=region,
         gsm=ea_svc_d,
         id=respno,
         round=round,
         town=townvill,
         ccode=ccode,
         cname=cname,
         internet_use=q92b,
         district=locationlevel1,
         one_party=q28a,
         military=q28b,
         one_man=q28c,
         pref_demo=q30,
         disc_pol=q14,
         court_decis=q42a,
         obey_law=q42b,
         pay_taxes=q42c,
         tax_need=q44,
         trust_tax=q52d,
         cor_tax=q53f,
         tax_difficult=q70a,
         avoid_tax_difficult=q70b,
         not_pay_services=q75a,
         not_pay_taxes=q75b,
         media_cor_reveal=q46,
         level_cor=q54,
         media_cor_act=q36,
         media_free=q17,
         complain_services=q26c,
         citizen_taxes=q26e,
         taxes_health=q65c,
         account=q31,
         vote=q21
         )

afro_w6%<>%
  select(food, water, medical, cooking, money, security, compar, age, tele_pos, rural, conditions_eco, conditions_country, educ, sex, conf_police, conf_armee, conf_court, conf_parl, conf_municipal, conf_pres, conf_elec, conf_coal, conf_oppo, cor_dep, cor_juge, cor_pres, cor_police, cor_muni, radio_news, tele_news, journal_news, internet_news, satis_demo, commu, prob, assoc, longitude, latitude, ethnie, feeleth, discri_eth, region, gsm, id, round, town, ccode, cname, internet_use, district, one_party, military, one_man, pref_demo, disc_pol, court_decis, obey_law, pay_taxes, tax_need, trust_tax, cor_tax, tax_difficult, avoid_tax_difficult, not_pay_services, not_pay_taxes, media_cor_reveal, level_cor, media_cor_act, media_free, complain_services, citizen_taxes, taxes_health, account, vote)

saveRDS(afro_w6, file="Data/Data_RDS/afro_w6.rds")

# Merging Afrobarometer waves

data_trust <- bind_rows(afro_w5, afro_w6, afro_w7)

rm(afro_w5, afro_w7, afro_w6)

#Unique ID variable creation and filtering NA's (400) and duplicates (4)

data_trust%<>%
  mutate(id_unique=paste0(id,round))%>%
  filter(!duplicated(id_unique))%>%
  filter(!is.na(latitude), !is.na(longitude))

```

**Merging with Country Variables**

```{r}

#Country Variables

country_var <-inner_join(country_var, corr_index, by ="ISO")%>%
  inner_join(gov_index, by="ISO")%>%
  inner_join(polstab_index, by="ISO")%>%
  inner_join(reg_index, by="ISO")%>%
  inner_join(rule_index, by="ISO")%>%
  inner_join(voiceac_index, by="ISO")%>%
  inner_join(gdppc, by="ISO")%>%
  inner_join(population, by="ISO")%>%
  inner_join(surface, by="ISO")

country_var %<>%
  mutate(cor2006_=as.numeric(cor2006_),
         cor2009_=as.numeric(cor2009_),
         gov2006_=as.numeric(gov2006_),
         gov2009_=as.numeric(gov2009_),
         polstab2006_=as.numeric(polstab2006_),
         polstab2009_=as.numeric(polstab2009_),
         reg2006_=as.numeric(reg2006_),
         reg2009_=as.numeric(reg2009_),
         rule2006_=as.numeric(rule2006_),
         rule2009_=as.numeric(rule2009_),
         voiceac2006_=as.numeric(voiceac2006_),
         voiceac2009_=as.numeric(voiceac2009_))

saveRDS(country_var, file="Data/Data_RDS/country_var.rds")

data_trust <- left_join(data_trust, country_var, by = "ccode")

rm(country_var, corr_index, gov_index, polstab_index, reg_index, rule_index, voiceac_index, gdppc, population, surface)

```

**Merging with Polity2 Democracy Index**

```{r}

vdem %<>%
  subset(select=c("country_name", "year", "e_polity2"))

vdem %<>%
  mutate(cname = case_when(
    country_name == "Benin" ~ "Benin",
    country_name == "Botswana" ~ "Botswana",
    country_name == "Burkina Faso" ~ "Burkina Faso",
    country_name == "Cape Verde" ~ "Cabo Verde",
    country_name == "Cameroon" ~ "Cameroon",
    country_name == "Ivory Coast" ~ "Côte d'Ivoire",
    country_name == "Eswatini" ~ "eSwatini",
    country_name == "Gabon" ~ "Gabon",
    country_name == "The Gambia" ~ "Gambia",
    country_name == "Ghana" ~ "Ghana",
    country_name == "Guinea" ~ "Guinea",
    country_name == "Kenya" ~ "Kenya",
    country_name == "Lesotho" ~ "Lesotho",
    country_name == "Liberia" ~ "Liberia",
    country_name == "Madagascar" ~ "Madagascar",
    country_name == "Malawi" ~ "Malawi",
    country_name == "Mali" ~ "Mali",
    country_name == "Mauritius" ~ "Mauritius",
    country_name == "Morocco" ~ "Morocco",
    country_name == "Mozambique" ~ "Mozambique",
    country_name == "Namibia" ~ "Namibia",
    country_name == "Niger" ~ "Niger",
    country_name == "Nigeria" ~ "Nigeria",
    country_name == "Sao Tome and Principe" ~ "São Tomé and Príncipe",
    country_name == "Senegal" ~ "Senegal",
    country_name == "Sierra Leone" ~ "Sierra Leone",
    country_name == "South Africa" ~ "South Africa",
    country_name == "Sudan" ~ "Sudan",
    country_name == "Tanzania" ~ "Tanzania",
    country_name == "Togo" ~ "Togo",
    country_name == "Tunisia" ~ "Tunisia",
    country_name == "Uganda" ~ "Uganda",
    country_name == "Zambia" ~ "Zambia",
    country_name == "Zimbabwe" ~ "Zimbabwe",
    country_name == "Algeria" ~ "Algeria",
    country_name == "Burundi" ~ "Burundi",
    country_name == "Egypt" ~ "Egypt",
    country_name == "Ethiopia" ~ "Ethiopia",
    TRUE ~ NA_character_
  ))

vdem %<>%
  mutate(ccode = as.numeric(case_when(
    cname == "Benin"~ 1,
    cname == "Botswana"~ 2,
    cname == "Burkina Faso"~ 3,
    cname == "Cabo Verde"~ 4,
    cname == "Cameroon"~ 5,
    cname == "Côte d'Ivoire"~ 6,
    cname == "eSwatini"~ 7,
    cname == "Gabon"~ 8,
    cname == "Gambia"~ 9,
    cname ==  "Ghana"~ 10,
    cname ==  "Guinea"~ 11,
    cname ==  "Kenya"~ 12,
    cname ==  "Lesotho"~ 13,
    cname ==  "Liberia"~ 14,
    cname ==  "Madagascar"~ 15,
    cname ==  "Malawi"~ 16,
    cname ==  "Mali"~ 17,
    cname ==  "Mauritius"~ 18,
    cname ==  "Morocco"~ 19,
    cname ==  "Mozambique"~ 20,
    cname ==  "Namibia"~ 21,
    cname ==  "Niger"~ 22,
    cname ==  "Nigeria"~ 23,
    cname ==  "São Tomé and Príncipe"~ 24,
    cname ==  "Senegal"~ 25,
    cname ==  "Sierra Leone"~ 26,
    cname ==  "South Africa"~ 27,
    cname ==  "Sudan"~ 28,
    cname ==  "Tanzania"~ 29,
    cname ==  "Togo"~ 30,
    cname ==  "Tunisia"~ 31,
    cname ==  "Uganda"~ 32,
    cname ==  "Zambia"~ 33,
    cname ==  "Zimbabwe"~ 34,
    cname ==  "Algeria"~ 35,
    cname ==  "Burundi"~ 36,
    cname ==  "Egypt"~ 37,
    cname == "Ethiopia" ~ 38,
    TRUE ~ NA
  )))

saveRDS(vdem, file="Data/Data_RDS/vdem.rds")

vdem_1618 <- vdem %>%
  filter(!is.na(ccode),year >= 2016 & year <= 2018)

vdem_scoremean_18 <- vdem_1618 %>%
  group_by(ccode) %>%
  summarise(polity_mean_2018 = round(mean(e_polity2, na.rm = TRUE)))

vdem18 <- left_join(vdem, vdem_scoremean_18, by = "ccode")

vdem18 %<>%
  mutate(polity_mean_2018=ifelse(year==2018, polity_mean_2018, NA))%>%
  filter(year==2018) %>%
  subset(select = c("ccode","polity_mean_2018"))%>%
  filter(!is.na(ccode))

vdem_1113 <- vdem %>%
  filter(!is.na(ccode),year >= 2011 & year <= 2013)

vdem_scoremean_13 <- vdem_1113 %>%
  group_by(ccode) %>%
  summarise(polity_mean_2013 = round(mean(e_polity2, na.rm = TRUE)))

vdem13 <- left_join(vdem, vdem_scoremean_13, by = "ccode")

vdem13 %<>%
  mutate(polity_mean_2013=ifelse(year==2013, polity_mean_2013, NA))%>%
  filter(year==2013) %>%
  subset(select = c("ccode","polity_mean_2013")) %>%
  filter(!is.na(ccode))

vdem_1415 <- vdem %>%
  filter(!is.na(ccode),year >= 2014 & year <= 2015)

vdem_scoremean_15 <- vdem_1415 %>%
  group_by(ccode) %>%
  summarise(polity_mean_2015 = round(mean(e_polity2, na.rm = TRUE)))

vdem15 <- left_join(vdem, vdem_scoremean_15, by = "ccode")

vdem15 %<>%
  mutate(polity_mean_2015=ifelse(year==2015, polity_mean_2015, NA))%>%
  filter(year==2015) %>%
  subset(select = c("ccode","polity_mean_2015")) %>%
  filter(!is.na(ccode))

data_trust <- left_join(data_trust, vdem18, by="ccode")
data_trust <- left_join(data_trust, vdem13, by="ccode")
data_trust <- left_join(data_trust, vdem15, by="ccode")

rm(vdem_1113,vdem_1618, vdem_1415, vdem_scoremean_13, vdem_scoremean_18,vdem_scoremean_15, vdem13, vdem18, vdem15, vdem)

```

**Merging with Juriglobe**

```{r}

juriglobe %<>%
  rename(gov_type="Forme\r\nde gouvernement") %>%
  mutate(
    presidential=(gov_type=="Présidentiel"),
    parlementarian=(gov_type=="Parlementaire"),
    semi_presidential=(gov_type=="Semi-présidentiel"),
    monarchical=(gov_type=="Monarchique")
  ) %>%
  mutate(
    presidential = as.numeric(presidential),
    parlementarian = as.numeric(parlementarian),
    semi_presidential = as.numeric(semi_presidential),
    monarchical = as.numeric(monarchical))%>%
  select(ccode, presidential, parlementarian, semi_presidential, monarchical)

saveRDS(juriglobe, file="Data/Data_RDS/juriglobe.rds")

data_trust <- left_join(data_trust, juriglobe, by="ccode")

rm(juriglobe)

```

**Merging with Legal Origin**

```{r}

saveRDS(legal_origin, file="Data/Data_RDS/legal_origin.rds")

data_trust <- left_join(data_trust, legal_origin, by="ISO")

rm(legal_origin)

```

**Add cities**

```{r}

data_trust <- left_join(data_trust, cities, by = "ISO")%>%
  select(-cname.y)%>%
  rename(cname=cname.x)

```

**Variable selection and listing the distinct values**

```{r}

excluded_variables <- c("longitude","latitude","region","id","round","town","district","ccode","cname","ISO","pop2018_","gdpcap2018_","superficie2018_","cor2018_","gov2018_","polstab2018_","reg2018_","rule2018_","voiceac2018_","LG_RI","LG_SE","FDI","PDI","ADI","DI","GCI","color","pop2013_","gdpcap2013_","superficie2013_","cor2013_","gov2013_","polstab2013_","reg2013_","rule2013_","voiceac2013_","pop2015_","gdpcap2015_","superficie2015_","cor2015_","gov2015_","polstab2015_","reg2015_","rule2015_","voiceac2015_","caplat","caplong","ncaplat","ncaplong","polity_mean_2018","polity_mean_2013","polity_mean_2015","presidential","parlementarian","semi_presidential","monarchical","legor", "id_unique")

analysis_variables <- setdiff(names(data_trust), excluded_variables)

unique_values_list <- lapply(analysis_variables, function(var) {
  unique_values_round5 <- unique(data_trust[data_trust$round == 5, var], na.rm = TRUE)
  unique_values_round6 <- unique(data_trust[data_trust$round == 6, var], na.rm = TRUE)
  unique_values_round7 <- unique(data_trust[data_trust$round == 7, var], na.rm = TRUE)

  return(list(round5 = unique_values_round5, round6 = unique_values_round6, round7 = unique_values_round7))
})

for (i in seq_along(analysis_variables)) {
  cat("Variable:", analysis_variables[i], "\n")
  cat("Observations possibles (Round 5):", unique_values_list[[i]]$round5, "\n")
  cat("Observations possibles (Round 6):", unique_values_list[[i]]$round6, "\n")
  cat("Observations possibles (Round 7):", unique_values_list[[i]]$round7, "\n\n")
}

```

**Variable treatment**

```{r, Variables corrections}

variables_to_process <- c("food", "water", "medical", "cooking", "money", "security", "compar", "conditions_eco", "conditions_country", 
                          "conf_police", "conf_armee", "conf_court", 
                          "conf_parl", "conf_municipal", "conf_pres", 
                          "conf_elec", "conf_coal", "conf_oppo", 
                          "cor_dep", "cor_juge", "cor_pres", "cor_police", 
                          "cor_muni", "radio_news", "tele_news", "journal_news", 
                          "internet_news", "satis_demo", "commu", "prob", "assoc", "sex", "rural", "gsm", "internet_use", "one_party", "military", "one_man", "pref_demo", "disc_pol", "court_decis", "obey_law", "pay_taxes", "tax_need", "trust_tax", "cor_tax", "tax_difficult", "avoid_tax_difficult", "not_pay_services", "not_pay_taxes", "media_cor_reveal", "level_cor", "media_cor_act", "media_free", "complain_services", "citizen_taxes", "taxes_health", "high_taxes", "tax_use", "avoid_taxes", "why_avoid_taxes", "vote")

data_trust %<>%
  mutate(across(all_of(variables_to_process), 
                ~na_if(.x, 9) %>% na_if(-1) %>% na_if(8) %>% na_if(998) %>% na_if(460) %>% na_if(99) %>% na_if(997)%>% na_if(98) %>% na_if(1340)%>% na_if(9997) %>% na_if(9999) %>% na_if(9995) %>% na_if(9998)))

#Tele_pos

data_trust%<>%
  mutate(
    tele_pos = if_else(
      round == 7,
      case_when(
        tele_pos == 2 ~ 1,
        tele_pos == 1 ~ 0,
        tele_pos == 0 ~ 0,
        TRUE ~ NA_real_
      ),
      case_when(
        tele_pos == 1 ~ 1,
        tele_pos == 0 ~ 0,
        TRUE ~ NA_real_
      )
    )
  )

#Age

data_trust%<>%
  mutate(age=na_if(age, -1))%>%
  mutate(age=na_if(age, 998))%>%
  mutate(age=na_if(age, 999))

#Educ

data_trust%<>%
  mutate(educ=na_if(educ, 99))%>%
  mutate(educ=na_if(educ, -1))%>%
  mutate(educ=na_if(educ, 98))

#ethnie

data_trust%<>%
  mutate(ethnie=na_if(ethnie,9990))%>%
  mutate(ethnie=na_if(ethnie,9995))%>%
  mutate(ethnie=na_if(ethnie,9997))%>%
  mutate(ethnie=na_if(ethnie,9998))%>%
  mutate(ethnie=na_if(ethnie,9999))%>%
  mutate(ethnie=na_if(ethnie,-1))%>%
  mutate(ethnie=na_if(ethnie,9996))

#discr_eth

data_trust%<>%
  mutate(discri_eth=na_if(discri_eth,7))%>%
  mutate(discri_eth=na_if(discri_eth,9))%>%
  mutate(discri_eth=na_if(discri_eth,997))%>%
  mutate(discri_eth=na_if(discri_eth,998))%>%
  mutate(discri_eth=na_if(discri_eth,-1))%>%
  mutate(discri_eth=na_if(discri_eth,99))%>%
  mutate(discri_eth=na_if(discri_eth,8))%>%
  mutate(discri_eth=na_if(discri_eth,98))

#feeleth

data_trust%<>%
  mutate(feeleth=na_if(feeleth,7))%>%
  mutate(feeleth=na_if(feeleth,9))%>%
  mutate(feeleth=na_if(feeleth,998))%>%
  mutate(feeleth=na_if(feeleth,-1))%>%
  mutate(feeleth=na_if(feeleth,997))%>%
  mutate(feeleth=na_if(feeleth,8))%>%
  mutate(feeleth=na_if(feeleth,99))

data_trust%<>%
  mutate(avoid_tax_difficult=na_if(avoid_tax_difficult,7))

#media_cor_act ; tax_need ; high_taxes; media_free: 5= agree with neither

#avoid_tax_difficult: 7= don't have to pay taxes

#why_avoid_taxes: 0=People don't avoid paying, 1=The tax system is unfair, 2=The taxes are too high, 3=People cannot afford to pay, 4=The poor services they receive from government, 5=Government does not listen to them, 6=Government wastes tax money, 7=Government officials steal tax money, 8=They know they will not be caught, 9=Greed / selfishness, 10=Ignorance, don't know how to pay or don’t understand need to pay, 661=Negligence, 780=Government stopped people from paying the tax(s), 1622=Employers don't deduct or don't give to government

#taxes_health: 6= it depends

unique_values_list <- lapply(analysis_variables, function(var) {
  unique_values_round5 <- unique(data_trust[data_trust$round == 5, var], na.rm = TRUE)
  unique_values_round6 <- unique(data_trust[data_trust$round == 6, var], na.rm = TRUE)
  unique_values_round7 <- unique(data_trust[data_trust$round == 7, var], na.rm = TRUE)

  return(list(round5 = unique_values_round5, round6 = unique_values_round6, round7 = unique_values_round7))
})

for (i in seq_along(analysis_variables)) {
  cat("Variable:", analysis_variables[i], "\n")
  cat("Observations possibles (Round 5):", unique_values_list[[i]]$round5, "\n")
  cat("Observations possibles (Round 6):", unique_values_list[[i]]$round6, "\n")
  cat("Observations possibles (Round 7):", unique_values_list[[i]]$round7, "\n\n")
}

rm(unique_values_list, analysis_variables, excluded_variables, i, variables_to_process)
```

**Distance variable creation**

```{r}

data_trust %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(caplong) & !is.na(caplat)) %>% 
 mutate(distance_cap = distGeo(
    cbind(longitude, latitude),
    cbind(caplong, caplat)
  ) / 1000)

data_trust %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(ncaplong) & !is.na(ncaplat)) %>% 
  mutate(distance_ncap = distGeo(
    cbind(longitude, latitude),
    cbind(ncaplong, ncaplat)
  ) / 1000)

data_trust %<>%
  filter(!is.na(caplong) & !is.na(caplat) &!is.na(ncaplong) & !is.na(ncaplat)) %>% 
   mutate(distance_cap_ncap = distGeo(
    cbind(caplong, caplat),
    cbind(ncaplong, ncaplat)
  ) / 1000)

data_trust %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(sndncaplong) & !is.na(sndncaplat)) %>% 
  mutate(distance_sndncap = distGeo(
    cbind(longitude, latitude),
    cbind(sndncaplong, sndncaplat)
  ) / 1000)

data_trust %<>%
  filter(!is.na(caplong) & !is.na(caplat) &!is.na(sndncaplong) & !is.na(sndncaplat)) %>% 
   mutate(distance_cap_sndncap = distGeo(
    cbind(caplong, caplat),
    cbind(sndncaplong, sndncaplat)
  ) / 1000)

data_trust%<>%
  mutate(distance_cap_10=distance_cap/10)

data_trust%<>%
  mutate(distance_ncap_10=distance_ncap/10)

data_trust%<>%
  mutate(distance_sndncap_10=distance_sndncap/10)

#Log distance

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_log=log(distance_cap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_ncap))%>%
  group_by(cname)%>%
  mutate(distance_ncap_log=log(distance_ncap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_sndncap))%>%
  group_by(cname)%>%
  mutate(distance_sndncap_log=log(distance_sndncap))%>%
  ungroup()

#Max distance normalization

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_max=max(distance_cap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_max95=quantile(distance_cap, probs = 0.95))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max=max(distance_ncap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max95=quantile(distance_ncap, probs = 0.95))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max=max(distance_sndncap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max95=quantile(distance_sndncap, probs = 0.95))%>%
  ungroup()

#Cap

data_trust %<>%
  filter(!is.na(distance_cap_max)) %>%
  group_by(cname)%>%
  mutate(distance_cap_max_norm = distance_cap/distance_cap_max)%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_cap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_cap_max_norm95 = if_else(distance_cap<=distance_cap_max95,distance_cap/ distance_cap_max95, NA_real_))%>%
  ungroup()

#Ncap

data_trust %<>%
  filter(!is.na(distance_ncap_max)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max_norm = distance_ncap/distance_ncap_max)%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_ncap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max_norm95 = if_else(distance_ncap<=distance_ncap_max95,distance_ncap/ distance_ncap_max95, NA_real_))%>%
  ungroup()

#sndNcap
data_trust %<>%
  filter(!is.na(distance_sndncap_max)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max_norm = distance_sndncap/distance_sndncap_max)%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_sndncap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max_norm95 = if_else(distance_sndncap<=distance_sndncap_max95,distance_sndncap/ distance_sndncap_max95, NA_real_))%>%
  ungroup()

#Mean distance normalization

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_mean=mean(distance_cap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_mean=mean(distance_ncap))%>%
  ungroup()

data_trust %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_mean=mean(distance_sndncap))%>%
  ungroup()

#Cap

data_trust %<>%
  filter(!is.na(distance_cap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_cap_mean_norm = distance_cap/distance_cap_mean)%>%
  ungroup()

#Ncap

data_trust %<>%
  filter(!is.na(distance_ncap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_mean_norm = distance_ncap/distance_ncap_mean)%>%
  ungroup()

#sndNcap
data_trust %<>%
  filter(!is.na(distance_sndncap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_mean_norm = distance_sndncap/distance_sndncap_mean)%>%
  ungroup()

##Distance quintiles by country

#Raw
data_trust%<>%
  filter(!is.na(distance_cap)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint = ntile(distance_cap, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint = ntile(distance_ncap, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint = ntile(distance_sndncap, 5))%>%
  ungroup()

#log

data_trust%<>%
  filter(!is.na(distance_cap_log)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_log = ntile(distance_cap_log, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_log)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_log = ntile(distance_ncap_log, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_log)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_log = ntile(distance_sndncap_log, 5))%>%
  ungroup()

#norm max
data_trust%<>%
  filter(!is.na(distance_cap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_max_norm = ntile(distance_cap_max_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_max_norm = ntile(distance_ncap_max_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_max_norm = ntile(distance_sndncap_max_norm, 5))%>%
  ungroup()

#norm mean
data_trust%<>%
  filter(!is.na(distance_cap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_mean_norm = ntile(distance_cap_mean_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_mean_norm = ntile(distance_ncap_mean_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_mean_norm = ntile(distance_sndncap_mean_norm, 5))%>%
  ungroup()

##Distance quintiles all sample

#Raw
data_trust%<>%
  filter(!is.na(distance_cap)) %>%
  mutate(dist_cap_quint_all = ntile(distance_cap, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap)) %>%
  mutate(dist_ncap_quint_all = ntile(distance_ncap, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap)) %>%
  mutate(dist_sndncap_quint_all = ntile(distance_sndncap, 5))%>%
  ungroup()

#log

data_trust%<>%
  filter(!is.na(distance_cap_log)) %>%
  mutate(dist_cap_quint_log_all = ntile(distance_cap_log, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_log)) %>%
  mutate(dist_ncap_quint_log_all = ntile(distance_ncap_log, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_log)) %>%
  mutate(dist_sndncap_quint_log_all = ntile(distance_sndncap_log, 5))%>%
  ungroup()

#norm max
data_trust%<>%
  filter(!is.na(distance_cap_max_norm)) %>%
  mutate(dist_cap_quint_max_norm_all = ntile(distance_cap_max_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_max_norm)) %>%
  mutate(dist_ncap_quint_max_norm_all = ntile(distance_ncap_max_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_max_norm)) %>%
  mutate(dist_sndncap_quint_max_norm_all = ntile(distance_sndncap_max_norm, 5))%>%
  ungroup()

#norm mean
data_trust%<>%
  filter(!is.na(distance_cap_mean_norm)) %>%
  mutate(dist_cap_quint_mean_norm_all = ntile(distance_cap_mean_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap_mean_norm)) %>%
  mutate(dist_ncap_quint_mean_norm_all = ntile(distance_ncap_mean_norm, 5))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap_mean_norm)) %>%
  mutate(dist_sndncap_quint_mean_norm_all = ntile(distance_sndncap_mean_norm, 5))%>%
  ungroup()

#Distance deciles

data_trust%<>%
  filter(!is.na(distance_cap)) %>%
  group_by(cname) %>%
  mutate(distance_cap_dec = ntile(distance_cap, 10))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_cap_max)) %>%
  group_by(cname) %>%
  mutate(distance_cap_dec_max = ntile(distance_cap_max, 10))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(distance_ncap_dec = ntile(distance_ncap, 10))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(distance_ncap_dec_max = ntile(distance_ncap_max, 10))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(distance_sndncap_dec = ntile(distance_sndncap, 10))%>%
  ungroup()

data_trust%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(distance_sndncap_dec_max = ntile(distance_sndncap_max, 10))%>%
  ungroup()
```

**Population and surface normalization**

```{r}

data_trust%<>%
  mutate(pop2018_=pop2018_ / 100000)%>%
  mutate(pop2013_=pop2013_ / 100000)%>%
  mutate(pop2015_=pop2015_ / 100000)%>%
  mutate(superficie2018_=superficie2018_ / 100)%>%
  mutate(superficie2013_=superficie2013_ / 100)%>%
  mutate(superficie2015_=superficie2015_ / 100)

#summary_table <- summary(data_trust, na.rm = TRUE)

```

**Cluster variables creation**

```{r}

#Cluster ethnic X cname

data_trust$cluster_var <- paste0(as.character(data_trust$ethnie),as.character(data_trust$cname))

#Cluster cname X round

data_trust$ef_cr <- paste0(as.character(data_trust$cname),as.character(data_trust$round))

data_trust%<>%
  mutate(country_round=paste0(round,ccode))

#Cluster cname X round X ethnic

data_trust$ef_cr_eth <- paste0(as.character(data_trust$cname),as.character(data_trust$round),as.character(data_trust$ethnie))

```

**Variables creation**

```{r}

#UK colonial origin variable creation

data_trust %<>%
  mutate(color_uk = if_else(color == "UK", 1, 0))

#Unique GDPPC variable

data_trust %<>%
mutate(gdppc = case_when(
    round == 5 ~ gdpcap2013_,
    round == 6 ~ gdpcap2015_,
    round == 7 ~ gdpcap2018_,
    TRUE ~ NA
  ))

#Unique population variable

data_trust %<>%
mutate(population = case_when(
    round == 5 ~ pop2013_,
    round == 6 ~ pop2015_,
    round == 7 ~ pop2018_,
    TRUE ~ NA
  ))

#Unique area variable

data_trust %<>%
mutate(area = case_when(
    round == 5 ~ superficie2013_,
    round == 6 ~ superficie2015_,
    round == 7 ~ superficie2018_,
    TRUE ~ NA
  ))

#Preference for democracy

data_trust %<>%
   mutate(pref_demo_simple=ifelse(pref_demo==3, 1, 0))

data_trust %<>%
   mutate(pref_demo_strict=ifelse(pref_demo==3 & one_party==1|one_party==2 & military==1|military==2 & one_man==1|one_man==2, 1, 0))

data_trust %<>%
   mutate(pref_demo_strict2=ifelse(pref_demo==3 & one_party==1 & military==1 & one_man==1, 1, 0))

#Satisfaction in democratic functionning

data_trust%<>%
  mutate(bin_satis_demo=ifelse(satis_demo>=3, 1, 0))

#Education

data_trust%<>%
  mutate(bin_educ_sec=ifelse(educ>=5, 1, 0))

data_trust%<>%
  mutate(educ_group=case_when(
    educ %in% 0 ~ 0,
    educ %in% c(1,2,3) ~ 1,
    educ %in% c(4,5) ~ 2,
    educ %in% c(6,7,8,9) ~ 3,
    TRUE ~ NA_integer_     
  ))

#Strict ethnic feeling
data_trust%<>%
  mutate(bin_feeleth=ifelse(feeleth<=2, 1, 0))

#Unsafety feeling
data_trust%<>%
  mutate(bin_security=ifelse(security>=2, 1, 0))

#Food need
data_trust%<>%
  mutate(bin_food=ifelse(food>=2, 1, 0))

#Money need
data_trust%<>%
  mutate(bin_money=ifelse(money>=2, 1, 0))

#Personal/country/comparison economic conditions
data_trust%<>%
  mutate(bin_conditions_eco=ifelse(conditions_eco>=3, 1, 0))%>%
  mutate(bin_conditions_country=ifelse(conditions_country>=3, 1, 0))%>%
  mutate(bin_compar=ifelse(compar>=3, 1, 0))

#Politics discussion
data_trust%<>%
  mutate(bin_disc_pol_no=ifelse(disc_pol==0, 1, 0))%>%
  mutate(bin_disc_pol_low=ifelse(disc_pol==1, 1, 0))%>%
  mutate(bin_disc_pol_high=ifelse(disc_pol==2, 1, 0))

#News and rural
data_trust%<>%
  mutate(bin_tele_news=ifelse(tele_news>=3, 1, 0))%>%
  mutate(bin_radio_news=ifelse(radio_news>=3, 1, 0))%>%
  mutate(bin_journal_news=ifelse(journal_news>=3, 1, 0))%>%
  mutate(bin_internet_news=ifelse(internet_news>=3, 1, 0))

data_trust%<>%
    mutate(rural = ifelse(rural == 3, 1, rural))

#Log GDPPC
data_trust%<>%
  mutate(log_gdppc=log(gdppc))

#Unique Polity2
data_trust %<>%
mutate(polity2 = case_when(
    round == 5 ~ polity_mean_2013,
    round == 6 ~ polity_mean_2015,
    round == 7 ~ polity_mean_2018,
    TRUE ~ NA
  ))

#Unique Rule of Law
data_trust %<>%
mutate(rule_index = case_when(
    round == 5 ~ rule2013_,
    round == 6 ~ rule2015_,
    round == 7 ~ rule2018_,
    TRUE ~ NA
  ))

#Unique Corruption Index
data_trust %<>%
mutate(corr_index = case_when(
    round == 5 ~ cor2013_,
    round == 6 ~ cor2015_,
    round == 7 ~ cor2018_,
    TRUE ~ NA
  ))

#Unique Governance Index
data_trust %<>%
mutate(gov_index = case_when(
    round == 5 ~ gov2013_,
    round == 6 ~ gov2015_,
    round == 7 ~ gov2018_,
    TRUE ~ NA
  ))

#Unique Political Stability Index
data_trust %<>%
mutate(polstab_index = case_when(
    round == 5 ~ polstab2013_,
    round == 6 ~ polstab2015_,
    round == 7 ~ polstab2018_,
    TRUE ~ NA
  ))

#Unique Regulatory Quality Index
data_trust %<>%
mutate(reg_index = case_when(
    round == 5 ~ reg2013_,
    round == 6 ~ reg2015_,
    round == 7 ~ reg2018_,
    TRUE ~ NA
  ))

#Unique Voice Accountability Index
data_trust %<>%
mutate(voiceac_index = case_when(
    round == 5 ~ voiceac2013_,
    round == 6 ~ voiceac2015_,
    round == 7 ~ voiceac2018_,
    TRUE ~ NA
  ))

#Weighted institutional trust index
#data_trust %<>%
 # group_by(id_unique)%>%
#  mutate(weighted_inst_trust = ifelse(all(is.na(c(conf_pres, conf_parl, conf_elec))), NA, weighted.mean(c(conf_pres, conf_parl, conf_elec), na.rm = TRUE)))%>%
#  ungroup()

#Mean institutional trust index
data_trust %<>%
  mutate(mean_inst_trust = (trust_pres+ trust_parl + trust_elec) / 
           rowSums(!is.na(cbind(trust_pres, trust_parl, trust_elec))))

#data_trust %>% select(weighted_inst_trust, conf_parl, conf_pres, conf_elec)%>%View()

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

```

```{r}
### Après avoir fait tourner le script ADM.RMD ###

data_trust <- readRDS("Data/Data_RDS/data_trust2.rds")

data_trust %<>%
  group_by(NAME_1, round) %>%
  mutate(internet_use_adm1 = if_else(!is.na(internet_use) & NAME_1 != "NA", mean(internet_use, na.rm = TRUE), NA_real_)) %>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round) %>%
  mutate(internet_use_adm2 = if_else(!is.na(internet_use) & NAME_2 != "NA", mean(internet_use, na.rm = TRUE), NA_real_)) %>%
  ungroup()

data_trust %<>%
  group_by(NAME_3, round) %>%
  mutate(internet_use_adm3 = if_else(!is.na(internet_use) & NAME_3 != "NA", mean(internet_use, na.rm = TRUE), NA_real_)) %>%
  ungroup()

summary(select(data_trust, internet_use_adm1, internet_use_adm2, internet_use_adm3))

### Après avoir fait tourner le script popdensity.R ###

summary(select(data_trust, popdensity_1, popdensity_2, popdensity_3))

data_trust%<>%
  group_by(NAME_1, round)%>%
  mutate(internet_use_adm1_pop=internet_use_adm1*popdensity_1)%>%
  ungroup()

data_trust%<>%
  group_by(NAME_2, round)%>%
  mutate(internet_use_adm2_pop=internet_use_adm2*popdensity_2)%>%
  ungroup()

data_trust%<>%
  group_by(NAME_3, round)%>%
  mutate(internet_use_adm3_pop=internet_use_adm3*popdensity_3)%>%
  ungroup()

#summary(select(data_trust, internet_use_adm1_pop, internet_use_adm2_pop, internet_use_adm3_pop))

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
data_trust %<>%
  mutate(age_2 = age^2)

data_trust %<>%
  group_by(NAME_1) %>%
  mutate(region1_id = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(ccode, region1_id) %>%
  mutate(region1_ccode = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(round, region1_id) %>%
  mutate(region1_round = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2) %>%
  mutate(region2_id = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(ccode, region2_id) %>%
  mutate(region2_ccode = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(round, region2_id) %>%
  mutate(region2_round = cur_group_id())%>%
  ungroup()

data_trust %<>%
  group_by(NAME_3) %>%
  mutate(region3_id = cur_group_id()) %>%
  ungroup()

data_trust%<>%
  group_by(ccode, region3_id) %>%
  mutate(region3_ccode = cur_group_id())%>%
  ungroup()

data_trust%<>%
  group_by(round, region3_id) %>%
  mutate(region3_round = cur_group_id())%>%
  ungroup()

data_trust%<>%
  mutate(r5=if_else(round==5, 1, 0))%>%
  mutate(r6=if_else(round==6, 1, 0))%>%
  mutate(r7=if_else(round==7, 1, 0))%>%
  mutate(r6_7=if_else(round==6|round==7, 1, 0))

data_trust %<>%
  mutate(cor_tax = as.double(cor_tax))

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
did_use_internet_trust_r7_5 <- data_trust

did_use_internet_trust_r7_5 %<>%
  filter(!is.na(NAME_2))%>%
  filter(round %in% c(5, 7)) %>%
  group_by(NAME_2) %>%
  filter(all(c(5, 7) %in% round)) %>%
  ungroup()

did_use_internet_trust_r7_5%<>%
  select(cname, NAME_2, round, internet_use_adm2)%>%
  distinct(NAME_2, round, .keep_all = TRUE)%>%
  arrange(NAME_2)

did_use_internet_trust_r7_5%<>%
 group_by(NAME_2) %>%
 mutate(diff_internet_use_adm2_r7_5 = internet_use_adm2[round == 7] - internet_use_adm2[round == 5])%>%
  arrange(NAME_2,round)%>%
  ungroup()

did_use_internet_trust_r7_5 %<>% distinct(NAME_2, .keep_all = TRUE)

did_use_internet_trust_r7_5%<>%
  select(NAME_2, diff_internet_use_adm2_r7_5)

data_trust %<>% left_join(did_use_internet_trust_r7_5, by="NAME_2")

rm(did_use_internet_trust_r7_5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
did_use_internet_trust_r6_5 <- data_trust

did_use_internet_trust_r6_5 %<>%
  filter(!is.na(NAME_2))%>%
  filter(round %in% c(5, 6)) %>%
  group_by(NAME_2) %>%
  filter(all(c(5, 6) %in% round)) %>%
  ungroup()

did_use_internet_trust_r6_5%<>%
  select(cname, NAME_2, round, internet_use_adm2)%>%
  distinct(NAME_2, round, .keep_all = TRUE)%>%
  arrange(NAME_2)

did_use_internet_trust_r6_5%<>%
 group_by(NAME_2) %>%
 mutate(diff_internet_use_adm2_r6_5 = internet_use_adm2[round == 6] - internet_use_adm2[round == 5])%>%
  arrange(NAME_2,round)%>%
  ungroup()

did_use_internet_trust_r6_5 %<>% distinct(NAME_2, .keep_all = TRUE)

did_use_internet_trust_r6_5%<>%
  select(NAME_2, diff_internet_use_adm2_r6_5)

data_trust %<>% left_join(did_use_internet_trust_r6_5, by="NAME_2")

rm(did_use_internet_trust_r6_5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
data_trust%<>%
  mutate(diff_internet_use_adm2=case_when(round==7~diff_internet_use_adm2_r7_5,
                                          round==6~diff_internet_use_adm2_r6_5))

#data_trust %>% select(cname, NAME_2, round, internet_use_adm2, diff_internet_use_adm2_r7_5, diff_internet_use_adm2_r6_5, diff_internet_use_adm2)%>%arrange(NAME_2)%>%View()

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
#data_trust %<>%
#  group_by(NAME_2, round)%>%
#  mutate(weighted_inst_trust_adm2=mean(weighted_inst_trust, na.rm = TRUE))%>%
#  ungroup()

#data_trust %<>%
#  group_by(NAME_1, round)%>%
#  mutate(weighted_inst_trust_adm1=mean(weighted_inst_trust, na.rm = TRUE))%>%
#  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(conf_parl_adm2=mean(conf_parl, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(feelnat_adm2=mean(feeleth, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2)%>%
  mutate(dist_cap_max_norm_adm2=mean(distance_cap_max_norm, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2)%>%
  mutate(dist_cap_quint_adm2=mean(dist_cap_quint, na.rm = TRUE))%>%
  ungroup()

#cor_pres, cor_juge, cor_dep, cor_tax, cor_muni

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(cor_pres_adm2=mean(cor_pres, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(cor_dep_adm2=mean(cor_dep, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(cor_juge_adm2=mean(cor_juge, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(cor_tax_adm2=mean(cor_tax, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(cor_muni_adm2=mean(cor_muni, na.rm = TRUE))%>%
  ungroup()

data_trust %<>%
  group_by(NAME_2, round)%>%
  mutate(internet_news_adm2=mean(internet_news, na.rm = TRUE))%>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/data_trust2.rds")

```

```{r}
did_weighted_inst_trust_r7_5 <- data_trust

did_weighted_inst_trust_r7_5 %<>%
  filter(!is.na(NAME_2))%>%
  filter(round %in% c(5, 7)) %>%
  group_by(NAME_2) %>%
  filter(all(c(5, 7) %in% round)) %>%
  ungroup()

did_weighted_inst_trust_r7_5%<>%
  select(cname, NAME_2, round, weighted_inst_trust_adm2)%>%
  distinct(NAME_2, round, .keep_all = TRUE)%>%
  arrange(NAME_2)

did_weighted_inst_trust_r7_5%<>%
 group_by(NAME_2) %>%
 mutate(diff_inst_trust_adm2_r7_5 = weighted_inst_trust_adm2[round == 7] - weighted_inst_trust_adm2[round == 5])%>%
  arrange(NAME_2,round)%>%
  ungroup()

did_weighted_inst_trust_r7_5 %<>% distinct(NAME_2, .keep_all = TRUE)

did_weighted_inst_trust_r7_5%<>%
  select(NAME_2, diff_inst_trust_adm2_r7_5)

data_trust %<>% left_join(did_weighted_inst_trust_r7_5, by="NAME_2")

rm(did_weighted_inst_trust_r7_5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

```

```{r}
did_weighted_inst_trust_r6_5 <- data_trust

did_weighted_inst_trust_r6_5 %<>%
  filter(!is.na(NAME_2))%>%
  filter(round %in% c(5, 6)) %>%
  group_by(NAME_2) %>%
  filter(all(c(5, 6) %in% round)) %>%
  ungroup()

did_weighted_inst_trust_r6_5%<>%
  select(cname, NAME_2, round, weighted_inst_trust_adm2)%>%
  distinct(NAME_2, round, .keep_all = TRUE)%>%
  arrange(NAME_2)

did_weighted_inst_trust_r6_5%<>%
 group_by(NAME_2) %>%
 mutate(diff_inst_trust_adm2_r6_5 = weighted_inst_trust_adm2[round == 6] - weighted_inst_trust_adm2[round == 5])%>%
  arrange(NAME_2,round)%>%
  ungroup()

did_weighted_inst_trust_r6_5 %<>% distinct(NAME_2, .keep_all = TRUE)

did_weighted_inst_trust_r6_5%<>%
  select(NAME_2, diff_inst_trust_adm2_r6_5)

data_trust %<>% left_join(did_weighted_inst_trust_r6_5, by="NAME_2")

rm(did_weighted_inst_trust_r6_5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

```

```{r}
data_trust%<>%
  mutate(diff_inst_trust_adm2=case_when(round==7~diff_inst_trust_adm2_r7_5,
                                          round==6~diff_inst_trust_adm2_r6_5))

#data_trust %>% select(cname, NAME_2, round, inst_trust_adm2, diff_inst_trust_adm2_r7_5, diff_inst_trust_adm2_r6_5, diff_inst_trust_adm2)%>%arrange(NAME_2)%>%View()

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

```

```{r}
countries <- unique(data_trust$ISO)

qog <- read.csv("Data/Data_raw/qog_std_ts_jan24.csv")

qog %<>%
  filter(year==2013|year==2015|year==2018)

qog%<>%
  filter(ccodealp %in% countries)

qog %<>%
  select(year, ccodealp, aii_q55, aii_q56, aii_q57, fhp_mclr5, fhp_mcpp5, fhp_score5, fhp_status5, gcb_pmedia, rsf_pfi, sgi_qd, vdem_mecorrpt, wvs_confpr, wvs_conftv)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(ISO=ccodealp, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)

qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2013 ~ 5,
                   round==2015 ~ 6,
                   round==2018 ~ 7))

data_trust %<>% left_join(qog, by=c("ISO", "round"))

```

```{r}
data_trust %<>%
  rename(feelnat=feeleth)

data_trust%<>%
  mutate(color = case_when(
    ISO == "BDI" ~ "BEL",
    ISO == "LBR" ~ NA_character_,
    TRUE ~ color
  ))
```

```{r}

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q29)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q29)%>%
  rename(account=Q29)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

data_trust %>%
  select(round, id, account)%>%
  filter(round==7)%>%
  summary()

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q31)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q31)

afro_w6%<>%
  rename(account=q31)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

rm(afro_w6)

data_trust %>%
  select(round, id, account.y)%>%
  filter(round==7)%>%
  summary()

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q33)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q33)

afro_w5%<>%
  rename(account=q33)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

rm(afro_w5)

data_trust %>%
  select(round, id, account)%>%
  filter(round==5)%>%
  summary()

data_trust%<>%
  mutate(account = case_when(
    round == 6 ~ account.y,
    round == 7 ~ account.x,
    round== 5  ~ account
  ))

data_trust%<>%
  select(-account.y, -account.x)

data_trust %<>%
  mutate(account=case_when(
    account %in% c(5,-1, 9, 8, 998) ~ NA_real_,
    TRUE~account
  ))

```

```{r}

data_trust %<>%
  group_by(NAME_2, round) %>%
  mutate(feelnat_adm2 = if_else(!is.na(feelnat) & NAME_2 != "NA", mean(feelnat, na.rm = TRUE), NA_real_)) %>%
  ungroup()

data_trust %<>%
  group_by(NAME_1, round) %>%
  mutate(feelnat_adm1 = if_else(!is.na(feelnat) & NAME_1 != "NA", mean(feelnat, na.rm = TRUE), NA_real_)) %>%
  ungroup()

```

```{r}
data_trust%<>%
  mutate(area_log = if_else(!is.na(area), log(area), NA_real_))
```

```{r}
data_trust%<>%
  mutate(ceeac=ifelse(ISO%in%c("BDI","CMR","GAB","STP"), 1, 0))%>%
  mutate(cedeao=ifelse(ISO%in%c("BEN","BFA", "CIV", "GMB", "GHA", "GIN","LBR","MLI", "NER","NGA","SLE","SEN","TGO"), 1, 0))%>%
  mutate(sadc=ifelse(ISO%in%c("ZAF", "BWA", "MDG", "NAM", "SWZ", "TZA", "ZMB", "ZWE"), 1, 0))%>%
  mutate(cae=ifelse(ISO%in%c("BDI", "KEN", "SDN", "TZA", "UGA"), 1, 0))

```

** Correction rural NA **

```{r}
data_trust%>%
  select(rural, id_unique, round, cname, NAME_1, NAME_2, NAME_3, longitude, latitude)%>%
  filter(is.na(rural))%>%
  distinct(NAME_2)%>%
  print(n=100)

data_trust%>%
  select(rural, NAME_1, NAME_2, NAME_3, latitude, longitude)%>%
  filter(NAME_2=="TA Santhe")%>%
  View()

data_trust%>%
  select(rural, NAME_1, NAME_2, NAME_3, latitude, longitude)%>%
  filter(NAME_2=="Lilongwe City")%>%
  count(rural)

data_trust%<>%
  mutate(rural=ifelse(NAME_2=="TA Mwenewenya" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Kyungu" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="SC Kampingo Sibande" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Mwase" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="Nkhotakota Game Reserve" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="Lilongwe City" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Kaphuka" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="SC Chowe" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Mpama" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Mkhumba" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Nsamala" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="Lake Malawi" & is.na(rural), 2, rural))%>%
  mutate(rural=ifelse(NAME_2=="Mangochi Town" & is.na(rural), 1, rural))%>%
  mutate(rural=ifelse(NAME_2=="TA Santhe" & is.na(rural), 2, rural))
```

** Add vote **

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

data_trust%<>%select(-vote)

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q22)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q22)%>%
  rename(vote=Q22)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(vote = if_else(vote %in% c(0, 2, 3, 4, 5 ,6 , 7), 0, if_else(vote == 1, 1, NA_real_)))

data_trust %>%
  select(round, id, vote)%>%
  filter(round==7)%>%
  summary()

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q21)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q21)

afro_w6%<>%
  rename(vote=q21)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(vote.y = if_else(vote.y %in% c(0, 2, 3, 4, 5 ,6 , 7), 0, if_else(vote.y == 1, 1, NA_real_)))

data_trust %>%
  select(round, id, vote.y)%>%
  filter(round==6)%>%
  summary()

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q27)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q27)

afro_w5%<>%
  rename(vote=q27)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

rm(afro_w5)

data_trust%<>%
  mutate(vote = if_else(vote %in% c(0, 2, 3, 4, 5 ,6 , 7), 0, if_else(vote == 1, 1, NA_real_)))

data_trust %>%
  select(round, id, vote)%>%
  filter(round==5)%>%
  summary()

data_trust%<>%
  mutate(vote = case_when(
    round == 6 ~ vote.y,
    round == 7 ~ vote.x,
    round== 5  ~ vote
  ))

data_trust%<>%
  select(-vote.y, -vote.x)

data_trust%>%
  select(round, vote, rural)%>%
  group_by(round, rural)%>%
  do(data.frame(summary = capture.output(summary(.))))%>%
  print(n=100)

```

** Add social media question **
```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q12E)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q12E)%>%
  rename(sm_news=Q12E)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(sm_news = if_else(sm_news %in% c(0, 1, 2, 3, 4), sm_news, NA_real_))

data_trust %>%
  select(round, id, sm_news)%>%
  filter(round==7)%>%
  summary()

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q12e)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q12e)

afro_w6%<>%
  rename(sm_news=q12e)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(sm_news.y = if_else(sm_news.y %in% c(0, 1, 2, 3, 4), sm_news.y, NA_real_))

data_trust %>%
  select(round, id, sm_news.y)%>%
  filter(round==6)%>%
  summary()

rm(afro_w6)

data_trust%<>%
  mutate(sm_news = case_when(
    round == 6 ~ sm_news.y,
    round == 7 ~ sm_news.x))

data_trust%<>%
  select(-sm_news.y, -sm_news.x)

data_trust%>%
  select(round, sm_news)%>%
  group_by(round)%>%
  do(data.frame(summary = capture.output(summary(.))))%>%
  print(n=50)

data_trust%>%
  select(round, vote)%>%
  group_by(round)%>%
  do(data.frame(summary = capture.output(summary(.))))%>%
  print(n=50)

```

```{r}
afro_w7%>%
  count(URBRUR)

afro_w6%>%
  count(urbrur)

afro_w5%>%
  count(urbrur)

```

```{r}
data_trust%>%
  select(internet_news, round, rural)%>%
  group_by(round, rural)%>%
  do(data.frame(summary = capture.output(summary(.))))%>%
  print(n=100)

data_trust%>%
  select(internet_use, round, rural)%>%
  group_by(round, rural)%>%
  do(data.frame(summary = capture.output(summary(.))))%>%
  print(n=100)

```

** Add variables on trust in parties and institutional performances
```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q43E, Q43F, Q58A, Q58B, Q58C)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q43E, Q43F, Q58A, Q58B, Q58C)%>%
  rename(trust_govpart=Q43E, trust_opppart=Q43F, perf_pres=Q58A, perf_mp=Q58B, perf_local=Q58C)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(trust_govpart = if_else(trust_govpart %in% c(0, 1, 2, 3), trust_govpart, NA_real_))%>%
  mutate(trust_opppart = if_else(trust_opppart %in% c(0, 1, 2, 3), trust_opppart, NA_real_))%>%
  mutate(perf_pres = if_else(perf_pres %in% c(1, 2, 3, 4), perf_pres, NA_real_))%>%
  mutate(perf_mp = if_else(perf_mp %in% c(1, 2, 3, 4), perf_mp, NA_real_))%>%
  mutate(perf_local = if_else(perf_local %in% c(1, 2, 3, 4), perf_local, NA_real_))

data_trust %>%
  select(round, id, trust_govpart, trust_opppart, perf_pres, perf_mp, perf_local, dist_cap_quint_max_norm)%>%
  filter(round==7, dist_cap_quint_max_norm==2)%>%
  summary()

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q52f, q52g, q68a, q68b, q68c)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q52f, q52g, q68a, q68b, q68c)%>%
  rename(trust_govpart=q52f, trust_opppart=q52g, perf_pres=q68a, perf_mp=q68b, perf_local=q68c)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(trust_govpart.y = if_else(trust_govpart.y %in% c(0, 1, 2, 3), trust_govpart.y, NA_real_))%>%
  mutate(trust_opppart.y = if_else(trust_opppart.y %in% c(0, 1, 2, 3), trust_opppart.y, NA_real_))%>%
  mutate(perf_pres.y = if_else(perf_pres.y %in% c(1, 2, 3, 4), perf_pres.y, NA_real_))%>%
  mutate(perf_mp.y = if_else(perf_mp.y %in% c(1, 2, 3, 4), perf_mp.y, NA_real_))%>%
  mutate(perf_local.y = if_else(perf_local.y %in% c(1, 2, 3, 4), perf_local.y, NA_real_))

data_trust%<>%
  mutate(trust_govpart = case_when(
    round == 6 ~ trust_govpart.y,
    round == 7 ~ trust_govpart.x))%>%
  mutate(trust_opppart = case_when(
    round == 6 ~ trust_opppart.y,
    round == 7 ~ trust_opppart.x))%>%
  mutate(perf_pres = case_when(
    round == 6 ~ perf_pres.y,
    round == 7 ~ perf_pres.x))%>%
  mutate(perf_mp = case_when(
    round == 6 ~ perf_mp.y,
    round == 7 ~ perf_mp.x))%>%
  mutate(perf_local = case_when(
    round == 6 ~ perf_local.y,
    round == 7 ~ perf_local.x))

data_trust%<>%
  select(-c(trust_govpart.y, trust_govpart.x, trust_opppart.y, trust_opppart.x, perf_pres.x, perf_pres.y, perf_mp.x, perf_mp.y, perf_local.x, perf_local.y))

data_trust %>%
  select(round, id, trust_govpart, trust_opppart, perf_pres, perf_mp, perf_local, dist_cap_quint_max_norm)%>%
  filter(round==7, dist_cap_quint_max_norm==5)%>%
  summary()

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q59f, q59g, q71a, q71b, q71c)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q59f, q59g, q71a, q71b, q71c)%>%
  rename(trust_govpart=q59f, trust_opppart=q59g, perf_pres=q71a, perf_mp=q71b, perf_local=q71c)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(trust_govpart.y = if_else(trust_govpart.y %in% c(0, 1, 2, 3), trust_govpart.y, NA_real_))%>%
  mutate(trust_opppart.y = if_else(trust_opppart.y %in% c(0, 1, 2, 3), trust_opppart.y, NA_real_))%>%
  mutate(perf_pres.y = if_else(perf_pres.y %in% c(1, 2, 3, 4), perf_pres.y, NA_real_))%>%
  mutate(perf_mp.y = if_else(perf_mp.y %in% c(1, 2, 3, 4), perf_mp.y, NA_real_))%>%
  mutate(perf_local.y = if_else(perf_local.y %in% c(1, 2, 3, 4), perf_local.y, NA_real_))

data_trust%<>%
  mutate(trust_govpart = case_when(
    round == 5 ~ trust_govpart.y,
    round %in% c(6,7) ~ trust_govpart.x))%>%
  mutate(trust_opppart = case_when(
    round == 5 ~ trust_opppart.y,
    round %in% c(6,7) ~ trust_opppart.x))%>%
  mutate(perf_pres = case_when(
    round == 5 ~ perf_pres.y,
    round %in% c(6,7) ~ perf_pres.x))%>%
  mutate(perf_mp = case_when(
    round == 5 ~ perf_mp.y,
    round %in% c(6,7) ~ perf_mp.x))%>%
  mutate(perf_local = case_when(
    round == 5 ~ perf_local.y,
    round %in% c(6,7) ~ perf_local.x))

data_trust%<>%
  select(-c(trust_govpart.y, trust_govpart.x, trust_opppart.y, trust_opppart.x, perf_pres.x, perf_pres.y, perf_mp.x, perf_mp.y, perf_local.x, perf_local.y))

data_trust %>%
  select(round, id, trust_govpart, trust_opppart, perf_pres, perf_mp, perf_local, dist_cap_quint_max_norm)%>%
  filter(round==5, dist_cap_quint_max_norm==5)%>%
  summary()

rm(afro_w5)

```

** Add variables on protest participation

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q26E)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q26E)%>%
  rename(protest=Q26E)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(protest = if_else(protest %in% c(0, 1, 2, 3, 4), protest, NA_real_))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q27e)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q27e)%>%
  rename(protest=q27e)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(protest.y = if_else(protest.y %in% c(0, 1, 2, 3, 4), protest.y, NA_real_))

data_trust%<>%
  mutate(protest = case_when(
    round == 6 ~ protest.y,
    round == 7 ~ protest.x))

data_trust%<>%
  select(-c(protest.y, protest.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q26d)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q26d)%>%
  rename(protest=q26d)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(protest.y = if_else(protest.y %in% c(0, 1, 2, 3, 4), protest.y, NA_real_))

data_trust%<>%
  mutate(protest = case_when(
    round == 5 ~ protest.y,
    round %in% c(6,7) ~ protest.x))

data_trust%<>%
  select(-c(protest.y, protest.x))

rm(afro_w5)

data_trust%<>%
  mutate(protest = if_else(!is.na(protest) & protest %in% c(0, 1), 0, if_else(!is.na(protest) & protest %in% c(2, 3, 4), 1, NA_real_)))

```

** Rename variables
```{r}
data_trust%<>%
  rename(trust_local=conf_municipal)

data_trust%<>%
  rename(trust_pres=conf_pres)%>%
  rename(trust_parl=conf_parl)%>%
  rename(trust_elec=conf_elec)

```

** Add variables on level of corruption and local corruption

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q45)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q45)%>%
  rename(corr_level=Q45)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(corr_level = if_else(corr_level %in% c(1, 2, 3, 4, 5), corr_level, NA_real_))

data_trust%<>%
  mutate(
    corr_level = case_when(
      corr_level == 5 ~ 1,
      corr_level == 4 ~ 2,
      corr_level == 3 ~ 3,
      corr_level == 2 ~ 4,
      corr_level == 1 ~ 5,
      TRUE ~ NA_real_
    )
  )

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q54)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q54)%>%
  rename(corr_level=q54)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(corr_level.y = if_else(corr_level.y %in% c(1, 2, 3, 4, 5), corr_level.y, NA_real_))

data_trust%<>%
  mutate(corr_level = case_when(
    round == 6 ~ corr_level.y,
    round == 7 ~ corr_level.x))

data_trust%<>%
  mutate(
    corr_level = case_when(
      corr_level == 5 ~ 1,
      corr_level == 4 ~ 2,
      corr_level == 3 ~ 3,
      corr_level == 2 ~ 4,
      corr_level == 1 ~ 5,
      TRUE ~ NA_real_
    )
  )

data_trust%<>%
  select(-c(corr_level.y, corr_level.x))

rm(afro_w6)

data_trust%>%
  select(corr_level, round)%>%
  filter(round %in% c(6,7))%>%
  summary()

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q44D)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q44D)%>%
  rename(corr_local=Q44D)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(corr_local = if_else(corr_local %in% c(0, 1, 2, 3), corr_local, NA_real_))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q53d)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q53d)%>%
  rename(corr_local=q53d)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(corr_local.y = if_else(corr_local.y %in% c(0, 1, 2, 3), corr_local.y, NA_real_))

data_trust%<>%
  mutate(corr_local = case_when(
    round == 6 ~ corr_local.y,
    round == 7 ~ corr_local.x))

data_trust%<>%
  select(-c(corr_local.y, corr_local.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q60d)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q60d)%>%
  rename(corr_local=q60d)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(corr_local.y = if_else(corr_local.y %in% c(0, 1, 2, 3), corr_local.y, NA_real_))

data_trust%<>%
  mutate(corr_local = case_when(
    round == 5 ~ corr_local.y,
    round %in% c(6,7) ~ corr_local.x))

data_trust%<>%
  select(-c(corr_local.y, corr_local.x))

rm(afro_w5)

data_trust%<>%
  rename(corr_dep=cor_dep,
         corr_juge=cor_juge, 
         corr_pres=cor_pres,
         corr_police=cor_police,
         corr_muni=cor_muni,
         corr_tax=cor_tax)

```

** Transformation feelnat en trois niveaux

```{r}
data_trust%>%
  select(feelnat)%>%
  summary()

data_trust%<>%
  mutate(feelnat_cat = case_when(
      !is.na(feelnat) & feelnat %in% c(1, 2) ~ 1,
      !is.na(feelnat) & feelnat == 3 ~ 2,
      !is.na(feelnat) & feelnat %in% c(4, 5) ~ 3,
      TRUE ~ NA_real_))

```

** Add country economic performance

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q6)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q6)%>%
  rename(perf_country=Q6)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(perf_country = if_else(perf_country %in% c(1, 2, 3, 4, 5), perf_country, NA_real_))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q6)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q6)%>%
  rename(perf_country=q6)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(perf_country.y = if_else(perf_country.y %in% c(1, 2, 3, 4, 5), perf_country.y, NA_real_))

data_trust%<>%
  mutate(perf_country = case_when(
    round == 6 ~ perf_country.y,
    round == 7 ~ perf_country.x))

data_trust%<>%
  select(-c(perf_country.y, perf_country.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q5a)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q5a)%>%
  rename(perf_country=q5a)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(perf_country.y = if_else(perf_country.y %in% c(1, 2, 3, 4, 5), perf_country.y, NA_real_))

data_trust%<>%
  mutate(perf_country = case_when(
    round == 5 ~ perf_country.y,
    round %in% c(6,7) ~ perf_country.x))

data_trust%<>%
  select(-c(perf_country.y, perf_country.x))

rm(afro_w5)

```

** Creation strict national feeling
```{r}
data_trust%<>%
  mutate(feelnat_bin = case_when(
      !is.na(feelnat) & feelnat %in% c(4, 5) ~ 1,
      !is.na(feelnat) & feelnat %in% c(1, 2, 3) ~ 0,
      TRUE ~ NA_real_))

```

** Transformation pref democratie

```{r}
#Preference for democracy

data_trust %>%
  mutate(pref_demo_simple = ifelse(is.na(pref_demo), NA, ifelse(pref_demo == 3, 1, 0)))%>%
  select(pref_demo_simple)%>%
  summary()

data_trust %<>%
  mutate(
    na_count = rowSums(is.na(cbind(one_party, military, one_man))),
    pref_demo_strict = case_when(
      # Deux ou plus des trois variables sont NA
      na_count >= 2 ~ NA_real_,
      # `pref_demo` est 3 et au moins deux des variables sont dans {1, 2}
      pref_demo == 3 & 
      (sum(c(one_party, military, one_man) %in% c(1, 2), na.rm = TRUE) >= 2) ~ 1,
      # Sinon, la valeur est 0
      TRUE ~ 0
    ))

data_trust %<>%
  mutate(
    na_count = rowSums(is.na(cbind(one_party, military, one_man))),
    pref_demo_strict2 = case_when(
      # Deux ou plus des trois variables sont NA
      na_count >= 2 ~ NA_real_,
      # `pref_demo` est 3 et toutes les variables sont égales à 1
      pref_demo == 3 & one_party == 1 & military == 1 & one_man == 1 ~ 1,
      # Sinon, la valeur est 0
      TRUE ~ 0
    ))

```

** Add occupation

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q94)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q94)%>%
  rename(emp=Q94)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(emp = case_when(
    emp %in% c(0, 1) ~ 0,
    emp %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q95)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q95)%>%
  rename(emp=q95)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(emp.y = case_when(
    emp.y %in% c(0, 1) ~ 0,
    emp.y %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(emp = case_when(
    round == 6 ~ emp.y,
    round == 7 ~ emp.x))

data_trust%<>%
  select(-c(emp.y, emp.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q96)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q96)%>%
  rename(emp=q96)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(emp.y = case_when(
    emp.y %in% c(0, 1) ~ 0,
    emp.y %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(emp = case_when(
    round == 5 ~ emp.y,
    round %in% c(6,7) ~ emp.x))

data_trust%<>%
  select(-c(emp.y, emp.x))

rm(afro_w5)

data_trust%>%select(disc_pol)%>%summary()
```

** Media dummies

```{r}
data_trust%<>%
  mutate(radio_news_bin=case_when(
    radio_news%in%c(0,1) ~ 0,
    radio_news%in%c(2,3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(tele_news_bin=case_when(
    tele_news%in%c(0,1) ~ 0,
    tele_news%in%c(2,3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(journal_news_bin=case_when(
    journal_news%in%c(0,1, 2) ~ 0,
    journal_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(internet_news_bin=case_when(
    internet_news%in%c(0,1, 2) ~ 0,
    internet_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(radio_news_bin2=case_when(
    radio_news%in%c(0,1, 2) ~ 0,
    radio_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(tele_news_bin2=case_when(
    tele_news%in%c(0,1, 2) ~ 0,
    tele_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(journal_news_bin2=case_when(
    journal_news%in%c(0,1, 2) ~ 0,
    journal_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(internet_news_bin2=case_when(
    internet_news%in%c(0,1, 2) ~ 0,
    internet_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

```

** Education secondaire

```{r}
data_trust%<>%
  mutate(educ_sec=case_when(
    educ %in% c(5, 6,7,8,9) ~ 1,
    educ %in% c(0,1,2, 3, 4) ~0,
    TRUE ~ NA_real_     
  ))

data_trust%<>%
  mutate(educ_sec_2=case_when(
    educ %in% c(4, 5, 6,7,8,9) ~ 1,
    educ %in% c(0,1,2, 3) ~0,
    TRUE ~ NA_real_     
  ))

```

** Add EA

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, EANUMB_AB)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, EANUMB_AB)%>%
  rename(EA=EANUMB_AB)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(EA_unique = if_else(!is.na(EA), paste0(EA,ccode,round), NA))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, eanumb_ab)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, eanumb_ab)%>%
  rename(EA=eanumb_ab)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(EA_unique.y = if_else(!is.na(EA.y), paste0(EA.y,ccode,round), NA))

data_trust%<>%
  mutate(EA_unique = case_when(
    round == 6 ~ EA_unique.y,
    round == 7 ~ EA_unique))

data_trust%<>%
  select(-c(EA.y, EA.x, EA_unique.y))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, eanumb_ab)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, eanumb_ab)%>%
  rename(EA=eanumb_ab)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(EA_unique.y = if_else(!is.na(EA), paste0(EA,ccode,round), NA))

data_trust%<>%
  mutate(EA_unique = case_when(
    round == 5 ~ EA_unique.y,
    round %in% c(6,7) ~ EA_unique))

data_trust%<>%
  select(-c(EA, EA_unique.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, EANUMB_AB)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, EANUMB_AB)%>%
  rename(EA=EANUMB_AB)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(EA_unique.y = if_else(!is.na(EA), paste0(EA,ccode,round), NA))

data_trust%<>%
  mutate(EA_unique = case_when(
    round == 8 ~ EA_unique.y,
    round %in% c(5,6,7) ~ EA_unique))

data_trust%<>%
  select(-c(EA, EA_unique.y))

rm(afro_w8)

```

** Add extent

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q35)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q35)%>%
  rename(extent=Q35)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q40)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q40)%>%
  rename(extent=q40)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(extent = case_when(
    round == 6 ~ extent.y,
    round == 7 ~ extent.x))

data_trust%<>%
  select(-c(extent.y, extent.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q42)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q42)%>%
  rename(extent=q42)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(extent = case_when(
    round == 5 ~ extent.y,
    round %in% c(6,7) ~ extent.x))

data_trust%<>%
  select(-c(extent.y, extent.x))

rm(afro_w5)

data_trust%>%
  select(extent)%>%
  summary()

data_trust%<>%
  mutate(extent = if_else(extent %in% c(1, 2, 3, 4), extent, NA_real_))

data_trust%<>%
  mutate(extent_bin = case_when(
    extent %in% c(1, 2) ~ 0,
    extent %in% c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

```

```{r}

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

#Mean local participation
data_trust %<>%
group_by(id_unique) %>%
mutate(mean_local_part = ifelse(all(!is.na(c(assoc, commu, prob))), 
                                      mean(c(assoc, commu, prob), na.rm = TRUE), 
                                      NA)) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(mean_local_part = ifelse(all(!is.na(c(assoc, commu, prob))), 
                                  mean(c(assoc, commu, prob), na.rm = TRUE), 
                                  NA_real_)) %>%
  ungroup()

data_trust%<>%
  mutate(internet_use_bin=case_when(
    internet_use%in%c(0,1) ~ 0,
    internet_use%in%c(2,3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(internet_use_bin2=case_when(
    internet_use%in%c(0,1, 2) ~ 0,
    internet_use%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust %<>%
  mutate(mean_inst_trust_bin = case_when(
    mean_inst_trust >= median(mean_inst_trust, na.rm = TRUE) ~ 1,
    mean_inst_trust < median(mean_inst_trust, na.rm = TRUE) ~ 0,
    TRUE ~ NA_real_
  )) %>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

***Add gov_type
```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

juriglobe <- read_excel("Data/Data_Raw/FR_index.xlsx")

juriglobe %<>%
  rename(gov_type="Forme\r\nde gouvernement") %>%
  mutate(
    presidential=(gov_type=="Présidentiel"),
    parlementarian=(gov_type=="Parlementaire"),
    semi_presidential=(gov_type=="Semi-présidentiel"),
    monarchical=(gov_type=="Monarchique")
  ) %>%
  mutate(
    presidential = as.numeric(presidential),
    parlementarian = as.numeric(parlementarian),
    semi_presidential = as.numeric(semi_presidential),
    monarchical = as.numeric(monarchical))%>%
  select(ccode, presidential, parlementarian, semi_presidential, monarchical)

data_trust <- left_join(data_trust, juriglobe, by="ccode")

rm(juriglobe)

data_trust%<>%
  mutate(gov_type = case_when(
    presidential == 1 ~ "Presidential",
    parlementarian == 1 ~ "Parliamentarian",
    monarchical == 1 ~ "Monarchical",
    semi_presidential == 1 ~ "Semi-presidential",
    TRUE ~ "NA"  # Assurez-vous qu'il y a une valeur par défaut
  ))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

** Add elec_fair

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q23)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q23)%>%
  rename(elec_fair=Q23)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q22)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q22)%>%
  rename(elec_fair=q22)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(elec_fair = case_when(
    round == 6 ~ elec_fair.y,
    round == 7 ~ elec_fair.x))

data_trust%<>%
  select(-c(elec_fair.y, elec_fair.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q28)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q28)%>%
  rename(elec_fair=q28)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(elec_fair = case_when(
    round == 5 ~ elec_fair.y,
    round %in% c(6,7) ~ elec_fair.x))

data_trust%<>%
  select(-c(elec_fair.y, elec_fair.x))

rm(afro_w5)

data_trust%>%
  select(elec_fair)%>%
  summary()

data_trust%<>%
  mutate(elec_fair = if_else(elec_fair %in% c(1, 2, 3, 4), elec_fair, NA_real_))

data_trust%<>%
  mutate(elec_fair_bin = case_when(
    elec_fair %in% c(1, 2) ~ 0,
    elec_fair %in% c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

** Create separate distance samples

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(ccode)%>%
  mutate(distance_max_med=median(distance_cap_max_norm))

data_trust %<>%
  filter(!is.na(distance_cap))%>%
  group_by(ccode)%>%
  mutate(distance_max_bin=case_when(
    distance_cap_max_norm>=distance_max_med~1,
    distance_cap_max_norm<distance_max_med~0,
    TRUE~NA_real_))

data_trust%>%
  select(distance_max_med, distance_max_bin)%>%
  summary()

data_trust%<>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

data_trust%<>%
  mutate(coverage_bin = coalesce(coverage3G_r6, coverage3G_r7, coverage2G_r5, coverage2G_r6, coverage2G_r7))

data_trust%>%
  select(coverage_bin)%>%
  summary()

table(data_trust$coverage_bin, data_trust$round)

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

```{r}
# Create a summary table indicating whether each combination of NAME_2 and round is covered
coverage_status <- data_trust %>%
  group_by(NAME_2, round) %>% 
  summarise(covered = any(pot_cvg > 0), .groups = 'drop')  # Check if any `pot_cvg` > 0 in each group

# Create a table showing the distribution of coverage status by round
table(coverage_status$covered, coverage_status$round)

# Summarize the duration of coverage for each NAME_2
coverage_duration <- coverage_status %>%
  group_by(NAME_2) %>%
  summarise(duration = sum(covered), .groups = 'drop')  # Sum the coverage status to get total duration

# Determine the first appearance of coverage for each NAME_2
first_appearance <- data_trust %>%
  filter(pot_cvg > 0) %>%
  group_by(NAME_2) %>%
  summarise(first_round = min(round), .groups = 'drop')  # Get the earliest round with coverage

# Calculate the duration since the first appearance of coverage
duration_since_first_appearance <- data_trust %>%
  left_join(first_appearance, by = "NAME_2") %>%  # Join with `first_appearance` to get `first_round`
  mutate(
    duration = ifelse(pot_cvg > 0, round - first_round + 1, 0)  # Calculate duration since first appearance
  ) %>%
  group_by(NAME_2, round) %>%
  summarise(
    duration_since_first = max(duration, na.rm = TRUE),  # Get the maximum duration for each group
    .groups = 'drop'
  )

data_trust2 <- data_trust

data_trust2 %<>%
  left_join(duration_since_first_appearance, by = c("NAME_2", "round"))  # Join with duration information

data_trust2%>%
  select(duration_since_first)%>%
  summary()

table(data_trust2$duration_since_first, data_trust2$round)

saveRDS(data_trust2, file="Data/Data_RDS/data_trust_report3.rds")

write_dta(data_trust2, "Data/Data_dta/data_trust_report3.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

regions_all_rounds <- data_trust %>%
  group_by(NAME_2) %>%
  summarise(rounds_present = n_distinct(round), .groups = 'drop') %>%
  filter(rounds_present == 3)

df_filtered <- data_trust %>%
  semi_join(regions_all_rounds, by = "NAME_2")

# Trouver la première apparition pour les régions filtrées
first_appearance <- df_filtered %>%
  filter(pot_cvg >0) %>%
  group_by(NAME_2) %>%
  summarise(first_round = min(round), .groups = 'drop')

# Calculer la durée de couverture depuis la première apparition
duration_since_first_appearance <- df_filtered %>%
  left_join(first_appearance, by = "NAME_2") %>%
  mutate(
    duration = ifelse(pot_cvg >0, round - first_round + 1, 0)
  ) %>%
  group_by(NAME_2, round) %>%
  summarise(
    duration_since_first = max(duration, na.rm = TRUE),
    .groups = 'drop'
  )

df_with_duration <- df_filtered %>%
  left_join(duration_since_first_appearance, by = c("NAME_2", "round"))

table(df_with_duration$NAME_2, df_with_duration$round)

saveRDS(df_with_duration, file="Data/Data_RDS/data_trust_report4.rds")

write_dta(df_with_duration, "Data/Data_dta/data_trust_report4.dta")

```

** Add trust_trad

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q43J)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q43J)%>%
  rename(trust_trad=Q43J)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q52k)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q52k)%>%
  rename(trust_trad=q52k)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(trust_trad = case_when(
    round == 6 ~ trust_trad.y,
    round == 7 ~ trust_trad.x))

data_trust%<>%
  select(-c(trust_trad.y, trust_trad.x))

data_trust%>%
  select(trust_trad)%>%
  summary()

data_trust%<>%
  mutate(trust_trad = if_else(trust_trad %in% c(0, 1, 2, 3), trust_trad, NA_real_))

data_trust%<>%
  mutate(trust_trad_bin = case_when(
    trust_trad %in% c(0, 1) ~ 0,
    trust_trad %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

** Add corr_trad

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q44G)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q44G)%>%
  rename(corr_trad=Q44G)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q53h)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q53h)%>%
  rename(corr_trad=q53h)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(corr_trad = case_when(
    round == 6 ~ corr_trad.y,
    round == 7 ~ corr_trad.x))

data_trust%<>%
  select(-c(corr_trad.y, corr_trad.x))

data_trust%>%
  select(corr_trad)%>%
  summary()

data_trust%<>%
  mutate(corr_trad = if_else(corr_trad %in% c(0, 1, 2, 3), corr_trad, NA_real_))

data_trust%<>%
  mutate(corr_trad_bin = case_when(
    corr_trad %in% c(0, 1) ~ 0,
    corr_trad %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

** create mean_inst_corr

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_30_09.rds")

data_trust$corr_pres <- as.numeric(data_trust$corr_pres)
data_trust$corr_dep <- as.numeric(data_trust$corr_dep)
data_trust$corr_juge <- as.numeric(data_trust$corr_juge)

data_trust %<>%
  mutate(mean_inst_corr = (corr_pres + corr_dep + corr_juge) / 
           rowSums(!is.na(cbind(corr_pres, corr_dep, corr_juge))))

data_trust%>%
  filter(round==8)%>%
  select(mean_inst_corr)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

```

** create mean_pop_log

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")

data_trust%<>%
  mutate(mean_pop_log=log(mean_pop+1))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_report2.rds")
write_dta(data_trust, "Data/Data_dta/data_trust_report2.dta")

data_trust <- readRDS("Data/Data_RDS/data_trust_30_09.rds")

data_trust%<>%
  mutate(mean_pop=as.numeric(mean_pop))%>%
  mutate(mean_pop_log=log(mean_pop+1))

saveRDS(data_trust, file="Data/Data_RDS/data_trust_30_09.rds")
write_dta(data_trust, "Data/Data_dta/data_trust_30_09.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_test_report2.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(vote_party = case_when(
    round == 7 ~ vote_party.y,
    round == 8 ~ vote_party.x))

data_trust%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(vote_party = case_when(
    round == 6 ~ vote_party.y,
    round %in% c(7,8) ~ vote_party.x))

data_trust%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(vote_party = case_when(
    round == 5 ~ vote_party.y,
    round %in% c(6,7,8) ~ vote_party.x))

data_trust%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust_30_09.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_30_09.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_30_09.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")
afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")
afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")
afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w8$DATEINTR <- trimws(afro_w8$DATEINTR)

afro_w8%>%select(DATEINTR)%>%count(DATEINTR)%>%print(n=2000)

afro_w7$DATEINTR <- trimws(afro_w7$DATEINTR)

afro_w7%>%select(DATEINTR)%>%count(DATEINTR)%>%print(n=2000)

afro_w6$dateintr <- trimws(afro_w6$dateintr)

afro_w6%>%select(dateintr)%>%arrange(dateintr)%>%count(dateintr)

afro_w5$dateintr <- trimws(afro_w5$dateintr)

afro_w5%>%select(dateintr)%>%arrange(dateintr)%>%count(dateintr)

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, DATEINTR)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, DATEINTR)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, DATEINTR)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, DATEINTR)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

data_trust%<>%
  mutate(DATEINTR = case_when(
    round == 7 ~ DATEINTR.y,
    round == 8 ~ DATEINTR.x))

data_trust%<>%
  select(-c(DATEINTR.y, DATEINTR.x))

rm(afro_w7)

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, dateintr)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, dateintr)%>%
  rename(DATEINTR=dateintr)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(DATEINTR = case_when(
    round == 6 ~ DATEINTR.y,
    round %in% c(7,8) ~ DATEINTR.x))

data_trust%<>%
  select(-c(DATEINTR.y, DATEINTR.x))

rm(afro_w6)

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, dateintr)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, dateintr)%>%
  rename(DATEINTR=dateintr)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(DATEINTR = case_when(
    round == 5 ~ DATEINTR.y,
    round %in% c(6,7,8) ~ DATEINTR.x))

data_trust%<>%
  select(-c(DATEINTR.y, DATEINTR.x))

rm(afro_w5)

saveRDS(data_trust, file="Data/Data_RDS/data_trust_30_09.rds")

write_dta(data_trust, "Data/Data_dta/data_trust_30_09.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_merge2.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q4A)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q4A)%>%
  rename(conditions_country=Q4A)

afro_w8%<>%
  mutate(conditions_country = if_else(conditions_country %in% c(1, 2, 3, 4, 5), conditions_country, NA_real_))

afro_w8%<>%
  mutate(bin_conditions_country=ifelse(conditions_country>=3, 1, 0))

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(bin_conditions_country = case_when(
    round == 8 ~ bin_conditions_country.y,
    round %in% c(5,6,7) ~ bin_conditions_country.x))

data_trust%<>%
  select(-c(bin_conditions_country.y, bin_conditions_country.x, conditions_country))

glimpse(data_trust)

rm(afro_w8)

data_trust%>%
  select(bin_conditions_country)%>%
  summary()

```

```{r}
data_trust %<>%
  mutate(mean_inst_corr = (corr_pres+ corr_dep + corr_juge) / 
           rowSums(!is.na(cbind(corr_pres, corr_dep, corr_juge))))

data_trust %<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_trust = ifelse(all(is.na(c(trust_pres, trust_parl, trust_elec))), NA, weighted.mean(c(trust_pres, trust_parl, trust_elec), na.rm = TRUE)))%>%
  ungroup()

data_trust %<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_corr = ifelse(all(is.na(c(corr_pres, corr_dep, corr_juge))), NA, weighted.mean(c(corr_pres, corr_dep, corr_juge), na.rm = TRUE)))%>%
  ungroup()

data_trust%>%
  select(mean_inst_trust, weighted_inst_trust, mean_inst_corr, weighted_inst_corr)%>%
  summary()

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df4.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q43A, Q43B, Q43C)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q43A, Q43B, Q43C)%>%
  rename(know_pres=Q43A,
         know_parl=Q43B,
         know_elec=Q43C)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q52a, q52b, q52c)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q52a, q52b, q52c)%>%
 rename(know_pres=q52a,
         know_parl=q52b,
         know_elec=q52c)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(know_pres = case_when(
    round == 6 ~ know_pres.y,
    round == 7 ~ know_pres.x),
    know_parl = case_when(
    round == 6 ~ know_parl.y,
    round == 7 ~ know_parl.x),
    know_elec = case_when(
    round == 6 ~ know_elec.y,
    round == 7 ~ know_elec.x))

data_trust%<>%
  select(-c(know_pres.x, know_parl.x, know_elec.x, know_pres.y, know_parl.y, know_elec.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q59a, q59b, q59c)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q59a, q59b, q59c)%>%
 rename(know_pres=q59a,
         know_parl=q59b,
         know_elec=q59c)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(know_pres = case_when(
    round == 5 ~ know_pres.y,
    round %in% c(6,7) ~ know_pres.x),
    know_parl = case_when(
    round == 5 ~ know_parl.y,
    round %in% c(6,7) ~ know_parl.x),
    know_elec = case_when(
    round == 5 ~ know_elec.y,
    round %in% c(6,7) ~ know_elec.x))

data_trust%<>%
  select(-c(know_pres.x, know_parl.x, know_elec.x, know_pres.y, know_parl.y, know_elec.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q41A, Q41B, Q41C)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q41A, Q41B, Q41C)%>%
rename(know_pres=Q41A,
         know_parl=Q41B,
         know_elec=Q41C)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(know_pres = case_when(
    round == 8 ~ know_pres.y,
    round %in% c(5,6,7) ~ know_pres.x),
    know_parl = case_when(
    round == 8 ~ know_parl.y,
    round %in% c(5,6,7) ~ know_parl.x),
    know_elec = case_when(
    round == 8 ~ know_elec.y,
    round %in% c(5,6,7) ~ know_elec.x))

data_trust%<>%
  select(-c(know_pres.x, know_parl.x, know_elec.x, know_pres.y, know_parl.y, know_elec.y))

rm(afro_w8)

data_trust%<>%
  mutate(know_pres = if_else(know_pres %in% c(0, 1, 2, 3, 4, 9), know_pres, NA_real_),
         know_parl = if_else(know_parl %in% c(0, 1, 2, 3, 4, 9), know_parl, NA_real_),
         know_elec = if_else(know_elec %in% c(0, 1, 2, 3, 4, 9), know_elec, NA_real_))

data_trust %<>%
  mutate(know_pres = if_else(!is.na(know_pres) & know_pres %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(know_pres) & know_pres == 9, 1, know_pres)),
         know_parl = if_else(!is.na(know_parl) & know_parl %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(know_parl) & know_parl == 9, 1, know_parl)),
         know_elec = if_else(!is.na(know_elec) & know_elec %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(know_elec) & know_elec == 9, 1, know_elec))
         )

glimpse(data_trust)

data_trust%<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_trust_know = ifelse(all(is.na(c(know_pres, know_parl, know_elec))), NA, weighted.mean(c(know_pres, know_parl, know_elec), na.rm = TRUE)))%>%
  ungroup()

data_trust %<>%
  mutate(mean_inst_trust_know = (know_pres+ know_parl + know_elec) / 
           rowSums(!is.na(cbind(know_pres, know_parl, know_elec))))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")

write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q85A)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q85A)%>%
  rename(unfair_eth=Q85A)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q88a)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q88a)%>%
 rename(unfair_eth=q88a)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(unfair_eth = case_when(
    round == 6 ~ unfair_eth.y,
    round == 7 ~ unfair_eth.x))

data_trust%<>%
  select(-c(unfair_eth.x, unfair_eth.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q85a)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q85a)%>%
 rename(unfair_eth=q85a)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(unfair_eth = case_when(
    round == 5 ~ unfair_eth.y,
    round %in% c(6,7) ~ unfair_eth.x))

data_trust%<>%
  select(-c(unfair_eth.x, unfair_eth.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q84C)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q84C)%>%
  rename(unfair_eth=Q84C)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(unfair_eth = case_when(
    round == 8 ~ unfair_eth.y,
    round %in% c(5,6,7) ~ unfair_eth.x))

data_trust%<>%
  select(-c(unfair_eth.x, unfair_eth.y))

rm(afro_w8)

data_trust%<>%
  mutate(unfair_eth = if_else(unfair_eth %in% c(0, 1, 2, 3), unfair_eth, NA_real_))

data_trust %<>%
  mutate(unfair_eth_bin = case_when(
    !is.na(unfair_eth) & unfair_eth %in% c(0, 1) ~ 0,
    !is.na(unfair_eth) & unfair_eth %in% c(2, 3) ~ 1,
    TRUE ~ NA_real_
  ))

glimpse(data_trust)

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")

write_dta(data_trust, "Data/Data_dta/final_df5.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

data_trust %<>%
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id() + max(name2_id)) %>%
  ungroup()

data_trust %<>%
  mutate(region_time = case_when(
    ISO %in% countries_adm2 ~ name2_id * 10000 + round, 
    ISO %in% countries_adm1 ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
  mutate(region_time = as.integer(as.factor(region_time)))

data_trust%>%
  select(region2_round, region_time)%>%
  summarise(n=n())
library(psych)

describe(data_trust$region2_round)

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")

write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust%<>%
  mutate(corr_pres_bin=case_when(
    corr_pres%in%c(0,1) ~ 0,
    corr_pres%in%c(2,3) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(corr_dep_bin=case_when(
    corr_dep%in%c(0,1) ~ 0,
    corr_dep%in%c(2,3) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust%<>%
  mutate(corr_juge_bin=case_when(
    corr_juge%in%c(0,1) ~ 0,
    corr_juge%in%c(2,3) ~ 1,
    TRUE ~ NA_real_
  ))

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q44A, Q44B, Q44F)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q44A, Q44B, Q44F)%>%
  rename(corr_pres_know=Q44A,
         corr_dep_know=Q44B,
         corr_juge_know=Q44F)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q53a, q53b, q53g)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q53a, q53b, q53g)%>%
 rename(corr_pres_know=q53a,
         corr_dep_know=q53b,
         corr_juge_know=q53g)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(corr_pres_know = case_when(
    round == 6 ~ corr_pres_know.y,
    round == 7 ~ corr_pres_know.x),
    corr_dep_know = case_when(
    round == 6 ~ corr_dep_know.y,
    round == 7 ~ corr_dep_know.x),
    corr_juge_know = case_when(
    round == 6 ~ corr_juge_know.y,
    round == 7 ~ corr_juge_know.x))

data_trust%<>%
  select(-c(corr_pres_know.x, corr_dep_know.x, corr_juge_know.x, corr_pres_know.y, corr_dep_know.y, corr_juge_know.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q60a, q60b, q60g)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q60a, q60b, q60g)%>%
 rename(corr_pres_know=q60a,
         corr_dep_know=q60b,
         corr_juge_know=q60g)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(corr_pres_know = case_when(
    round == 5 ~ corr_pres_know.y,
    round %in% c(6,7) ~ corr_pres_know.x),
    corr_dep_know = case_when(
    round == 5 ~ corr_dep_know.y,
    round %in% c(6,7) ~ corr_dep_know.x),
    corr_juge_know = case_when(
    round == 5 ~ corr_juge_know.y,
    round %in% c(6,7) ~ corr_juge_know.x))

data_trust%<>%
  select(-c(corr_pres_know.x, corr_dep_know.x, corr_juge_know.x, corr_pres_know.y, corr_dep_know.y, corr_juge_know.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q42A, Q42B, Q42G)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q42A, Q42B, Q42G)%>%
rename(corr_pres_know=Q42A,
         corr_dep_know=Q42B,
         corr_juge_know=Q42G)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(corr_pres_know = case_when(
    round == 8 ~ corr_pres_know.y,
    round %in% c(5,6,7) ~ corr_pres_know.x),
    corr_dep_know = case_when(
    round == 8 ~ corr_dep_know.y,
    round %in% c(5,6,7) ~ corr_dep_know.x),
    corr_juge_know = case_when(
    round == 8 ~ corr_juge_know.y,
    round %in% c(5,6,7) ~ corr_juge_know.x))

data_trust%<>%
  select(-c(corr_pres_know.x, corr_dep_know.x, corr_juge_know.x, corr_pres_know.y, corr_dep_know.y, corr_juge_know.y))

rm(afro_w8)

data_trust%<>%
  mutate(corr_pres_know = if_else(corr_pres_know %in% c(0, 1, 2, 3, 4, 9), corr_pres_know, NA_real_),
         corr_dep_know = if_else(corr_dep_know %in% c(0, 1, 2, 3, 4, 9), corr_dep_know, NA_real_),
         corr_juge_know = if_else(corr_juge_know %in% c(0, 1, 2, 3, 4, 9), corr_juge_know, NA_real_))

data_trust %<>%
  mutate(corr_pres_know = if_else(!is.na(corr_pres_know) & corr_pres_know %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(corr_pres_know) & corr_pres_know == 9, 1, corr_pres_know)),
         corr_dep_know = if_else(!is.na(corr_dep_know) & corr_dep_know %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(corr_dep_know) & corr_dep_know == 9, 1, corr_dep_know)),
         corr_juge_know = if_else(!is.na(corr_juge_know) & corr_juge_know %in% c(0, 1, 2, 3, 4), 0,
                             if_else(!is.na(corr_juge_know) & corr_juge_know == 9, 1, corr_juge_know))
         )

glimpse(data_trust)

data_trust%<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_corr_know = ifelse(all(is.na(c(corr_pres_know, corr_dep_know, corr_juge_know))), NA, weighted.mean(c(corr_pres_know, corr_dep_know, corr_juge_know), na.rm = TRUE)))%>%
  ungroup()

data_trust %<>%
  mutate(mean_inst_corr_know = (corr_pres_know+ corr_dep_know + corr_juge_know) / 
           rowSums(!is.na(cbind(corr_pres_know, corr_dep_know, corr_juge_know))))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")

write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

countries <- unique(data_trust$ISO)

qog <- read.csv("Data/Data_raw/qog_std_ts_jan24.csv")

qog %<>%
  filter(year%in%c(2011, 2014, 2016, 2019))

qog%<>%
  filter(ccodealp %in% countries)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(ISO=ccodealp, med_free=aii_q55, citiz_self_censor=aii_q56, vdem_med_free=vdem_mecorrpt)

qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2011 ~ 5,
                   round==2014 ~ 6,
                   round==2016 ~ 7,
                   round==2019 ~ 8))

data_trust %<>% left_join(qog, by=c("ISO", "round"))

glimpse(data_trust)

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

data_trust$internet_news <- as.numeric(as.character(data_trust$internet_news))

data_trust %<>%
  group_by(NAME_2, round) %>%
  mutate(internet_news_adm2 = if_else(!is.na(NAME_2), mean(internet_news, na.rm = TRUE), NA_real_)) %>%
  ungroup()

data_trust %<>%
  group_by(NAME_1, round) %>%
  mutate(internet_news_adm1 = if_else(!is.na(NAME_1), mean(internet_news, na.rm = TRUE), NA_real_)) %>%
  ungroup()

data_trust %<>%
  mutate(internet_news_region = case_when(
    ISO %in% countries_adm1 ~ internet_news_adm1,
    TRUE ~ internet_news_adm2))

data_trust%>%
  select(internet_news, internet_news_adm2, internet_news_adm1, internet_news_region)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust%<>%
  mutate(EA_unique2 = if_else(!is.na(id_unique), paste0(id_unique,ccode), NA))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q83)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q83)%>%
rename(trust_gen=Q83)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

rm(afro_w8)

data_trust%>%
  select(trust_gen)%>%
  summary()

data_trust%<>%
  mutate(trust_gen = if_else(trust_gen %in% c(0, 1), trust_gen, NA_real_))

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q87)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q87)%>%
 rename(trust_gen=q87)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(trust_gen = case_when(
    round == 5 ~ trust_gen.y,
    round %in% c(6,7,8) ~ trust_gen.x))

data_trust%<>%
  select(-c(trust_gen.x, trust_gen.y))

rm(afro_w5)

data_trust%<>%
  mutate(trust_gen = if_else(trust_gen %in% c(0, 1), trust_gen, NA_real_))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q29, Q32)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q29, Q32)%>%
  rename(check_citiz=Q29,
         check_parl=Q32)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q31, q34)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q31, q34)%>%
 rename(check_citiz=q31,
        check_parl=q34)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

data_trust%<>%
  mutate(check_citiz = case_when(
    round == 6 ~ check_citiz.y,
    round == 7 ~ check_citiz.x),
    check_parl=case_when(
      round==6 ~ check_parl.y,
      round==7 ~ check_parl.x
    ))

data_trust%<>%
  select(-c(check_citiz.x, check_citiz.y, check_parl.x, check_parl.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q33, q36)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q33, q36)%>%
 rename(check_citiz=q33,
        check_parl=q36)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

data_trust%<>%
  mutate(check_citiz = case_when(
    round == 5 ~ check_citiz.y,
    round %in% c(6,7) ~ check_citiz.x),
    check_parl = case_when(
    round == 5 ~ check_parl.y,
    round %in% c(6,7) ~ check_parl.x)
    )

data_trust%<>%
  select(-c(check_citiz.x, check_citiz.y, check_parl.x, check_parl.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q22, Q29)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q22, Q29)%>%
  rename(check_citiz=Q22,
         check_parl=Q29)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(check_citiz = case_when(
    round == 8 ~ check_citiz.y,
    round %in% c(5,6,7) ~ check_citiz.x),
    check_parl = case_when(
    round == 8 ~ check_parl.y,
    round %in% c(5,6,7) ~ check_parl.x))

data_trust%<>%
  select(-c(check_citiz.x, check_citiz.y, check_parl.x, check_parl.y))

rm(afro_w8)

data_trust%<>%
  mutate(check_citiz = if_else(check_citiz %in% c(1, 2, 3, 4, 5), check_citiz, NA_real_))%>%
  mutate(check_parl = if_else(check_parl %in% c(1, 2, 3, 4, 5), check_citiz, NA_real_))

data_trust %<>%
  mutate(check_citiz_bin = case_when(
    !is.na(check_citiz) & check_citiz %in% c(1, 2, 5) ~ 0,
    !is.na(check_citiz) & check_citiz %in% c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust %<>%
  mutate(check_parl_bin = case_when(
    !is.na(check_parl) & check_parl %in% c(1, 2, 5) ~ 0,
    !is.na(check_parl) & check_parl %in% c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

glimpse(data_trust)

data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_check_mean = ifelse(all(is.na(c(check_citiz_bin, check_parl_bin))), NA, mean(c(check_citiz_bin, check_parl_bin), na.rm = TRUE)))%>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")

write_dta(data_trust, "Data/Data_dta/final_df5.dta")
```

```{r}
data_trust %<>%
  mutate(satis_demo_bin = case_when(
    !is.na(satis_demo) & satis_demo %in% c(0, 1, 2) ~ 0,
    !is.na(satis_demo) & satis_demo %in% c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

```{r}
data_trust%>%
  distinct(ISO, .keep_all = TRUE)%>%
  select(ISO, area_0_km2)%>%
  View()
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

data_trust %<>%
  mutate(mean_inst_trust_2 = (trust_pres+ trust_parl) / 
           rowSums(!is.na(cbind(trust_pres, trust_parl))))

data_trust %<>%
  mutate(mean_inst_corr_2 = (corr_pres+ corr_dep) / 
           rowSums(!is.na(cbind(corr_pres, corr_dep))))

data_trust %<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_trust_2 = ifelse(all(is.na(c(trust_pres, trust_parl))), NA, weighted.mean(c(trust_pres, trust_parl), na.rm = TRUE)))%>%
  ungroup()

data_trust %<>%
 group_by(id_unique)%>%
  mutate(weighted_inst_corr_2 = ifelse(all(is.na(c(corr_pres, corr_dep))), NA, weighted.mean(c(corr_pres, corr_dep), na.rm = TRUE)))%>%
  ungroup()

data_trust%>%
  select(mean_inst_trust, weighted_inst_trust, mean_inst_corr, weighted_inst_corr, mean_inst_trust_2, weighted_inst_trust_2, mean_inst_corr_2, weighted_inst_corr_2)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

data_trust%<>%
  select(-perf_pres)

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q56A, Q56B, Q56C, Q56D, Q56E, Q56F, Q56G, Q56H, Q56I, Q56K, Q56L, Q56M,
         Q99, Q58A, Q58B, Q58D)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique,  Q56A, Q56B, Q56C, Q56D, Q56E, Q56F, Q56G, Q56H, Q56I, Q56K, Q56L, Q56M,
         Q99,
         Q58A, Q58B, Q58D)%>%
  rename(perf_eco=Q56A,
         perf_poor=Q56B,
         perf_job=Q56C,
         perf_price=Q56D,
         perf_ineq=Q56E,
         perf_crime=Q56F,
         perf_health=Q56G,
         perf_educ=Q56H,
         perf_water=Q56I,
         perf_corr=Q56K,
         perf_road=Q56L,
         perf_elect=Q56M,
         vote_no=Q99,
         perf_pres=Q58A,
         perf_parl=Q58B,
         perf_trad=Q58D)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q66a, q66b, q66c, q66d, q66e, q66f, q66g, q66h, q66i, q66k, q66l, q66m,
         q99,
         q68a, q68b, q68d)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q66a, q66b, q66c, q66d, q66e, q66f, q66g, q66h, q66i, q66k, q66l, q66m,
         q99,
         q68a, q68b, q68d)%>%
 rename(perf_eco=q66a,
        perf_poor=q66b,
        perf_job=q66c,
        perf_price=q66d,
        perf_ineq=q66e,
        perf_crime=q66f,
        perf_health=q66g,
        perf_educ=q66h,
        perf_water=q66i,
        perf_corr=q66k,
        perf_road=q66l,
        perf_elect=q66m,
        vote_no=q99,
        perf_pres=q68a,
        perf_parl=q68b,
        perf_trad=q68d)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 6 ~ perf_eco.y,
    round == 7 ~ perf_eco.x),
    perf_poor = case_when(
    round == 6 ~ perf_poor.y,
    round == 7 ~ perf_poor.x),
    perf_job = case_when(
    round == 6 ~ perf_job.y,
    round == 7 ~ perf_job.x),
    perf_price = case_when(
    round == 6 ~ perf_price.y,
    round == 7 ~ perf_price.x),
    perf_ineq = case_when(
    round == 6 ~ perf_ineq.y,
    round == 7 ~ perf_ineq.x),
    perf_crime = case_when(
    round == 6 ~ perf_crime.y,
    round == 7 ~ perf_crime.x),
    perf_health = case_when(
    round == 6 ~ perf_health.y,
    round == 7 ~ perf_health.x),
    perf_educ = case_when(
    round == 6 ~ perf_educ.y,
    round == 7 ~ perf_educ.x),
    perf_water = case_when(
    round == 6 ~ perf_water.y,
    round == 7 ~ perf_water.x),
    perf_corr = case_when(
    round == 6 ~ perf_corr.y,
    round == 7 ~ perf_corr.x),
    perf_road = case_when(
    round == 6 ~ perf_road.y,
    round == 7 ~ perf_road.x),
    perf_elect = case_when(
    round == 6 ~ perf_elect.y,
    round == 7 ~ perf_elect.x),
    vote_no = case_when(
    round == 6 ~ vote_no.y,
    round == 7 ~ vote_no.x),
    perf_pres = case_when(
    round == 6 ~ perf_pres.y,
    round == 7 ~ perf_pres.x),
    perf_parl = case_when(
    round == 6 ~ perf_parl.y,
    round == 7 ~ perf_parl.x),
    perf_trad = case_when(
    round == 6 ~ perf_trad.y,
    round == 7 ~ perf_trad.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x, perf_trad.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y, perf_trad.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q65a, q65b, q65c, q65d, q65e, q65f, q65g, q65h, q65i, q65k, q65n, q65o,
         q99,
         q71a, q71b)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique,q65a, q65b, q65c, q65d, q65e, q65f, q65g, q65h, q65i, q65k, q65n, q65o,
         q99,
         q71a, q71b)%>%
 rename(perf_eco=q65a,
        perf_poor=q65b,
        perf_job=q65c,
        perf_price=q65d,
        perf_ineq=q65e,
        perf_crime=q65f,
        perf_health=q65g,
        perf_educ=q65h,
        perf_water=q65i,
        perf_corr=q65k,
        perf_road=q65n,
        perf_elect=q65o,
        vote_no=q99,
        perf_pres=q71a,
        perf_parl=q71b)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(across(c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, 
                  perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, 
                  perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, 
                  perf_pres.x, perf_parl.x,perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, 
                  perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, 
                  perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, 
                  perf_pres.y, perf_parl.y), ~ as.numeric(.)))

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 5 ~ perf_eco.y,
    round %in% c(6,7) ~ perf_eco.x),
    perf_poor = case_when(
    round == 5 ~ perf_poor.y,
    round %in% c(6,7) ~ perf_poor.x),
    perf_job = case_when(
    round == 5 ~ perf_job.y,
    round %in% c(6,7) ~ perf_job.x),
    perf_price = case_when(
    round == 5 ~ perf_price.y,
    round %in% c(6,7) ~ perf_price.x),
    perf_ineq = case_when(
    round == 5 ~ perf_ineq.y,
    round %in% c(6,7) ~ perf_ineq.x),
    perf_crime = case_when(
    round == 5 ~ perf_crime.y,
    round %in% c(6,7) ~ perf_crime.x),
    perf_health = case_when(
    round == 5 ~ perf_health.y,
    round %in% c(6,7) ~ perf_health.x),
    perf_educ = case_when(
    round == 5 ~ perf_educ.y,
    round %in% c(6,7) ~ perf_educ.x),
    perf_water = case_when(
    round == 5 ~ perf_water.y,
    round %in% c(6,7) ~ perf_water.x),
    perf_corr = case_when(
    round == 5 ~ perf_corr.y,
    round %in% c(6,7) ~ perf_corr.x),
    perf_road = case_when(
    round == 5 ~ perf_road.y,
    round %in% c(6,7) ~ perf_road.x),
    perf_elect = case_when(
    round == 5 ~ perf_elect.y,
    round %in% c(6,7) ~ perf_elect.x),
    vote_no = case_when(
    round == 5 ~ vote_no.y,
    round %in% c(6,7) ~ vote_no.x),
    perf_pres = case_when(
    round == 5 ~ perf_pres.y,
    round %in% c(6,7) ~ perf_pres.x),
    perf_parl = case_when(
    round == 5 ~ perf_parl.y,
    round %in% c(6,7) ~ perf_parl.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q50A, Q50B, Q50C, Q50D, Q50E, Q50F, Q50G, Q50H, Q50I, Q50J, Q50K, Q50L,
         Q99,
         Q51A, Q51B, Q51D)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q50A, Q50B, Q50C, Q50D, Q50E, Q50F, Q50G, Q50H, Q50I, Q50J, Q50K, Q50L,
         Q99,
         Q51A, Q51B, Q51D)%>%
  rename(perf_eco=Q50A,
         perf_poor=Q50B,
         perf_job=Q50C,
         perf_price=Q50D,
         perf_ineq=Q50E,
         perf_crime=Q50F,
         perf_health=Q50G,
         perf_educ=Q50H,
         perf_water=Q50I,
         perf_corr=Q50J,
         perf_road=Q50K,
         perf_elect=Q50L,
         vote_no=Q99,
         perf_pres=Q51A,
         perf_parl=Q51B,
         perf_trad=Q51D)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 8 ~ perf_eco.y,
    round %in% c(5,6,7) ~ perf_eco.x),
    perf_poor = case_when(
    round == 8 ~ perf_poor.y,
    round %in% c(5,6,7) ~ perf_poor.x),
    perf_job = case_when(
    round == 8 ~ perf_job.y,
    round %in% c(5,6,7) ~ perf_job.x),
    perf_price = case_when(
    round == 8 ~ perf_price.y,
    round %in% c(5,6,7) ~ perf_price.x),
    perf_ineq = case_when(
    round == 8 ~ perf_ineq.y,
    round %in% c(5,6,7) ~ perf_ineq.x),
    perf_crime = case_when(
    round == 8 ~ perf_crime.y,
    round %in% c(5,6,7) ~ perf_crime.x),
    perf_health = case_when(
    round == 8 ~ perf_health.y,
    round %in% c(5,6,7) ~ perf_health.x),
    perf_educ = case_when(
    round == 8 ~ perf_educ.y,
    round %in% c(5,6,7) ~ perf_educ.x),
    perf_water = case_when(
    round == 8 ~ perf_water.y,
    round %in% c(5,6,7) ~ perf_water.x),
    perf_corr = case_when(
    round == 8 ~ perf_corr.y,
    round %in% c(5,6,7) ~ perf_corr.x),
    perf_road = case_when(
    round == 8 ~ perf_road.y,
    round %in% c(5,6,7) ~ perf_road.x),
    perf_elect = case_when(
    round == 8 ~ perf_elect.y,
    round %in% c(5,6,7) ~ perf_elect.x),
    vote_no = case_when(
    round == 8 ~ vote_no.y,
    round %in% c(5,6,7) ~ vote_no.x),
    perf_pres = case_when(
    round == 8 ~ perf_pres.y,
    round %in% c(5,6,7) ~ perf_pres.x),
    perf_parl = case_when(
    round == 8 ~ perf_parl.y,
    round %in% c(5,6,7) ~ perf_parl.x),
    perf_trad = case_when(
    round == 8 ~ perf_trad.y,
    round %in% c(5,6,7) ~ perf_trad.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x, perf_trad.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y, perf_trad.y))

rm(afro_w8)

data_trust%<>%
  mutate(perf_eco = if_else(perf_eco %in% c(1, 2, 3, 4), perf_eco, NA_real_))%>%
  mutate(perf_poor = if_else(perf_poor %in% c(1, 2, 3, 4), perf_poor, NA_real_))%>%
  mutate(perf_job = if_else(perf_job %in% c(1, 2, 3, 4), perf_job, NA_real_))%>%
  mutate(perf_price = if_else(perf_price %in% c(1, 2, 3, 4), perf_price, NA_real_))%>%
  mutate(perf_ineq = if_else(perf_ineq %in% c(1, 2, 3, 4), perf_ineq, NA_real_))%>%
  mutate(perf_crime = if_else(perf_crime %in% c(1, 2, 3, 4), perf_crime, NA_real_))%>%
  mutate(perf_health = if_else(perf_health %in% c(1, 2, 3, 4), perf_health, NA_real_))%>%
  mutate(perf_educ = if_else(perf_educ %in% c(1, 2, 3, 4), perf_educ, NA_real_))%>%
  mutate(perf_water = if_else(perf_water %in% c(1, 2, 3, 4), perf_water, NA_real_))%>%
  mutate(perf_corr = if_else(perf_corr %in% c(1, 2, 3, 4), perf_corr, NA_real_))%>%
  mutate(perf_road = if_else(perf_road %in% c(1, 2, 3, 4), perf_road, NA_real_))%>%
  mutate(perf_elect = if_else(perf_elect %in% c(1, 2, 3, 4), perf_elect, NA_real_))%>%
  mutate(perf_pres = if_else(perf_pres %in% c(1, 2, 3, 4), perf_pres, NA_real_))%>%
  mutate(perf_parl = if_else(perf_parl %in% c(1, 2, 3, 4), perf_parl, NA_real_))%>%
  mutate(perf_trad = if_else(perf_trad %in% c(1, 2, 3, 4), perf_trad, NA_real_))%>%
  mutate(vote_no=ifelse(vote_no == 9997, 1, 
                      ifelse(vote_no %in% c(9995, 9998, 9999, -1), NA_real_, 0)))

glimpse(data_trust)

data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_perf_obj = ifelse(all(is.na(c(perf_eco, perf_poor, perf_job, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect))), NA, mean(c(perf_eco, perf_poor, perf_job, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect), na.rm = TRUE)))%>%
  ungroup()

data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_perf_pol = ifelse(all(is.na(c(perf_pres, perf_parl))), NA, mean(c(perf_pres, perf_parl), na.rm = TRUE)))%>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

data_trust%<>%
  select(-perf_pres)

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q56A, Q56B, Q56C, Q56D, Q56E, Q56F, Q56G, Q56H, Q56I, Q56K, Q56L, Q56M,
         Q99, Q58A, Q58B, Q58D)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique,  Q56A, Q56B, Q56C, Q56D, Q56E, Q56F, Q56G, Q56H, Q56I, Q56K, Q56L, Q56M,
         Q99,
         Q58A, Q58B, Q58D)%>%
  rename(perf_eco=Q56A,
         perf_poor=Q56B,
         perf_job=Q56C,
         perf_price=Q56D,
         perf_ineq=Q56E,
         perf_crime=Q56F,
         perf_health=Q56G,
         perf_educ=Q56H,
         perf_water=Q56I,
         perf_corr=Q56K,
         perf_road=Q56L,
         perf_elect=Q56M,
         vote_no=Q99,
         perf_pres=Q58A,
         perf_parl=Q58B,
         perf_trad=Q58D)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q66a, q66b, q66c, q66d, q66e, q66f, q66g, q66h, q66i, q66k, q66l, q66m,
         q99,
         q68a, q68b, q68d)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q66a, q66b, q66c, q66d, q66e, q66f, q66g, q66h, q66i, q66k, q66l, q66m,
         q99,
         q68a, q68b, q68d)%>%
 rename(perf_eco=q66a,
        perf_poor=q66b,
        perf_job=q66c,
        perf_price=q66d,
        perf_ineq=q66e,
        perf_crime=q66f,
        perf_health=q66g,
        perf_educ=q66h,
        perf_water=q66i,
        perf_corr=q66k,
        perf_road=q66l,
        perf_elect=q66m,
        vote_no=q99,
        perf_pres=q68a,
        perf_parl=q68b,
        perf_trad=q68d)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 6 ~ perf_eco.y,
    round == 7 ~ perf_eco.x),
    perf_poor = case_when(
    round == 6 ~ perf_poor.y,
    round == 7 ~ perf_poor.x),
    perf_job = case_when(
    round == 6 ~ perf_job.y,
    round == 7 ~ perf_job.x),
    perf_price = case_when(
    round == 6 ~ perf_price.y,
    round == 7 ~ perf_price.x),
    perf_ineq = case_when(
    round == 6 ~ perf_ineq.y,
    round == 7 ~ perf_ineq.x),
    perf_crime = case_when(
    round == 6 ~ perf_crime.y,
    round == 7 ~ perf_crime.x),
    perf_health = case_when(
    round == 6 ~ perf_health.y,
    round == 7 ~ perf_health.x),
    perf_educ = case_when(
    round == 6 ~ perf_educ.y,
    round == 7 ~ perf_educ.x),
    perf_water = case_when(
    round == 6 ~ perf_water.y,
    round == 7 ~ perf_water.x),
    perf_corr = case_when(
    round == 6 ~ perf_corr.y,
    round == 7 ~ perf_corr.x),
    perf_road = case_when(
    round == 6 ~ perf_road.y,
    round == 7 ~ perf_road.x),
    perf_elect = case_when(
    round == 6 ~ perf_elect.y,
    round == 7 ~ perf_elect.x),
    vote_no = case_when(
    round == 6 ~ vote_no.y,
    round == 7 ~ vote_no.x),
    perf_pres = case_when(
    round == 6 ~ perf_pres.y,
    round == 7 ~ perf_pres.x),
    perf_parl = case_when(
    round == 6 ~ perf_parl.y,
    round == 7 ~ perf_parl.x),
    perf_trad = case_when(
    round == 6 ~ perf_trad.y,
    round == 7 ~ perf_trad.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x, perf_trad.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y, perf_trad.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q65a, q65b, q65c, q65d, q65e, q65f, q65g, q65h, q65i, q65k, q65n, q65o,
         q99,
         q71a, q71b)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique,q65a, q65b, q65c, q65d, q65e, q65f, q65g, q65h, q65i, q65k, q65n, q65o,
         q99,
         q71a, q71b)%>%
 rename(perf_eco=q65a,
        perf_poor=q65b,
        perf_job=q65c,
        perf_price=q65d,
        perf_ineq=q65e,
        perf_crime=q65f,
        perf_health=q65g,
        perf_educ=q65h,
        perf_water=q65i,
        perf_corr=q65k,
        perf_road=q65n,
        perf_elect=q65o,
        vote_no=q99,
        perf_pres=q71a,
        perf_parl=q71b)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(across(c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, 
                  perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, 
                  perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, 
                  perf_pres.x, perf_parl.x,perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, 
                  perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, 
                  perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, 
                  perf_pres.y, perf_parl.y), ~ as.numeric(.)))

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 5 ~ perf_eco.y,
    round %in% c(6,7) ~ perf_eco.x),
    perf_poor = case_when(
    round == 5 ~ perf_poor.y,
    round %in% c(6,7) ~ perf_poor.x),
    perf_job = case_when(
    round == 5 ~ perf_job.y,
    round %in% c(6,7) ~ perf_job.x),
    perf_price = case_when(
    round == 5 ~ perf_price.y,
    round %in% c(6,7) ~ perf_price.x),
    perf_ineq = case_when(
    round == 5 ~ perf_ineq.y,
    round %in% c(6,7) ~ perf_ineq.x),
    perf_crime = case_when(
    round == 5 ~ perf_crime.y,
    round %in% c(6,7) ~ perf_crime.x),
    perf_health = case_when(
    round == 5 ~ perf_health.y,
    round %in% c(6,7) ~ perf_health.x),
    perf_educ = case_when(
    round == 5 ~ perf_educ.y,
    round %in% c(6,7) ~ perf_educ.x),
    perf_water = case_when(
    round == 5 ~ perf_water.y,
    round %in% c(6,7) ~ perf_water.x),
    perf_corr = case_when(
    round == 5 ~ perf_corr.y,
    round %in% c(6,7) ~ perf_corr.x),
    perf_road = case_when(
    round == 5 ~ perf_road.y,
    round %in% c(6,7) ~ perf_road.x),
    perf_elect = case_when(
    round == 5 ~ perf_elect.y,
    round %in% c(6,7) ~ perf_elect.x),
    vote_no = case_when(
    round == 5 ~ vote_no.y,
    round %in% c(6,7) ~ vote_no.x),
    perf_pres = case_when(
    round == 5 ~ perf_pres.y,
    round %in% c(6,7) ~ perf_pres.x),
    perf_parl = case_when(
    round == 5 ~ perf_parl.y,
    round %in% c(6,7) ~ perf_parl.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q50A, Q50B, Q50C, Q50D, Q50E, Q50F, Q50G, Q50H, Q50I, Q50J, Q50K, Q50L,
         Q99,
         Q51A, Q51B, Q51D)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q50A, Q50B, Q50C, Q50D, Q50E, Q50F, Q50G, Q50H, Q50I, Q50J, Q50K, Q50L,
         Q99,
         Q51A, Q51B, Q51D)%>%
  rename(perf_eco=Q50A,
         perf_poor=Q50B,
         perf_job=Q50C,
         perf_price=Q50D,
         perf_ineq=Q50E,
         perf_crime=Q50F,
         perf_health=Q50G,
         perf_educ=Q50H,
         perf_water=Q50I,
         perf_corr=Q50J,
         perf_road=Q50K,
         perf_elect=Q50L,
         vote_no=Q99,
         perf_pres=Q51A,
         perf_parl=Q51B,
         perf_trad=Q51D)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(perf_eco = case_when(
    round == 8 ~ perf_eco.y,
    round %in% c(5,6,7) ~ perf_eco.x),
    perf_poor = case_when(
    round == 8 ~ perf_poor.y,
    round %in% c(5,6,7) ~ perf_poor.x),
    perf_job = case_when(
    round == 8 ~ perf_job.y,
    round %in% c(5,6,7) ~ perf_job.x),
    perf_price = case_when(
    round == 8 ~ perf_price.y,
    round %in% c(5,6,7) ~ perf_price.x),
    perf_ineq = case_when(
    round == 8 ~ perf_ineq.y,
    round %in% c(5,6,7) ~ perf_ineq.x),
    perf_crime = case_when(
    round == 8 ~ perf_crime.y,
    round %in% c(5,6,7) ~ perf_crime.x),
    perf_health = case_when(
    round == 8 ~ perf_health.y,
    round %in% c(5,6,7) ~ perf_health.x),
    perf_educ = case_when(
    round == 8 ~ perf_educ.y,
    round %in% c(5,6,7) ~ perf_educ.x),
    perf_water = case_when(
    round == 8 ~ perf_water.y,
    round %in% c(5,6,7) ~ perf_water.x),
    perf_corr = case_when(
    round == 8 ~ perf_corr.y,
    round %in% c(5,6,7) ~ perf_corr.x),
    perf_road = case_when(
    round == 8 ~ perf_road.y,
    round %in% c(5,6,7) ~ perf_road.x),
    perf_elect = case_when(
    round == 8 ~ perf_elect.y,
    round %in% c(5,6,7) ~ perf_elect.x),
    vote_no = case_when(
    round == 8 ~ vote_no.y,
    round %in% c(5,6,7) ~ vote_no.x),
    perf_pres = case_when(
    round == 8 ~ perf_pres.y,
    round %in% c(5,6,7) ~ perf_pres.x),
    perf_parl = case_when(
    round == 8 ~ perf_parl.y,
    round %in% c(5,6,7) ~ perf_parl.x),
    perf_trad = case_when(
    round == 8 ~ perf_trad.y,
    round %in% c(5,6,7) ~ perf_trad.x)
    )

data_trust%<>%
  select(-c(perf_eco.x, perf_poor.x, perf_job.x, perf_price.x, perf_ineq.x, perf_crime.x, perf_health.x, perf_educ.x, perf_water.x, perf_corr.x, perf_road.x, perf_elect.x, vote_no.x, perf_pres.x, perf_parl.x, perf_trad.x,
            perf_eco.y, perf_poor.y, perf_job.y, perf_price.y, perf_ineq.y, perf_crime.y, perf_health.y, perf_educ.y, perf_water.y, perf_corr.y, perf_road.y, perf_elect.y, vote_no.y, perf_pres.y, perf_parl.y, perf_trad.y))

rm(afro_w8)

data_trust%<>%
  mutate(perf_eco = if_else(perf_eco %in% c(1, 2, 3, 4), perf_eco, NA_real_))%>%
  mutate(perf_poor = if_else(perf_poor %in% c(1, 2, 3, 4), perf_poor, NA_real_))%>%
  mutate(perf_job = if_else(perf_job %in% c(1, 2, 3, 4), perf_job, NA_real_))%>%
  mutate(perf_price = if_else(perf_price %in% c(1, 2, 3, 4), perf_price, NA_real_))%>%
  mutate(perf_ineq = if_else(perf_ineq %in% c(1, 2, 3, 4), perf_ineq, NA_real_))%>%
  mutate(perf_crime = if_else(perf_crime %in% c(1, 2, 3, 4), perf_crime, NA_real_))%>%
  mutate(perf_health = if_else(perf_health %in% c(1, 2, 3, 4), perf_health, NA_real_))%>%
  mutate(perf_educ = if_else(perf_educ %in% c(1, 2, 3, 4), perf_educ, NA_real_))%>%
  mutate(perf_water = if_else(perf_water %in% c(1, 2, 3, 4), perf_water, NA_real_))%>%
  mutate(perf_corr = if_else(perf_corr %in% c(1, 2, 3, 4), perf_corr, NA_real_))%>%
  mutate(perf_road = if_else(perf_road %in% c(1, 2, 3, 4), perf_road, NA_real_))%>%
  mutate(perf_elect = if_else(perf_elect %in% c(1, 2, 3, 4), perf_elect, NA_real_))%>%
  mutate(perf_pres = if_else(perf_pres %in% c(1, 2, 3, 4), perf_pres, NA_real_))%>%
  mutate(perf_parl = if_else(perf_parl %in% c(1, 2, 3, 4), perf_parl, NA_real_))%>%
  mutate(perf_trad = if_else(perf_trad %in% c(1, 2, 3, 4), perf_trad, NA_real_))%>%
  mutate(vote_no=ifelse(vote_no == 9997, 1, 
                      ifelse(vote_no %in% c(9995, 9998, 9999, -1), NA_real_, 0)))

glimpse(data_trust)

data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_perf_obj = ifelse(all(is.na(c(perf_eco, perf_poor, perf_job, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect))), NA, mean(c(perf_eco, perf_poor, perf_job, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect), na.rm = TRUE)))%>%
  ungroup()

data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_perf_pol = ifelse(all(is.na(c(perf_pres, perf_parl))), NA, mean(c(perf_pres, perf_parl), na.rm = TRUE)))%>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust%<>%
  group_by(id_unique)%>%
  mutate(weighted_inst_know_2 = ifelse(all(is.na(c(know_pres, know_parl))), NA, mean(c(know_pres, know_parl), na.rm = TRUE)))%>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

afro_w7 <- read_sav("Data/Data_Raw/R7_Merged data_34ctry_4Dec18.sav")

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q25A, Q25E, Q54B)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q25A, Q25E, Q54B)%>%
  rename(contact_counc=Q25A,
         contact_trad=Q25E,
         listen_counc=Q54B)

data_trust <- left_join(data_trust, afro_w7, by="id_unique")

rm(afro_w7)

afro_w6 <- read.csv("Data/Data_Raw/afb_full_r6.csv_")

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q24a, q24e, q59b)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q24a, q24e, q59b)%>%
 rename(contact_counc=q24a,
        contact_trad=q24e,
        listen_counc=q59b)

data_trust <- left_join(data_trust, afro_w6, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(contact_counc = case_when(
    round == 6 ~ contact_counc.y,
    round == 7 ~ contact_counc.x),
    contact_trad = case_when(
    round == 6 ~ contact_trad.y,
    round == 7 ~ contact_trad.x),
    listen_counc = case_when(
    round == 6 ~ listen_counc.y,
    round == 7 ~ listen_counc.x))

data_trust%<>%
  select(-c(contact_counc.x, contact_counc.y, contact_trad.x, contact_trad.y, listen_counc.x, listen_counc.y))

glimpse(data_trust)

rm(afro_w6)

afro_w5 <- read.csv("Data/Data_Raw/afb_full_r5.csv_")

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q30a, q62b)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q30a, q62b)%>%
 rename(contact_counc=q30a,
        listen_counc=q62b)

data_trust <- left_join(data_trust, afro_w5, by="id_unique")

glimpse(data_trust)

data_trust%<>%
  mutate(contact_counc = case_when(
    round == 5 ~ contact_counc.y,
    round %in% c(6,7) ~ contact_counc.x),
    listen_counc = case_when(
    round == 5 ~ listen_counc.y,
    round %in% c(6,7) ~ listen_counc.x))

data_trust%<>%
  select(-c(contact_counc.x, contact_counc.y, listen_counc.x, listen_counc.y))

rm(afro_w5)

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q12A, Q12D, Q38B, Q38C)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q12A, Q12D, Q38B, Q38C)%>%
  rename(contact_counc=Q12A,
         contact_trad=Q12D,
         listen_counc=Q38B,
         listen_trad=Q38C)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(contact_counc = case_when(
    round == 8 ~ contact_counc.y,
    round %in% c(5,6,7) ~ contact_counc.x),
    contact_trad = case_when(
    round == 8 ~ contact_trad.y,
    round %in% c(5,6,7) ~ contact_trad.x),
    listen_counc = case_when(
    round == 8 ~ listen_counc.y,
    round %in% c(5,6,7) ~ listen_counc.x))

data_trust%<>%
  select(-c(contact_counc.x, contact_counc.y, contact_trad.x, contact_trad.y, listen_counc.x, listen_counc.y))

rm(afro_w8)

glimpse(data_trust)

data_trust%<>%
  mutate(contact_counc = if_else(contact_counc %in% c(0, 1, 2, 3), contact_counc, NA_real_))%>%
  mutate(contact_trad = if_else(contact_trad %in% c(0, 1, 2, 3), contact_trad, NA_real_))%>%
  mutate(listen_counc = if_else(listen_counc %in% c(0, 1, 2, 3), listen_counc, NA_real_))%>%
  mutate(listen_counc = if_else(listen_counc %in% c(0, 1, 2, 3), listen_counc, NA_real_))

glimpse(data_trust)

data_trust%<>%
  mutate(commu = as.numeric(commu),
    prob = as.numeric(prob))

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_1 = rowMeans(
      cbind(commu, prob), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_2 = rowMeans(
      cbind(commu, prob, contact_counc), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_3 = rowMeans(
      cbind(commu, prob, contact_trad), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_4 = rowMeans(
      cbind(contact_counc, contact_trad, listen_counc, listen_trad), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_5 = rowMeans(
      cbind(contact_counc, contact_trad), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_6 = rowMeans(
      cbind(listen_counc, listen_trad), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

data_trust %<>%
  group_by(id_unique) %>%
  mutate(weighted_local_7 = rowMeans(
      cbind(contact_trad, listen_trad), 
      na.rm = TRUE
    )
  ) %>%
  ungroup()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust%>%
  select(ethnie)%>%
  summary()

data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q81)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q81)%>%
  rename(ethnie=Q81)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(ethnie = case_when(
    round == 8 ~ ethnie.y,
    round %in% c(5,6,7) ~ ethnie.x))

data_trust%<>%
  select(-c(ethnie.x, ethnie.y))

rm(afro_w8)

glimpse(data_trust)

data_trust%<>%
  mutate(ethnie = if_else(ethnie %in% c(9990, 9995, 9998, 9999, -1, 94),NA_real_ , ethnie))

glimpse(data_trust)

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

glimpse(data_trust)

data_trust%<>%
  select(-rsf_index)

countries <- unique(data_trust$ISO)

year2012 <- read.csv("data/data_Raw/rsf/2012.csv", sep=";", stringsAsFactors=TRUE)

year2012%<>%
  filter(ISO%in%countries)%>%
  select(ISO, Score.N)%>%
  rename(rsf_index=Score.N)%>%
  mutate(rsf_index=as.numeric(rsf_index))%>%
  mutate(round=5)

year2012%>%
  select(rsf_index)%>%
  summary()

year2014 <- read.csv("data/data_Raw/rsf/2014.csv", sep=";", stringsAsFactors=TRUE)

year2014%<>%
  filter(ISO%in%countries)%>%
  select(ISO, Score.N)%>%
  rename(rsf_index=Score.N)%>%
  mutate(rsf_index=as.numeric(rsf_index))%>%
  mutate(round=6)

year2014%>%
  select(rsf_index)%>%
  summary()

year2016 <- read.csv("data/data_Raw/rsf/2016.csv", sep=";", stringsAsFactors=TRUE)

year2016%<>%
  filter(ISO%in%countries)%>%
  select(ISO, Score.N)%>%
  rename(rsf_index=Score.N)%>%
  mutate(rsf_index=as.numeric(rsf_index))%>%
  mutate(round=7)

year2016%>%
  select(rsf_index)%>%
  summary()

year2019 <- read.csv("data/data_Raw/rsf/2019.csv", sep=";", stringsAsFactors=TRUE)

year2019%<>%
  filter(ISO%in%countries)%>%
  select(ISO, Score.N)%>%
  rename(rsf_index=Score.N)%>%
  mutate(rsf_index=as.numeric(rsf_index))%>%
  mutate(round=8)

year2019%>%
  select(rsf_index)%>%
  summary()

data_trust <- data_trust %>% left_join(year2012,by=c("ISO", "round"))
data_trust <- data_trust %>% left_join(year2014,by=c("ISO", "round"))

data_trust%<>%
  mutate(rsf_index=case_when(
           round==5~rsf_index.x,
           round==6~rsf_index.y))

data_trust%<>%
  select(-rsf_index.x, -rsf_index.y)

data_trust <- data_trust %>% left_join(year2016,by=c("ISO", "round"))

data_trust%<>%
  mutate(rsf_index=case_when(
           round%in%c(5,6)~rsf_index.x,
           round==7~rsf_index.y))

data_trust%<>%
  select(-rsf_index.x, -rsf_index.y)

data_trust <- data_trust %>% left_join(year2019,by=c("ISO", "round"))

data_trust%<>%
  mutate(rsf_index=case_when(
           round%in%c(5,6,7)~rsf_index.x,
           round==8~rsf_index.y))

data_trust%<>%
  select(-rsf_index.x, -rsf_index.y)

data_trust%>%
  select(rsf_index)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

glimpse(data_trust)

qog <- read.csv("Data/Data_raw/qog_std_ts_jan24.csv")

qog%<>%
  select(year, ccodealp, fhp_mcpp5)%>%
  rename(ISO=ccodealp, fh_med_index=fhp_mcpp5)

qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2011 ~ 5,
                   round==2014 ~ 6,
                   round==2016 ~ 7,
                   round==2019 ~ 8))

data_trust %<>% left_join(qog, by=c("ISO", "round"))

glimpse(data_trust)

data_trust%>%
  select(fh_med_index)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8_filter <- afro_w8%>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

removed_rows <- anti_join(afro_w8, afro_w8_filter, by = colnames(afro_w8))

afro_w8_filter%>%
  filter(COUNTRY==3)%>%
  select(Q41A)%>%
  filter(Q41A!=9)%>%
  summary()

data_trust%>%
  filter(ISO=="BEN", round==8)%>%
  select(trust_pres)%>%
  summary()

```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df6.rds")

data_trust%<>%
  mutate(sex=as.numeric(sex))

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8 %<>%
  filter(!is.na(EA_GPS_LA), !is.na(LOCATION.LEVEL.2)) %>%
  filter(!duplicated(RESPNO)) %>%
  select(RESPNO, Q1, Q101) %>%
  rename(id = RESPNO,
         age = Q1,
         sex = Q101) %>%
  mutate(round = 8,
         id_unique = paste0(id, round)) %>%
  select(id_unique, age, sex)

data_trust <- left_join(data_trust, afro_w8, by="id_unique")

data_trust%<>%
  mutate(age = case_when(
    round == 8 ~ age.y,
    round %in% c(5,6,7) ~ age.x),
    sex = case_when(
    round == 8 ~ sex.y,
    round %in% c(5,6,7) ~ sex.x))

data_trust%<>%
  select(-c(age.x, age.y, sex.x, sex.y))

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")

```

```{r}
data_trust%>%
  filter(round==7)%>%
  distinct(cname)

data_trust%>%
  distinct(cname)

afro_w7%>%
  filter(COUNTRY==6)%>%
  View()

```

### 2025-02-24 script/discontinuity_merge.Rmd
import folders

```{r}
# Data manipulation and utility
library(dplyr)      # Data manipulation
library(readr)      # Data import/export
library(magrittr)   # Pipe operator (%>%)

# Statistical analysis and modeling
library(estimatr)   # Robust regression
library(car)        # Companion to Applied Regression (e.g., recoding variables)

# Visualization
library(ggplot2)    # Plotting
library(texreg)     # Exporting regression results to LaTeX/HTML

# Spatial and geospatial analysis
library(sf)         # Simple Features for R
library(geosphere)  # Geospatial functions
library(rnaturalearth)     # Natural Earth map data
library(rnaturalearthdata) # Data for rnaturalearth

# Specialized packages
library(rdrobust)   # Regression discontinuity designs
library(murdock)    # Specific package, assuming you have a need for it

library(haven)

setwd("~/Working paper/Trust/Script")
getwd()
```

```{r}
# Load the Murdock ethnic groups map (1956)
murdock <- murdock::murdock

# Convert the Murdock map to an 'sf' (Simple Features) object for spatial data manipulation
murdock_sf <- st_as_sf(murdock)

# Define a set of African countries of interest by specifying their names
countries <- ne_countries(country = c("Benin","Botswana","Burkina Faso","Cameroon","Ivory Coast",
                                    "Guinea","Kenya","Liberia","Malawi","Mali",
                                    "Mozambique","Namibia","Niger","Nigeria","Sierra Leone",
                                    "United Republic of Tanzania","Uganda","Zambia","Zimbabwe",
                                    "Ghana"))

# Convert the selected countries into an 'sf' object for spatial operations
countries_sf <- st_as_sf(countries)

# Extract the individual boundaries of the selected African countries
boundaries <- st_boundary(countries_sf)

ggplot() +
  geom_sf(data = murdock_sf, aes(color = "Murdock"), fill = "transparent", size = 1) +
  geom_sf(data = boundaries, aes(color = "Country Borders"), lwd = 1) +
  scale_color_manual(
    values = c("Murdock" = "black", "Country Borders" = "red"),
    labels = c("Contemporary Country Borders", "Historical Ethnic Areas"),
    name = NULL 
  ) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),         
    legend.key = element_rect(fill = "transparent", color = NA),
    legend.text = element_text(size = 8),
    legend.position = c(0.25, 0.35)
  )

#ggsave("murdock_map.jpg", width = 10, height = 6, dpi = 300)

# Create a 50km buffer around the African country borders
buffer <- st_buffer(boundaries, dist = 25000)

# Plot the Murdock map with the 25km buffers around the African borders
ggplot() +
  geom_sf(data = murdock_sf, fill = "transparent", color = "black", size = 1) + # Murdock map in black
  geom_sf(data = buffer, color = "red", lwd = 1.5) + # 25km buffer around borders in red
  theme_minimal() +
  ggtitle("25km Buffer of African Borders and Murdock Ethnic Zones (1956)")
```

```{r}
# List of countries of interest
countries <- c("Benin","Botswana","Burkina Faso","Cameroon","Ivory Coast",
                                    "Guinea","Kenya","Liberia","Malawi","Mali",
                                    "Mozambique","Namibia","Niger","Nigeria","Sierra Leone",
                                    "United Republic of Tanzania","Uganda","Zambia","Zimbabwe",
                                    "Ghana")

# Buffer distances
buffer_distances <- c(50000, 40000, 30000, 25000, 20000, 15000, 10000)

# Loop over each country and buffer distance
for (country in countries) {

  # Select the countries surrounding the target country (excluding the current one)
  surrounding_countries <- countries[countries != country]
  surrounding_countries_sf <- st_as_sf(ne_countries(country = surrounding_countries))

  # Loop over each buffer distance
  for (dist in buffer_distances) {

    # Create buffer for the target country
    buffer_country <- st_buffer(subset(countries_sf, countries_sf$sovereignt == country), dist = dist)

    # Find the intersection with the surrounding countries
    inter_country <- st_intersection(buffer_country, surrounding_countries_sf)

    # Plot the intersection geometry
    plot(inter_country$geometry, main = paste(country, "-", dist / 1000, "km buffer"))
  }
}

# List of objects to keep
objects_to_keep <- c("data_trust_test", "union_list", "murdock_sf", "countries", "countries_sf", "buffer", "buffer_distances")

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

```{r}
# Storage lists
intersections_list <- list()

# Loop through buffer distances and countries to store intersections
for (dist in buffer_distances) {
  intersections <- lapply(countries, function(country) {
    # Create buffer for each country at the specified distance
    buffer <- st_buffer(subset(countries_sf, countries_sf$sovereignt == country), dist = dist)
    # Get the surrounding countries excluding the current one
    surrounding_countries <- countries[countries != country]
    surrounding_countries_sf <- st_as_sf(ne_countries(country = surrounding_countries))
    # Perform intersection and return it
    st_intersection(buffer, surrounding_countries_sf)
  })

  # Combine all intersections for the current buffer distance
  intersections_list[[as.character(dist)]] <- do.call(rbind, intersections)
}

# Perform union on the combined intersections for each distance
unions_list <- lapply(intersections_list, function(intersections) {
  union <- st_union(intersections)
  st_as_sf(union)
})

# Example of plotting the 25km buffer result
ggplot() +
  geom_sf(data = murdock_sf, fill = "transparent", color = "black", size = 1) +
  geom_sf(data = unions_list[["20000"]], color = "red", lwd=1, fill="transparent") +  # 25km buffer
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),         
    legend.key = element_rect(fill = "transparent", color = NA),
    legend.text = element_text(size = 8),
    legend.position = c(0.25, 0.35)
  )

#ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)

# List of objects to keep
objects_to_keep <- c("data_trust_test", "unions_list", "murdock_sf")

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

```{r}
# Load data
data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/data_merge.rds")
bdd_geo <- read_csv("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/bdd_geo_w8.csv")

# Merge and clean data
data_trust_test %<>%
  left_join(bdd_geo, by = "id_unique") %>%
  select(-...1) %>%
  mutate(
    distance_border_km = distance_border / 1000,
    distance_border_km2 = distance_border_km^2,
    distance_border_km3 = distance_border_km^3
  )

# Convert to spatial data and filter by borders
border_sample_50_union <- unions_list[["50000"]]
border_sample_40_union <- unions_list[["40000"]]
border_sample_30_union <- unions_list[["30000"]]
border_sample_25_union <- unions_list[["25000"]]
border_sample_20_union <- unions_list[["20000"]]
border_sample_15_union <- unions_list[["15000"]]
border_sample_10_union <- unions_list[["10000"]]

data_trust_test_sf <- st_as_sf(data_trust_test, coords = c("longitude", "latitude"), crs = st_crs(border_sample_50_union))

# Define a function to filter data based on border polygons
filter_by_border <- function(data, borders) {
  lapply(borders, function(border) {
    border_valid <- st_make_valid(border)
    st_filter(data, border_valid)
  })
}

# List of border polygons
borders <- list(
  border_sample_50_union,
  border_sample_40_union,
  border_sample_30_union,
  border_sample_25_union,
  border_sample_20_union,
  border_sample_15_union,
  border_sample_10_union
)

# Filter data
filtered_data_list <- filter_by_border(data_trust_test_sf, borders)
names(filtered_data_list) <- c("50", "40", "30", "25", "20", "15", "10")

# Remove border polygons
rm(list = names(borders))

# Prepare Murdock map
murdock <- murdock_sf %>%
  select(NAME, geometry) %>%
  rename(murdock_names = NAME)

# Join filtered data with Murdock map
df_list <- lapply(filtered_data_list, function(data) {
  st_join(data, murdock)
})

# Plot
ggplot() +
  geom_sf(data = murdock_sf, fill = "transparent", color = "black", size = 1) +
  geom_sf(data = df_list$`20`, size = 0.75, shape = 19, color = "red") +
  ggtitle("Individuals living less than 50 km from a border and Murdock's (1956) historical ethnic homeland") +
  theme_void()

# List of objects to keep
objects_to_keep <- c("df_list", "data_trust_test", "murdock_sf", "unions_list")

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

```{r}
# Load country boundaries
countries <- ne_countries(scale = "medium", continent = "Africa", returnclass = "sf")

# Prepare data
individuals <- data_trust_test %>%
  select(longitude, latitude, ISO) %>%
  na.omit()

capitals <- data_trust_test %>%
  select(caplong, caplat, ISO) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

# Combine individuals and capitals into a single data frame for plotting
combined_points <- bind_rows(
  individuals %>% mutate(category = "observations"),
  capitals %>% mutate(category = "capitals")
)

selected_countries <- countries%>%
  filter(name%in%c("Benin","Botswana","Burkina Faso","Cameroon","Côte d'Ivoire",
                                    "Guinea","Kenya","Liberia","Malawi","Mali",
                                    "Mozambique","Namibia","Niger","Nigeria","Sierra Leone",
                                    "Tanzania","Uganda","Zambia","Zimbabwe",
                                    "Ghana"))

selected_capitals <- capitals %>%
  filter(ISO%in% c("BEN", "BFA", "BWA", "CMR", "CIV", "GHA", "GIN", "KEN", "LBR", "MLI", "MWI", "MOZ", "NAM", "NER", "NGA", "SLE", "TZA", "UGA", "ZMB", "ZWE"))

# Plot
ggplot() +
  geom_sf(data = countries, fill = "white", color = "black") +
  theme_void() +
  geom_sf(data = selected_countries, fill = "green3", color = "black") +
    geom_point(data = selected_capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "red", show.legend = FALSE)

#ggsave("writing/presentation/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)

selected_countries <- countries %>% 
  filter(iso_a3 %in% c("BEN", "NER"))

selected_individuals <- individuals %>%
  filter(ISO%in% c("BEN", "NER"))

selected_capitals <- capitals %>%
  filter(ISO%in% c("BEN", "NER"))

test <- murdock_sf%>%
  distinct(NAME)

selected_murdock <- murdock_sf%>%
  filter(NAME=="DENDI")

#test <- unions_list[["20000"]]

#test %<>%
  filter(ISO%in%c("BEN", "NER"))

# Create the plot
#ggplot() +
  # Base map with country borders
#    geom_sf(data = selected_countries, fill = "white", color = "black") +
#  geom_sf(data = selected_murdock, fill = "green", color = "darkgreen", size = 1, alpha=0.5) +
  # Use theme_void to create a clean background
#  theme_void() + 
  # Adding capital cities with refined aesthetics
#  geom_point(data = selected_capitals, 
#             aes(x = longitude, y = latitude, color = "Capitals"), 
#             size = 2, shape = 22, fill = "red", show.legend = FALSE) +

#geom_label(aes(x = 2.5, y = 10, label = "Benin"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
#      geom_label(aes(x = 4, y = 14.5, label = "Niger"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +

#geom_text(aes(x = 2.4, y = 13.75, label = "Niamey"), color = "black", size = 5) +
#geom_text(aes(x = 2.2, y = 6.6, label = "Porto-Novo"), color = "black", size = 5) +

#  labs(color = NULL) +
#    coord_sf(xlim = c(0, 5), ylim = c(6, 18), expand = FALSE)

# Save the plot if needed
#ggsave("writing/presentation/bdd_map.jpg", width = 10, height = 10, units = "in", dpi = 300)

# List of objects to keep
objects_to_keep <- c("df_list")

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

```{r}
process_df <- function(df, threshold) {
  df_filtered <- subset(df, distance_border < threshold)
  df_filtered$cluster_frontiere <- paste(df_filtered$murdock_names, df_filtered$round, sep = "_")
  return(df_filtered)
}

# Apply the function to each data frame in the list with respective thresholds
df_list <- lapply(names(df_list), function(name) {
  df <- df_list[[name]]
  threshold <- case_when(
  name == "50" ~ 50000,
  name == "40" ~ 40000,
  name == "30" ~ 30000,
  name == "25" ~ 25000,
  name == "20" ~ 20000,
  name == "15" ~ 15000,
  name == "10" ~ 10000,
  TRUE ~ NA_real_
)
  df_filtered <- process_df(df, threshold)
  return(df_filtered)
})

# Update the names of the list to match the original names
names(df_list) <- c("df_50", "df_40", "df_30", "df_25", "df_20", "df_15", "df_10")
```

```{r}
convert_labelled_to_factors <- function(df) {
  df %>%
    mutate(across(where(haven::is.labelled), haven::as_factor))
}

# Apply the function to each data frame in the list
df_list <- lapply(df_list, convert_labelled_to_factors)

# Optionally, update list names if needed
names(df_list) <- c("df_50", "df_40", "df_30", "df_25", "df_20", "df_15", "df_10")

rm("convert_labelled_to_factors", "process_df")
```

```{r}
df_50 <- df_list$df_50

list_columns <- sapply(df_50, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_50[list_columns] <- lapply(df_50[list_columns], function(x) sapply(x, toString))

df_50%<>%as.data.frame()

df_50 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_50, file="Data/Data_RDS/df_50_merge.rds")

write_dta(df_50, "Data/Data_dta/df_50_merge.dta")
```

```{r}
df_40 <- df_list$df_40

list_columns <- sapply(df_40, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_40[list_columns] <- lapply(df_40[list_columns], function(x) sapply(x, toString))

df_40%<>%as.data.frame()

df_40 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_40, file="Data/Data_RDS/df_40_merge.rds")

write_dta(df_40, "Data/Data_dta/df_40_merge.dta")
```

```{r}
df_30 <- df_list$df_30

list_columns <- sapply(df_30, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_30[list_columns] <- lapply(df_30[list_columns], function(x) sapply(x, toString))

df_30%<>%as.data.frame()

df_30 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_30, file="Data/Data_RDS/df_30_merge.rds")

write_dta(df_30, "Data/Data_dta/df_30_merge.dta")
```

```{r}
df_25 <- df_list$df_25

list_columns <- sapply(df_25, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_25[list_columns] <- lapply(df_25[list_columns], function(x) sapply(x, toString))

df_25%<>%as.data.frame()

df_25 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_25, file="Data/Data_RDS/df_25_merge.rds")

write_dta(df_25, "Data/Data_dta/df_25_merge.dta")
```

```{r}
df_20 <- df_list$df_20

list_columns <- sapply(df_20, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_20[list_columns] <- lapply(df_20[list_columns], function(x) sapply(x, toString))

df_20%<>%as.data.frame()

df_20 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_20, file="Data/Data_RDS/df_20_merge.rds")

write_dta(df_20, "Data/Data_dta/df_20_merge.dta")
```

```{r}
df_15 <- df_list$df_15

list_columns <- sapply(df_15, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_15[list_columns] <- lapply(df_15[list_columns], function(x) sapply(x, toString))

df_15%<>%as.data.frame()

df_15 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_15, file="Data/Data_RDS/df_15_merge.rds")

write_dta(df_15, "Data/Data_dta/df_15_merge.dta")
```

```{r}
df_10 <- df_list$df_10

list_columns <- sapply(df_10, is.list)

# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
df_10[list_columns] <- lapply(df_10[list_columns], function(x) sapply(x, toString))

df_10%<>%as.data.frame()

df_10 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_10, file="Data/Data_RDS/df_10_merge.rds")

write_dta(df_10, "Data/Data_dta/df_10_merge.dta")
```

### 2025-02-24 script/discontinuity_w8.Rmd
import folders

--- 2025-02-24 script/discontinuity_merge.Rmd
@@
 
-setwd("~/Working paper/Trust/Script")
+setwd("~/working_paper/trust/")
 getwd()
@@
 
-#ggsave("murdock_map.jpg", width = 10, height = 6, dpi = 300)
+ggsave("plots/discontinuity/murdock_map.jpg", width = 10, height = 6, dpi = 300)
 
@@
 # Get all objects in the current environment
-all_objects <- ls()
 
 # Determine which objects to remove
-objects_to_remove <- setdiff(all_objects, objects_to_keep)
 
 # Remove the unnecessary objects
-rm(list = objects_to_remove)
+
 ```
@@
 
-#ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)
+ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)
 
@@
 # Load data
-data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/data_merge.rds")
-bdd_geo <- read_csv("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/bdd_geo_w8.csv")
+data_trust_test <- readRDS("data/data_rds/data_final_r.rds")
+bdd_geo <- read_csv("data/data_raw/bdd_geo_w8.csv")
 
@@
 # List of objects to keep
-objects_to_keep <- c("df_list", "data_trust_test", "murdock_sf", "unions_list")
+objects_to_keep <- c("df_list", "data_trust_test")
 
 # Get all objects in the current environment
-all_objects <- ls()
 
 # Determine which objects to remove
-objects_to_remove <- setdiff(all_objects, objects_to_keep)
 
 # Remove the unnecessary objects
-rm(list = objects_to_remove)
+
 ```
@@
 individuals <- data_trust_test %>%
-  select(longitude, latitude, ISO) %>%
+  select(longitude, latitude, iso) %>%
   na.omit()
@@
 capitals <- data_trust_test %>%
-  select(caplong, caplat, ISO) %>%
+  select(caplong, caplat, iso) %>%
   na.omit() %>%
@@
 selected_capitals <- capitals %>%
-  filter(ISO%in% c("BEN", "BFA", "BWA", "CMR", "CIV", "GHA", "GIN", "KEN", "LBR", "MLI", "MWI", "MOZ", "NAM", "NER", "NGA", "SLE", "TZA", "UGA", "ZMB", "ZWE"))
+  filter(iso%in% c("BEN", "BFA", "BWA", "CMR", "CIV", "GHA", "GIN", "KEN", "LBR", "MLI", "MWI", "MOZ", "NAM", "NER", "NGA", "SLE", "TZA", "UGA", "ZMB", "ZWE"))
 
@@
   theme_void() +
-  geom_sf(data = selected_countries, fill = "green3", color = "black") +
+  geom_sf(data = selected_countries, fill = "#E94849", color = "black") +
     geom_point(data = selected_capitals, 
              aes(x = longitude, y = latitude), 
-             size = 2, shape = 22, fill = "red", show.legend = FALSE)
+             size = 2, shape = 22, fill = "black", show.legend = FALSE)
 
-#ggsave("writing/presentation/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
+ggsave("plots/map/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
 
-selected_countries <- countries %>% 
-  filter(iso_a3 %in% c("BEN", "NER"))
+#selected_countries <- countries %>% 
+ # filter(iso_a3 %in% c("BEN", "NER"))
 
-selected_individuals <- individuals %>%
-  filter(ISO%in% c("BEN", "NER"))
+#selected_individuals <- individuals %>%
+ # filter(iso%in% c("BEN", "NER"))
 
-selected_capitals <- capitals %>%
-  filter(ISO%in% c("BEN", "NER"))
+#selected_capitals <- capitals %>%
+ # filter(iso%in% c("BEN", "NER"))
 
-test <- murdock_sf%>%
-  distinct(NAME)
+#test <- murdock_sf%>%
+#  distinct(NAME)
 
-selected_murdock <- murdock_sf%>%
-  filter(NAME=="DENDI")
+#selected_murdock <- murdock_sf%>%
+#  filter(NAME=="DENDI")
 
@@
 #test %<>%
-  filter(ISO%in%c("BEN", "NER"))
+ # filter(iso%in%c("BEN", "NER"))
 
@@
 
+df_50$murdock_round <- paste0(df_50$murdock_names, df_50$round, sep="_")
+
 df_50 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_50, file="Data/Data_RDS/df_50_merge.rds")
+df_50 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_50, "Data/Data_dta/df_50_merge.dta")
+saveRDS(df_50, file="data/data_rds/df_50.rds")
+
+write_dta(df_50, "data/data_dta/df_50.dta")
+
+df_50 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_50 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_50, file="data/data_rds/df_50_2.rds")
+
+write_dta(df_50, "data/data_dta/df_50_2.dta")
+
 ```
@@
 
+df_40$murdock_round <- paste0(df_40$murdock_names, df_40$round, sep="_")
+
 df_40 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_40, file="Data/Data_RDS/df_40_merge.rds")
+df_40 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_40, "Data/Data_dta/df_40_merge.dta")
+saveRDS(df_40, file="data/data_rds/df_40.rds")
+
+write_dta(df_40, "data/data_dta/df_40.dta")
+
+df_40 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_40 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_40, file="data/data_rds/df_40_2.rds")
+
+write_dta(df_40, "data/data_dta/df_40_2.dta")
 ```
@@
 
+df_30$murdock_round <- paste0(df_30$murdock_names, df_30$round, sep="_")
+
 df_30 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_30, file="Data/Data_RDS/df_30_merge.rds")
+df_30 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_30, "Data/Data_dta/df_30_merge.dta")
+saveRDS(df_30, file="data/data_rds/df_30.rds")
+write_dta(df_30, "data/data_dta/df_30.dta")
+
+df_30 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_30 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_30, file="data/data_rds/df_30_2.rds")
+
+write_dta(df_30, "data/data_dta/df_30_2.dta")
+
 ```
@@
 
+df_25$murdock_round <- paste0(df_25$murdock_names, df_25$round, sep="_")
+
 df_25 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_25, file="Data/Data_RDS/df_25_merge.rds")
+df_25 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_25, "Data/Data_dta/df_25_merge.dta")
+saveRDS(df_25, file="data/data_rds/df_25.rds")
+
+write_dta(df_25, "data/data_dta/df_25.dta")
+
+df_25 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_25 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_25, file="data/data_rds/df_25_2.rds")
+
+write_dta(df_25, "data/data_dta/df_25_2.dta")
 ```
@@
 
+df_20$murdock_round <- paste0(df_20$murdock_names, df_20$round, sep="_")
+
 df_20 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_20, file="Data/Data_RDS/df_20_merge.rds")
+df_20 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_20, "Data/Data_dta/df_20_merge.dta")
+saveRDS(df_20, file="data/data_rds/df_20.rds")
+
+write_dta(df_20, "data/data_dta/df_20.dta")
+
+df_20 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_20 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_20, file="data/data_rds/df_20_2.rds")
+
+write_dta(df_20, "data/data_dta/df_20_2.dta")
 ```
@@
 
+df_15$murdock_round <- paste0(df_15$murdock_names, df_15$round, sep="_")
+
 df_15 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_15, file="Data/Data_RDS/df_15_merge.rds")
+df_15 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_15, "Data/Data_dta/df_15_merge.dta")
+saveRDS(df_15, file="data/data_rds/df_15.rds")
+
+write_dta(df_15, "data/data_dta/df_15.dta")
+
+df_15 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_15 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_15, file="data/data_rds/df_15_2.rds")
+
+write_dta(df_15, "data/data_dta/df_15_2.dta")
 ```
@@
 
+df_10$murdock_round <- paste0(df_10$murdock_names, df_10$round, sep="_")
+
 df_10 %<>%
   group_by(murdock_names) %>%
-  filter(n_distinct(ISO) >= 2)%>%
+  filter(n_distinct(iso) >= 2)%>%
   ungroup()
 
-saveRDS(df_10, file="Data/Data_RDS/df_10_merge.rds")
+df_10 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
 
-write_dta(df_10, "Data/Data_dta/df_10_merge.dta")
+saveRDS(df_10, file="data/data_rds/df_10.rds")
+
+write_dta(df_10, "data/data_dta/df_10.dta")
+
+df_10 %<>%
+  group_by(murdock_round) %>%
+  filter(n_distinct(iso) >= 2)%>%
+ungroup()
+
+df_10 %<>%
+  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
+
+saveRDS(df_10, file="data/data_rds/df_10_2.rds")
+
+write_dta(df_10, "data/data_dta/df_10_2.dta")
 ```

### 2025-02-24 script/internet_adm2.Rmd
import folders

```{r}
setwd("~/Working paper/Trust/Script")
getwd()
```

```{r}
library(raster)
library(rgdal)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(sf)
library(exactextractr)
library(ggplot2)
```

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins/Mobile Coverage Explorer v2019 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_BJ2G_2019.tif"
```

```{r}
gg <- raster(tiff_file)

print(gg)

gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))

print(gg_wgs84)
```

```{r}
rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

gg_wgs84_recode <- calc(gg_wgs84, fun=rc)

plot(gg_wgs84_recode)

rm(coords, gg, gg_wgs84, values, rc, tiff_file)
```

```{r}
shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"

country <- readOGR(shapefile_path)

if (!identical(crs(gg_wgs84_recode), crs(country))) {
  country <- spTransform(country, crs(gg_wgs84_recode))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country)

rm(shapefile_path, gg_wgs84_recode, gg_wgs84_cropped)

dev.off()

plot(gg_wgs84_masked)
```

```{r}
# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/BEN_pd_2019_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

print(pop)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

print(pop_wgs84)

plot(pop_wgs84)

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country)

rm(data_file, pop, pop_wgs84, pop_wgs84_cropped)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

rm(pop_wgs84_masked)

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

# Afficher le raster résultant avec les contours du country
plot(gg_pop, main="Couverture Pondérée par Densité de Population")
plot(country, add=TRUE, border="darkgrey")

graphics.off()

plot(gg_wgs84_masked)
plot(pop_wgs84_resampled)
plot(gg_pop)

png("plots/gg_pop/chemin_vers_le_plot.png", width = 800, height = 600)
plot(gg_wgs84_masked)
dev.off()

png("plots/gg_pop/chemin_vers_le_plot2.png", width = 800, height = 600)
plot(pop_wgs84_resampled)
dev.off()

png("plots/gg_pop/chemin_vers_le_plot3.png", width = 800, height = 600)
plot(gg_pop, main="Couverture Pondérée par Densité de Population")
dev.off()

```

```{r}

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
regions <- st_make_valid(regions)

mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')

regions$mean_gg <- mean_gg

ggplot() +
  geom_sf(data = regions, aes(fill = mean_gg), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Internet Coverage")+
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Internet Coverage ADM2 - Round 8")

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

ggplot() +
  geom_sf(data = regions, aes(fill = mean_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_pop), max(regions$mean_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Population Density ADM2 - Round 7")

mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

regions$mean_gg_pop <- mean_gg_pop

ggplot() +
  geom_sf(data = regions, aes(fill = mean_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_gg_pop), max(regions$mean_gg_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")

regions$pot_gg_pop <- mean_gg_pop/mean_pop

ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")

```

```{r}
data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/final_df5.rds")

capitals <- data_trust_test %>%
  select(caplong, caplat, ISO) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

capitals%<>%
  filter(ISO=="BEN")%>%
  distinct(ISO, .keep_all = TRUE)

png("plots/gg_pop/no_pop_weighting.png", width = 800, height = 600)

#Avant
ggplot() +
  geom_sf(data = regions, aes(fill = mean_gg), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$mean_gg), max(regions$mean_gg)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "No Population Weighting")

dev.off()

#Après
png("plots/gg_pop/pop_weighted.png", width = 800, height = 600, dpi=300)

ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "black") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Internet Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = NULL) +
  geom_point(data = capitals, 
             aes(x = longitude, y = latitude), 
             size = 4, shape = 22, fill = "green", show.legend = FALSE)+
  geom_text(aes(x = 2.5, y = 6.2, label = "Porto-Novo"), color = "black", size = 4, fontface="bold") +
    theme_minimal() +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),
    legend.position = c(1 ,0.35),
    plot.title = element_text(hjust = 0.5, size = 5, face = "bold")
  )

ggsave("plots/gg_pop/pop_weighted3.jpg", width = 8, height = 6, dpi = 300)

dev.off()
```

#3G Data
##2019
###ADM2
*Note pays:
BEN: 2018
BFA: 2014
BWA: /
CMR: 2017
CIV: /
GHA: 2014
GIN: 2012
KEN: 2013
LBR: 2013
MLI: /
MWI: 2014
MOZ: /
NAM: /
NER: 2013
NGA: 2012
SEN: 2015
SLE: 2014
TZA: 2014
UGA: 2013
ZMB: 2014
ZWE: 2015
```{r}
countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "CMR", "NAM", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Botswana, Ivory Coast, Mali ,Togo in 2018

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2019 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2019.tif")

ggg <- raster(tiff_file)
ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
}

# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2019_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')

regions$mean_ggg <- mean_ggg

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')

regions$mean_ggg_pop <- mean_ggg_pop

regions$pot_ggg_pop <- mean_ggg_pop/mean_pop

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=8)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_ggg_pop_2=pot_ggg_pop,
         mean_ggg_pop_2=mean_ggg_pop,
         mean_pop_2=mean_pop,
         mean_ggg_2=mean_ggg)

data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)
```

##2016
###ADM2

*Note pays:
BEN: 2018
BFA: 2014
BWA: /
CMR: 2017
CIV: /
GHA: 2014
GIN: 2012
KEN: 2013
LBR: 2013
MLI: /
MWI: 2014
MOZ: /
NAM: /
NER: 2013
NGA: 2012
SEN: 2015
SLE: 2014
TZA: 2014
UGA: 2013
ZMB: 2014
ZWE: 2015

```{r}
countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Botswana, Ivory Coast, Mali ,Togo in 2018

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2016.tif")

ggg <- raster(tiff_file)
ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
}

# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')

regions$mean_ggg <- mean_ggg

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')

regions$mean_ggg_pop <- mean_ggg_pop

regions$pot_ggg_pop <- mean_ggg_pop/mean_pop

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=7)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_ggg_pop_2=pot_ggg_pop,
         mean_ggg_pop_2=mean_ggg_pop,
         mean_pop_2=mean_pop,
         mean_ggg_2=mean_ggg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2014
###ADM2
```{r}
countries_adm2 <- c("GIN", "LBR", "NER", "KEN","NGA","UGA", "ZWE")

#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2014

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")

ggg <- raster(tiff_file)
ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
}

# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')

regions$mean_ggg <- mean_ggg

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')

regions$mean_ggg_pop <- mean_ggg_pop

regions$pot_ggg_pop <- mean_ggg_pop/mean_pop

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=6)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_ggg_pop_2=pot_ggg_pop,
         mean_ggg_pop_2=mean_ggg_pop,
         mean_pop_2=mean_pop,
         mean_ggg_2=mean_ggg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

#2G Data

##2019
###ADM2

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Senegal, Togo in 2019

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

## Etape 1 de Guriev et al.

tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2019 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2019.tif")

gg <- raster(tiff_file)
gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
gg_wgs84_recode <- calc(gg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

## Etape 2 de Guriev et al.

data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2019_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

## Etape 3 de Guriev et al.
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

## Etape 4 de Guriev et al.
mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

## Etape 5 de Guriev et al.
mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

## Etape 6 de Guriev et al.
regions$mean_gg_pop <- mean_gg_pop
regions$mean_pop <- mean_pop

## Etape 7 de Guriev et al.
regions$pot_gg_pop <- mean_gg_pop/mean_pop

## Moyenne couverture 2G non pondérée par la densité de population
mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
regions$mean_gg <- mean_gg

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=8)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  select(-c(mean_pop_2.x, mean_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2016
###ADM2

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
#No Senegal, Togo in 2016

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

## Etape 1 de Guriev et al.

tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")

gg <- raster(tiff_file)
gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
gg_wgs84_recode <- calc(gg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

## Etape 2 de Guriev et al.

data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

## Etape 3 de Guriev et al.
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

## Etape 4 de Guriev et al.
mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

## Etape 5 de Guriev et al.
mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

## Etape 6 de Guriev et al.
regions$mean_gg_pop <- mean_gg_pop
regions$mean_pop <- mean_pop

## Etape 7 de Guriev et al.
regions$pot_gg_pop <- mean_gg_pop/mean_pop

## Moyenne couverture 2G non pondérée par la densité de population
mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
regions$mean_gg <- mean_gg

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=7)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2014
###ADM2

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Senegal, Togo in 2014

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")

gg <- raster(tiff_file)
gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
gg_wgs84_recode <- calc(gg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')

regions$mean_gg <- mean_gg

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

regions$mean_gg_pop <- mean_gg_pop

regions$pot_gg_pop <- mean_gg_pop/mean_pop

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=6)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2011
###ADM2

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB")
#No Senegal, Togo in 2011

rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")

gg <- raster(tiff_file)
gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
gg_wgs84_recode <- calc(gg_wgs84, fun=rc)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

# Lecture du fichier de données
data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')

regions$mean_gg <- mean_gg

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

regions$mean_gg_pop <- mean_gg_pop

regions$pot_gg_pop <- mean_gg_pop/mean_pop

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=5)

accumulated_results <- rbind(accumulated_results, regions)

}

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(data_trust)

data_trust %<>%
  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

```

```{r}
data_trust%<>%
    mutate(pot_cvg_2=ifelse(is.na(pot_ggg_pop_2), pot_gg_pop_2, pot_ggg_pop_2))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

### 2025-02-24 script/internet_weighted.Rmd
import folders

--- 2025-02-24 script/internet_adm2.Rmd
@@
 dev.off()
+```
+
+#3G Maps
+##2016
+###ADM2
+
+*Note pays:
+BEN: /
+BFA: 2014
+BWA: /
+CMR: /
+CIV: /
+GHA: 2014
+GIN: 2012
+KEN: 2013
+LBR: 2013
+MLI: /
+MWI: 2014
+MOZ: /
+NAM: /
+NER: 2013
+NGA: 2012
+SEN: 2015
+SLE: 2014
+TZA: 2014
+UGA: 2013
+ZMB: 2014
+ZWE: 2015
+
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE")
+#No Botswana, Ivory Coast, Mali ,Togo in 2018
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2016.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==7)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 3G Coverage ADM2 - Round 7", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2016.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm1_valid %>%
+  filter(ISO == country, round==7)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 3G Coverage ADM1 - Round 7", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+
+##2014
+###ADM2
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("GIN", "LBR", "NER")
+#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2015
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 3G Coverage ADM2 - Round 6", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("KEN","NGA","UGA", "ZWE")
+# No Mozambique in 2015
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm1_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 3G Coverage ADM1 - Round 6", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+
+#2G Maps
+*Note pays 2G
+BEN: 2008
+BFA: 2014
+BWA: 2011
+CMR: 2015
+CIV: 2006
+GHA: 2014
+GIN: 2012
+KEN: 2011
+LBR: 2013
+MLI: 2004
+MWI: 2008
+MOZ: 2013
+NAM: 2008
+NER: 2014
+NGA: 2012
+SEN: /
+SLE: 2014
+TZA: 2008
+UGA: 2009
+ZMB: 2008
+ZWE: 2012
+
+##2016
+###ADM2
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2018
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==7)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM2 - Round 7", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==7)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM1 - Round 7", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)
+
+}
+```
+##2014
+*Note pays 2G
+BEN: 2008
+BFA: 2014
+BWA: 2011
+CMR: 2015
+CIV: 2006
+GHA: 2014
+GIN: 2012
+KEN: 2011
+LBR: 2013
+MLI: 2004
+MWI: 2008
+MOZ: 2013
+NAM: 2008
+NER: 2014
+NGA: 2012
+SEN: /
+SLE: 2014
+TZA: 2008
+UGA: 2009
+ZMB: 2008
+ZWE: 2012
+
+###ADM2
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2015
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM2 - Round 6", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM1 - Round 6", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)
+
+}
+```
+##2011
+*Note pays 2G
+BEN: 2008
+BFA: 2014
+BWA: 2011
+CMR: 2015
+CIV: 2006
+GHA: 2014
+GIN: 2012
+KEN: 2011
+LBR: 2013
+MLI: 2004
+MWI: 2008
+MOZ: 2013
+NAM: 2008
+NER: 2014
+NGA: 2012
+SEN: /
+SLE: 2014
+TZA: 2008
+UGA: 2009
+ZMB: 2008
+ZWE: 2012
+
+###ADM2
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2013
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM2 - Round 5", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r5.jpg"), plot = plot, width = 10, height = 8)
+
+}
+
+```
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+panel_sf <- data_trust_report_adm2_valid %>%
+  filter(ISO == country, round==6)
+
+panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
+
+plot <- ggplot() +
+  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
+    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
+  labs(title = paste(country, "- 2G Coverage ADM1 - Round 5", sep = " "))
+
+  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r5.jpg"), plot = plot, width = 10, height = 8)
+
+}
 ```
@@
 ```{r}
-countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "CMR", "NAM", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
+countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "CMR", "NAM")
 #No Botswana, Ivory Coast, Mali ,Togo in 2018
+
+glimpse(afro_w8)
 
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_ggg_pop_2=pot_ggg_pop,
-         mean_ggg_pop_2=mean_ggg_pop,
-         mean_pop_2=mean_pop,
-         mean_ggg_2=mean_ggg)
-
-data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
-
-data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
-
-data_trust%<>%
+afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+glimpse(afro_w8)
+
+afro_w8%<>%
   distinct(id_unique, .keep_all = TRUE)
+
+```
+
+###ADM1
+```{r}
+countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2019 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2019.tif")
+
+ggg <- raster(tiff_file)
+ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
+ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
+ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
+ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2019_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
+
+mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')
+
+regions$mean_ggg <- mean_ggg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')
+
+regions$mean_ggg_pop <- mean_ggg_pop
+
+regions$pot_ggg_pop <- mean_ggg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
+  mutate(round=8)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+afro_w8 %<>%
+  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
+  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
+  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))
+
+afro_w8%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
 ```
@@
 ```{r}
-countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
+data_trust_report_adm2 <- readRDS("Data/Data_RDS/data_trust_report_adm2.rds")
+
+countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE")
 #No Botswana, Ivory Coast, Mali ,Togo in 2018
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+data_trust%<>%
+  select(-pot_ggg_pop, -pot_gg_pop, -pot_cvg, -mean_ggg, -mean_ggg_pop, -mean_gg, -mean_gg_pop, -mean_pop.x, mean)
+
+glimpse(data_trust)
+
+data_trust%<>%
+  select(-mean_ggg.x,
+-mean_ggg_pop.x,
+-pot_ggg_pop.x, 
+-mean_pop.x,
+-pot_ggg_pop.y, 
+-mean_ggg_pop.y, 
+-mean_pop.y, 
+-mean_ggg.y)
+
+data_trust%<>%
+  select(
+-mean_gg,
+-mean_gg_pop,
+-pot_gg_pop,
+-pot_cvg)
 
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_ggg_pop_2=pot_ggg_pop,
-         mean_ggg_pop_2=mean_ggg_pop,
-         mean_pop_2=mean_pop,
-         mean_ggg_2=mean_ggg)
-
 data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
@@
 glimpse(data_trust)
-
-data_trust %<>%
-  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
-  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
-  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))
 
@@
 
-```
-
-##2014
-###ADM2
-```{r}
-countries_adm2 <- c("GIN", "LBR", "NER", "KEN","NGA","UGA", "ZWE")
-
-#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2014
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
 
@@
 
-for (country in countries_adm2) {
+for (country in countries_adm1) {
 
   # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
   regions <- st_read(shapefile)
@@
 
-  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2016.tif")
 
@@
 # Lecture du fichier de données
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
 
@@
   rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
+  mutate(round=7)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+data_trust %<>%
+  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
+  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
+  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+##2014
+###ADM2
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("GIN", "LBR", "NER")
+#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2014
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")
+
+ggg <- raster(tiff_file)
+ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
+ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
+ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
+ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
+
+mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')
+
+regions$mean_ggg <- mean_ggg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')
+
+regions$mean_ggg_pop <- mean_ggg_pop
+
+regions$pot_ggg_pop <- mean_ggg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
   select(ISO, NAME_2, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_ggg_pop_2=pot_ggg_pop,
-         mean_ggg_pop_2=mean_ggg_pop,
-         mean_pop_2=mean_pop,
-         mean_ggg_2=mean_ggg)
-
 data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
 
-glimpse(data_trust)
-
 data_trust %<>%
-  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
-  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
-  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))
+  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
+  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
+  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))
 
@@
 
-```
-
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("KEN","NGA","UGA", "ZWE")
+# No Mozambique in 2014
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country,"3G_2014.tif")
+
+ggg <- raster(tiff_file)
+ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
+ggg_wgs84_recode <- calc(ggg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster ggg_wgs84_recode selon les frontières du country
+ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
+ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de ggg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
+
+mean_ggg <- exact_extract(ggg_wgs84_masked, regions, 'mean')
+
+regions$mean_ggg <- mean_ggg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_ggg_pop <- exact_extract(ggg_pop, regions, 'mean')
+
+regions$mean_ggg_pop <- mean_ggg_pop
+
+regions$pot_ggg_pop <- mean_ggg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
+  mutate(round=6)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+data_trust %<>%
+  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
+  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
+  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
 #2G Data
@@
 ```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
 #No Senegal, Togo in 2019
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_gg_pop_2=pot_gg_pop,
-         mean_gg_pop_2=mean_gg_pop,
-         mean_pop_2=mean_pop,
-         mean_gg_2=mean_gg)
-
-data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
-
-glimpse(data_trust)
-
-data_trust %<>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  select(-c(mean_pop_2.x, mean_pop_2.y))
-
-data_trust%<>%
+afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+glimpse(afro_w8)
+
+afro_w8 %<>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  select(-c(mean_pop.x, mean_pop.y))
+
+afro_w8%<>%
   distinct(id_unique, .keep_all = TRUE)
-
-```
-
-##2016
-###ADM2
-
-```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-#No Senegal, Togo in 2016
+```
+
+###ADM1
+```{r}
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
@@
 
-## Etape 1 de Guriev et al.
-
-tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2019 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2019.tif")
 
@@
 
-## Etape 2 de Guriev et al.
-
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2019_1km_UNadj_ASCII_XYZ.csv")
 
@@
 
-## Etape 3 de Guriev et al.
+# Multiplier les valeurs des deux rasters
 gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
 
-## Etape 4 de Guriev et al.
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
 mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
 
-## Etape 5 de Guriev et al.
-mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
-
-## Etape 6 de Guriev et al.
 regions$mean_gg_pop <- mean_gg_pop
-regions$mean_pop <- mean_pop
-
-## Etape 7 de Guriev et al.
+
 regions$pot_gg_pop <- mean_gg_pop/mean_pop
-
-## Moyenne couverture 2G non pondérée par la densité de population
-mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
-regions$mean_gg <- mean_gg
 
@@
   rename(ISO=GID_0)%>%
-  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
-  mutate(round=7)
+  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
+  mutate(round=8)
 
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_gg_pop_2=pot_gg_pop,
-         mean_gg_pop_2=mean_gg_pop,
-         mean_pop_2=mean_pop,
-         mean_gg_2=mean_gg)
-
-data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
-
-glimpse(data_trust)
-
-data_trust %<>%
-  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
-  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
-  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))
-
-data_trust%<>%
+afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+glimpse(afro_w8)
+
+afro_w8 %<>%
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
+
+afro_w8%<>%
   distinct(id_unique, .keep_all = TRUE)
-
-```
-
-##2014
+```
+
+##2016
 ###ADM2
@@
 ```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-#No Senegal, Togo in 2014
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2016
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
 
@@
 
-  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")
+## Etape 1 de Guriev et al.
+
+tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")
 
@@
 
-# Lecture du fichier de données
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+## Etape 2 de Guriev et al.
+
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
 
@@
 
-# Multiplier les valeurs des deux rasters
+## Etape 3 de Guriev et al.
 gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
 
+## Etape 4 de Guriev et al.
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+## Etape 5 de Guriev et al.
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+## Etape 6 de Guriev et al.
+regions$mean_gg_pop <- mean_gg_pop
+regions$mean_pop <- mean_pop
+
+## Etape 7 de Guriev et al.
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+## Moyenne couverture 2G non pondérée par la densité de population
 mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
-
 regions$mean_gg <- mean_gg
-
-mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
-
-regions$mean_pop <- mean_pop
-
-mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
-
-regions$mean_gg_pop <- mean_gg_pop
-
-regions$pot_gg_pop <- mean_gg_pop/mean_pop
 
@@
   select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
-  mutate(round=6)
+  mutate(round=7)
 
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_gg_pop_2=pot_gg_pop,
-         mean_gg_pop_2=mean_gg_pop,
-         mean_pop_2=mean_pop,
-         mean_gg_2=mean_gg)
-
 data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
 
-glimpse(data_trust)
-
 data_trust %<>%
-  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
-  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
-  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  select(-c(mean_pop.x, mean_pop.y))
 
@@
 
-```
-
-##2011
-###ADM2
-
-```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB")
-#No Senegal, Togo in 2011
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
 
@@
 
-  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2016 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2016.tif")
 
@@
 # Lecture du fichier de données
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2016_1km_UNadj_ASCII_XYZ.csv")
 
@@
   rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
+  mutate(round=7)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+data_trust %<>%
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+##2014
+###ADM2
+
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2014
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
+  mutate(round=6)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+data_trust %<>%
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2014 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2014.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2014_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
+  mutate(round=6)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+data_trust %<>%
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+##2011
+###ADM2
+
+```{r}
+data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
+#No Senegal, Togo in 2011
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm2) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
   select(ISO, NAME_2, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
@@
 
-glimpse(accumulated_results)
-
-accumulated_results%<>%
-  rename(pot_gg_pop_2=pot_gg_pop,
-         mean_gg_pop_2=mean_gg_pop,
-         mean_pop_2=mean_pop,
-         mean_gg_2=mean_gg)
-
 data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
 
-glimpse(data_trust)
-
 data_trust %<>%
-  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
-  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
-  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
-  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
-  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
 
@@
 
-```
-
-```{r}
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+###ADM1
+```{r}
+data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
+
+countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB")
+
+data_trust <- readRDS("Data/Data_RDS/data_trust.rds")
+
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+accumulated_results <- data.frame()
+
+for (country in countries_adm1) {
+
+  # Lecture du fichier shapefile
+  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+  tiff_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins_recode/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country,"2G_2011.tif")
+
+gg <- raster(tiff_file)
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
+}
+
+# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
+gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
+gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)
+
+# Lecture du fichier de données
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
+pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+# Vérifier si les résolutions sont les mêmes
+if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
+  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+# Vérifier de nouveau les étendues et les résolutions
+if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+# Multiplier les valeurs des deux rasters
+gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
+
+mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
+
+regions$mean_gg <- mean_gg
+
+mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
+
+regions$mean_pop <- mean_pop
+
+mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
+
+regions$mean_gg_pop <- mean_gg_pop
+
+regions$pot_gg_pop <- mean_gg_pop/mean_pop
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
+  mutate(round=5)
+
+accumulated_results <- rbind(accumulated_results, regions)
+
+}
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
+
+data_trust %<>%
+  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
+  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
+  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
+  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
+  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))
+
 data_trust%<>%
-    mutate(pot_cvg_2=ifelse(is.na(pot_ggg_pop_2), pot_gg_pop_2, pot_ggg_pop_2))
-
-saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
-write_dta(data_trust, "Data/Data_dta/final_df5.dta")
-
-```
+  distinct(id_unique, .keep_all = TRUE)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```
+
+```{r}
+
+data_trust%<>%
+    mutate(mean_cvg=ifelse(is.na(pot_ggg_pop), pot_gg_pop, pot_ggg_pop))
+
+data_trust%<>%
+  rename(pot_cvg=mean_cvg)
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+afro_w8%<>%
+    mutate(mean_cvg=ifelse(is.na(pot_ggg_pop), pot_gg_pop, pot_ggg_pop))
+
+afro_w8%<>%
+  rename(pot_cvg=mean_cvg)
+
+saveRDS(afro_w8, file="Data/Data_RDS/afro_w8.rds")
+
+write_dta(afro_w8, "Data/Data_dta/afro_w8.dta")
+
+```
+
+```{r}
+data_trust_report2<- data_trust_report
+
+paste(names(data_trust_report2), collapse=",")
+
+data_trust_report2%<>%
+  select(coverage2G_r7,coverage_status2G_r7,coverage2G_r6,coverage_status2G_r6,coverage2G_r5,coverage_status2G_r5,coverage3G_r7,coverage_status3G_r7,coverage3G_r6,coverage_status3G_r6,mean_coverage_r7,mean_coverage_r6,mean_coverage_r5,mean_status_r7,mean_status_r6,mean_status_r5, round, id_unique, ISO)
+
+data_trust %<>% left_join(data_trust_report2, by=c("ISO", "id_unique", "round"))
+
+saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")
+
+write_dta(data_trust, "Data/Data_dta/data_trust.dta")
+
+```

### 2025-02-24 script/lightning.Rmd
import folders

```{r}
setwd("~/Working paper/trust/script")
getwd()
```

```{r}
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(ncdf4)
library(sf)
library(raster)
library(exactextractr)
library(rgdal)
library(ggplot2)
```

```{r}
ncpath <- "data/data_raw/"
ncname <- "VHRFC"  
ncfname <- paste(ncpath, ncname, ".nc", sep="")
ncin <- nc_open(ncfname)
print(ncin)

FRD <- ncvar_get(ncin, "VHRFC_LIS_FRD")
dim(FRD)

lon <- ncvar_get(ncin, "Longitude")
lat <- ncvar_get(ncin, "Latitude")

r_FRD <- raster(t(FRD), 
                xmn=min(lon), xmx=max(lon), 
                ymn=min(lat), ymx=max(lat),
                crs=CRS("+proj=longlat +datum=WGS84"))

r_FRD <- flip(r_FRD, direction = "y")

nc_close(ncin)
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
```

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

accumulated_results <- data.frame()

for (country in countries_adm2) {
shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

print(pop)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

pop_wgs84_cropped <- crop(pop_resampled, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

plot(pop_wgs84_masked)

pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

if (!all(res(masked) == res(pop_wgs84_masked))) {
  pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

if (!compareRaster(masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

Lightning_risk <- masked / (1 + pop_resampled)

shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

mean_flash <- exact_extract(masked, regions, 'mean')

regions$mean_flash <- mean_flash

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, mean_flash)

accumulated_results <- rbind(accumulated_results, regions)
}

rounds <- data.frame(round = rep(5:8, each = nrow(accumulated_results)))

expanded_data <- accumulated_results[rep(1:nrow(accumulated_results), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(ISO, NAME_2, round, .keep_all = TRUE)

data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust)

data_trust%>%
  select(mean_flash)%>%
  summary()
```
###ADM1
```{r}
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

accumulated_results <- data.frame()

for (country in countries_adm1) {
shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

print(pop)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

pop_wgs84_cropped <- crop(pop_resampled, extent(country_shp))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

plot(pop_wgs84_masked)

pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

if (!all(res(masked) == res(pop_wgs84_masked))) {
  pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

if (!compareRaster(masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

Lightning_risk <- masked / (1 + pop_resampled)

shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

mean_flash <- exact_extract(masked, regions, 'mean')

regions$mean_flash <- mean_flash

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_flash)

accumulated_results <- rbind(accumulated_results, regions)
}

rounds <- data.frame(round = rep(5:8, each = nrow(accumulated_results)))

expanded_data <- accumulated_results[rep(1:nrow(accumulated_results), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(ISO, NAME_1, round, .keep_all = TRUE)

data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_1", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust)

data_trust %<>%
  mutate(mean_flash = coalesce(mean_flash.x, mean_flash.y))%>%
  select(-c(mean_flash.x, mean_flash.y))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

data_trust%<>%
  mutate(tv=case_when(
    round==5 ~ 1,
    round==6 ~ 2,
    round==7 ~ 3,
    round==8 ~ 4,
  ))
glimpse(data_trust)
```

```{r}
saveRDS(data_trust, file="Data/Data_RDS/data_merge2.rds")
write_dta(data_trust, "Data/Data_dta/data_merge2.dta")
```

```{r}
shapefile_path <- "data/data_raw/gadm/gadm41_BEN_0.shp"

country <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country))) {
  country <- spTransform(country, crs(r_FRD))
}

# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
gg_wgs84_cropped <- crop(r_FRD, extent(country))
gg_wgs84_masked <- mask(gg_wgs84_cropped, country)

dev.off()

plot(gg_wgs84_masked)
```

```{r}
# Lecture du fichier de données
data_file <- paste0("data/data_raw/pop_density/BEN_PD_2011_1km_UNadj_ASCII_XYZ.csv")

pop <- raster(data_file)

print(pop)

pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

print(pop_wgs84)

plot(pop_wgs84)

# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
pop_wgs84_cropped <- crop(pop_wgs84, extent(country))
pop_wgs84_masked <- mask(pop_wgs84_cropped, country)

rm(data_file, pop, pop_wgs84, pop_wgs84_cropped)

# Vérifier si les résolutions sont les mêmes
if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
} else {
  pop_wgs84_resampled <- pop_wgs84_masked
}

rm(pop_wgs84_masked)

# Vérifier de nouveau les étendues et les résolutions
if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
}

# Multiplier les valeurs des deux rasters
gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

# Afficher le raster résultant avec les contours du country
plot(gg_pop, main="Couverture Pondérée par Densité de Population")
plot(country, add=TRUE, border="darkgrey")

graphics.off()

plot(gg_wgs84_masked)
plot(pop_wgs84_resampled)
plot(gg_pop)

```

```{r}

regions <- st_read("data/data_raw/gadm/gadm41_BEN_2.shp")
regions <- st_make_valid(regions)

mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')

regions$mean_gg <- mean_gg

ggplot() +
  geom_sf(data = regions, aes(fill = mean_gg), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Internet Coverage")+
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Internet Coverage ADM2 - Round 8")

mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')

regions$mean_pop <- mean_pop

ggplot() +
  geom_sf(data = regions, aes(fill = mean_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_pop), max(regions$mean_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Population Density ADM2 - Round 7")

mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')

regions$mean_gg_pop <- mean_gg_pop

ggplot() +
  geom_sf(data = regions, aes(fill = mean_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_gg_pop), max(regions$mean_gg_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")

regions$pot_gg_pop <- mean_gg_pop/mean_pop

ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")

```

```{r}
data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_RDS/final_df5.rds")

capitals <- data_final_nlp %>%
  select(caplong, caplat, iso) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

capitals%<>%
  filter(iso=="BEN")%>%
  distinct(iso, .keep_all = TRUE)

ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "black") +
  scale_fill_distiller(palette = "RdPu", direction = 1, name = "Lightning strikes", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = NULL) +
  geom_point(data = capitals, 
             aes(x = longitude, y = latitude), 
             size = 4, shape = 22, fill = "green", show.legend = FALSE)+
  geom_text(aes(x = 2.5, y = 6.2, label = "Porto-Novo"), color = "black", size = 4, fontface="bold") +
    theme_minimal() +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),
    legend.position = c(1 ,0.35),
    plot.title = element_text(hjust = 0.5, size = 5, face = "bold")
  )

ggsave("plots/lightning_strikes/lightning_strikes.jpg", width = 8, height = 6, dpi = 300)

dev.off()
```

### 2025-02-24 script/lightning_adm2.Rmd
import folders

--- 2025-02-24 script/lightning.Rmd
@@
 ```{r}
-setwd("~/Working paper/trust/script")
+setwd("~/Working paper/Trust/Script")
 getwd()
@@
 ```{r}
-ncpath <- "data/data_raw/"
+ncpath <- "data/data_Raw/"
 ncname <- "VHRFC"  
@@
 ```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
@@
 for (country in countries_adm2) {
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_",country,"_0.shp")
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
 
@@
 
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
 
@@
 
-shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_", country,"_2.shp")
+shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
   regions <- st_read(shapefile)
@@
 
+glimpse(expanded_data)
+
+expanded_data%<>%
+  rename(mean_flash_2=mean_flash)
+
 data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_2", "round"))
@@
 data_trust%>%
-  select(mean_flash)%>%
+  select(mean_flash, mean_flash_2)%>%
   summary()
-```
-###ADM1
-```{r}
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
-accumulated_results <- data.frame()
-
-for (country in countries_adm1) {
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(r_FRD), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(r_FRD))
-}
-
-cropped <- crop(r_FRD, extent(country_shp))
-masked <- mask(cropped, country_shp)
-
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
-
-pop <- raster(data_file)
-
-print(pop)
-
-pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
-
-pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")
-
-pop_wgs84_cropped <- crop(pop_resampled, extent(country_shp))
-pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
-
-plot(pop_wgs84_masked)
-
-pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")
-
-if (!all(res(masked) == res(pop_wgs84_masked))) {
-  pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
-} else {
-  pop_wgs84_resampled <- pop_wgs84_masked
-}
-
-if (!compareRaster(masked, pop_wgs84_resampled)) {
-  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
-}
-
-Lightning_risk <- masked / (1 + pop_resampled)
-
-shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-mean_flash <- exact_extract(masked, regions, 'mean')
-
-regions$mean_flash <- mean_flash
-
-regions %<>%
-  as.data.frame()
-
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_1, mean_flash)
-
-accumulated_results <- rbind(accumulated_results, regions)
-}
-
-rounds <- data.frame(round = rep(5:8, each = nrow(accumulated_results)))
-
-expanded_data <- accumulated_results[rep(1:nrow(accumulated_results), times = 4), ]
-
-expanded_data$round <- rounds$round
-
-expanded_data <- expanded_data %>% distinct(ISO, NAME_1, round, .keep_all = TRUE)
-
-data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_1", "round"))
-
-data_trust%<>%
-  distinct(id_unique, .keep_all = TRUE)
-
-glimpse(data_trust)
-
-data_trust %<>%
-  mutate(mean_flash = coalesce(mean_flash.x, mean_flash.y))%>%
-  select(-c(mean_flash.x, mean_flash.y))
-
-data_trust%<>%
-  distinct(id_unique, .keep_all = TRUE)
-
-data_trust%<>%
-  mutate(tv=case_when(
-    round==5 ~ 1,
-    round==6 ~ 2,
-    round==7 ~ 3,
-    round==8 ~ 4,
-  ))
 glimpse(data_trust)
@@
 ```{r}
-saveRDS(data_trust, file="Data/Data_RDS/data_merge2.rds")
-write_dta(data_trust, "Data/Data_dta/data_merge2.dta")
+saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
+write_dta(data_trust, "Data/Data_dta/final_df5.dta")
 ```
@@
 ```{r}
-shapefile_path <- "data/data_raw/gadm/gadm41_BEN_0.shp"
+shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"
 
@@
 # Lecture du fichier de données
-data_file <- paste0("data/data_raw/pop_density/BEN_PD_2011_1km_UNadj_ASCII_XYZ.csv")
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/BEN_pd_2011_1km_UNadj_ASCII_XYZ.csv")
 
@@
 
-regions <- st_read("data/data_raw/gadm/gadm41_BEN_2.shp")
+regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
 regions <- st_make_valid(regions)
@@
 ```{r}
-data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/trust/script/data/data_RDS/final_df5.rds")
+data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/final_df5.rds")
 
-capitals <- data_final_nlp %>%
-  select(caplong, caplat, iso) %>%
+capitals <- data_trust_test %>%
+  select(caplong, caplat, ISO) %>%
   na.omit() %>%
@@
 capitals%<>%
-  filter(iso=="BEN")%>%
-  distinct(iso, .keep_all = TRUE)
+  filter(ISO=="BEN")%>%
+  distinct(ISO, .keep_all = TRUE)
 

### 2025-02-24 script/lightning_cell.Rmd
import folders

--- 2025-02-24 script/lightning_adm2.Rmd
@@
 library(ggplot2)
+library(terra)
 ```
@@
 ```{r}
-data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
-```
-
-###ADM2
-```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+countries <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", 
+               "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", 
+               "ZMB", "ZWE")
 
@@
 
-for (country in countries_adm2) {
+for (country in countries) {
 shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
@@
 
-shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
+data_trust <- readRDS("Data/Data_RDS/data_merge2.rds")
 
-mean_flash <- exact_extract(masked, regions, 'mean')
+data_trust%<>%
+  filter(ISO==country)
 
-regions$mean_flash <- mean_flash
+zones_sf <- st_as_sf(data_trust, coords = c("longitude", "latitude"), crs = 4326)
+eclairs_raster <- rast(Lightning_risk)
 
-regions %<>%
-  as.data.frame()
+eclairs_values <- extract(eclairs_raster, zones_sf)
 
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_2, mean_flash)
+zones_sf$eclairs_count <- eclairs_values
 
-accumulated_results <- rbind(accumulated_results, regions)
+pop_density_values <- extract(pop_resampled, zones_sf)
+
+zones_sf$population_density <- pop_density_values
+
+final_df <- zones_sf
+
+light_cell_vector <- unlist(final_df$light_cell)
+
+light_cell_vector <- final_df$eclairs_count[[2]]
+
+final_df$light_cell <- light_cell_vector
+
+final_df%<>%
+  select(-eclairs_count)
+
+final_df%<>%
+  select(geometry, light_cell, population_density)
+
+accumulated_results <- rbind(accumulated_results, final_df)
 }
 
-rounds <- data.frame(round = rep(5:8, each = nrow(accumulated_results)))
+accumulated_results2 <- accumulated_results
 
-expanded_data <- accumulated_results[rep(1:nrow(accumulated_results), times = 4), ]
+accumulated_results2 %<>% 
+  mutate(longitude = st_coordinates(geometry)[,1],
+         latitude = st_coordinates(geometry)[,2])
 
-expanded_data$round <- rounds$round
+accumulated_results2 %<>%
+  st_drop_geometry()
 
-expanded_data <- expanded_data %>% distinct(ISO, NAME_2, round, .keep_all = TRUE)
+accumulated_results2%<>%
+  distinct(longitude, latitude, .keep_all = TRUE)
 
-glimpse(expanded_data)
+data_trust <- readRDS("Data/Data_RDS/data_merge2.rds")
 
-expanded_data%<>%
-  rename(mean_flash_2=mean_flash)
+data_trust2 <- data_trust
 
-data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_2", "round"))
+data_trust2 %<>% left_join(accumulated_results2, by = c("latitude", "longitude"))
 
-data_trust%<>%
-  distinct(id_unique, .keep_all = TRUE)
+data_trust2%<>%
+  rename(pop_cell=population_density)
 
-glimpse(data_trust)
+glimpse(data_trust2)
 
-data_trust%>%
-  select(mean_flash, mean_flash_2)%>%
-  summary()
-
-glimpse(data_trust)
-```
-
-```{r}
-saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
-write_dta(data_trust, "Data/Data_dta/final_df5.dta")
-```
-
-```{r}
-shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"
-
-country <- readOGR(shapefile_path)
-
-if (!identical(crs(r_FRD), crs(country))) {
-  country <- spTransform(country, crs(r_FRD))
-}
-
-# Recadrer et masquer le raster gg_wgs84_recode selon les frontières du country
-gg_wgs84_cropped <- crop(r_FRD, extent(country))
-gg_wgs84_masked <- mask(gg_wgs84_cropped, country)
-
-dev.off()
-
-plot(gg_wgs84_masked)
-```
-
-```{r}
-# Lecture du fichier de données
-data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/BEN_pd_2011_1km_UNadj_ASCII_XYZ.csv")
-
-pop <- raster(data_file)
-
-print(pop)
-
-pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
-
-print(pop_wgs84)
-
-plot(pop_wgs84)
-
-# Recadrer et masquer le raster pop_wgs84 selon les frontières du country
-pop_wgs84_cropped <- crop(pop_wgs84, extent(country))
-pop_wgs84_masked <- mask(pop_wgs84_cropped, country)
-
-rm(data_file, pop, pop_wgs84, pop_wgs84_cropped)
-
-# Vérifier si les résolutions sont les mêmes
-if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
-  # Ajuster la résolution de pop_wgs84_masked à celle de gg_wgs84_masked
-  pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
-} else {
-  pop_wgs84_resampled <- pop_wgs84_masked
-}
-
-rm(pop_wgs84_masked)
-
-# Vérifier de nouveau les étendues et les résolutions
-if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
-  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
-}
-
-# Multiplier les valeurs des deux rasters
-gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
-
-# Afficher le raster résultant avec les contours du country
-plot(gg_pop, main="Couverture Pondérée par Densité de Population")
-plot(country, add=TRUE, border="darkgrey")
-
-graphics.off()
-
-plot(gg_wgs84_masked)
-plot(pop_wgs84_resampled)
-plot(gg_pop)
+saveRDS(data_trust2, file="Data/Data_RDS/final_df2.rds")
+write_dta(data_trust2, "Data/Data_dta/final_df2.dta")
 
@@
 ```{r}
-
-regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
-regions <- st_make_valid(regions)
-
-mean_gg <- exact_extract(gg_wgs84_masked, regions, 'mean')
-
-regions$mean_gg <- mean_gg
-
-ggplot() +
-  geom_sf(data = regions, aes(fill = mean_gg), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Internet Coverage")+
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
-  labs(title = "Benin - Internet Coverage ADM2 - Round 8")
-
-mean_pop <- exact_extract(pop_wgs84_resampled, regions, 'mean')
-
-regions$mean_pop <- mean_pop
-
-ggplot() +
-  geom_sf(data = regions, aes(fill = mean_pop), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_pop), max(regions$mean_pop)), labels = c(0, 1)) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
-  labs(title = "Benin - Population Density ADM2 - Round 7")
-
-mean_gg_pop <- exact_extract(gg_pop, regions, 'mean')
-
-regions$mean_gg_pop <- mean_gg_pop
-
-ggplot() +
-  geom_sf(data = regions, aes(fill = mean_gg_pop), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$mean_gg_pop), max(regions$mean_gg_pop)), labels = c(0, 1)) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
-  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")
-
-regions$pot_gg_pop <- mean_gg_pop/mean_pop
-
-ggplot() +
-  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "Pop Density", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
-  labs(title = "Benin - Weighted Population Density ADM2 - Round 7")
-
+data_trust <- readRDS("Data/Data_RDS/data_merge2.rds")
 ```
@@
 ```{r}
-data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/final_df5.rds")
+zones_sf <- st_as_sf(data_trust, coords = c("longitude", "latitude"), crs = 4326)
+eclairs_raster <- rast(r_FRD)
 
-capitals <- data_trust_test %>%
-  select(caplong, caplat, ISO) %>%
-  na.omit() %>%
-  rename(longitude = caplong, latitude = caplat)
+#zones_buffer <- st_buffer(zones_sf, dist = 10000)
 
-capitals%<>%
-  filter(ISO=="BEN")%>%
-  distinct(ISO, .keep_all = TRUE)
+eclairs_values <- extract(eclairs_raster, zones_sf)
 
-ggplot() +
-  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "black") +
-  scale_fill_distiller(palette = "RdPu", direction = 1, name = "Lightning strikes", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = NULL) +
-  geom_point(data = capitals, 
-             aes(x = longitude, y = latitude), 
-             size = 4, shape = 22, fill = "green", show.legend = FALSE)+
-  geom_text(aes(x = 2.5, y = 6.2, label = "Porto-Novo"), color = "black", size = 4, fontface="bold") +
-    theme_minimal() +
-  theme(
-    panel.grid.major = element_blank(),  
-    panel.grid.minor = element_blank(),  
-    panel.background = element_blank(),   
-    axis.text = element_blank(),         
-    axis.ticks = element_blank(),         
-    axis.title = element_blank(),
-    legend.position = c(1 ,0.35),
-    plot.title = element_text(hjust = 0.5, size = 5, face = "bold")
-  )
+#eclairs_values <- extract(eclairs_raster, vect(zones_buffer), fun = mean)
 
-ggsave("plots/lightning_strikes/lightning_strikes.jpg", width = 8, height = 6, dpi = 300)
+zones_sf$eclairs_count <- eclairs_values
 
-dev.off()
+final_df <- st_drop_geometry(zones_sf)
+
+light_cell_vector <- unlist(final_df$light_cell)
+
+light_cell_vector <- final_df$eclairs_count[[2]]
+
+final_df$light_cell <- light_cell_vector
+
+final_df%<>%
+  select(-eclairs_count)
+glimpse(final_df)
+
+saveRDS(final_df, file="Data/Data_RDS/final_df.rds")
+write_dta(final_df, "Data/Data_dta/final_df.dta")
+
 ```

### 2025-02-24 script/lightning_no_var.Rmd
import folders

--- 2025-02-24 script/lightning_adm2.Rmd
@@
 ```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
 
@@
 
-glimpse(expanded_data)
-
-expanded_data%<>%
-  rename(mean_flash_2=mean_flash)
-
 data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_2", "round"))
@@
 data_trust%>%
-  select(mean_flash, mean_flash_2)%>%
+  select(mean_flash)%>%
   summary()
+```
+###ADM1
+```{r}
+countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
+accumulated_results <- data.frame()
+
+for (country in countries_adm1) {
+shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
+
+country_shp <- readOGR(shapefile_path)
+
+if (!identical(crs(r_FRD), crs(country_shp))) {
+  country_shp <- spTransform(country_shp, crs(r_FRD))
+}
+
+cropped <- crop(r_FRD, extent(country_shp))
+masked <- mask(cropped, country_shp)
+
+data_file <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/",country,"_pd_2011_1km_UNadj_ASCII_XYZ.csv")
+
+pop <- raster(data_file)
+
+print(pop)
+
+pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
+
+pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")
+
+pop_wgs84_cropped <- crop(pop_resampled, extent(country_shp))
+pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)
+
+plot(pop_wgs84_masked)
+
+pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")
+
+if (!all(res(masked) == res(pop_wgs84_masked))) {
+  pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
+} else {
+  pop_wgs84_resampled <- pop_wgs84_masked
+}
+
+if (!compareRaster(masked, pop_wgs84_resampled)) {
+  stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+}
+
+Lightning_risk <- masked / (1 + pop_resampled)
+
+shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
+  regions <- st_read(shapefile)
+  regions <- st_make_valid(regions)
+
+mean_flash <- exact_extract(masked, regions, 'mean')
+
+regions$mean_flash <- mean_flash
+
+regions %<>%
+  as.data.frame()
+
+regions %<>%
+  rename(ISO=GID_0)%>%
+  select(ISO, NAME_1, mean_flash)
+
+accumulated_results <- rbind(accumulated_results, regions)
+}
+
+rounds <- data.frame(round = rep(5:8, each = nrow(accumulated_results)))
+
+expanded_data <- accumulated_results[rep(1:nrow(accumulated_results), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(ISO, NAME_1, round, .keep_all = TRUE)
+
+data_trust %<>% left_join(expanded_data, by=c("ISO", "NAME_1", "round"))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+glimpse(data_trust)
+
+data_trust %<>%
+  mutate(mean_flash = coalesce(mean_flash.x, mean_flash.y))%>%
+  select(-c(mean_flash.x, mean_flash.y))
+
+data_trust%<>%
+  distinct(id_unique, .keep_all = TRUE)
+
+data_trust%<>%
+  mutate(tv=case_when(
+    round==5 ~ 1,
+    round==6 ~ 2,
+    round==7 ~ 3,
+    round==8 ~ 4,
+  ))
 glimpse(data_trust)
@@
 ```{r}
-saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
-write_dta(data_trust, "Data/Data_dta/final_df5.dta")
+saveRDS(data_trust, file="Data/Data_RDS/data_merge2.rds")
+write_dta(data_trust, "Data/Data_dta/data_merge2.dta")
+```
+
+```{r}
+tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/collins/Mobile Coverage Explorer v2011 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_BJ2G_2011.tif"
+```
+
+```{r}
+gg <- raster(tiff_file)
+
+print(gg)
+
+gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
+
+print(gg_wgs84)
+```
+
+```{r}
+rc <- function(x) {
+  ifelse(is.na(x), 0,
+         ifelse(x < 1, 0,
+                ifelse(x >= 1, 1, NA)))
+}
+
+gg_wgs84_recode <- calc(gg_wgs84, fun=rc)
+
+plot(gg_wgs84_recode)
+
+rm(coords, gg, gg_wgs84, values, rc, tiff_file)
 ```
@@
 gg_wgs84_masked <- mask(gg_wgs84_cropped, country)
+
+rm(shapefile_path, gg_wgs84_recode, gg_wgs84_cropped)
 
@@
 
+png("plots/gg_pop/no_pop_weighting.png", width = 800, height = 600)
+
+#Avant
+ggplot() +
+  geom_sf(data = regions, aes(fill = mean_gg), color = "white") +
+  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$mean_gg), max(regions$mean_gg)), labels = c(0, 1)) +
+  theme_minimal() +
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
+  labs(title = "No Population Weighting")
+
+dev.off()
+
+#Après
+png("plots/gg_pop/pop_weighted.png", width = 800, height = 600, dpi=300)
+
 ggplot() +

### 2025-02-24 script/nighttime.Rmd
import folders

```{r}
setwd("~/Working paper/Trust/Script")
getwd()
```

```{r}
library(raster)
library(rgdal)
library(dplyr)
library(magrittr)
library(sf)
library(exactextractr)
library(ggplot2)
library(haven)
```

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"
```

```{r}
night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

print(night_wgs84)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

```{r}
shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"

country <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country))) {
  country <- spTransform(country, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country))
night_wgs84_masked <- mask(night_wgs84_cropped, country)

rm(shapefile_path, night_wgs84_cropped)

dev.off()

plot(night_wgs84_masked)
```

```{r}
library(exactextractr)
library(scales)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
regions <- st_make_valid(regions)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

png("plots/ntl/test2.png", width = 800, height = 600)

ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - NTL ADM2 - Round 7")

dev.off()

```

#NTL Maps
##2016
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2

```{r}

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)

}

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)

}

```

##2014
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2014.tif"

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)

}

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)

}

```

##2011
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2011.tif"

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2

```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==5)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

labels = label_number(accuracy = 0.01)

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)

}

```

###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night_log <- log(mean_night+1)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==5)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)

}
```

#Data

##2019

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2019.tif"

night_wgs84 <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, mean_night, mean_night_log)%>%
  mutate(round=8)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test%<>%
  select(-c("mean_night", "mean_night_log"))

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust_test)

data_trust_test%>%
  select(mean_night, ISO, round)%>%
  filter(!is.na(mean_night))%>%
  View()

```
###ADM1
```{r}
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

accumulated_results <- data.frame()

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=8)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)
```

##2016

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"

night_wgs84 <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2
```{r}

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, mean_night, mean_night_log)%>%
  mutate(round=7)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

accumulated_results <- data.frame()

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=7)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2014
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2014.tif"

night_wgs84 <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, mean_night, mean_night_log)%>%
  mutate(round=6)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

accumulated_results <- data.frame()

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=6)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```

##2011

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2011.tif"

night_wgs84 <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

values(night_wgs84)[values(night_wgs84) < 0] <- 0

```

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

accumulated_results <- data.frame()

for (country in countries_adm2) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_2, mean_night, mean_night_log)%>%
  mutate(round=5)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust_test)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

accumulated_results <- data.frame()

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')

regions$mean_night <- mean_night

regions$mean_night_log <- log(mean_night+1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=5)

accumulated_results <- rbind(accumulated_results, regions)

}

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```

```{r}
saveRDS(data_trust_test, file="Data/Data_RDS/data_trust_test_report2.rds")

write_dta(data_trust_test, "Data/Data_dta/data_trust_test_report2.dta")

```

### 2025-02-24 script/nighttime_adm2.Rmd
import folders

--- 2025-02-24 script/nighttime.Rmd
@@
 
-```{r}
-tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"
-```
-
-```{r}
-night <- raster(tiff_file)
-
-print(night)
-
-night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
-
-print(night_wgs84)
-
-values(night_wgs84)[values(night_wgs84) < 0] <- 0
-
-```
-
-```{r}
-shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"
-
-country <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country))) {
-  country <- spTransform(country, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country))
-night_wgs84_masked <- mask(night_wgs84_cropped, country)
-
-rm(shapefile_path, night_wgs84_cropped)
-
-dev.off()
-
-plot(night_wgs84_masked)
-```
-
-```{r}
-library(exactextractr)
-library(scales)
-
-regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
-regions <- st_make_valid(regions)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night <- mean_night
-
-regions$mean_night_log <- log(mean_night+1)
-
-png("plots/ntl/test2.png", width = 800, height = 600)
-
-ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
-  labs(title = "Benin - NTL ADM2 - Round 7")
-
-dev.off()
-
-```
-
-#NTL Maps
-##2016
-```{r}
-tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"
-
-night <- raster(tiff_file)
-
-print(night)
-
-night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
-
-values(night_wgs84)[values(night_wgs84) < 0] <- 0
-
-```
-
-###ADM2
-
-```{r}
-
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm2) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm2_valid %>%
-  filter(ISO == country, round==7)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM2 - Round 7", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)
-
-}
-
-```
-###ADM1
-```{r}
-
-countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm1_valid %>%
-  filter(ISO == country, round==7)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM1 - Round 7", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)
-
-}
-
-```
-
-##2014
-```{r}
-tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2014.tif"
-
-night <- raster(tiff_file)
-
-print(night)
-
-night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
-
-values(night_wgs84)[values(night_wgs84) < 0] <- 0
-
-```
-
-###ADM2
-```{r}
-data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
-
-countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm2) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84 selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm2_valid %>%
-  filter(ISO == country, round==6)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM2 - Round 6", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)
-
-}
-
-```
-###ADM1
-```{r}
-
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84 selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm1_valid %>%
-  filter(ISO == country, round==6)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM1 - Round 6", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)
-
-}
-
-```
-
-##2011
-```{r}
-tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2011.tif"
-
-night <- raster(tiff_file)
-
-print(night)
-
-night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
-
-values(night_wgs84)[values(night_wgs84) < 0] <- 0
-
-```
-
-###ADM2
-
-```{r}
-data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")
-
-countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm2) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84 selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm2_valid %>%
-  filter(ISO == country, round==5)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-labels = label_number(accuracy = 0.01)
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM2 - Round 5", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)
-
-}
-
-```
-
-###ADM1
-```{r}
-
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84 selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night_log <- log(mean_night+1)
-
-panel_sf <- data_trust_report_adm1_valid %>%
-  filter(ISO == country, round==5)
-
-panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))
-
-plot <- ggplot() +
-  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
-  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
-    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
-  theme_minimal() +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
-  labs(title = paste(country, "- NTL ADM1 - Round 5", sep = " "))
-
-  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)
-
-}
-```
-
 #Data
@@
 
-print(night)
+#print(night)
 
-night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
+#night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))
 
@@
 
-```
-
-###ADM2
-```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO","GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
@@
 
-data_trust_test%<>%
-  select(-c("mean_night", "mean_night_log"))
+accumulated_results%<>%
+  rename(mean_night_2=mean_night,
+         mean_night_log_2=mean_night_log)
 
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+glimpse(accumulated_results)
 
-data_trust_test%<>%
+data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
+
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+data_trust%<>%
   distinct(id_unique, .keep_all = TRUE)
 
-glimpse(data_trust_test)
-
-data_trust_test%>%
-  select(mean_night, ISO, round)%>%
-  filter(!is.na(mean_night))%>%
-  View()
-
-```
-###ADM1
-```{r}
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-accumulated_results <- data.frame()
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night <- mean_night
-
-regions$mean_night_log <- log(mean_night+1)
-
-regions %<>%
-  as.data.frame()
-
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_1, mean_night, mean_night_log)%>%
-  mutate(round=8)
-
-accumulated_results <- rbind(accumulated_results, regions)
-
-}
-
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
-
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
-
-data_trust_test%<>%
-  distinct(id_unique, .keep_all = TRUE)
+glimpse(data_trust)
 ```
@@
 
-```
-
-###ADM2
-```{r}
-
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
@@
 
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+accumulated_results%<>%
+  rename(mean_night_2=mean_night,
+         mean_night_log_2=mean_night_log)
 
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
+glimpse(accumulated_results)
 
-data_trust_test%<>%
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+data_trust%<>%
   distinct(id_unique, .keep_all = TRUE)
 
-```
-###ADM1
-```{r}
+data_trust %<>%
+  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
+  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
+  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))
 
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-accumulated_results <- data.frame()
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night <- mean_night
-
-regions$mean_night_log <- log(mean_night+1)
-
-regions %<>%
-  as.data.frame()
-
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_1, mean_night, mean_night_log)%>%
-  mutate(round=7)
-
-accumulated_results <- rbind(accumulated_results, regions)
-
-}
-
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
-
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
-
-data_trust_test%<>%
-  distinct(id_unique, .keep_all = TRUE)
+glimpse(data_trust)
 
@@
 
-```
-
-###ADM2
-```{r}
-countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
 
@@
 
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+accumulated_results%<>%
+  rename(mean_night_2=mean_night,
+         mean_night_log_2=mean_night_log)
 
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
+glimpse(accumulated_results)
 
-data_trust_test%<>%
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+data_trust%<>%
   distinct(id_unique, .keep_all = TRUE)
 
-```
-###ADM1
-```{r}
+data_trust %<>%
+  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
+  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
+  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))
 
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-accumulated_results <- data.frame()
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night <- mean_night
-
-regions$mean_night_log <- log(mean_night+1)
-
-regions %<>%
-  as.data.frame()
-
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_1, mean_night, mean_night_log)%>%
-  mutate(round=6)
-
-accumulated_results <- rbind(accumulated_results, regions)
-
-}
-
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
-
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
-
-data_trust_test%<>%
-  distinct(id_unique, .keep_all = TRUE)
-
+glimpse(data_trust)
 ```
@@
 
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+accumulated_results%<>%
+  rename(mean_night_2=mean_night,
+         mean_night_log_2=mean_night_log)
 
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
+glimpse(accumulated_results)
 
-data_trust_test%<>%
+data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))
+
+data_trust%<>%
   distinct(id_unique, .keep_all = TRUE)
 
-glimpse(data_trust_test)
+data_trust %<>%
+  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
+  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
+  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))
 
-```
-###ADM1
-```{r}
-
-countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
-
-accumulated_results <- data.frame()
-
-for (country in countries_adm1) {
-
-  # Lecture du fichier shapefile
-  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
-  regions <- st_read(shapefile)
-  regions <- st_make_valid(regions)
-
-shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_",country,"_0.shp")
-
-country_shp <- readOGR(shapefile_path)
-
-if (!identical(crs(night_wgs84), crs(country_shp))) {
-  country_shp <- spTransform(country_shp, crs(night_wgs84))
-}
-
-# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
-night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
-night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)
-
-mean_night <- exact_extract(night_wgs84_masked, regions, 'mean')
-
-regions$mean_night <- mean_night
-
-regions$mean_night_log <- log(mean_night+1)
-
-regions %<>%
-  as.data.frame()
-
-regions %<>%
-  rename(ISO=GID_0)%>%
-  select(ISO, NAME_1, mean_night, mean_night_log)%>%
-  mutate(round=5)
-
-accumulated_results <- rbind(accumulated_results, regions)
-
-}
-
-data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))
-
-data_trust_test %<>%
-  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
-  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
-  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))
-
-data_trust_test%<>%
-  distinct(id_unique, .keep_all = TRUE)
+glimpse(data_trust)
 
@@
 ```{r}
-saveRDS(data_trust_test, file="Data/Data_RDS/data_trust_test_report2.rds")
-
-write_dta(data_trust_test, "Data/Data_dta/data_trust_test_report2.dta")
-
+saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
+write_dta(data_trust, "Data/Data_dta/final_df5.dta")
 ```

### 2025-02-24 script/president.Rmd
import folders

```{r}
setwd("~/Working paper/Trust/Script")
getwd()
```

```{r}
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(ncdf4)
library(sf)
library(rgdal)
library(ggplot2)
```

```{r}
data_president <- read_xlsx("Data/Data_raw/data_president.xlsx")
data_president%<>%
  filter(!is.na(date_of_election))
```

```{r}
data_trust <- readRDS("Data/Data_RDS/final_df5.rds")
```

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
```

```{r}
# Charger les bibliothèques nécessaires
library(sf)
library(dplyr)

# Initialiser un DataFrame pour stocker les résultats
results <- data.frame()

# Boucle sur chaque combinaison unique de pays (ISO) et de période (round)
for (i in 1:nrow(unique_combinations)) {

  # Sélectionner le pays et le round actuels
  ISO <- unique_combinations$ISO[i]
  round <- unique_combinations$round[i]

  # Filtrer les données des présidents pour le pays et la période (round) actuels
  data_filtered <- data_president %>%
    filter(ISO == !!ISO, round == !!round)

  # Si le filtrage ne retourne aucune ligne, passer à la prochaine itération
  if (nrow(data_filtered) == 0) {
    warning(paste("Pas de données pour le pays", ISO, "et la période", round))
    next
  }

  # Générer le chemin du shapefile pour le pays actuel
  shapefile_path <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", ISO, "_2.shp")

  # Vérifier si le fichier existe
  if (file.exists(shapefile_path)) {
    # Lire le shapefile et corriger les géométries si nécessaire
    regions_sf <- st_read(shapefile_path)
    regions_sf <- st_make_valid(regions_sf)

    # Convertir les lieux de naissance des présidents en objet spatial (sf)
    presidents_sf <- st_as_sf(data_filtered, coords = c("long_nais", "lat_nais"), crs = 4326)

    # Joindre les lieux de naissance aux régions pour identifier la région
    presidents_with_region <- st_join(presidents_sf, regions_sf, join = st_within)

    # Ajouter les colonnes pour le pays et le round dans les résultats
    presidents_with_region$ISO <- ISO
    presidents_with_region$round <- round

    # Ajouter les résultats pour cette combinaison au DataFrame final
    results <- rbind(results, presidents_with_region)

  } else {
    # Message d'avertissement si le shapefile du pays est manquant
    warning(paste("Shapefile pour le pays", ISO, "n'existe pas dans le chemin spécifié."))
  }
}

results%<>%
  select(ISO, round, NAME_1, NAME_2)

results%<>%
  select(-geometry)

results%<>%
  rename(NAME_2_pres=NAME_2,
         NAME_1_pres=NAME_1)

data_trust %<>% left_join(results, by=c("ISO", "round"))

data_trust %<>%
  mutate(pres_adm2=ifelse(NAME_2_pres==NAME_2, 1, 0))

data_trust %<>%
  mutate(pres_adm1=ifelse(NAME_1_pres==NAME_1, 1, 0))

saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")

```

### 2025-02-24 script/script superficie.Rmd
import folders

```{r}
setwd("~/Working paper/Trust/Script")
getwd()
```

```{r}
library(raster)
library(dplyr)
library(magrittr)
library(sf)
library(exactextractr)
library(ggplot2)
library(haven)
library(terra)
library(rnaturalearth)
library(haven)

```

```{r}
final_df5 <- readRDS("Data/Data_RDS/final_df5.rds")

data_keep <- subset(final_df5, select = c("id_unique","latitude","longitude"))
data_keep_sf <- st_as_sf(data_keep, coords = c("longitude", "latitude"), crs = 4326)

remove(final_df5,data_keep)
```

```{r, adm0}
countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

all_regions_0 <- list()

for (country in countries) {

  shapefile_0 <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country, "_0.shp")

  if (file.exists(shapefile_0)) {
    regions_0 <- st_read(shapefile_0, quiet = TRUE)
    regions_0 <- st_make_valid(regions_0)

    if (is.na(st_crs(regions_0))) {
      regions_0 <- st_set_crs(regions_0, 4326)
    }

    regions_0$country_code <- country
    regions_0$area_0_km2 <- as.numeric(st_area(regions_0)) / 10^6

    all_regions_0[[country]] <- regions_0
  } else {
    message("Fichier manquant pour ", country)
  }
}

df_regions_0 <- do.call(rbind, all_regions_0)
df_regions_0 <- st_make_valid(df_regions_0)

df_regions_0 <- st_transform(df_regions_0, crs = st_crs(data_keep_sf))

data_keep_sf_0 <- st_join(data_keep_sf, df_regions_0[, c("country_code", "area_0_km2")], join = st_intersects)

data_keep_sf_0%>%
  distinct(country_code, .keep_all = TRUE)%>%
  View()
```

```{r, adm1}
countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

all_regions_1 <- list()

for (country in countries) {

  shapefile_1 <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country, "_1.shp")

  if (file.exists(shapefile_1)) {
    regions_1 <- st_read(shapefile_1, quiet = TRUE)
    regions_1 <- st_make_valid(regions_1)

    if (is.na(st_crs(regions_1))) {
      regions_1 <- st_set_crs(regions_1, 4326)
    }

    regions_1$country_code <- country
    regions_1$area_1_km2 <- as.numeric(st_area(regions_1)) / 10^6

    all_regions_1[[country]] <- regions_1
  } else {
    message("Fichier manquant pour ", country)
  }
}

df_regions_1 <- do.call(rbind, all_regions_1)
df_regions_1 <- st_make_valid(df_regions_1)

df_regions_1 <- st_transform(df_regions_1, crs = st_crs(data_keep_sf))

data_keep_sf_1 <- st_join(data_keep_sf_0, df_regions_1[, c("country_code", "area_1_km2")], join = st_intersects)

```

```{r}
countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

all_regions_2 <- list()

for (country in countries) {

  shapefile_2 <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country, "_2.shp")

  if (file.exists(shapefile_2)) {
    regions_2 <- st_read(shapefile_2, quiet = TRUE)
    regions_2 <- st_make_valid(regions_2)

    if (is.na(st_crs(regions_2))) {
      regions_2 <- st_set_crs(regions_2, 4326)
    }

    regions_2$country_code <- country
    regions_2$area_2_km2 <- as.numeric(st_area(regions_2)) / 10^6

    all_regions_2[[country]] <- regions_2
  } else {
    message("Fichier manquant pour ", country)
  }
}

df_regions_2 <- do.call(rbind, all_regions_2)
df_regions_2 <- st_make_valid(df_regions_2)

df_regions_2 <- st_transform(df_regions_2, crs = st_crs(data_keep_sf))

data_keep_sf_2 <- st_join(data_keep_sf_1, df_regions_2[, c("country_code", "area_2_km2")], join = st_intersects)

data_superficie <- st_drop_geometry(data_keep_sf_2)
data_superficie <- subset(data_superficie, select=c("id_unique","country_code","area_0_km2","area_1_km2","area_2_km2"))

remove(all_regions_2, regions_2, country, df_regions_2, shapefile_2, countries, data_keep_sf_1, data_keep_sf_2)

saveRDS(data_superficie, file="Data/Data_RDS/data_area.rds")
write_dta(data_superficie, "Data/Data_dta/data_area.dta")

data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust %<>% left_join(data_superficie, by="id_unique")
glimpse(data_trust)

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")

```

```{r, adm2}
Sys.setenv(SHAPE_RESTORE_SHX = "YES")
countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

all_regions_2 <- list()

for (country in countries) {

  shapefile_2 <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_2.shp")

  if (file.exists(shapefile_2)) {
    regions_2 <- st_read(shapefile_2, quiet = TRUE)
    regions_2 <- st_make_valid(regions_2)

    if (is.na(st_crs(regions_2))) {
      regions_2 <- st_set_crs(regions_2, 4326)  # Définir le CRS à EPSG:4326
    }

    regions_2 <- st_transform(regions_2, crs = 32630)

    regions_2$country_code <- country

    regions_2$area_2_km2 <- as.numeric(st_area(regions_2)) / 10^6

      all_regions_2[[country]] <- regions_2
  } else {
    message("Fichier manquant pour ", country)
  }
}

df_regions_2 <- do.call(rbind, all_regions_2)

df_regions_2 <- st_make_valid(df_regions_2)

df_regions_2 <- st_transform(df_regions_2, crs = st_crs(data_keep_sf_1))

data_keep_sf_2 <- st_join(data_keep_sf_1, df_regions_2[, c("country_code", "area_2_km2")], join = st_intersects)

data_superficie <- st_drop_geometry(data_keep_sf_2)
data_superficie <- subset(data_superficie, select=c("id_unique","country_code","area_0_km2","area_1_km2","area_2_km2"))

remove(all_regions_2, regions_2, country, df_regions_2, shapefile_2, countries, data_keep_sf_1, data_keep_sf_2)

saveRDS(data_superficie, file="Data/Data_RDS/data_area.rds")
write_dta(data_superficie, "Data/Data_dta/data_area.dta")

data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust %<>% left_join(data_superficie, by="id_unique")

data_trust%<>%
  select(-country_code)

glimpse(data_trust)

data_trust%<>%
  mutate(area_region=case_when(
    ISO%in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")~area_2_km2,
    ISO%in%c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")~area_1_km2
  ))

data_trust%<>%
  mutate(area_region_log=log(1+area_region))

data_trust%>%
  select(area_region, area_region_log)%>%
  summary()

saveRDS(data_trust, file="Data/Data_RDS/final_df6.rds")
write_dta(data_trust, "Data/Data_dta/final_df6.dta")

data_trust%>%
distinct(ISO, .keep_all = TRUE)%>%
  select(ISO, area_0_km2)%>%
View()
```

### 2025-02-24 script/tests.Rmd
import folders

```{r}
load("C:/Users/Redha CHABA/Desktop/clea_lc_20240419.RData")

clea <- clea_lc_20240419

names(clea)

clea%<>%
  filter(rg=="Africa")

clea%>%
  distinct(ctr_n)%>%
  arrange(ctr_n)%>%
  View()

clea%>%
  distinct(ctr_n)%>%
  arrange(ctr_n)%>%
  filter(ctr_n%in%countries)%>%
  View()

clea%>%
  distinct(ctr_n, yr, cst_n, .keep_all = TRUE)%>%
  arrange(ctr_n, yr, cst_n )%>%
  filter(between(yr, 2011, 2018))%>%
  filter(ctr_n%in%countries)%>%
  filter(to1!=-990.0000000)%>%
  distinct(ctr_n, .keep_all = TRUE)%>%
  View()

clea%>%
  filter(ctr_n=="Nigeria")%>%
  distinct(yr)%>%
  View()

data_trust%>%
  distinct(ISO)%>%
print(n=25)

countries <- c("Benin", "Burkina Faso", "Botswana", "Cameroon", "Ivory Coast", 
               "Ghana", "Guinea", "Kenya", "Liberia", "Mali", 
               "Malawi", "Mozambique", "Namibia", "Niger", "Nigeria", 
               "Sierra Leone", "Tanzania", "Uganda", "Zambia", "Zimbabwe")

```

```{r}
afro_w7$DATEINTR <- trimws(afro_w7$DATEINTR)

afro_w7%>%select(DATEINTR)%>%count(DATEINTR)%>%print(n=2000)

afro_w6$dateintr <- trimws(afro_w6$dateintr)

afro_w6%>%select(dateintr)%>%arrange(dateintr)%>%count(dateintr)

afro_w5$dateintr <- trimws(afro_w5$dateintr)

afro_w5%>%select(dateintr)%>%arrange(dateintr)%>%count(dateintr)

```

```{r}

afro_w7%>%
  group_by(COUNTRY)%>%
  count(EANUMB_AB)%>%
  View()

afro_w7$COUNTRY

```

```{r}
afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")
countries <- data_trust %>% distinct(ISO) %>% pull(ISO)

afro_w8%<>%
mutate(ISO = case_when(
    COUNTRY == 2  ~ "AGO",
    COUNTRY == 3  ~ "BEN",
    COUNTRY == 4  ~ "BWA",
    COUNTRY == 5  ~ "BFA",
    COUNTRY == 6  ~ "CPV",
    COUNTRY == 7  ~ "CMR",
    COUNTRY == 8  ~ "CIV",
    COUNTRY == 9  ~ "SWZ",
    COUNTRY == 10 ~ "ETH",
    COUNTRY == 11 ~ "GAB",
    COUNTRY == 12 ~ "GMB",
    COUNTRY == 13 ~ "GHA",
    COUNTRY == 14 ~ "GIN",
    COUNTRY == 15 ~ "KEN",
    COUNTRY == 16 ~ "LSO",
    COUNTRY == 17 ~ "LBR",
    COUNTRY == 19 ~ "MWI",
    COUNTRY == 20 ~ "MLI",
    COUNTRY == 21 ~ "MUS",
    COUNTRY == 22 ~ "MAR",
    COUNTRY == 23 ~ "MOZ",
    COUNTRY == 24 ~ "NAM",
    COUNTRY == 25 ~ "NER",
    COUNTRY == 26 ~ "NGA",
    COUNTRY == 28 ~ "SEN",
    COUNTRY == 29 ~ "SLE",
    COUNTRY == 30 ~ "ZAF",
    COUNTRY == 31 ~ "SDN",
    COUNTRY == 32 ~ "TZA",
    COUNTRY == 33 ~ "TGO",
    COUNTRY == 34 ~ "TUN",
    COUNTRY == 35 ~ "UGA",
    COUNTRY == 36 ~ "ZMB",
    COUNTRY == 37 ~ "ZWE",
    TRUE ~ NA_character_
  ))

afro_w8%<>%
  filter(ISO%in%countries)

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  mutate(round=rep(8, times = length("RESPNO")))%>%
  mutate(id=RESPNO)%>%
  mutate(id_unique=paste0(id,round))

afro_w8%<>%
rename(latitude=EA_GPS_LA,
       longitude=EA_GPS_LO,
       age=Q1,
       sex=Q101,
       rural=URBRUR,
       feelnat=Q82B,
       internet_use=Q92I,
       tele_pos=Q92B,
       internet_news=Q55D,
       tele_news=Q55B,
       radio_news=Q55A,
       journal_news=Q55C,
       sm_news=Q55E,
       prob=Q11B,
       commu=Q11A,
       corr_pres=Q42A,
       corr_dep=Q42B,
       corr_juge=Q42F,
       corr_local=Q42D,
       corr_level=Q43A,
       vote=Q13,
       trust_govpart=Q41E,
       trust_opppart=Q41F,
       perf_pres=Q51A,
       perf_mp=Q51B,
       perf_local=Q51C,
       perf_country=Q6A,
       trust_local=Q41D,
       trust_parl=Q41B,
       trust_pres=Q41A,
       trust_elec=Q41C,
       protest=Q11C,
       pref_demo=Q21,
       satis_demo=Q37,
       educ=Q97,
       emp=Q95A,
       disc_pol=Q9,
       extent=Q36,
       elec_fair=Q14,
       trust_trad=Q41K,
       corr_trad=Q42H,
       one_man=Q20C,
       one_party=Q20A,
       military=Q20B)

afro_w8%<>%
  select(ISO, round, id_unique,
         latitude, longitude, age, sex, rural, feelnat, internet_use, tele_pos, internet_news, tele_news,
         radio_news, journal_news, sm_news, prob, commu, corr_pres, corr_dep, corr_juge, corr_local, 
         corr_level, vote, trust_govpart, trust_opppart, perf_pres, perf_mp, perf_local, perf_country, 
         trust_local, trust_parl, trust_pres, trust_elec, protest, pref_demo, satis_demo, 
         educ, emp, disc_pol, extent, elec_fair, trust_trad, corr_trad, one_man, one_party, military)

country_var <- read_excel("Data/Data_Raw/country_var.xlsx")
gdppc <- read_excel("Data/Data_Raw/gdppc.xls")
population <- read_excel("Data/Data_Raw/pop.xls")
surface <- read_excel("Data/Data_Raw/surface.xls")
corr_index <- read_excel("Data/Data_Raw/corr_index.xlsx")

vdem <- readRDS("Data/Data_Raw/V-Dem-CY-Full+Others-v13.rds")
juriglobe <- read_excel("Data/Data_Raw/FR_index.xlsx")
cities <- read_excel("Data/Data_Raw/cities.xlsx")

country_var <-inner_join(country_var, corr_index, by ="ISO")%>%
  inner_join(gdppc, by="ISO")%>%
  inner_join(population, by="ISO")%>%
  inner_join(surface, by="ISO")

country_var%<>%
  select(ISO,cor2019_,gdpcap2019_, pop2019_, superficie2019_)

afro_w8 <- left_join(afro_w8, country_var, by = "ISO")

afro_w8%<>%
  rename(corr_index=cor2019_,
         gdppc=gdpcap2019_,
         area=superficie2019_,
         population=pop2019_)

afro_w8%<>%
  mutate(population=as.numeric(population) / 100000)%>%
  mutate(area=as.numeric(area) / 100)

afro_w8 <- left_join(afro_w8, cities, by = "ISO")

qog <- read.csv("Data/Data_raw/qog_std_ts_jan24.csv")

qog %<>%
  filter(year==2019)

countries <- unique(data_trust$ISO)

qog%<>%
  filter(ccodealp %in% countries)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(ISO=ccodealp, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)

qog%<>%
  rename(round=year)%>%
  mutate(round=8)

afro_w8 %<>% left_join(qog, by=c("ISO", "round"))

variables_to_process <- c("rural", "feelnat", "internet_use", "tele_pos", "internet_news", "tele_news",
         "radio_news", "journal_news", "sm_news", "prob", "commu", "corr_pres", "corr_dep", "corr_juge", "corr_local", 
         "corr_level", "vote", "trust_govpart", "trust_opppart", "perf_pres", "perf_mp", "perf_local", "perf_country", 
         "trust_local", "trust_parl", "trust_pres", "trust_elec", "protest", "pref_demo", "satis_demo",
         "emp", "disc_pol", "extent", "elec_fair", "trust_trad", "corr_trad", "one_man", "one_party", "military")

afro_w8 %<>%
  mutate(across(all_of(variables_to_process), 
                ~na_if(.x, 9) %>% na_if(-1) %>% na_if(8) %>% na_if(998) %>% na_if(460) %>% na_if(99) %>% na_if(997)%>% na_if(98) %>% na_if(1340)%>% na_if(9997) %>% na_if(9999) %>% na_if(9995) %>% na_if(9998)))

afro_w8%<>%
  mutate(educ=na_if(educ, 99))%>%
  mutate(educ=na_if(educ, -1))%>%
  mutate(educ=na_if(educ, 98))%>%
  mutate(feelnat=na_if(feelnat,7))

afro_w8%<>%
    mutate(rural = ifelse(rural == 3, 1, rural))

table_ccode<- data_trust%>%
  select(ISO, ccode)%>%
  distinct(ccode, .keep_all = TRUE)

afro_w8<- left_join(afro_w8, table_ccode, by="ISO")

afro_w8%<>%
  mutate(country_round=paste0(round,ccode))

afro_w8 %<>%
   mutate(pref_demo_simple=ifelse(pref_demo==3, 1, 0))%>%
  mutate(pref_demo_strict=ifelse(pref_demo==3 & one_party==1|one_party==2 & military==1|military==2 & one_man==1|one_man==2, 1, 0))%>%
   mutate(pref_demo_strict2=ifelse(pref_demo==3 & one_party==1 & military==1 & one_man==1, 1, 0))

rm(surface, population, juriglobe, gdppc, corr_index, cities, table_ccode, country_var, qog)

afro_w8%>%
  select(age)%>%
  summary()

glimpse(afro_w8)
```

```{r}
data_trust <- readRDS("Data/Data_RDS/data_trust_report2.rds")
afro_w8 <- readRDS("Data/Data_RDS/afro_w8.rds")

is_convertible_to_numeric <- function(column) {
  suppressWarnings(!any(is.na(as.numeric(as.character(column)))))
}

for (col in intersect(names(data_trust), names(afro_w8))) {
  if (is_convertible_to_numeric(data_trust[[col]]) && is_convertible_to_numeric(afro_w8[[col]])) {
    data_trust[[col]] <- as.numeric(as.character(data_trust[[col]]))
    afro_w8[[col]] <- as.numeric(as.character(afro_w8[[col]]))
  } else {
    data_trust[[col]] <- as.character(data_trust[[col]])
    afro_w8[[col]] <- as.character(afro_w8[[col]])
  }
}

data_trust_test <- bind_rows(data_trust, afro_w8)

library(tidyr)

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(presidential = ifelse(is.na(presidential), NA, presidential)) %>%
  ungroup() %>%
  fill(presidential, .direction = "updown")

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(parlementarian = ifelse(is.na(parlementarian), NA, parlementarian)) %>%
  ungroup() %>%
  fill(parlementarian, .direction = "updown")

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(semi_presidential = ifelse(is.na(semi_presidential), NA, semi_presidential)) %>%
  ungroup() %>%
  fill(semi_presidential, .direction = "updown")

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(monarchical = ifelse(is.na(monarchical), NA, monarchical)) %>%
  ungroup() %>%
  fill(monarchical, .direction = "updown")

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(gov_type = ifelse(is.na(gov_type), NA, gov_type)) %>%
  ungroup() %>%
  fill(gov_type, .direction = "updown")

data_trust_test%>%
  select(presidential, semi_presidential, monarchical, parlementarian, gov_type)%>%
  summary()

country_var <- read_excel("Data/Data_Raw/country_var.xlsx")
gdppc <- read_excel("Data/Data_Raw/gdppc.xls")
population <- read_excel("Data/Data_Raw/pop.xls")
corr_index <- read_excel("Data/Data_Raw/corr_index.xlsx")
cities <- read_excel("Data/Data_Raw/cities.xlsx")

country_var <-inner_join(country_var, corr_index, by ="ISO")%>%
  inner_join(gdppc, by="ISO")%>%
  inner_join(population, by="ISO")

country_var%<>%
  select(ISO,cor2019_,gdpcap2019_, pop2019_,cor2016_,gdpcap2016_, pop2016_, cor2014_, gdpcap2014_, pop2014_, cor2011_,gdpcap2011_, pop2011_)

data_trust_test%<>%
  select(-c("gdppc", "population", "corr_index", "vdem_polyarchy", "vdem_med_corrupt", "med_self_censor", "citiz_self_censor", "cname", "capname", "caplong", "caplat", "ncapname", "ncaplong", "ncaplat","sndncapname", "sndncaplong", "sndncaplat"))

data_trust_test %<>% left_join(country_var, by=c("ISO"))

data_trust_test %<>%
mutate(gdppc = case_when(
    round == 5 ~ gdpcap2011_,
    round == 6 ~ gdpcap2014_,
    round == 7 ~ gdpcap2016_,
    round == 8 ~ gdpcap2019_,
    TRUE ~ NA
  ))

data_trust_test %<>%
mutate(population = case_when(
    round == 5 ~ pop2011_,
    round == 6 ~ pop2014_,
    round == 7 ~ pop2016_,
    round == 8 ~ pop2019_,
    TRUE ~ NA
  ))

data_trust_test %<>%
mutate(corr_index = case_when(
    round == 5 ~ cor2011_,
    round == 6 ~ cor2014_,
    round == 7 ~ cor2016_,
    round == 8 ~ cor2019_,
    TRUE ~ NA
  ))

data_trust_test%<>%
  mutate(gdppc=as.numeric(gdppc))%>%
  mutate(population=as.numeric(population))%>%
  mutate(corr_index=as.numeric(corr_index))

data_trust_test%>%
  select(gdppc, population, corr_index)%>%
  summary()

countries <- unique(data_trust_test$ISO)

qog <- read.csv("Data/Data_raw/qog_std_ts_jan24.csv")

qog %<>%
  filter(year==2011|year==2014|year==2016|year==2019)

qog%<>%
  filter(ccodealp %in% countries)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(ISO=ccodealp, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)

qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2011 ~ 5,
                   round==2014 ~ 6,
                   round==2016 ~ 7,
                   round==2019 ~ 8))

data_trust_test %<>% left_join(qog, by=c("ISO", "round"))

data_trust_test %<>% left_join(cities, by=c("ISO"))

glimpse(data_trust_test)

```

```{r}

data_trust_test%<>%
  filter(longitude > -75)

data_trust_test %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(caplong) & !is.na(caplat)) %>% 
 mutate(distance_cap = distGeo(
    cbind(longitude, latitude),
    cbind(caplong, caplat)
  ) / 1000)

data_trust_test %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(ncaplong) & !is.na(ncaplat)) %>% 
  mutate(distance_ncap = distGeo(
    cbind(longitude, latitude),
    cbind(ncaplong, ncaplat)
  ) / 1000)

data_trust_test %<>%
  filter(!is.na(caplong) & !is.na(caplat) &!is.na(ncaplong) & !is.na(ncaplat)) %>% 
   mutate(distance_cap_ncap = distGeo(
    cbind(caplong, caplat),
    cbind(ncaplong, ncaplat)
  ) / 1000)

data_trust_test %<>%
  filter(!is.na(longitude) & !is.na(latitude) & !is.na(sndncaplong) & !is.na(sndncaplat)) %>% 
  mutate(distance_sndncap = distGeo(
    cbind(longitude, latitude),
    cbind(sndncaplong, sndncaplat)
  ) / 1000)

data_trust_test %<>%
  filter(!is.na(caplong) & !is.na(caplat) &!is.na(sndncaplong) & !is.na(sndncaplat)) %>% 
   mutate(distance_cap_sndncap = distGeo(
    cbind(caplong, caplat),
    cbind(sndncaplong, sndncaplat)
  ) / 1000)

data_trust_test%<>%
  mutate(distance_cap_10=distance_cap/10)

data_trust_test%<>%
  mutate(distance_ncap_10=distance_ncap/10)

data_trust_test%<>%
  mutate(distance_sndncap_10=distance_sndncap/10)

#Log distance

data_trust_test %<>%
  filter(!is.na(distance_cap))%>%
  mutate(distance_cap_log=log(distance_cap+1))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_ncap))%>%
  group_by(cname)%>%
  mutate(distance_ncap_log=log(distance_ncap+1))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_sndncap))%>%
  group_by(cname)%>%
  mutate(distance_sndncap_log=log(distance_sndncap+1))%>%
  ungroup()

#Max distance normalization

data_trust_test %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_max=max(distance_cap))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_max95=quantile(distance_cap, probs = 0.95))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max=max(distance_ncap))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max95=quantile(distance_ncap, probs = 0.95))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max=max(distance_sndncap))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max95=quantile(distance_sndncap, probs = 0.95))%>%
  ungroup()

#Cap

data_trust_test %<>%
  filter(!is.na(distance_cap_max)) %>%
  group_by(cname)%>%
  mutate(distance_cap_max_norm = distance_cap/distance_cap_max)%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_cap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_cap_max_norm95 = if_else(distance_cap<=distance_cap_max95,distance_cap/ distance_cap_max95, NA_real_))%>%
  ungroup()

#Ncap

data_trust_test %<>%
  filter(!is.na(distance_ncap_max)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max_norm = distance_ncap/distance_ncap_max)%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_ncap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_max_norm95 = if_else(distance_ncap<=distance_ncap_max95,distance_ncap/ distance_ncap_max95, NA_real_))%>%
  ungroup()

#sndNcap
data_trust_test %<>%
  filter(!is.na(distance_sndncap_max)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max_norm = distance_sndncap/distance_sndncap_max)%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_sndncap_max95)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_max_norm95 = if_else(distance_sndncap<=distance_sndncap_max95,distance_sndncap/ distance_sndncap_max95, NA_real_))%>%
  ungroup()

#Mean distance normalization

data_trust_test %<>%
  filter(!is.na(distance_cap))%>%
  group_by(cname)%>%
  mutate(distance_cap_mean=mean(distance_cap))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_mean=mean(distance_ncap))%>%
  ungroup()

data_trust_test %<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_mean=mean(distance_sndncap))%>%
  ungroup()

#Cap

data_trust_test %<>%
  filter(!is.na(distance_cap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_cap_mean_norm = distance_cap/distance_cap_mean)%>%
  ungroup()

#Ncap

data_trust_test %<>%
  filter(!is.na(distance_ncap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_ncap_mean_norm = distance_ncap/distance_ncap_mean)%>%
  ungroup()

#sndNcap
data_trust_test %<>%
  filter(!is.na(distance_sndncap_mean)) %>%
  group_by(cname)%>%
  mutate(distance_sndncap_mean_norm = distance_sndncap/distance_sndncap_mean)%>%
  ungroup()

##Distance quintiles by country

#Raw
data_trust_test%<>%
  filter(!is.na(distance_cap)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint = ntile(distance_cap, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint = ntile(distance_ncap, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint = ntile(distance_sndncap, 5))%>%
  ungroup()

#log

data_trust_test%<>%
  filter(!is.na(distance_cap_log)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_log = ntile(distance_cap_log, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_log)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_log = ntile(distance_ncap_log, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_log)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_log = ntile(distance_sndncap_log, 5))%>%
  ungroup()

#norm max
data_trust_test%<>%
  filter(!is.na(distance_cap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_max_norm = ntile(distance_cap_max_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_max_norm = ntile(distance_ncap_max_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_max_norm)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_max_norm = ntile(distance_sndncap_max_norm, 5))%>%
  ungroup()

#norm mean
data_trust_test%<>%
  filter(!is.na(distance_cap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_cap_quint_mean_norm = ntile(distance_cap_mean_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_ncap_quint_mean_norm = ntile(distance_ncap_mean_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_mean_norm)) %>%
  group_by(cname) %>%
  mutate(dist_sndncap_quint_mean_norm = ntile(distance_sndncap_mean_norm, 5))%>%
  ungroup()

##Distance quintiles all sample

#Raw
data_trust_test%<>%
  filter(!is.na(distance_cap)) %>%
  mutate(dist_cap_quint_all = ntile(distance_cap, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap)) %>%
  mutate(dist_ncap_quint_all = ntile(distance_ncap, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap)) %>%
  mutate(dist_sndncap_quint_all = ntile(distance_sndncap, 5))%>%
  ungroup()

#log

data_trust_test%<>%
  filter(!is.na(distance_cap_log)) %>%
  mutate(dist_cap_quint_log_all = ntile(distance_cap_log, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_log)) %>%
  mutate(dist_ncap_quint_log_all = ntile(distance_ncap_log, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_log)) %>%
  mutate(dist_sndncap_quint_log_all = ntile(distance_sndncap_log, 5))%>%
  ungroup()

#norm max
data_trust_test%<>%
  filter(!is.na(distance_cap_max_norm)) %>%
  mutate(dist_cap_quint_max_norm_all = ntile(distance_cap_max_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_max_norm)) %>%
  mutate(dist_ncap_quint_max_norm_all = ntile(distance_ncap_max_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_max_norm)) %>%
  mutate(dist_sndncap_quint_max_norm_all = ntile(distance_sndncap_max_norm, 5))%>%
  ungroup()

#norm mean
data_trust_test%<>%
  filter(!is.na(distance_cap_mean_norm)) %>%
  mutate(dist_cap_quint_mean_norm_all = ntile(distance_cap_mean_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap_mean_norm)) %>%
  mutate(dist_ncap_quint_mean_norm_all = ntile(distance_ncap_mean_norm, 5))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap_mean_norm)) %>%
  mutate(dist_sndncap_quint_mean_norm_all = ntile(distance_sndncap_mean_norm, 5))%>%
  ungroup()

#Distance deciles

data_trust_test%<>%
  filter(!is.na(distance_cap)) %>%
  group_by(cname) %>%
  mutate(distance_cap_dec = ntile(distance_cap, 10))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_cap_max)) %>%
  group_by(cname) %>%
  mutate(distance_cap_dec_max = ntile(distance_cap_max, 10))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(distance_ncap_dec = ntile(distance_ncap, 10))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_ncap)) %>%
  group_by(cname) %>%
  mutate(distance_ncap_dec_max = ntile(distance_ncap_max, 10))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(distance_sndncap_dec = ntile(distance_sndncap, 10))%>%
  ungroup()

data_trust_test%<>%
  filter(!is.na(distance_sndncap)) %>%
  group_by(cname) %>%
  mutate(distance_sndncap_dec_max = ntile(distance_sndncap_max, 10))%>%
  ungroup()

data_trust%>%
  select(distance_cap_max_norm, distance_sndncap_max_norm, distance_cap)%>%
  summary()

data_trust_test%>%
  select(distance_cap_max_norm, distance_sndncap_max_norm, distance_cap)%>%
  summary()

glimpse(data_trust_test)
```

```{r}
data_trust_test <- readRDS("Data/Data_RDS/data_trust_test_report2.rds")

data_trust_test %<>%
  mutate(trust_pres = as.numeric(trust_pres),
    trust_parl = as.numeric(trust_parl),
    trust_elec = as.numeric(trust_elec)
  )

data_trust_test %<>%
group_by(id_unique) %>%
mutate(mean_inst_trust = ifelse(all(!is.na(c(trust_pres, trust_parl, trust_elec))), 
                                      mean(c(trust_pres, trust_parl, trust_elec), na.rm = TRUE), 
                                      NA)) %>%
  ungroup()

data_trust_test%>%
  filter(is.na(bin_conditions_eco))%>%
  View()

afro_w8 <- read_sav("Data/Data_Raw/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q4B)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q4B)%>%
  rename(conditions_eco=Q4B)

afro_w8%<>%
  mutate(bin_conditions_eco=ifelse(conditions_eco>=3, 1, 0))

afro_w8%<>%
  select(id_unique, bin_conditions_eco)

data_trust_test <- left_join(data_trust_test, afro_w8, by="id_unique")

glimpse(data_trust_test)

data_trust_test%>%
  select(bin_conditions_eco, ISO, round)%>%
  filter(is.na(bin_conditions_eco))%>%
  View()

data_trust_test%<>%
  mutate(bin_conditions_eco = case_when(
    round == 8 ~ bin_conditions_eco.y,
    round %in% c(5,6,7) ~ bin_conditions_eco.x))

data_trust_test%<>%
  select(-c(bin_conditions_eco.y, bin_conditions_eco.x))

str(data_trust_test)

data_trust_test %<>%
  mutate(age=as.numeric(age))%>%
  mutate(age_2 = age^2)

data_trust_test%<>%
    mutate(educ=as.numeric(educ))%>%
    mutate(educ_sec=case_when(
    educ %in% c(5, 6,7,8,9) ~ 1,
    educ %in% c(0,1,2, 3, 4) ~0,
    TRUE ~ NA_real_     
  ))

data_trust_test %<>%
  group_by(NAME_2) %>%
  mutate(region2_id = cur_group_id())%>%
  ungroup()

data_trust_test %<>%
  group_by(round, region2_id) %>%
  mutate(region2_round = cur_group_id())%>%
  ungroup()

data_trust_test%<>%
  mutate(area_log = if_else(!is.na(area), log(area), NA_real_))

data_trust_test%<>%
  mutate(log_gdppc=log(gdppc))

data_trust_test %<>%
  group_by(ISO) %>%
  mutate(color = ifelse(is.na(color), NA, color)) %>%
  ungroup() %>%
  fill(color, .direction = "updown")

data_trust_test %<>%
  mutate(mean_inst_trust_bin = case_when(
    mean_inst_trust >= median(mean_inst_trust, na.rm = TRUE) ~ 1,
    mean_inst_trust < median(mean_inst_trust, na.rm = TRUE) ~ 0,
    TRUE ~ NA_real_
  )) %>%
  ungroup()

data_trust_test%<>%
  mutate(internet_news_bin=case_when(
    internet_news%in%c(0,1, 2) ~ 0,
    internet_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

data_trust_test%<>%
  mutate(internet_news_bin2=case_when(
    internet_news%in%c(0,1, 2) ~ 0,
    internet_news%in%c(3, 4) ~ 1,
    TRUE ~ NA_real_
  ))

saveRDS(data_trust_test, file="Data/Data_RDS/data_trust_test_report2.rds")

write_dta(data_trust_test, "Data/Data_dta/data_trust_test_report2.dta")
```

### 2025-02-24 tables/v_1/tables.tex
import folders

--- 2024-11-20 wp/tables.tex
@@
 \documentclass[11pt]{article}
+
+\usepackage[dvipsnames]{xcolor}
 
@@
 
-\usepackage{hyperref}
-\hypersetup{
-        colorlinks=true,
-        breaklinks,
-        allcolors=[RGB]{128,0,0}
-}
-
 \let\oldFootnote\footnote
@@
 \usepackage{rotating}
-\usepackage{graphicx}
 \usepackage{subcaption}
-\usepackage{seqsplit}
 \usepackage{amsmath,amsfonts,amssymb,amsthm}
@@
 \usepackage{float}
-%\usepackage[multiple]{footmisc}
-%\usepackage{longtable}
-\usepackage{adjustbox}
-\usepackage{rotating}
-
 \usepackage{bbding} % checkmark symbol
@@
 \usepackage{natbib}
-%\usepackage[autostyle]{csquotes}
-%\usepackage[backend=bibtex, style=authoryear, natbib=true]{biblatex}
-%\addbibresource{CCH.bib}
 
-%%For Hypotheses and Subhypotheses
-%\usepackage{ntheorem}
 \newtheorem{hyp}{Hypothesis}
@@
 \makeatother
-%%%
 
@@
 
-%Expectation opperator
+%Expectation operator
 \newcommand{\Expect}{{\rm I\kern-.3em E}}
@@
 
+\usepackage{titlesec}
+\usepackage[dvipsnames]{xcolor}
+
+\titleformat{\section}
+{\color{WildStrawberry}\normalfont\LARGE\bfseries}
+{\color{WildStrawberry}\thesection}{1em}{}
+
+\titleformat{\subsection}
+{\color{ForestGreen}\normalfont\Large\bfseries}
+{\color{ForestGreen}\thesubsection}{1em}{}
+
+\titleformat{\subsubsection}
+{\color{NavyBlue}\normalfont\large\bfseries}
+{\color{NavyBlue}\thesubsubsection}{1em}{}
+
+\titleformat{\paragraph}[runin]
+{\normalfont\normalsize\bfseries}
+{}{0pt}{}
+
+\titleformat{\subparagraph}[runin]
+{\normalfont\normalsize\bfseries}
+{}{0pt}{}
+
+% Adjust spacing after headings
+\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}
+\titlespacing*{\subsection}{0pt}{\baselineskip}{\baselineskip}
+\titlespacing*{\subsubsection}{0pt}{\baselineskip}{\baselineskip}
+\titlespacing*{\paragraph}{0pt}{\baselineskip}{\baselineskip}
+\titlespacing*{\subparagraph}{0pt}{\baselineskip}{\baselineskip}
+
+% Adjust numbering depth
+\setcounter{secnumdepth}{3} % Number subsubsections
+
+\usepackage{hyperref}
+\usepackage{chngcntr}
+\usepackage{lscape}
+\usepackage{rotate}
+\usepackage{pdflscape}
+
+\usepackage{booktabs}      % For professional table lines
+\usepackage{multirow}      % For merged cells across rows
+\usepackage{makecell}      % For better cell formatting
+\usepackage{array}         % For advanced array and table formatting
+\usepackage{colortbl}      % If you want to use colored cells
+
 \begin{document}
 
-\title{Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}
+\title{The Death of Distance: Mobile Internet
+and Political Trust in Africa \\  \vspace{0.75cm} \underline{Tables}}
 
 \vspace{1cm}
-
-\author{
-\textbf{Illan Barriola} \\ CRED -- Paris II \\
-\and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
-}
 
@@
     %\footnotesize
-    \resizebox{12cm}{!}{
+    \resizebox{8cm}{!}{
     \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
@@
 
-     Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
-     \medskip
-     &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
+     Distance from the capital&       0.300***&       0.298***&       0.618***&       0.341** \\
+     \smallskip
+     &      (0.04)   &      (0.03)   &      (0.15)   &      (0.16)   \\
      \midrule
@@
     \smallskip
-    Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
-    Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\
-
+    Observations           &      107,117   &      111,570   &       10,790   &       11,924   \\
+    Adjusted-R$^2$         &       0.105   &       0.156   &       0.140   &       0.172   \\
                           \bottomrule
-    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
 Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
 The set of individual controls
-    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+    education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+(3) and (4) also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
@@
         %\footnotesize
-        \resizebox{17cm}{!}{
+        \resizebox{12cm}{!}{
         \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
@@
 
-    Distance from the capital &0.463***&&&& 1.361***\\      
+    Distance from the capital&       0.453***&&&&       1.523***\\
     \smallskip
-    &      (0.05)   &&&&     (0.49)   \\
-    Internet coverage     &       0.029   &&&&       1.470**  \\
+    &      (0.05)   &&&&      (0.56)   \\
+    Internet coverage&      -0.015   &&&&       1.770** \\
 \smallskip
-    & (0.06)   &&&&      (0.64)    \\ 
+&      (0.06)   &&&&      (0.69)   \\
+Distance from the capital $\times$ Internet coverage&     -0.466***&&&&       -2.950**         \\
 \smallskip
-    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
-    \smallskip  &       (0.10)   &&&               &      (1.09) \\
+            &      (0.10)   &&&&        (1.45)           \\
 
@@
     \smallskip&& (0.00) && (0.00) \\
-    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
+    Distance from the capital city $\times$ Lightning strikes&&-0.000 && -0.001***\\
     \medskip&& (0.00) && (0.00)\\
@@
          \midrule
-        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-&-\\
+        SW \emph{F} - Lightning strikes &-&-& 13.74&- &-\\
         \smallskip
-        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-&-\\
+        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 8.62 &-&-\\
         \smallskip
@@
         \smallskip
-        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
-        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
+        Observations       &       111,570    &113,243 & 113,243&       111,570  \\
+        Adjusted-R$^2$    &       0.158     &-&-&-&  \\
                               \bottomrule
-        \multicolumn{6}{p{27cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
+        \multicolumn{6}{p{25cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
         \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
-        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
@@
             \sffamily
-            \caption{{Other outcomes}}
+            \caption{{Political accountability}}
             \centering
             %\footnotesize
-            \resizebox{18cm}{!}{
+            \resizebox{12cm}{!}{
             \begin{tabular}{@{\extracolsep{5pt}} l c c}
@@
 
-             Distance from the capital&   -1.306***&       1.560***\\
+            Distance from the capital&      -0.932***&       1.874***\\
             \smallskip
-             &      (0.40)   &      (0.52)   \\
-             Internet coverage     &      -1.370***&       1.565**  \\
+            &      (0.28)   &      (0.65)   \\
+            Internet coverage&       -1.163***&       2.089***\\
             \smallskip
-             &      (0.47)   &      (0.62)   \\
-             Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
+            &        (0.41)   &      (0.77) \\
+            Distance from the capital $\times$ Internet coverage&       2.104***&      -4.200** \\
             \medskip
-             &       (0.92)   &      (1.16)   \\
+            &      (0.74)   &      (1.69)   \\
+
              \midrule
@@
             \smallskip
-            Observations      &       99,414   &       98,512  \\            \bottomrule
+            Observations      &      74,959   &      111,696  \\            \bottomrule
             \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-            includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+            includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
@@
                 %\footnotesize
-              \resizebox{16cm}{!}{
+                \resizebox{10cm}{!}{
                 \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
@@
 
-               Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
+              Distance from the capital&      -8.382   &       1.083** &       2.367   &       0.938***\\
               \smallskip
-               &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
-               Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
+              &      (24.71)   &      (0.42)   &      (1.50)   &      (0.32)   \\
+              Internet coverage&      -5.260   &       1.004   &       2.653*  &       0.762   \\
               \smallskip
-               &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
-            Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
+              &      (19.11)   &      (0.74)   &      (1.49)   &      (0.69)   \\
+              Distance from the capital $\times$ Internet coverage&      18.335   &      -2.149*  &      -5.132   &      -1.524**  \\
               \medskip
-            &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\
+              &       (52.59)   &      (1.25)   &      (3.92)   &      (0.77)   \\
 
@@
                 \smallskip
-              Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
+                Observations          &       50,288   &       61,282   &       51,737   &       59,833  \\
                 \bottomrule
                 \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+                includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
@@
                     %\footnotesize
-                \resizebox{16cm}{!}{
-                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
+                    \resizebox{10cm}{!}{
+                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
                     \\
@@
                     \toprule
-                & \multicolumn{8}{c}{2SLS: Political trust}\\
-                \cmidrule(r){2-9}
-                & \multicolumn{8}{c}{{Base sample}}\\
-                \cmidrule(r){2-9}
-                &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}&  \multicolumn{4}{c}{{Age}}\\
+                    & \multicolumn{4}{c}{2SLS: Political trust}\\
+                    \cmidrule(r){2-5}
+                    & \multicolumn{4}{c}{{Base sample}}\\
+                    \cmidrule(r){2-5}
+                    &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}\\
                     \cmidrule(r){2-3}
                         \cmidrule(r){4-5}
-                    \cmidrule(r){6-9}
-                    & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}} & \multicolumn{1}{c}{{18-25}}& \multicolumn{1}{c}{{26-35}}& \multicolumn{1}{c}{{36-44}}& \multicolumn{1}{c}{{45+}}\\
+                        & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}}\\
                         \cmidrule(r){2-2}
@@
                         \cmidrule(r){5-5}
-                    \cmidrule(r){6-6}
-                    \cmidrule(r){7-7}
-                    \cmidrule(r){8-8}
-                    \cmidrule(r){9-9}
-                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
+                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
                      \midrule
 
-                 Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961***&       1.295** &       0.965   &       1.438** &       1.723*** \\
+                       Distance from the capital&        1.467***&       1.440   &       1.074** &       2.666***\\
                        \smallskip
-                 &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)   &      (0.57)   &      (0.63)   &      (0.56)   &      (0.59)   \\
-                 Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***&       1.439*  &       0.982   &       1.236*  &       2.540***\\
+                       &      (0.45)   &      (1.44)   &      (0.54)   &      (0.89)  \\
+                       Internet coverage&       1.613** &       1.632   &       0.525   &       4.471***\\
                        \smallskip
-                 &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   &      (0.74)   &      (0.76)   &      (0.72)   &      (0.87)   \\
-                   Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447*  &      -1.994   &      -1.477   &      -2.577** &      -3.103**  \\
+                       &     (0.63)   &      (1.34)   &      (0.62)   &      (1.48)    \\
+                       Distance from the capital $\times$ Internet coverage&      -2.901** &      -2.688   &      -1.787   &      -5.898** \\
                        \medskip
-                   &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)   &      (1.24)   &      (1.38)   &      (1.28)   &      (1.39)   \\
+                       &       (1.24)   &      (3.22)   &      (1.12)   &      (2.55)    \\
+
                      \midrule
                      \smallskip
-                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes\\
+                    Individual \& regional controls  & Yes & Yes & Yes & Yes\\
                     \smallskip
-                Country X Round FE       & Yes& Yes & Yes& Yes & Yes& Yes & Yes& Yes\\
+                    Country X Round FE       & Yes& Yes & Yes& Yes\\
                     \smallskip
-                Observations         &       36,389   &       62,039   &       37,348   &       60,887   &       25,442   &       29,913   &       20,074   &       23,246   \\
+                    Observations         &        79,394   &       32,176   &       42,509   &       69,061\\
                     \bottomrule
-                \multicolumn{9}{p{24cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+                    \multicolumn{5}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
+                    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
@@
 
+\newpage
+
+\centering{\large{\textbf{APPENDIX}}}
+
 \begin{table}[H]
   \sffamily
-              \caption{{Generalized trust}}
+  \caption{{Effect of internet coverage on internet news consumption and internet use}}
   \centering
   %\footnotesize
-              \resizebox{16cm}{!}{
-              \begin{tabular}{@{\extracolsep{5pt}} l c c}
+  \resizebox{8cm}{!}{
+  \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
   \\
@@
   \toprule
-              & \multicolumn{2}{c}{2SLS}\\
+  &  \multicolumn{4}{c}{{OLS}}  \\
+  \cmidrule(r){2-5}
+  & \multicolumn{2}{c}{{Internet news}} & \multicolumn{2}{c}{{Internet use}}\\
       \cmidrule(r){2-3}
-              & \multicolumn{2}{c}{{Base sample: rounds 5 $\&$ 8}}\\
-              \cmidrule(r){2-3}
-                  & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Generalized trust}}\\
-                  \cmidrule(r){2-2}
-                  \cmidrule(r){3-3}
-                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
+      \cmidrule(r){4-5}
+      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
    \midrule
-               Distance from the capital&       1.358** &      -0.157   \\
-               \smallskip
-               &      (0.62)   &      (0.17)    \\
-               Internet coverage    &       1.508   &      -0.101    \\
-               \smallskip
-               &      (0.94)   &      (0.23)   \\
-               Distance from the capital $\times$ Internet coverage&      -2.161*  &       0.542   \\
-               \medskip
-               &      (1.22)   &      (0.33)   \\
+
+   Internet coverage &       0.900***&       1.127***&       0.948***&       1.217***\\
+   \medskip&      (0.06)   &      (0.05)   &      (0.06)   &      (0.06)   \\
 
@@
    \smallskip
-              Individual \& regional controls  & Yes & Yes\\
+  Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
   \smallskip
-              Country X Round FE       & Yes& Yes\\
+  Country controls & Yes& No& Yes& No\\
   \smallskip
-              Observations         &     49,404   &       49,362\\
+  Round FE & Yes & No& Yes & No\\
+  \smallskip
+  Country X Round FE       & No & Yes& No & Yes\\
+  \smallskip
+  Ethnic homeland FE & No & No & Yes& Yes\\
+  \smallskip
+  Observations          &    120,988   &      120,988   &      120,859   &      120,859    \\
+  Adjusted-R$^2$         &       0.092   &       0.148   &       0.100   &       0.158 \\
                         \bottomrule
-              \multicolumn{3}{p{14cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-              \end{tabular}
-              }
-              \end{table}
-
-              \begin{table}[H]
-                \sffamily
-                \caption{{Effect of distance from the capital on institutional trust (President, Parliament, Electoral commission)}}
-                \centering
-                %\footnotesize
-                \resizebox{16cm}{!}{
-                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                \\
-                \toprule
-                \toprule
-                &  \multicolumn{6}{c}{{Trust in institutions (President, Parliament, Electoral commission)}}  \\
-                \cmidrule(r){2-7}
-                &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                \cmidrule(r){2-6}
-                \cmidrule(r){7-7}
-                & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                    \cmidrule(r){2-3}
-                    \cmidrule(r){4-5}
-                    \cmidrule(r){6-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                 \midrule
-
-                 Distance from the capital&    0.295***&       0.301***&       0.563***&       0.306 &       0.483***&       1.738***\\
-                 \smallskip
-                 &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20) &      (0.05)   &      (0.58) \\
-                 Internet coverage &&&&&       0.016   &       2.035*** \\
-                 \smallskip
-
-                 &&&&&      (0.06)   &      (0.71)\\
-                 Distance from the capital $\times$ Internet coverage &&&&&      -0.458***&-2.992**\\
-                 \medskip
-                 &&&&&      (0.10) & (1.32)\\
-                 \midrule
-                 \smallskip
-                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                \smallskip
-                Country controls & Yes& No& Yes& No& No& No\\
-                \smallskip
-                Round FE & Yes & No& Yes & No& No& No\\
-                \smallskip
-                Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                \smallskip
-                Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                \smallskip
-                Observations           &   98,499   &       98,499   &        4,202   &        4,202   & 98,499   &       98,499 \\
-                Adjusted-R$^2$        &        0.164   &       0.198   &       0.148   &       0.184  & 0.200   &       - \\
-
-                                      \bottomrule
-                \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+  \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
+  includes measures of: normalized distance from the capital normalized distance from the largest non-capital city, age, age squared, sex,
+  education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
@@
     \sffamily
-                  \caption{{Effect of distance from the capital on trust in president}}
-                  \centering
-                  %\footnotesize
-                  \resizebox{16cm}{!}{
-                  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                  \\
-                  \toprule
-                  \toprule
-                  &  \multicolumn{6}{c}{{Trust in president}}  \\
-                  \cmidrule(r){2-7}
-                  &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                  \cmidrule(r){2-6}
-                  \cmidrule(r){7-7}
-                  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                      \cmidrule(r){2-3}
-                      \cmidrule(r){4-5}
-                      \cmidrule(r){6-6}
-                      \cmidrule(r){7-7}
-                      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                   \midrule
-
-                   Distance from the capital&       0.287***&       0.262***&       0.799***&       0.343   &       0.473***&       1.517**\\
-                   \smallskip
-                   &      (0.05)   &      (0.03)   &      (0.19)   &      (0.25)   &      (0.06)   &      (0.63) \\
-                   Internet coverage &&&&       &       0.047   &       1.659**  \\
-                   \smallskip
-                   &&&&    &      (0.07)   &      (0.81) \\
-                   Distance from the capital $\times$ Internet coverage &&&&&      -0.521***&-2.654*\\
-                   \medskip
-                   &&&&&      (0.12)  & (1.41) \\
-                   \midrule
-                   \smallskip
-                  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                  \smallskip
-                  Country controls & Yes& No& Yes& No& No& No\\
-                  \smallskip
-                  Round FE & Yes & No& Yes & No& No& No\\
-                  \smallskip
-                  Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                  \smallskip
-                  Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                  \smallskip
-                  Observations            &       97,261   &       97,261   &        4,149   &        4,149   &       97,261   &       97,261  \\
-                  Adjusted-R$^2$        &       0.137   &       0.180   &       0.180   &       0.215   &       0.182    &       - \\
-
-                                        \bottomrule
-                  \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                  \end{tabular}
-                  }
-                  \end{table}
-
-                  \begin{table}[H]
-                    \sffamily
-                    \caption{{Effect of distance from the capital on trust in parliament}}
-                    \centering
-                    %\footnotesize
-                    \resizebox{16cm}{!}{
-                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                    \\
-                    \toprule
-                    \toprule
-                    &  \multicolumn{6}{c}{{Trust in parliament}}  \\
-                    \cmidrule(r){2-7}
-                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                    \cmidrule(r){2-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                        \cmidrule(r){2-3}
-                        \cmidrule(r){4-5}
-                        \cmidrule(r){6-6}
-                        \cmidrule(r){7-7}
-                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                     \midrule
-
-                     Distance from the capital&       0.282***&       0.279***&       0.560***&       0.471** &       0.453***&       1.124***\\
-                     \smallskip
-                     &      (0.04)   &      (0.03)   &      (0.17)   &      (0.21)   &      (0.05)   &      (0.39) \\
-                     Internet coverage &&&&       &        0.007   &       1.169**  \\
-                     \smallskip
-                     &&&&    &      (0.06)   &      (0.52)   \\
-                     Distance from the capital $\times$ Internet coverage &&&&&      -0.442***& -1.776**\\
-                     \medskip
-                     &&&&&     (0.10)   &  (0.89) \\
-                     \midrule
-                     \smallskip
-                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                    \smallskip
-                    Country controls & Yes& No& Yes& No& No& No\\
-                    \smallskip
-                    Round FE & Yes & No& Yes & No& No& No\\
-                    \smallskip
-                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                    \smallskip
-                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                    \smallskip
-                    Observations            &      96,182   &       96,182   &        4,111   &        4,111   &       96,182   &       96,182  \\
-                    Adjusted-R$^2$        &        0.130   &       0.160   &       0.102   &       0.127   &       0.161   &       - \\
-
-                                          \bottomrule
-                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                    \end{tabular}
-                    }
-                    \end{table}
-
-                  \begin{table}[H]
-                    \sffamily
-                    \caption{{Effect of distance from the capital on trust in electoral commission}}
-                    \centering
-                    %\footnotesize
-                    \resizebox{16cm}{!}{
-                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                    \\
-                    \toprule
-                    \toprule
-                    &  \multicolumn{6}{c}{{Trust in electoral commission}}  \\
-                    \cmidrule(r){2-7}
-                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                    \cmidrule(r){2-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                        \cmidrule(r){2-3}
-                        \cmidrule(r){4-5}
-                        \cmidrule(r){6-6}
-                        \cmidrule(r){7-7}
-                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                     \midrule
-
-                     Distance from the capital&       0.319***&       0.365***&       0.366*  &       0.206   &       0.529***&       2.588***\\
-                     \smallskip
-                     &     (0.04)   &      (0.03)   &      (0.19)   &      (0.23)   &      (0.06)   &      (0.84) \\
-                     Internet coverage &&&&       &        0.003   &       3.252***  \\
-                     \smallskip
-                     &&&&    &      (0.07)   &      (0.95)   \\
-                     Distance from the capital $\times$ Internet coverage &&&&&     -0.418***&  -4.606**\\
-                     \medskip
-                     &&&&&      (0.11)    &  (1.93) \\
-                     \midrule
-                     \smallskip
-                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                    \smallskip
-                    Country controls & Yes& No& Yes& No& No& No\\
-                    \smallskip
-                    Round FE & Yes & No& Yes & No& No& No\\
-                    \smallskip
-                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                    \smallskip
-                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                    \smallskip
-                    Observations            &      94,926   &       94,926   &        4,035   &        4,035   &       94,926   &       94,926   \\
-                    Adjusted-R$^2$        &         0.118   &       0.144   &       0.094   &       0.137   &       0.145   &       - \\
-
-                                          \bottomrule
-                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                    \end{tabular}
-                    }
-                    \end{table}
-
-\begin{table}[H]
-  \sffamily
-  \caption{{Effect of distance from the capital on political trust}}
+    \caption{{Effect of distance from the capital on trust in president and parliament}}
     \centering
@@
     \cmidrule(r){2-9}
-  &  \multicolumn{4}{c}{{Vote against ruling party}}&  \multicolumn{4}{c}{{Country performance}}  \\
+    &  \multicolumn{4}{c}{{Trust in president}}&  \multicolumn{4}{c}{{Trust in parliament}}  \\
     \cmidrule(r){2-5}
@@
         \cmidrule(r){8-9}
-      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}&  \multicolumn{1}{c}{{(7)}}&  \multicolumn{1}{c}{{(8)}}\\
+        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
      \midrule
 
-   Distance from the capital&      -0.164***&      -0.101***&      -0.462***&      -0.334***&       0.183***&       0.153***&       0.272*  &      -0.034   \\
-   \medskip
-   &      (0.02)   &      (0.02)   &      (0.09)   &      (0.09)   &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20)   \\
+     Distance from the capital&       0.316***&       0.292***&       0.733***&       0.259   &       0.285***&       0.305***&       0.531***&       0.470***\\
+     \medskip&      (0.05)   &      (0.04)   &      (0.18)   &      (0.18)  &      (0.04)   &      (0.03)   &      (0.14)   &      (0.15) \\
+
 \midrule
      \smallskip
-  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes  \\
+    Individual \& regional controls  & Yes & Yes & Yes & Yes  & Yes & Yes & Yes & Yes \\
     \smallskip
@@
     \smallskip
-  Round FE & Yes & No& Yes & No& Yes & No& Yes & No\\
+    Round FE & Yes & No& Yes & No & Yes & No& Yes & No\\
     \smallskip
@@
     \smallskip
-  Observations           &       99,414   &       99,414   &        4,247   &        4,247   &       98,512   &       98,512   &        4,203   &        4,203   \\
-  Adjusted-R$^2$         &       0.082   &       0.147   &       0.167   &       0.249   &       0.140   &       0.161   &       0.166   &       0.184   \\
+    Observations           &      105,993   &      110,439   &       10,642   &       11,772  &      104,535   &      108,982   &       10,534   &       11,667    \\
+    Adjusted-R$^2$         &      0.084   &       0.138   &       0.173   &       0.200   &       0.095   &       0.134   &       0.086   &       0.120 \\
                           \bottomrule
-  \multicolumn{9}{p{21cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+    \multicolumn{9}{p{21cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
 Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
 The set of individual controls
-  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+    education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
 The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
@@
 
+    \begin{table}[H]
+      \sffamily
+      \caption{{Effect of distance from the capital on political trust - Different distance measures}}
+      \centering
+      %\footnotesize
+      \resizebox{18cm}{!}{
+      \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c c c c c}
+      \\
+      \toprule
+      \toprule
+      &  \multicolumn{12}{c}{{OLS}}  \\
+      \cmidrule(r){2-13}
+      &  \multicolumn{12}{c}{{Political trust}}  \\
+      \cmidrule(r){2-13}
+      & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
+          \cmidrule(r){2-3}
+          \cmidrule(r){4-5}
+          \cmidrule(r){6-7}
+          \cmidrule(r){8-9}
+          \cmidrule(r){10-11}
+          \cmidrule(r){12-13}
+          & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}} &  \multicolumn{1}{c}{{(9)}} &  \multicolumn{1}{c}{{(10)}} &  \multicolumn{1}{c}{{(11)}} &  \multicolumn{1}{c}{{(12)}}\\
+       \midrule
+
+       Distance from the capital (in 10km) &       0.004***&       0.003***&       0.009***&       0.003   \\
+       \smallskip
+       &      (0.00)   &      (0.00)   &      (0.00)   &      (0.00)   \\
+       log(Distance from the capital)&&&&&       0.039***&       0.042***&       0.158***&       0.088** \\
+       \smallskip
+       &&&&&      (0.01)   &      (0.01)   &      (0.04)   &      (0.04)   \\
+        Distance from the capital (mean normalization) &&&&&&&&&       0.107***&       0.101***&       0.234***&       0.107** \\
+       \medskip     &&&&&&&&&      (0.02)   &      (0.01)   &      (0.05)   &      (0.05)   \\
+
+  \midrule
+       \smallskip
+      Individual \& regional controls  & Yes & Yes & Yes & Yes  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
+      \smallskip
+      Country controls & Yes& No& Yes& No& Yes& No& Yes& No& Yes& No& Yes& No\\
+      \smallskip
+      Round FE & Yes & No& Yes & No & Yes & No& Yes & No & Yes & No& Yes & No\\
+      \smallskip
+      Country X Round FE       & No & Yes& No & Yes& No & Yes& No & Yes& No & Yes& No & Yes\\
+      \smallskip
+      Ethnic homeland FE & No & No & Yes& Yes& No & No & Yes& Yes& No & No & Yes& Yes\\
+      \smallskip
+      Observations            &      107,117   &      111,570   &       10,790   &       11,924   &      107,117   &      111,570   &       10,790   &       11,924 &      107,117   &      111,570   &       10,790   &       11,924   \\
+      Adjusted-R$^2$         &       0.107   &       0.156   &       0.142   &       0.172 &       0.103   &       0.154   &       0.139   &       0.173  &       0.105   &       0.156   &       0.141   &       0.172\\
+                            \bottomrule
+      \multicolumn{13}{p{32cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
+The set of individual controls
+      includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+      education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
+The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+      \end{tabular}
+      }
+      \end{table}
+
+      \begin{table}[H]
+        \sffamily
+        \caption{{Effect of distance from the capital on political trust - Non-linearities}}
+        \centering
+        %\footnotesize
+        \resizebox{18cm}{!}{
+        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c c c c c}
+        \\
+        \toprule
+        \toprule
+        &  \multicolumn{12}{c}{{OLS}}  \\
+        \cmidrule(r){2-13}
+        &  \multicolumn{12}{c}{{Political trust}}  \\
+        \cmidrule(r){2-13}
+        & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
+            \cmidrule(r){2-3}
+            \cmidrule(r){4-5}
+            \cmidrule(r){6-7}
+            \cmidrule(r){8-9}
+            \cmidrule(r){10-11}
+            \cmidrule(r){12-13}
+            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}} &  \multicolumn{1}{c}{{(9)}} &  \multicolumn{1}{c}{{(10)}} &  \multicolumn{1}{c}{{(11)}} &  \multicolumn{1}{c}{{(12)}}\\
+         \midrule
+         Distance from the capital (Q2)&      -0.005   &      -0.005   &       0.132   &       0.156*  \\
+         \smallskip
+         &      (0.03)   &      (0.02)   &      (0.11)   &      (0.09)   \\
+         Distance from the capital (Q3)&      -0.026   &      -0.021   &       0.269** &       0.193*  \\
+         \smallskip&      (0.04)   &      (0.03)   &      (0.13)   &      (0.10)   \\
+         Distance from the capital (Q4)&       0.102***&       0.102***&       0.371***&       0.214** \\
+         \smallskip&      (0.03)   &      (0.02)   &      (0.14)   &      (0.11)   \\
+         Distance from the capital (Q5)&       0.170***&       0.165***&       0.379***&       0.169   \\
+         \smallskip&      (0.04)   &      (0.03)   &      (0.14)   &      (0.11)   \\
+         Distance from the capital&&&&&  -0.438***&      -0.252** &       1.250***&       1.019** &      -0.981***&      -0.537** &       1.923** &       2.642***\\
+         \smallskip&&&&&     (0.15)   &      (0.11)   &      (0.48)   &      (0.40)   &      (0.38)   &      (0.26)   &      (0.89)   &      (0.76)   \\
+         Distance from the capital$^2$&&&&&      0.832***&       0.621***&      -0.619   &      -0.669** &       2.320** &       1.404** &      -2.227   &      -4.725***\\
+         \smallskip&&&&&     (0.16)   &      (0.12)   &      (0.41)   &      (0.34)  &      (0.91)   &      (0.64)   &      (1.78)   &      (1.65)  \\
+         Distance from the capital$^3$&&&&&&&&&      -1.077*  &      -0.567   &       1.043   &       2.658** \\
+         \medskip
+         &&&&&&&&&      (0.61)   &      (0.45)   &      (1.11)   &      (1.05)   \\
+
+    \midrule
+         \smallskip
+        Individual \& regional controls  & Yes & Yes & Yes & Yes  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
+        \smallskip
+        Country controls & Yes& No& Yes& No& Yes& No& Yes& No& Yes& No& Yes& No\\
+        \smallskip
+        Round FE & Yes & No& Yes & No & Yes & No& Yes & No & Yes & No& Yes & No\\
+        \smallskip
+        Country X Round FE       & No & Yes& No & Yes& No & Yes& No & Yes& No & Yes& No & Yes\\
+        \smallskip
+        Ethnic homeland FE & No & No & Yes& Yes& No & No & Yes& Yes& No & No & Yes& Yes\\
+        \smallskip
+        Observations            &      107,117   &      111,570   &       10,790   &       11,924   & 107,117   &      111,570   &       10,790   &       11,924   &      107,117   &      111,570   &       10,790   &       11,924 \\
+        Adjusted-R$^2$         &    0.106   &       0.157   &       0.138   &       0.173 & 0.107   &       0.157   &       0.141   &       0.173 &       0.108   &       0.157   &       0.141   &       0.174\\
+                              \bottomrule
+        \multicolumn{13}{p{29cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
+The set of individual controls
+        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+        education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
+The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+        \end{tabular}
+        }
+        \end{table}
+
+        \begin{table}[H]
+          \sffamily
+          \caption{{Effect of distance from the capital on political trust - Different border samples}}
+          \centering
+          %\footnotesize
+          \resizebox{8cm}{!}{
+          \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
+          \\
+          \toprule
+          \toprule
+          &  \multicolumn{4}{c}{{OLS}}  \\
+          \cmidrule(r){2-5}
+          &  \multicolumn{4}{c}{{Political trust}}  \\
+          \cmidrule(r){2-5}
+          & \multicolumn{2}{c}{{30-km buffer}} & \multicolumn{2}{c}{{50-km buffer}}\\
+              \cmidrule(r){2-3}
+              \cmidrule(r){4-5}
+              & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
+           \midrule
+
+          Distance from the capital&       0.629***&       0.147   &       0.561***&       0.274*  \\
+           \medskip
+           &      (0.16)   &      (0.19)   &      (0.14)   &      (0.14)   \\
+          \midrule
+           \smallskip
+          Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
+          \smallskip
+          Country controls & Yes& No& Yes& No\\
+          \smallskip
+          Round FE & Yes & No& Yes & No\\
+          \smallskip
+          Country X Round FE       & No & Yes& No & Yes\\
+          \smallskip
+          Ethnic homeland FE & No & No & Yes& Yes\\
+          \smallskip
+          Observations           &       7,568   &        8,543   &       13,352   &       14,729    \\
+          Adjusted-R$^2$         &        0.135   &       0.173   &       0.138   &       0.167   \\
+                                \bottomrule
+          \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the ethnic homeland x region x round level for the border samples are in parentheses.
+The set of individual controls
+          includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+          education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
+The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+          \end{tabular}
+          }
+          \end{table}
+
+          \begin{table}[H]
+            \sffamily
+            \caption{{Effect of distance from the capital on political trust - Media consumption}}
+            \centering
+            %\footnotesize
+            \resizebox{18cm}{!}{
+            \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c c c c c}
+            \\
+            \toprule
+            \toprule
+            &  \multicolumn{12}{c}{{OLS}}  \\
+            \cmidrule(r){2-13}
+            &  \multicolumn{4}{c}{{TV news}}&  \multicolumn{4}{c}{{Radio news}}&  \multicolumn{4}{c}{{Newspaper}}  \\
+            \cmidrule(r){2-5}
+            \cmidrule(r){6-9}
+            \cmidrule(r){10-13}
+            & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}} & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
+                \cmidrule(r){2-3}
+                \cmidrule(r){4-5}
+                \cmidrule(r){6-7}
+                \cmidrule(r){8-9}
+                \cmidrule(r){10-11}
+                \cmidrule(r){12-13}
+                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}} &  \multicolumn{1}{c}{{(9)}} &  \multicolumn{1}{c}{{(10)}} &  \multicolumn{1}{c}{{(11)}} &  \multicolumn{1}{c}{{(12)}}\\
+             \midrule
+             Distance from the capital&      -0.536***&      -0.531***&      -0.371** &      -0.361** &       0.057   &       0.007   &      -0.221   &      -0.306 &      -0.113***&      -0.081***&      -0.079   &       0.075  \\
+             \medskip
+             &      (0.04)   &      (0.04)   &      (0.15)   &      (0.18)   &      (0.05)   &      (0.04)   &      (0.16)   &      (0.20)   &      (0.04)   &      (0.03)   &      (0.10)   &      (0.12) \\
+
+        \midrule
+             \smallskip
+            Individual \& regional controls  & Yes & Yes & Yes & Yes  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
+            \smallskip
+            Country controls & Yes& No& Yes& No& Yes& No& Yes& No& Yes& No& Yes& No\\
+            \smallskip
+            Round FE & Yes & No& Yes & No & Yes & No& Yes & No & Yes & No& Yes & No\\
+            \smallskip
+            Country X Round FE       & No & Yes& No & Yes& No & Yes& No & Yes& No & Yes& No & Yes\\
+            \smallskip
+            Ethnic homeland FE & No & No & Yes& Yes& No & No & Yes& Yes& No & No & Yes& Yes\\
+            \smallskip
+            Observations            &      108,766   &      113,243   &       10,976   &       121,15  &  108,766   &      113,243   &       10,976   &       12,115  &      108,766   &      113,243   &       10,976   &       12,115\\
+            Adjusted-R$^2$         &   0.458   &       0.469   &       0.436   &       0.445 &       0.151   &       0.181   &       0.178   &       0.196 &       0.360   &       0.378   &       0.342   &       0.349  \\
+                                  \bottomrule
+            \multicolumn{13}{p{29cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
+The set of individual controls
+            includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+            education, employment status, rural/urban situation, personal economic conditions perception, interest in politics.
+Each media consumption measure (TV, radio, newspaper) is excluded from controls when it is the dependent variable.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
+The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+            \end{tabular}
+            }
+            \end{table}
+
+  \begin{table}[H]
+    \sffamily
+    \caption{{Effect of distance from the capital on internet news}}
+    \centering
+    %\footnotesize
+    \resizebox{8cm}{!}{
+    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
+    \\
+    \toprule
+    \toprule
+    &  \multicolumn{4}{c}{{OLS}}  \\
+    \cmidrule(r){2-5}
+    &  \multicolumn{4}{c}{{Internet news}}  \\
+    \cmidrule(r){2-5}
+    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
+        \cmidrule(r){2-3}
+        \cmidrule(r){4-5}
+        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
+     \midrule
+
+     Distance from the capital&      -0.080***&      -0.065** &       0.049   &       0.074 \\
+     \medskip
+     &      (0.03)   &      (0.03)   &      (0.09)   &      (0.09)\\
+
+\midrule
+     \smallskip
+    Individual \& regional controls  & Yes & Yes & Yes & Yes\\
+    \smallskip
+    Country controls & Yes& No& Yes& No\\
+    \smallskip
+    Round FE & Yes & No& Yes & No\\
+    \smallskip
+    Country X Round FE       & No & Yes& No & Yes\\
+    \smallskip
+    Ethnic homeland FE & No & No & Yes& Yes\\
+    \smallskip
+    Observations           &      107,592   &      112,051   &       108,86   &       12,019\\
+    Adjusted-R$^2$          &       0.422   &       0.432   &       0.387   &       0.386\\
+                          \bottomrule
+    \multicolumn{5}{p{12cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
+Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
+The set of individual controls
+    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
+    education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption.
+Border samples regressions also include a measure of ethnic discrimination.
+The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy.
+The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+    \end{tabular}
+    }
+    \end{table}
 \end{document}

### 2025-02-24 writing/presentation/Untitled-1.tex
import folders

\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{positioning} % Load the positioning library

\begin{document}

\centering    
\begin{tikzpicture}
    \tikzset{
      node distance=5mm and 0mm,
      boite/.style={fill=blue!50!cyan!70,draw,align=center,
        font=\footnotesize\bfseries,text=white},
      boite coins ronds/.style={boite,rounded corners=3pt},
      boite circulaire/.style={boite,circle},
      fleche/.style={
        line cap=round,-latex,line width=0.25mm,
        draw=blue!50!cyan!30},
      grosse fleche/.style={fleche,line width=1mm},
    }

    \node[boite coins ronds]  (one) {a\\Texte vraiment très long};    
    \node[boite coins round ,below=of one]  (a) {a\\Texte vraiment très long}; % Changed to use orange boite style
    \node[boite coins ronds,below left=of a] (b) {b\\Texte vraiment\\très long};
    \node[boite coins ronds,below right=of a] (c) {c\\Texte vraiment\\très long};
    \node[boite coins ronds,below=of c] (d) {d\\Texte vraiment\\très long};
    \node[boite coins ronds,below =of b] (e) {c\\Texte vraiment\\très long};
    \node[draw=none, fill=none] (dummy) at (0,-5) {}; % Create a dummy node at a specific position, not visible
    \node[boite coins ronds, below=of dummy] (trois) {3\\Texte vraiment\\très long};

    \begin{scope}[on background layer]
      \draw[fleche,shorten >=2mm]
      (a.west) -- (b.north) node[midway,left=4mm]{};
      \draw[fleche,shorten >=2mm]
      (a.east) -- (c.north) node[midway,right=4mm]{bla bla bla};
    \end{scope}
\end{tikzpicture}

\end{document}

### 2025-02-24 writing/presentation/bc_rg - Copy.tex
import folders

\documentclass[10pt]{beamer}
\usepackage[utf8]{inputenc}

\usepackage{multirow,rotating}
\usepackage{color}
\usepackage{tikz-cd}
\usepackage{array}
\usepackage{siunitx}
\usepackage{mathtools,nccmath}%
\usepackage{etoolbox, xparse} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsopn}
\usepackage{pifont}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}

\usetikzlibrary{positioning,backgrounds, arrows.meta}

\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\usetheme{CambridgeUS}
\usecolortheme{dolphin}
\makeatletter

\setbeamertemplate{footline}{%
    \hfill{\fontsize{8pt}{16pt}\selectfont\insertframenumber}\hspace{2em}\vspace{1em}
}

\newenvironment{hidepagenumberframe}
  {\setbeamertemplate{footline}{}\begin{frame}}
  {\end{frame}\setbeamertemplate{footline}{
     \hfill{\fontsize{8pt}{16pt}\selectfont\insertframenumber}\hspace{1em}}}

\makeatother

\setbeamertemplate{caption}[numbered]

% set colors
\definecolor{myNewColorA}{RGB}{158, 27,50}
\definecolor{myNewColorB}{RGB}{158, 27,50}
\definecolor{myNewColorC}{RGB}{158, 27,50} % {130,138,143}
\setbeamercolor*{palette primary}{bg=myNewColorC}
\setbeamercolor*{palette secondary}{bg=myNewColorB, fg = white}
\setbeamercolor*{palette tertiary}{bg=myNewColorA, fg = white}
\setbeamercolor*{titlelike}{fg=myNewColorA}
\setbeamercolor*{title}{bg=myNewColorA, fg = white}
\setbeamercolor*{item}{fg=myNewColorA}
\setbeamercolor*{caption name}{fg=myNewColorA}
\setbeamercolor*{button}{bg=myNewColorA,fg= white}

% Remove the button from appearing
%\setbeamertemplate{button}{}

% Disable navigation symbols
\setbeamertemplate{navigation symbols}{}

% Disable button template
%\setbeamertemplate{button}{}

% Optional: Remove footline (if needed)
%\setbeamertemplate{footline}{}

\setbeamercolor{date in head/foot}{fg=white}

\definecolor{rougeprez}{RGB}{158,27,50}

\usefonttheme{professionalfonts}

\definecolor{babyblueeyes}{rgb}{0.63, 0.79, 0.95}
\definecolor{apricot}{rgb}{0.98, 0.81, 0.69}
\definecolor{grannysmithapple}{rgb}{0.66, 0.89, 0.63}
\definecolor{carnationpink}{rgb}{1.0, 0.65, 0.79}
\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}

\usepackage{natbib}

%------------------------------------------------------------
% \titlegraphic{\includegraphics[height=0.75cm]{ua_eng_logo.png}}

% logo of my university

%\titlegraphic{%
%\includegraphics[width=3.0cm]{ua_seal.png}
%}

\setbeamerfont{title}{size=\large}
\setbeamerfont{subtitle}{size=\small}
%\setbeamerfont{author}{size=\small}
\setbeamerfont{date}{size=\footnotesize}
\setbeamerfont{institute}{size=\footnotesize}

%\date[\textcolor{white}{Conference Name, 2022}]
%{Conference full name\\
%Aug 29-30, 2022}

%------------------------------------------------------------
%This block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:
%\AtBeginSection[]
%{
%  \begin{frame}
%    \frametitle{Contents}
%    \tableofcontents[currentsection]
%  \end{frame}
%}
%\AtBeginSection[]{
 % \begin{frame}
 % \vfill
  %\centering
  %\begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    %\usebeamerfont{title}\insertsectionhead\par%
 % \end{beamercolorbox}
  %\vfill
  %\end{frame}

% ------Contents below---
%------------------------------------------------------------

\begin{document}
\author[I. Barriola, R. Chaba]{I. Barriola\inst{1} \and R. Chaba\inst{2}}

\institute{
	\inst{1} CRED, Paris Panthéon Assas University, Paris, France
	\and
	\inst{2} LEMMA, Paris Panthéon Assas University, Paris, France
}
\title{The Death of Distance: Mobile Internet and Political Trust in Africa}
\subtitle{Working Paper}
\date{February 3, 2025}

\begin{hidepagenumberframe}
    \titlepage
\end{hidepagenumberframe}

\begin{frame}{Introduction}
    \begin{itemize}\setlength\itemsep{1em}

        \item Puzzle: attitudes towards leaders and governments need not correspond to economic outcomes
        \begin{itemize}\setlength\itemsep{1em}

            \item Developing world: rural areas show higher government approval than urban areas, despite facing lower economic development and public good provision \textcolor{gray}{\textit{McKay et al., 2023; Bland et al. 2023; Brinkerhoff et al. 2018}}
        \end{itemize}
        \item Disconnect can stem from:
        \begin{itemize}\setlength\itemsep{1em}

            \item Behavioural patterns: lower expectations \textcolor{gray}{\textit{Gottlieb, 2016; McKay et al., 2023; Provenzano, 2024; Li, 2004}}
            \item Cultural factors: clientelist network \textcolor{gray}{\textit{Henn, 2023; Adida et al., 2020; Fujiwara and Wantchekon, 2013}}
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Introduction}
    \begin{itemize}\setlength\itemsep{1em}

        \item Informations frictions: prevent citizens from accurately assessing government performance \textcolor{gray}{\textit{Bhandari et al. 2023; Dunning et al. 2019; Chong et al. 2015}}
        \item Beyond the urban-rural divide: greater distance from the capital city reduces access to political information by limiting direct observations of state activities
        \item We investigate how distance to the capital city shapes opinion on national politics and whether access to information might mitigate this pattern
    \end{itemize}
\end{frame}

\begin{frame}{Empirical strategy overview}    
    \centering Combine Afrobarometer geocoded surveys data across 20 Sub-Saharan countries
between 2011-2021, with GSMA digital maps of mobile internet coverage\\\vfill
\vspace{1em}
    \centering We examine \textbf{(1)} how distance from the capital city shapes opinion on national politics and \textbf{(2)} whether access to information might mitigate this pattern \vfill  
    \vspace{1em}
    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}
        \item Effect of distance from the capital city on political trust: \textcolor{rougeprez}{\textbf{Border
        discontinuity design}} \vfill
        \begin{itemize}\setlength\itemsep{1em}

            \item Modern national borders that arbitrarily divided historical ethnic homelands \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014; Provenzano, 2024; McCauley and Posner, 2015}}\vfill
        \end{itemize}

        \item Effect of access to information on this pattern: \textcolor{rougeprez}{\textbf{Instrumental variable}}\vfill
        \begin{itemize}\setlength\itemsep{1em}

        \item Mobile internet diffusion in the 2010s: informational shock on national politics \vfill
        \item Instrument mobile internet infrastructure with lightning strike patterns \textcolor{gray}{\textit{Guriev et al., 2021; Manacorda and Tesei, 2020; Cariolle and Carrol, 2024}}\vfill
    \end{itemize}

    \end{enumerate}
\end{frame}

\begin{frame}{Main results}

    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}\setlength\itemsep{0.5em}
        \item \textcolor{rougeprez}{\textbf{Effect of distance from the capital city on political trust}}\\
        \begin{itemize}\setlength\itemsep{1em}

            \item Remote areas (↑ distance) show more positive opinion on national politics than areas near capitals
            \begin{itemize}\setlength\itemsep{1em}

                \item 29\% higher political trust relative to the unconditional standard deviation
                \item Robust to our border discontinuity design  
            \end{itemize}
        \end{itemize}
        \item \textcolor{rougeprez}{\textbf{Effect of access to information on this pattern}}\\
        \begin{itemize}\setlength\itemsep{1em}

            \item Mobile internet erase the spatial divide in opinions on national politics
            \begin{itemize}\setlength\itemsep{1em}

                \item Bring previously disconnected remote areas in line with the more critical assessments found near capitals
                \item Only in countries with state-controlled media and weak institutions
                \item Robust to our IV strategy  
            \end{itemize}
        \end{itemize}
        \item \textcolor{rougeprez}{\textbf{Effect of access to information on political accountability}}\\
            \begin{itemize}\setlength\itemsep{1em}

                \item Greater political accountability
                \begin{itemize}\setlength\itemsep{1em}

                \item Citizens become more critical in their assessments of the country's performance
                \item Show greater willingness to sanction the ruling party through voting  
            \end{itemize}
            \end{itemize}
        \end{enumerate}
    \vspace{0.5em}
\end{frame}

\begin{frame}{Main results}
    \begin{itemize}\setlength\itemsep{1em}

        \item Physical distance is an informational barrier that might preserve positive perceptions despite poor governance
        \item Near capitals: frequent interactions with the state institutions creates informed discontents\\
        $\rightarrow$ Compare actual performance with promised outcomes, leading to more critical assessments
        \item Remote areas: infrequent exposure to state institutions\\
        $\rightarrow$ Lack access to information about government activities due to limited direct experience 
        \item Mobile internet expansion reduces information costs: can give remote citizens access to information about government activities and break their detachment from national politics
    \end{itemize}
\end{frame}

\begin{frame}{Literature contribution}
    \begin{itemize}\setlength\itemsep{1em}

        \item Political economy of the capital city
        \begin{itemize}\setlength\itemsep{1em}

            \item \textcolor{blue}{Provenzano, 2024}: remote areas consume less news and maintain higher trust in leaders despite receiving fewer public goods
            \item \textcolor{blue}{Campante and Do, 2014}: isolated capitals see lower citizen awareness of state activities
            %\item \textcolor{blue}{Brinkerhoff et al. 2018}: distance-driven information deficit affects citizen's engagement and perceptions of government services
            \item \textcolor{blue}{Michalopoulos and Papaioannou, 2014}: national institutions' effects weaken with distance from capitals
        \end{itemize}
        $\rightarrow$ \textcolor{rougeprez}{Physical distance from the capital is an informational
        barrier that might preserve positive perceptions despite poor governance}
    \end{itemize}
\end{frame}

\begin{frame}{Literature contribution}
\begin{itemize}\setlength\itemsep{1em}

    \item Effect of internet on political behaviour
    \begin{itemize}\setlength\itemsep{1em}

        \item \textcolor{blue}{Guriev et al. 2021}: 3G access reduces government approval by exposing misgovernance
        \item \textcolor{blue}{Manacorda and Tesei, 2020}: mobile internet facilitates political mobilization
        \item \textcolor{blue}{Cariolle et al. 2024}: internet access can facilitates political misperceptions
    \end{itemize}
    $\rightarrow$ \textcolor{rougeprez}{Internet access reduces information frictions on government activities that have isolated remote areas}
    \item Physical isolation from capitals need not permanently determine political attitudes\\
    $\rightarrow$ Internet expansion can reshape long-standing spatial patterns by connecting remote citizens to national politics
\end{itemize}

\end{frame}

\begin{frame}{Data}

    \begin{columns}
    \begin{column}{0.5\textwidth}
    \begin{itemize}\setlength\itemsep{1em}
\setlength\itemsep{1em}
    \item Afrobarometer surveys accross 20 Sub-Saharan countries: rounds 5 to 8 (2011-2021)
    \vspace{0.05cm}
    \begin{itemize}\setlength\itemsep{1em}
\setlength\itemsep{0.05cm}
        \item Geolocated information on public opinion, media consumption and demographic characteristics at the individual level
        \item Distance from the capital city
    \end{itemize}
    \item GSMA: 2G/3G coverage
    \begin{itemize}\setlength\itemsep{1em}
\setlength\itemsep{0.05cm}
        \vspace{0.05cm}
        \item 1×1-kilometer binary grid cells
        \item Region level mean coverage
        \item Weighted with population density grid cells
    \end{itemize}
    %\item Other sources for controls: V-DEM, World Bank, Africa Integrity Indicators...
    \end{itemize}

    \end{column}
    \begin{column}{0.5\textwidth}

    \begin{figure}
        \centering
        \caption{Country Sample and Capital Cities}
        \includegraphics[width=6cm]{C:/Users/Redha CHABA/Documents/working_paper/trust/plots/map/obs_map.jpg}
    \end{figure}
    \end{column}
        \end{columns}
    \end{frame}

\begin{frame}{Empirical strategy - Distance and political trust}
    \centering \textbf{Effect of distance from the capital city on political trust}\vspace{1em}
        \begin{equation}
        trust_{irct} = \beta_{0} + \beta_{1}dist_{irc} + \Gamma X^{'}_{ir} + \mu_{ct} + \varepsilon_{irct}
        \end{equation}
        \begin{itemize}\setlength\itemsep{1em}

            \item $trust_{irct}$: Average trust in parliament and president \vfill
            \item $dist_{irc}$: Normalized distance from the capital \\
            \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014}}\vfill
            \item $X^{'}_{ir}$: Individual and regional controls\vfill
            \item $\mu_{ct}$: Country $\times$ round fixed effects\vfill
            \item $\varepsilon_{irct}$: Error term\vfill
            \item Robust standard errors clustered at the region x round level
        \end{itemize}
\end{frame}

\begin{frame}{Empirical strategy - Distance and political trust}
    \begin{figure}
        \centering
        \caption{Historical Ethnic Areas and Contemporary National Boundaries}
        \includegraphics[width=8cm]{murdock_map.jpg}
    \end{figure}

\end{frame}

\begin{frame}{Empirical strategy - Distance and political trust}

    \begin{figure}
        \centering
        \caption{Exemple: Dendi Ethnic Group}
        \includegraphics[width=2.8cm]{bdd_map.jpg}
    \end{figure}

\begin{equation}
trust_{irct}=\beta_{0}+\beta_{1}dist_{irc}+\Gamma X^{'}_{ir}+\textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\mu_{ct}+\varepsilon_{irct}
\end{equation}

\end{frame}

\begin{frame}{Empirical strategy - Distance and political trust}
    \centering \textcolor{rougeprez}{\textbf{Identification assumptions}}\vfill
    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}
        \item Two individuals living in the same historical ethnic region share similar geographical, social, and historical traits, except for their distance from the capitals\vfill
        \item The differences observed on either side of the country border are not attributable to institutional differences\vfill

\begin{equation}
    trust_{irct}=\beta_{0}+\beta_{1}dist_{irc}+\Gamma X^{'}_{ir}+ \textcolor[rgb]{0.0,0.6,0.0}{\theta Z^{'}_{ct}} + \textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\textcolor[rgb]{0.0,0.6,0.0}{\lambda_{t}}+\varepsilon_{ict}
    \end{equation}

    \end{enumerate}
\end{frame}

\begin{frame}{Distance increases political trust}

    \begin{table}[H]
        \sffamily
        \caption{{Effect of distance from the capital on political trust}}
        \centering
        %\footnotesize
        \resizebox{8cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        &  \multicolumn{4}{c}{{OLS}}  \\
        \cmidrule(r){2-5}
        &  \multicolumn{4}{c}{{Political trust}}  \\
        \cmidrule(r){2-5}
        & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
            \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

         Distance from the capital&       0.300***&       0.298***&       0.618***&       0.341** \\
         \smallskip
         &      (0.04)   &      (0.03)   &      (0.15)   &      (0.16)   \\
         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
        \smallskip
        Country controls & Yes& No& Yes& No\\
        \smallskip
        Round FE & Yes & No& Yes & No\\
        \smallskip
        Country X Round FE       & No & Yes& No & Yes\\
        \smallskip
        Ethnic homeland FE & No & No & Yes& Yes\\
        \smallskip
        Observations           &      107,117   &      111,570   &       10,790   &       11,924   \\
        Adjusted-R$^2$         &       0.105   &       0.156   &       0.140   &       0.172   \\
                              \bottomrule
        \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption. (3) and (4) also include a measure of ethnic discrimination. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
        \end{frame}

\begin{frame}{Distance increases political trust}

\begin{figure}
    \includegraphics[scale=0.1]{C:/Users/Redha CHABA/Documents/working_paper/trust/plots/discontinuity/discontinuity.jpg}
    \caption{Border discontinuity - \textit{Based on regression estimates from (3) of Table 1}}
\end{figure}

\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial patterns of opinion}}
\centering \textcolor{rougeprez}{\textbf{Effect of internet coverage on political trust by distance}}\vspace{1em}

\begin{equation}
    \fontsize{8}{10}\selectfont
\begin{split}
trust_{irct} = & \beta_{0} + \beta_{1} dist_{irc} + \beta_{2} \textcolor{red}{\textbf{internet\_coverage}_{irct}} + \beta_{3} \textcolor{red}{\textbf{dist} \times \textbf{internet\_coverage}_{irct}} \\
& + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{irct}
\end{split}
\end{equation}\vspace{1em}

\noindent
{\fontsize{9}{12}\selectfont
\textcolor{red}{\textbf{internet\_coverage}$_{irct}$:} Regional average of internet coverage weighted by population density \textcolor{gray}{\textit{Guriev et al., 2021, Cariolle and Carroll, 2024}}
}
\vfill

\begin{itemize}\setlength\itemsep{1em}

    \item \textcolor{red}{\textbf{Reverse causality:}} Areas with higher political trust might experience less deployment of internet infrastructure
\end{itemize}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial patterns of opinion}}
    \begin{figure}
        \centering
        \caption{Example: Benin Lightning strike and Internet Coverage}

        \begin{subfigure}{0.45\textwidth}
            \centering
            \includegraphics[width=3.8cm]{lightning_strikes.jpg}
            \caption{Lightning strike}
        \end{subfigure}
        \hspace{0.02\textwidth}
        \begin{subfigure}{0.45\textwidth}
            \centering
            \includegraphics[width=3.8cm]{internet_coverage_w8.jpg}
            \caption{Internet coverage (2020)}
        \end{subfigure}        
    \end{figure}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial patterns of opinion}}    
    \centering \textcolor{rougeprez}{\textbf{Lightning strike instrument}}
    \vspace{1.5em}
    \begin{itemize}\setlength\itemsep{1em}
\setlength\itemsep{1em}
        \item Instrument internet coverage
        using regional lightning strike patterns \textcolor{gray}{\textit{Manacorda and Tesei, 2020; Guriev
                et al., 2021; Cariolle and Carolle, 2024}}\vfill
        \item Areas with frequent lightning strike face higher infrastructure deployment and maintenance costs, while these weather patterns
                are plausibly exogenous to political trust\vfill
        \item Average daily lightning strike at the regional level using VHRFC data over 1998-2013, weighted by population density\vfill
    \end{itemize}
    \vspace{1em}

\centering \textcolor{rougeprez}{\textbf{Geographical instrument $\rightarrow$ focus on the base sample}}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial patterns of opinion}}
    \centering \textbf{First-stage}

    \begin{equation}
        \begin{split}
            \textcolor{red}{\textbf{internet\_coverage}_{irct}} = & \beta_{0} + 
            \beta_{1} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{lightning\_strike}_{r} \times t} + \Gamma X^{'}_{ir} \\
            & \quad + \mu_{ct}+ v_{irct}
        \end{split}
        \end{equation}\\

    \begin{equation}
    \begin{split}
        \textcolor{red}{\textbf{dist} \times \textbf{internet\_coverage}_{irct}} = & \beta_{0} + 
        \beta_{1} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{dist} \times \textbf{lightning\_strike}_{r} \times t} + \Gamma X^{'}_{ir} \\
        & \quad + \mu_{ct}+ v_{irct}
    \end{split}
    \end{equation}\\

    \centering \textbf{Second-stage}
    \fontsize{8}{10}\selectfont
    \begin{equation}
        \begin{split}
        trust_{irct} = & \beta_{0} + \beta_{1} dist_{irc} + \beta_{2}^{2S}\textcolor[rgb]{0.0,0.6,0.0}{\textbf{internet\_coverage}_{irct}} + \beta_{3}^{2S}\textcolor[rgb]{0.0,0.6,0.0}{\textbf{dist} \times \textbf{internet\_coverage}_{irct}} \\
        & + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{irct}
        \end{split}
        \end{equation}

\end{frame}

\begin{frame}{Internet mitigates spatial patterns of opinion}
    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance from the capital&       0.453***&&&&       1.523***\\
    \smallskip
    &      (0.05)   &&&&      (0.56)   \\
    Internet coverage&      -0.015   &&&&       1.770** \\
\smallskip
&      (0.06)   &&&&      (0.69)   \\
Distance from the capital $\times$ Internet coverage&     -0.466***&&&&       -2.950**         \\
\smallskip
            &      (0.10)   &&&&        (1.45)           \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&&-0.000 && -0.001***\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 13.74&- &-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 8.62 &-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       111,570    &113,243 & 113,243&       111,570  \\
        Adjusted-R$^2$    &       0.158     &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{25cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}
\end{frame}

\begin{frame}{Internet mitigates spatial patterns of opinion}

\begin{figure}
    \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/working_paper/trust/plots/marginal_effect/pol_trust.png}
    \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
\end{figure}

\end{frame}

\begin{frame}{Internet is effective in countries with weak institutions}
    \begin{table}[H]
        \sffamily
        \caption{{Media and institutions freedom}}
        \centering
        %\footnotesize
        \resizebox{10.5cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{2SLS: Political trust}\\
        \cmidrule(r){2-5}
        & \multicolumn{4}{c}{{Base sample}}\\
        \cmidrule(r){2-5}
        &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
        \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

      Distance from the capital&      -8.382   &       1.083** &       2.367   &       0.938***\\
      \smallskip
      &      (24.71)   &      (0.42)   &      (1.50)   &      (0.32)   \\
      Internet coverage&      -5.260   &       1.004   &       2.653*  &       0.762   \\
      \smallskip
      &      (19.11)   &      (0.74)   &      (1.49)   &      (0.69)   \\
      Distance from the capital $\times$ Internet coverage&      18.335   &      -2.149*  &      -5.132   &      -1.524**  \\
      \medskip
      &       (52.59)   &      (1.25)   &      (3.92)   &      (0.77)   \\

         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes & Yes& Yes\\
        \smallskip
        Observations          &       50,288   &       61,282   &       51,737   &       59,833  \\
        \bottomrule
        \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Internet enchances political accountability}
    \begin{table}[H]
        \sffamily
        \caption{{Political accountability}}
        \centering
        %\footnotesize
        \resizebox{11cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c}
        \\
        \toprule
        \toprule
        & \multicolumn{2}{c}{2SLS}\\
        \cmidrule(r){2-3}
        &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
         \midrule

        Distance from the capital&      -0.932***&       1.874***\\
        \smallskip
        &      (0.28)   &      (0.65)   \\
        Internet coverage&       -1.163***&       2.089***\\
        \smallskip
        &        (0.41)   &      (0.77) \\
        Distance from the capital $\times$ Internet coverage&       2.104***&      -4.200** \\
        \medskip
        &      (0.74)   &      (1.69)   \\

         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes\\
        \smallskip
        Observations      &      74,959   &      111,696  \\            \bottomrule
        \multicolumn{3}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Internet is effective on low educated and beyond the urban-rural divide}
    \begin{table}[H]
        \sffamily
        \caption{{Individual heterogeneity}}
        \centering
        %\footnotesize
        \resizebox{11cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{2SLS: Political trust}\\
        \cmidrule(r){2-5}
        & \multicolumn{4}{c}{{Base sample}}\\
        \cmidrule(r){2-5}
        &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}\\
        \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

           Distance from the capital&        1.467***&       1.440   &       1.074** &       2.666***\\
           \smallskip
           &      (0.45)   &      (1.44)   &      (0.54)   &      (0.89)  \\
           Internet coverage&       1.613** &       1.632   &       0.525   &       4.471***\\
           \smallskip
           &     (0.63)   &      (1.34)   &      (0.62)   &      (1.48)    \\
           Distance from the capital $\times$ Internet coverage&      -2.901** &      -2.688   &      -1.787   &      -5.898** \\
           \medskip
           &       (1.24)   &      (3.22)   &      (1.12)   &      (2.55)    \\

         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes & Yes& Yes\\
        \smallskip
        Observations         &        79,394   &       32,176   &       42,509   &       69,061\\
        \bottomrule
        \multicolumn{5}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Conclusion}

    \begin{itemize}\setlength\itemsep{1em}

        \item We document how distance from capitals creates information barriers that shape citizens' political behaviour
        \begin{itemize}\setlength\itemsep{1em}

            \item Remote areas have more positive opinions on national politics and country's performance despite limited experience with state institutions
            \item Broader literature on the disconnect between citizens' attitudes and government performance in developing countries
        \end{itemize}
        \item We show that internet expansion can disrupt these spatial patterns in political behaviour
        \begin{itemize}\setlength\itemsep{1em}

            \item Reduces information frictions that have isolated remote populations but only in countries with state-controlled media and weak institutions
            \item Internet access brings remote citizens' poltical assessments in line with the more critical views found near capitals
        \end{itemize}
        \item Previous works highlights that state capacity declines with distance from the capital, whith implications for economic development
        \begin{itemize}\setlength\itemsep{1em}

            \item We demonstrate that internet can reshape spatial patterns in political behaviour, suggesting that physical isolation need not permanently determine political attitudes
        \end{itemize}
    \end{itemize}

\end{frame}

\end{document}

### 2025-02-24 writing/presentation/bc_rg.tex
import folders

\documentclass[10pt]{beamer}
\usepackage[utf8]{inputenc}

\usepackage{multirow,rotating}
\usepackage{color}
\usepackage{tikz-cd}
\usepackage{array}
\usepackage{siunitx}
\usepackage{mathtools,nccmath}%
\usepackage{etoolbox, xparse} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsopn}
\usepackage{pifont}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}

\usetikzlibrary{positioning,backgrounds, arrows.meta}

\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\usetheme{CambridgeUS}
\usecolortheme{dolphin}
\makeatletter

\setbeamertemplate{footline}{%
    \hfill{\fontsize{8pt}{16pt}\selectfont\insertframenumber}\hspace{2em}\vspace{1em}
}

\newenvironment{hidepagenumberframe}
  {\setbeamertemplate{footline}{}\begin{frame}}
  {\end{frame}\setbeamertemplate{footline}{
     \hfill{\fontsize{8pt}{16pt}\selectfont\insertframenumber}\hspace{1em}}}

\makeatother

\setbeamertemplate{caption}[numbered]

% set colors
\definecolor{myNewColorA}{RGB}{158, 27,50}
\definecolor{myNewColorB}{RGB}{158, 27,50}
\definecolor{myNewColorC}{RGB}{158, 27,50} % {130,138,143}
\setbeamercolor*{palette primary}{bg=myNewColorC}
\setbeamercolor*{palette secondary}{bg=myNewColorB, fg = white}
\setbeamercolor*{palette tertiary}{bg=myNewColorA, fg = white}
\setbeamercolor*{titlelike}{fg=myNewColorA}
\setbeamercolor*{title}{bg=myNewColorA, fg = white}
\setbeamercolor*{item}{fg=myNewColorA}
\setbeamercolor*{caption name}{fg=myNewColorA}
\setbeamercolor*{button}{bg=myNewColorA,fg= white}
\definecolor{rougeprez}{RGB}{158,27,50}
% Remove the button from appearing
%\setbeamertemplate{button}{}

% Disable navigation symbols
\setbeamertemplate{navigation symbols}{}

% Disable button template
%\setbeamertemplate{button}{}

% Optional: Remove footline (if needed)
%\setbeamertemplate{footline}{}

\setbeamercolor{date in head/foot}{fg=white}

\usefonttheme{professionalfonts}

\definecolor{babyblueeyes}{rgb}{0.63, 0.79, 0.95}
\definecolor{apricot}{rgb}{0.98, 0.81, 0.69}
\definecolor{grannysmithapple}{rgb}{0.66, 0.89, 0.63}
\definecolor{carnationpink}{rgb}{1.0, 0.65, 0.79}
\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}

\usepackage{natbib}

%------------------------------------------------------------
% \titlegraphic{\includegraphics[height=0.75cm]{ua_eng_logo.png}}

% logo of my university

%\titlegraphic{%
%\includegraphics[width=3.0cm]{ua_seal.png}
%}

\setbeamerfont{title}{size=\large}
\setbeamerfont{subtitle}{size=\small}
%\setbeamerfont{author}{size=\small}
\setbeamerfont{date}{size=\footnotesize}
\setbeamerfont{institute}{size=\footnotesize}

%\date[\textcolor{white}{Conference Name, 2022}]
%{Conference full name\\
%Aug 29-30, 2022}

%------------------------------------------------------------
%This block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:
%\AtBeginSection[]
%{
%  \begin{frame}
%    \frametitle{Contents}
%    \tableofcontents[currentsection]
%  \end{frame}
%}
%\AtBeginSection[]{
 % \begin{frame}
 % \vfill
  %\centering
  %\begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    %\usebeamerfont{title}\insertsectionhead\par%
 % \end{beamercolorbox}
  %\vfill
  %\end{frame}

% ------Contents below---
%------------------------------------------------------------

\begin{document}
\author[I. Barriola, R. Chaba]{I. Barriola\inst{1} \and R. Chaba\inst{2}}

\institute{
	\inst{1} CRED, Paris Panthéon Assas University, Paris, France
	\and
	\inst{2} LEMMA, Paris Panthéon Assas University, Paris, France
}
\title{The Death of Distance: Mobile Internet and Political Trust in Africa}
\subtitle{Working Paper}
\date{February 3, 2025}

\begin{hidepagenumberframe}
    \titlepage
\end{hidepagenumberframe}

\begin{frame}{Context}
    \begin{quotation}
        \noindent \textbf{``The State stops at PK 12, twelve kilometers from the capital, Bangui.''}\\       
        \hfill -- A Central African Republic official \textcolor{gray}{\textit{(Bierschenk \& Olivier de Sardan, 1997)}} 
        \end{quotation}\smallskip \pause

    \begin{itemize}\setlength\itemsep{1em}
        \item Broader pattern of spatial disparity in state presence across Africa: state presence diminishes sharply with distance from
        capital cities \vfill \pause
        \item Colonial powers’ strategic placement of capital cities in \hyperlink{sample_map}{{peripheral locations}}
        \vfill \label{context}
        \begin{itemize}
            \item Most former colonial capitals became modern national capitals \vfill
            \item Persistent disparities in how African states
            interact with their populations \textcolor{gray}{\textit{Lewis, 1954; Bates, 1983}} \vfill
            \item Centralization formalized in 80\% of African constitutions \textcolor{gray}{\textit{Kuperman, 2015}} \vfill  \pause
        \end{itemize} 
        \item As distance from the capital
        increases, national institutions struggle to project their authority, leading to systematic
        variations in state presence \textcolor{gray}{\textit{Migdal, 1988; Herbst, 2000; Michalopoulos and Papaioannou,
        2014}} \vfill   \pause
        \vspace{1em}
        \centering Shape how citizens develop trust in political institutions, depending on their proximity to the capital city \vfill
    \end{itemize}
\end{frame}

\begin{frame}{Motivation}
        \centering Spatial variation in state presence creates two interrelated challenges that shape citizens’ relationship
        with political institutions\vfill   \pause
        \smallskip
        \setbeamertemplate{enumerate items}[default]

        \begin{enumerate}
            \item Information scarcity in remote areas alters how citizens process and respond to political information\vfil
            \begin{itemize}\setlength\itemsep{1em}
                \vspace{0.5em}
                \item Given the high costs of acquiring reliable information about government performance, citizens rationally adapt by relying
                on accessible but potentially biased sources: ethnic affiliations, partisan signals, and local
                social networks \textcolor{gray}{\textit{McKay et al., 2023; Brinkerhoff et al., 2018}}\vfill   \pause
                \item Without exposure to comparative benchmarks, these citizens lack reference points
                for evaluating public service quality, often normalizing suboptimal outcomes as the status
                quo \textcolor{gray}{\textit{Adida et al., 2020; Gottlieb, 2016; Provenzano, 2024}}\vfill
               \end{itemize}
            \end{enumerate}
        \end{frame}

\begin{frame}{Motivation}
    \setbeamertemplate{enumerate items}[default]

    \begin{enumerate}
        \setcounter{enumi}{1}
        \item Self-reinforcing cycle of low expectations and reduced engagement
        \begin{itemize}\setlength\itemsep{1em}
            \vspace{0.5em}
            \item Infrequent interactions with state institutions and officials lead citizens to downgrade their expectations
            of government capacity and responsiveness \textcolor{gray}{\textit{McKay et al., 2023; Brinkerhoff et al., 2018}}   \pause
            \item Systematic detachment from the state institutions develop
            a form of rational inattention: citizens who rarely encounter state services have little
            incentive to invest in monitoring government performance   \pause
            \item Physical and psychological
            distance from the capital further weakens national identification, creating a disconnect between
            remote populations and central institutions \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014;
            Campante et al., 2019; Brinkerhoff et al., 2018; McKay et al., 2023}}\vfill   \pause
        \end{itemize}
    \end{enumerate}

    \centering These dynamics converge into an equilibrium of uninformed, disengaged trust in remote areas that undermines political accountability \vfill
\end{frame}

\begin{frame}{Motivation}
\centering \textit{Uninformed trust} in political institutions can undermine democratic accountability and effective governance \vfill  \pause
\vspace{1em}
    \begin{itemize}\setlength\itemsep{1em}
        %\item Citizens may struggle to monitor and scrutinize public officials, weakening electoral accountability \textcolor{gray}{\textit{Dunning
        %et al., 2019; McKay et al., 2023}} \vfill
        \item Perpetuate a low-accountability equilibrium where politicians have weak incentives to deliver quality services or respond to
        citizen demands \textcolor{gray}{\textit{Gottlieb, 2016; Harding, 2015}} \vfill
        \begin{itemize}\setlength\itemsep{0.5em}
            \item Exacerbating regional inequalities \textcolor{gray}{\textit{Asher et al., 2018; Provenzano, 2024}} \vfill
            \item Slowing institutional development \textcolor{gray}{\textit{Kaasa
            and Andriani, 2022; Evans and Rose, 2012}} \vfill   \pause
        \end{itemize}
        \item Create opportunities for corruption and misallocation of resources \textcolor{gray}{\textit{Campante and Do, 2014; Campante et al.,
        2019; Guriev et al., 2021}} \vfill  \pause
        \vspace{1em}
      \centering How information frictions
        affect institutional development and whether a new information channel can
        reshape these spatial patterns \vfill
    \end{itemize}
\end{frame}

\begin{frame}{Motivation}
    \begin{itemize}\setlength\itemsep{1em}
        \vspace{0.5em}
        \item Expansion of mobile
        internet access can disrupt this equilibrium by reducing information barriers in previously
        isolated areas \vfill  \pause
        \begin{itemize}
        \item Provide both the tools and motivation for monitoring government
            performance \textcolor{gray}{\textit{Manacorda and Tesei, 2020; Guriev et al., 2021}} \vfill  \pause
            \item Rapid expansion of mobile internet in Sub-Saharan Africa – from virtually no access in 2010 to 40\% coverage by 2021 \textcolor{gray}{\textit{GSMA}} \vfill  \pause
        \end{itemize}
            \item Depends on important scope conditions \vfill  \pause
            \begin{itemize}
            \item Governments may capture these new information flows or the deployment of its infrastructure \textcolor{gray}{\textit{Chen and Xu, 2017; Morozov, 2012}} \vfill  \pause
            \item Regional and ethnic favoritism from ruling governments \textcolor{gray}{\textit{Franck and Rainer, 2012;
              Hodler and Raschky, 2014; Kramon and Posner, 2016; De Luca et al., 2018}} \vfill
            \end{itemize}
              %\item The resulting transformation could strengthen electoral accountability \textcolor{gray}{\textit{Donati, 2023}}, enhance
         %   political responsiveness \textcolor{gray}{\textit{Grossman et al., 2021}} \vfill
        %\item Reshape the spatial distribution
        %    of state capacity \textcolor{gray}{\textit{Pierskalla et al., 2017; Campante and Do, 2014;
        %    Campante et al., 2019}} \vfill
    \end{itemize}
\end{frame}

\begin{frame}{This paper}
    \begin{center}
        How mobile internet expansion affects political trust across
        varying distances from Sub-Saharan African capitals  \pause
        \end{center}\vfill
    \begin{itemize}\setlength\itemsep{1em}
\item Remote areas are more prone to \textit{uninformed trust} in political institutions due to both information scarcity and low expectation-engagement cycle\vfill  \pause
\item Mobile internet potentially breaks this information barrier by reducing the cost of accessing
information about government performance, particularly in previously isolated areas\vfill  \pause
\item Mobile internet can reduce the distance effect on political trust, causing a "death of distance" that transforms \textit{uninformed trust} into active engagement\vfill
    \end{itemize}
\end{frame}

\begin{frame}{This paper}
\centering
\begin{tikzpicture}
        \tikzset{
          node distance=5mm and 0mm,
          boite/.style={
            fill=blue!50!cyan!70,draw,align=center,
            font=\footnotesize\bfseries,text=black,
          },
          boite coins ronds/.style={boite,rounded corners=3pt},
          boite circulaire/.style={boite,circle},
          fleche/.style={
            line cap=round,-latex,line width=0.25mm,
            draw=blue!50!cyan!30,
          },
          grosse fleche/.style={fleche,line width=1mm},
          }
        \node[boite coins ronds, fill=babyblueeyes]  (a) {Non-centralized capital city};    
        \node[boite coins ronds, fill=babyblueeyes, below=of a]  (b) {Spatial disparities in citizens-states interaction};
        \node[boite coins ronds, fill=apricot, below left=1cm and -0.7cm of b] (c) {Close to the capital};
        \node[boite coins ronds, fill=grannysmithapple, below right=1cm and -0.7cm of b] (d) {Far from the capital};
        \node[boite coins ronds, fill=grannysmithapple, below=1cm of d] (f) {Low information\\(- State contact - Media access)};
        \node[boite coins ronds,fill=apricot, below = 1cm of c] (e) {High information\\(+ State contact + Media access)};
        \node[draw=none, fill=none] (dummy) at (0,-5) {}; % Create a dummy node at a specific position, not visible
        \node[boite coins ronds, fill=carnationpink] (g) at (0,-5.8) {Spatial heterorogeneity in political trust};

        \begin{scope}[on background layer]
            \draw[fleche,draw=babyblueeyes, shorten >=1mm]
            (a.south) -- (b.north) node[midway]{};  
            \draw[fleche,draw=babyblueeyes, shorten >=1mm]
            (b.west) -- (c.north) node[midway]{};
            \draw[fleche,draw=babyblueeyes, shorten >=1mm]
            (b.east) -- (d.north) node[midway]{};
            \draw[fleche,draw=apricot, shorten >=1mm]
            (c.south) -- (e.north) node[midway]{};
            \draw[fleche,draw=grannysmithapple, shorten >=1mm]
            (d.south) -- (f.north) node[midway]{};
            \draw[fleche,draw=apricot, shorten >=1mm]
            (e.south) -- (g.west)  node[midway]{};
            \draw[fleche,draw=grannysmithapple, shorten >=1mm]
            (f.south) -- (g.east)  node[midway]{};

        \end{scope}
      \end{tikzpicture}
    \end{frame}

    \begin{frame}{This paper}
        \centering
        \begin{tikzpicture}
                \tikzset{
                  node distance=5mm and 0mm,
                  boite/.style={
                    fill=blue!50!cyan!70,draw,align=center,
                    font=\footnotesize\bfseries,text=black,
                  },
                  boite coins ronds/.style={boite,rounded corners=3pt},
                  boite circulaire/.style={boite,circle},
                  fleche/.style={
                    line cap=round,-latex,line width=0.25mm,
                    draw=blue!50!cyan!30,
                  },
                  grosse fleche/.style={fleche,line width=1mm},
                  }
                \node[boite coins ronds, fill=babyblueeyes]  (a) {Non-centralized capital city};    
                \node[boite coins ronds, fill=babyblueeyes, below=of a]  (b) {Spatial disparities in citizens-states interaction};
                \node[boite coins ronds, fill=apricot, below left=1cm and -0.7cm of b] (c) {Close to the capital};
                \node[boite coins ronds, fill=grannysmithapple, below right=1cm and -0.7cm of b] (d) {Far from the capital};
                \node[boite coins ronds, fill=grannysmithapple, below=1cm of d] (f) {Low information\\(- State contact - Media access)};
                \node[boite coins ronds,fill=apricot, below = 1cm of c] (e) {High information\\(+ State contact + Media access)};
                \node[boite coins ronds,fill=brilliantlavender] (dummy) at (0,-4.15) {Internet\\expansion}; % Create a dummy node at a specific position, not visible
                \node[boite coins ronds, fill=carnationpink] (g) at (0,-5.8){Spatial heterorogeneity in political trust};

                \begin{scope}[on background layer]
                    \draw[fleche,draw=babyblueeyes, shorten >=1mm]
                    (a.south) -- (b.north) node[midway]{};  
                    \draw[fleche,draw=babyblueeyes, shorten >=1mm]
                    (b.west) -- (c.north) node[midway]{};
                    \draw[fleche,draw=babyblueeyes, shorten >=1mm]
                    (b.east) -- (d.north) node[midway]{};
                    \draw[fleche,draw=apricot, shorten >=1mm]
                    (c.south) -- (e.north) node[midway]{};
                    \draw[fleche,draw=grannysmithapple, shorten >=1mm]
                    (d.south) -- (f.north) node[midway]{};
                    \draw[fleche,draw=apricot, shorten >=1mm]
                    (e.south) -- (g.west)  node[midway]{};
                    \draw[fleche,draw=grannysmithapple, shorten >=1mm]
                    (f.south) -- (g.east)  node[midway]{};
                    \draw[fleche,draw=brilliantlavender, shorten >=1mm]
                    (dummy.west) -- (e.east)  node[midway]{};
                    \draw[fleche,draw=brilliantlavender, shorten >=1mm]
                    (dummy.east) -- (f.west)  node[midway]{};

                \end{scope}
              \end{tikzpicture}
            \end{frame}

            %\begin{frame}{This paper}

                %\begin{itemize}
                    %\item Economic theory suggest that better information leads to more efficient outcomes in political institutions \textcolor{gray}{\textit{Besley and Burgess, 2002;
                    %Banerjee et al., 2011; Fujiwara and Wantchekon, 2013; Larreguy et al., 2020}} \vfill
                    %\item We document a spatial pattern in Sub-Saharan Africa:\\ \vfill
                    %\vspace{1em}
                    %\begin{center} Citizens living in remote areas have \textcolor{rougeprez}{\textbf{limited exposure to state institutions}} and \textcolor{rougeprez}{\textbf{reduced access to information infrastructure}} but they report \textcolor[rgb]{0.0,0.6,0.0}{\textbf{higher trust in state institutions}} relative to those near capitals \vfill
                    %\end{center}
                %\end{itemize}
            %\hspace{2.5em}$\Rightarrow$ \textit{Uninformed trust}
            %\begin{itemize}
                %\item Internet coverage reduces spatial disparities in political trust
            %\end{itemize}
            %\end{frame}

            %\begin{frame}{This paper}
             %   \centering The extent to which this potential is realized likely depends on several important scope conditions \vfill  \pause
             %   \begin{itemize}\setlength\itemsep{1em}
              %      \item Regional and ethnic favoritism from ruling governments \textcolor{gray}{\textit{Franck and Rainer, 2012;
              %      Hodler and Raschky, 2014; Kramon and Posner, 2016; De Luca et al., 2018}} \vfill  \pause
              %      \item Threatened governments may try to capture the functioning of these new information flows or the deployment of its infrastructure to
              %      preserve their advantages \textcolor{gray}{\textit{Chen and Xu, 2017; Morozov, 2012}} \vfill  \pause
              %      \item The quality and reliability of the information; if mobile
              %      internet facilitates misinformation and manipulation \textcolor{gray}{\textit{Cariolle et al., 2024; Van Zoonen et al., 2024}}, it could actually undermine rather than
              %      strengthen accountability linkages
              %  \end{itemize}    
           % \end{frame}

            \begin{frame}{Empirical strategy overview}    
                \centering Combine Afrobarometer geocoded surveys data across 20 Sub-Saharan countries
between 2011-2021, with GSMA digital maps of mobile internet coverage\\\vfill
\vspace{1em}
                \centering We examine \textbf{(1)} spatial disparities in political trust and \textbf{(2)} how mobile internet access expansion may affect these differences \vfill  \pause
                \vspace{1em}
                \setbeamertemplate{enumerate items}[default]
                \begin{enumerate}
                    \item Effect of capital city distance on political trust: \textcolor{rougeprez}{\textbf{Border
                    discontinuity design}} \vfill
                    \begin{itemize}
                        \item Colonial boundaries - which became modern national borders
                        - that arbitrarily divided historical ethnic homelands \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014; Provenzano, 2024}}\vfill
                        \item Sharp variations in citizens’
                        distances from their respective national capital\vfill  \pause
                    \end{itemize}

                    \item Internet coverage effect: \textcolor{rougeprez}{\textbf{Instrumental variable}}\vfill

                    \begin{itemize}
                    \item Instrument for internet coverage using lightning strike
                    patterns \textcolor{gray}{\textit{Manacorda and Tesei, 2020; Guriev et al., 2021}}\vfill
                    \item Areas with frequent lightning strikes have
                    higher costs for internet infrastructure deployment and maintenance, while these weather
                    patterns are plausibly exogenous to political trust\vfill
                \end{itemize}

                \end{enumerate}
            \end{frame}

\begin{frame}{Main results}

    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}\setlength\itemsep{0.5em}
        \item \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Distance from the capital effect}}\\
        \begin{itemize}
            \item Remote areas (↑ distance) show a 27\% higher political trust relative to the unconditional standard deviation
            \begin{itemize}
                \item Robust to border discontinuity design using national boundaries overlapping ethnic areas  \pause
            \end{itemize}
        \end{itemize}
        \item \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Internet coverage effect}}\\
        \begin{itemize}
            \item Internet coverage reduces spatial disparities in political trust
            \begin{itemize}
                \item Strong negative interaction between distance and internet coverage
                \item Robust to IV strategy using lightning strike patterns  \pause
            \end{itemize}
        \end{itemize}
        \item \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Political accountability}}\\
            \begin{itemize}
                \item Citizens with internet access in remote areas are more critical of the economy
                \item They are more willing to sanction the ruling party through voting  \pause
            \end{itemize}
        \item  \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Information censorship}}
        \begin{itemize}
            \item Stronger effect where the government controls the traditional media and institutions
            \item Major source of news when no other independent information are available  \pause
        \end{itemize}

    \end{enumerate}
    \vspace{0.5em}
    \begin{center}
        \textbf{Internet access facilitates the shift from \textit{uninformed trust} to active democratic engagement, particularly in previously isolated areas}
    \end{center}
\end{frame}

\begin{frame}{Literature contribution}

    \begin{itemize}\setlength\itemsep{1em}
        \item Geography of trust \vfill
        \begin{itemize}
            \item Distance from administrative centers \textcolor{gray}{\textit{Brinkerhoff et al. 2018; Bland et al., 2023; Li, 2004}} \vfill
            \item Higher institutional trust in rural area \textcolor{gray}{\textit{McKay et al., 2023; Li, 2004}} \vfill
        \end{itemize}
        \textcolor{rougeprez}{\textbf{$\rightarrow$ Distance shapes citizens’ political trust}}\vfill
        \item Political economy of the capital city \vfill
        \begin{itemize}
            \item National institutions’ reach \textcolor{gray}{\textit{Herbst, 2000; Michalopoulos and Papaioannou, 2014}} \vfill
            \item Democratic accountability \textcolor{gray}{\textit{Provenzano, 2024; Gottlieb, 2016}} \vfill
            \item State capacity \textcolor{gray}{\textit{Pierskalla et al., 2017; Müller-Crepon, 2023}}  \vfill
        \end{itemize}
        \textcolor{rougeprez}{$\rightarrow$ \textbf{Strategic placement affects patterns of political trust and democratic engagement}}\vfill

        \item Internet role in accountability and governance information\vfill
        \begin{itemize}
            \item Governance satisfaction \textcolor{gray}{\textit{Guriev et al., 2021; Cariolle et al., 2024; Miner, 2015}} \vfill
            \item Electoral accountability \textcolor{gray}{\textit{Donati, 2023; Chong et al., 2015}} \vfill
        \end{itemize}
        \textcolor{rougeprez}{$\rightarrow$ \textbf{Connectivity reshapes spatial patterns of accountability}}\vfill
    \end{itemize}
    \end{frame}

\begin{frame}{Data}

    \begin{columns}
    \begin{column}{0.5\textwidth}
    \begin{itemize}\setlength\itemsep{1em}
    \item Afrobarometer surveys accross 20 Sub-Saharan countries: rounds 5 to 8 (2011-2021)
    \vspace{0.05cm}
    \begin{itemize}\setlength\itemsep{0.05cm}
        \item Geolocated information on public opinion, media consumption and demographic characteristics at the individual level
        \item Distance from the capital city
    \end{itemize}
    \item Collins Bartholomew’s Mobile Coverage Explorer: 2G/3G network coverage (2011-2021)
    \begin{itemize}\setlength\itemsep{0.05cm}
        \vspace{0.05cm}
        \item 1×1-kilometer binary grid cells
        \item Regional level mean coverage
        \item Weighted by UN-adjusted population density grid cells
    \end{itemize}
    %\item Other sources for controls: V-DEM, World Bank, Africa Integrity Indicators...
    \end{itemize}

    \end{column}
    \begin{column}{0.5\textwidth}

    \begin{figure}
        \centering
        \caption{Country Sample and Capital Cities}
        \includegraphics[width=6cm]{obs_map.jpg}
    \end{figure}
    \end{column}
        \end{columns}
    \end{frame}

\begin{frame}{Empirical strategy - Spatial disparities in political trust}
    \centering \textbf{Effect of distance from the capital city on political trust}\vspace{1em}
        \begin{equation}
        trust_{ict} = \beta_{0} + \beta_{1}distance_{ict} + \gamma X^{'}_{ir} + \mu_{ct} + \varepsilon_{ict}
        \end{equation}
        \begin{itemize}
            \item $trust_{ict}$: Average trust in parliament and president (0-3 scale)\vfill
            \item $distance_{ict}$: Relative distance measure (0-1 scale)\\
            \vspace{0.1cm}
            $\rightarrow{}$ \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014}}\vfill
            \item $X^{'}_{ir}$: Set of individual and regional controls\vfill
            \item $\mu_{ct}$: Country $\times$ round fixed effects\vfill
            \item $\epsilon_{ict}$: Error term\vfill
            \item Robust standard errors clustered at the region x round level
        \end{itemize}
\end{frame}

\begin{frame}{Empirical strategy - Spatial disparities in political trust}

    \centering \textcolor{rougeprez}{\textbf{Border discontinuity design}} \vfill
    \begin{itemize}\setlength\itemsep{1em}
            \item Colonial boundaries - which became modern national borders
            - that arbitrarily divided historical ethnic homelands  \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014; Provenzano, 2024}}\vfill
            \item These arbitrary divisions created
            quasi-random national affiliations in border regions, generating sharp variations in citizens’
            distances from their respective national capital \vfill
            \item Compare individuals from the same ethnic group who, due to colonial boundaries, live at different distances
            from their capital cities \vfill
        \end{itemize}
\end{frame}

\begin{frame}{Empirical strategy - Spatial disparities in political trust}
    \begin{figure}
        \centering
        \caption{Historical Ethnic Areas and Contemporary National Boundaries}
        \includegraphics[width=8cm]{murdock_map.jpg}
    \end{figure}

\end{frame}

\begin{frame}{Empirical strategy - Spatial disparities in political trust}

    \begin{figure}
        \centering
        \caption{Exemple: Dendi Ethnic Group}
        \includegraphics[width=2.8cm]{bdd_map.jpg}
    \end{figure}

\begin{equation}
trust_{ict}=\beta_{0}+\beta_{1}distance_{ict}+\gamma X^{'}_{ir}+\textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\mu_{ct}+\varepsilon_{ict}
\end{equation}

\end{frame}

\begin{frame}{Empirical strategy - Spatial disparities in political trust}
    \centering \textcolor{rougeprez}{\textbf{Identification assumptions}}\vfill
    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}
        \item Two individuals living in the same historical ethnic region share similar geographical, social, and historical traits, except for their distance from the capitals\vfill
        \item The differences observed on either side of the country border are not attributable to institutional differences\vfill

\begin{equation}
    trust_{ict}=\beta_{0}+\beta_{1}distance_{ict}+\gamma X^{'}_{ir}+ \textcolor[rgb]{0.0,0.6,0.0}{\theta Z^{'}_{ct}} + \textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\textcolor[rgb]{0.0,0.6,0.0}{\lambda_{t}}+\varepsilon_{ict}
    \end{equation}

    \end{enumerate}
\end{frame}

\begin{frame}{Distance increases political trust}

    \begin{table}[H]
        \sffamily
        \caption{{Effect of distance from the capital on political trust}}
        \centering
        %\footnotesize
        \resizebox{8cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        &  \multicolumn{4}{c}{{OLS}}  \\
        \cmidrule(r){2-5}
        &  \multicolumn{4}{c}{{Political trust}}  \\
        \cmidrule(r){2-5}
        & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
            \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

         Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
         \medskip
         &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
        \smallskip
        Country controls & Yes& No& Yes& No\\
        \smallskip
        Round FE & Yes & No& Yes & No\\
        \smallskip
        Country X Round FE       & No & Yes& No & Yes\\
        \smallskip
        Ethnic homeland FE & No & No & Yes& Yes\\
        \smallskip
        Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
        Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\

                              \bottomrule
        \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
    \end{frame}

\begin{frame}{Distance increases political trust}

\begin{figure}
    \includegraphics[scale=0.1]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/discontinuity/discontinuity.jpg}
    \caption{Border discontinuity - \textit{Based on regression estimates from (3) of Table 1}}
\end{figure}

\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial disparities}}
\centering \textcolor{rougeprez}{\textbf{Effect of internet coverage on political trust by distance}}\vspace{1em}

\begin{equation}
    \fontsize{8}{10}\selectfont
\begin{split}
trust_{ict} = & \beta_{0} + \beta_{1} distance_{ict} + \beta_{2} \textcolor{red}{\textbf{internet\_coverage}_{ict}} + \beta_{3} \textcolor{red}{\textbf{distance} \times \textbf{internet\_coverage}_{ict}} \\
& + \gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{ict}
\end{split}
\end{equation}\vspace{1em}

\noindent
{\fontsize{9}{12}\selectfont
\textcolor{red}{\textbf{internet\_coverage}$_{ict}$:} Regional average of internet coverage weighted by population density \textcolor{gray}{\textit{Guriev et al., 2021, Cariolle and Carroll, 2024}}
}
\vfill

\begin{itemize}
    \item \textcolor{red}{\textbf{Reverse causality:}} Areas with higher political trust might experience less deployment of internet infrastructure
\end{itemize}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial disparities}}
    \begin{figure}
        \centering
        \caption{Example: Benin Lightning Strikes and Internet Coverage}

        \begin{subfigure}{0.45\textwidth}
            \centering
            \includegraphics[width=3.8cm]{lightning_strikes.jpg}
            \caption{Lightning strikes}
        \end{subfigure}
        \hspace{0.02\textwidth}
        \begin{subfigure}{0.45\textwidth}
            \centering
            \includegraphics[width=3.8cm]{internet_coverage_w8.jpg}
            \caption{Internet coverage (2019-2021)}
        \end{subfigure}

    \end{figure}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial disparities}}    
    \centering \textcolor{rougeprez}{\textbf{Lightning strikes instrument}}
    \vspace{1.5em}
    \begin{itemize}\setlength\itemsep{1em}
        \item Instrument internet coverage
        using regional lightning strike patterns \textcolor{gray}{\textit{Manacorda and Tesei, 2020; Guriev
                et al., 2021; Cariolle and Carolle, 2024}}\vfill
        \item Areas with frequent lightning strikes face higher infrastructure deployment and maintenance costs, while these weather patterns
                are plausibly exogenous to political trust\vfill
        \item Average daily lightning strikes at the regional level using VHRFC data over 1998-2013, weighted by regional population density\vfill
    \end{itemize}
    \vspace{1em}

\centering \textcolor{rougeprez}{\textbf{Geographical instrument $\rightarrow$ focus on the base sample}}
\end{frame}

\begin{frame}{{\fontsize{13}{12}\selectfont
    Empirical strategy - Internet coverage and spatial disparities}}
    \centering \textbf{First-stage}

    \begin{equation}
        \begin{split}
            \textcolor{red}{\textbf{internet\_coverage}_{ict}} = & \beta_{0} + 
            \beta_{1} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{lightning\_strike}_{r} \times t} + \gamma X^{'}_{ir} \\
            & \quad + \mu_{ct}+ v_{ict}
        \end{split}
        \end{equation}\\

    \begin{equation}
    \begin{split}
        \textcolor{red}{\textbf{distance} \times \textbf{internet\_coverage}_{ict}} = & \beta_{0} + 
        \beta_{1} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{distance} \times \textbf{lightning\_strike}_{r} \times t} + \gamma X^{'}_{ir} \\
        & \quad + \mu_{ct}+ v_{ict}
    \end{split}
    \end{equation}\\

    \centering \textbf{Second-stage}
    \fontsize{8}{10}\selectfont
    \begin{equation}
        \begin{split}
        trust_{ict} = & \beta_{0} + \beta_{1} distance_{ict} + \beta_{2}^{2S}\textcolor[rgb]{0.0,0.6,0.0}{\textbf{internet\_coverage}_{ict}} + \beta_{3}^{2S}\textcolor[rgb]{0.0,0.6,0.0}{\textbf{distance} \times \textbf{internet\_coverage}_{ict}} \\
        & + \gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{ict}
        \end{split}
        \end{equation}

\end{frame}

\begin{frame}{Internet mitigates spatial disparities}\label{IV-Base}
    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{11cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance from the capital &0.463***&&&& 1.361***\\      
    \smallskip
    &      (0.05)   &&&&     (0.49)   \\
    Internet coverage     &       0.029   &&&&       1.470**  \\
    \smallskip
    & (0.06)   &&&&      (0.64)    \\ 
    \smallskip
    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
    \smallskip  &       (0.10)   &&&               &      (1.09) \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{21.7cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}

        \hyperlink{IV-BDD}{\scalebox{1}{\beamerbutton{IV - Border sample}}}

\end{frame}

\begin{frame}{Internet mitigates spatial disparities}

\begin{figure}
    \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/trust_inst.png}
    \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
\end{figure}

\end{frame}

\begin{frame}{Null effect of internet on generalized trust}                        
    \begin{table}[H]
        \sffamily
        \caption{{Generalized trust}}
        \centering
        %\footnotesize
        \resizebox{10cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c}
        \\
        \toprule
        \toprule
        & \multicolumn{2}{c}{2SLS}\\
        \cmidrule(r){2-3}
        & \multicolumn{2}{c}{{Base sample: rounds 5 $\&$ 8}}\\
        \cmidrule(r){2-3}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Generalized trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
         \midrule
         Distance from the capital&       1.358** &      -0.157   \\
         \smallskip
         &      (0.62)   &      (0.17)    \\
         Internet coverage    &       1.508   &      -0.101    \\
         \smallskip
         &      (0.94)   &      (0.23)   \\
         Distance from the capital $\times$ Internet coverage&      -2.161*  &       0.542   \\
         \medskip
         &      (1.22)   &      (0.33)   \\

         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes\\
        \smallskip
        Observations         &     49,404   &       49,362\\
        \bottomrule
        \multicolumn{3}{p{14cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Internet enchances political accountability}
    \begin{table}[H]
        \sffamily
        \caption{{Political accountability}}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c}
        \\
        \toprule
        \toprule
        & \multicolumn{2}{c}{2SLS}\\
        \cmidrule(r){2-3}
        &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
         \midrule

         Distance from the capital&   -1.306***&       1.560***\\
         \smallskip
         &      (0.40)   &      (0.52)   \\
         Internet coverage     &      -1.370***&       1.565**  \\
         \smallskip
         &      (0.47)   &      (0.62)   \\
         Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
         \medskip
         &       (0.92)   &      (1.16)   \\
         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes\\
        \smallskip
        Observations      &       99,414   &       98,512  \\            \bottomrule
        \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Internet mitigates spatial disparities}

    \begin{figure}
        \centering
        \caption{Marginal effect of Distance from the capital as a function of Internet coverage}

        \begin{subfigure}{0.46\textwidth}
            \centering
            \includegraphics[scale=0.042]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/vote_oppo.png}
            \caption{Vote against rulling party}
        \end{subfigure}
        \hspace{0.03\textwidth}
        \begin{subfigure}{0.46\textwidth}
            \centering
            \includegraphics[scale=0.042]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/perf_country.png}
            \caption{Country performance}
        \end{subfigure}

    \end{figure}

    \end{frame}

    \begin{frame}{Information censorship}

    \begin{table}[H]
        \sffamily
        \caption{{Media and institutions freedom}}
        \centering
        %\footnotesize
        \resizebox{10cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{2SLS: Political trust}\\
        \cmidrule(r){2-5}
        & \multicolumn{4}{c}{{Base sample}}\\
        \cmidrule(r){2-5}
        &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
        \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

         Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
         \smallskip
         &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
         Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
         \smallskip
         &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
      Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
      \medskip
      &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\

         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes & Yes& Yes\\
        \smallskip
        Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
        \bottomrule
        \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

%\begin{frame}{Internet mitigates spatial disparities}

%    \begin{figure}
%        \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/trust_inst_wo_low_cov.png}
%        \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
%    \end{figure}

%    \end{frame}

%\begin{frame}{Internet mitigates spatial disparities}

%    \begin{figure}
%        \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/vote_oppo.png}
%        \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
%    \end{figure}

%    \end{frame}

%\begin{frame}{Internet mitigates spatial disparities}

%    \begin{figure}
%        \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/vote_oppo_wo_low_cov.png}
%        \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
%    \end{figure}

%    \end{frame}

%\begin{frame}{Internet mitigates spatial disparities}

%    \begin{figure}
%        \includegraphics[scale=0.07]{C:/Users/Redha CHABA/Documents/Working paper/trust/script/plots/marginal_effect/perf_country_wo_low_cov.png}
%        \caption{Marginal effect of Distance from the capital as a function of Internet coverage}
%    \end{figure}

%    \end{frame}

\begin{frame}{Conclusion}
    \begin{itemize}\setlength\itemsep{1em}
        \item \textbf{Trust in political institutions} promotes state legitimacy, civic engagement, social cohesion\vfill
        \item \textbf{Nature of trust} is key for expecting favorable outcomes\vfill
        \item High levels of political trust with low information \textbf{can be misleading} and undermine democratic accountability
        and effective governance\vfill
        \item \textbf{Remote areas} are more prone to \textit{uninformed trust} in political institutions due
        to both information scarcity and low expectation-engagement cycle\vfill

    \end{itemize}
\end{frame}

\begin{frame}{Conclusion}

    \begin{itemize}\setlength\itemsep{1em}
        \item \textbf{Mobile internet} potentially breaks information barriers by reducing the
        cost of accessing information about the government\vfill
        \item Replace \textit{uninformed trust} with critical evaluation to restore accountability mechanisms needed for institutional development\vfill
        %\item Stronger effect where the \textbf{government controls} the traditional media and institutions\vfill
    \end{itemize}

\end{frame}

\begin{frame}{IV - Border sample}
    \label{IV-BDD}
    \begin{table}[H]
    \sffamily
    \caption{IV - Border sample : Effect of internet coverage on political trust by distance}
    \centering
    %\footnotesize
    \resizebox{11cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{5}{c}{{Border sample}}\\
    \cmidrule(r){2-6}
    & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-5}
        \cmidrule(r){6-6}
        & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){5-5}    
        \cmidrule(r){6-6}    
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital & 0.640**&&&&  1.214***\\      
\smallskip
&      (0.26)   &&&&     (0.42)   \\
Internet coverage     &      0.620** &&&&       0.809  \\
\smallskip
&  (0.30)   &&&&      (1.02)    \\ 
\smallskip
Distance from the capital $\times$ Internet coverage&      -0.535&&&&       -2.559**\\
\smallskip  &       (0.46)    &&&&      (1.18) \\

Lightning strikes && 0.002 && 0.003***  \\
\smallskip&& (0.00) && (0.00) \\
Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.003***\\
\medskip&& (0.00) && (0.00)\\

     \midrule
    SW \emph{F} - Lightning strikes &-&-& 12.45 &- &-\\
    \smallskip
    SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 16.25 &-&-\\
    \smallskip
    Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
    \smallskip
    Country X Round FE       & Yes & Yes&- & Yes & Yes \\
    \smallskip
    Ethnic homeland FE& Yes & Yes&- & Yes & Yes \\
    \smallskip
    Observations       &       4,189    &4,247 && 4,247&      4,189  \\
    Adjusted-R$^2$    &       0.190    &-&-&-&  \\
                          \bottomrule
    \multicolumn{6}{p{21.7cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
    \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
\end{tabular}}
    \end{table}

    \hyperlink{IV-Base}{\beamerbutton{IV - Base sample}}

\end{frame}

\begin{frame}{Individual heterogeneity}

    \begin{table}[H]
        \sffamily
        \caption{{Individual heterogeneity}}
        \centering
        %\footnotesize
        \resizebox{10cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{2SLS: Political trust}\\
        \cmidrule(r){2-5}
        & \multicolumn{4}{c}{{Base sample}}\\
        \cmidrule(r){2-5}
        &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}\\
        \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
         \midrule

         Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961*** \\
         \smallskip
         &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)  \\
         Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***\\
         \smallskip
         &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   \\
           Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447* \\
           \medskip
           &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)    \\
         \midrule
         \smallskip
        Individual \& regional controls  & Yes & Yes & Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes& Yes & Yes& Yes\\
        \smallskip
        Observations         &       36,389   &       62,039   &       37,348   &       60,887\\
        \bottomrule
        \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
        \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{IV - Internet news}
    \begin{table}[H]
    \sffamily
    \caption{IV - Base sample : Effect of internet news on political trust by distance}
    \centering
    %\footnotesize
    \resizebox{11cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{5}{c}{{Border sample}}\\
    \cmidrule(r){2-6}
    & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-5}
        \cmidrule(r){6-6}
        & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet news}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet news}} & \multicolumn{1}{c}{{Political trust}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){5-5}    
        \cmidrule(r){6-6}    
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital & 0.301***&&&&       0.768***\\      
\smallskip
&      (0.03)   &&&&      (0.12)   \\
Internet news     &      -0.010*  &&&&      -0.308  \\
\smallskip
&    (0.01)   & &&&     (0.23)    \\ 
\smallskip
Distance from the capital $\times$ Internet news&      -0.045***&&&&      -0.800***\\
\smallskip  &       (0.01)    &&&&      (0.17) \\

Internet coverage &&  0.253*** && -0.129***  \\
\smallskip&& (0.057) && (0.037) \\
Distance from the capital city $\times$ Internet coverage&& -0.077 && 0.622***\\
\medskip&& (0.09) && (0.07)\\

     \midrule
    SW \emph{F} - Internet coverage &-&-& 28.25 &- &-\\
    \smallskip
    SW \emph{F} - Distance $\times$ Internet coverage &-&-& 81.36 &-&-\\
    \smallskip
    Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
    \smallskip
    Country X Round FE       & Yes & Yes&- & Yes & Yes \\
    \smallskip
    Ethnic homeland FE& Yes & Yes&- & Yes & Yes \\
    \smallskip
    Observations       &       97,686    &98,849&& 98,849&      97,686  \\
    Adjusted-R$^2$    &       0.198     &-&-&-&  \\
                          \bottomrule
    \multicolumn{6}{p{21.7cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
    \emph{Notes}: Robust standard errors clustered at the x region x round level are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
\end{tabular}}
    \end{table}
\end{frame}

\begin{frame}{IV - Social media news}
    \begin{table}[H]
    \sffamily
    \caption{IV - Base sample : Effect of social media news on political trust by distance}
    \centering
    %\footnotesize
    \resizebox{11cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{5}{c}{{Border sample}}\\
    \cmidrule(r){2-6}
    & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-5}
        \cmidrule(r){6-6}
        & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Social medias news}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Social medias news}} & \multicolumn{1}{c}{{Political trust}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){5-5}    
        \cmidrule(r){6-6}    
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital & 0.340***&&&&       0.656***\\      
\smallskip
&       (0.04)   &&&&      (0.13)   \\
Social medias news     &       -0.013** &&&&      -0.623  \\
\smallskip
&     (0.01)   &&&&      (0.38)    \\ 
\smallskip
Distance from the capital $\times$ Social medias news&      -0.045***&&&&       -0.500***\\
\smallskip  &       (0.01)    &&&&      (0.15)   \\

Internet coverage && 0.212*** && -0.249***  \\
\smallskip&& (0.07) && (0.05) \\
Distance from the capital city $\times$ Internet coverage&& -0.120 && 0.949***\\
\medskip&& (0.11) && (0.09)\\

     \midrule
    SW \emph{F} - Internet coverage &-&-&  10.39 &- &-\\
    \smallskip
    SW \emph{F} - Distance $\times$ Internet coverage &-&-& 63.93 &-&-\\
    \smallskip
    Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
    \smallskip
    Country X Round FE       & Yes & Yes&- & Yes & Yes \\
    \smallskip
    Ethnic homeland FE& Yes & Yes&- & Yes & Yes \\
    \smallskip
    Observations       &        70,234     &71,103&& 71,103&       70,234   \\
    Adjusted-R$^2$    &        0.207     &-&-&-&  \\
                          \bottomrule
    \multicolumn{6}{p{21.7cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
    \emph{Notes}: Robust standard errors clustered at the x region x round level are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
\end{tabular}}
    \end{table}

\end{frame}

\begin{frame}{Country sample and capital cities}
\label{sample_map}
    \begin{figure}
        \centering
        \caption{Country Sample and Capital Cities}
        \includegraphics[scale=0.075]{obs_map.jpg}
    \end{figure}

    \begin{tikzpicture}[remember picture, overlay]
        \node[anchor=south west] at (current page.south west) [xshift=1cm, yshift=0.5cm] {%
            \hyperlink{context}{\beamerbutton{Back}}};
    \end{tikzpicture}

\end{frame}

\end{document}

### 2025-02-24 writing/report/presentation.tex
import folders

\documentclass[10pt]{beamer}
\usepackage[utf8]{inputenc}

\usepackage{multirow,rotating}
\usepackage{color}
\usepackage{tikz-cd}
\usepackage{array}
\usepackage{siunitx}
\usepackage{mathtools,nccmath}%
\usepackage{etoolbox, xparse} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsopn}
\usepackage{pifont}
\usepackage{xcolor}
\usepackage{booktabs}

\usepackage{float}

\usepackage{epstopdf}
\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\usetheme{CambridgeUS}
\usecolortheme{dolphin}
\makeatletter
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor%~~\beamer@ifempty{\insertshortinstitute}{}{(\insertshortinstitute)}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother

\setbeamertemplate{caption}[numbered]

% set colors
\definecolor{myNewColorA}{RGB}{158, 27,50}
\definecolor{myNewColorB}{RGB}{158, 27,50}
\definecolor{myNewColorC}{RGB}{158, 27,50} % {130,138,143}
\setbeamercolor*{palette primary}{bg=myNewColorC}
\setbeamercolor*{palette secondary}{bg=myNewColorB, fg = white}
\setbeamercolor*{palette tertiary}{bg=myNewColorA, fg = white}
\setbeamercolor*{titlelike}{fg=myNewColorA}
\setbeamercolor*{title}{bg=myNewColorA, fg = white}
\setbeamercolor*{item}{fg=myNewColorA}
\setbeamercolor*{caption name}{fg=myNewColorA}
\setbeamercolor*{button}{bg=myNewColorA,fg= white}
\usefonttheme{professionalfonts}
\usepackage{natbib}

%------------------------------------------------------------
% \titlegraphic{\includegraphics[height=0.75cm]{ua_eng_logo.png}}

% logo of my university

%\titlegraphic{%
%\includegraphics[width=3.0cm]{ua_seal.png}
%}

\setbeamerfont{title}{size=\large}
\setbeamerfont{subtitle}{size=\small}
%\setbeamerfont{author}{size=\small}
\setbeamerfont{date}{size=\footnotesize}
\setbeamerfont{institute}{size=\footnotesize}

%\date[\textcolor{white}{Conference Name, 2022}]
%{Conference full name\\
%Aug 29-30, 2022}

%------------------------------------------------------------
%This block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:
%\AtBeginSection[]
%{
%  \begin{frame}
%    \frametitle{Contents}
%    \tableofcontents[currentsection]
%  \end{frame}
%}
%\AtBeginSection[]{
 % \begin{frame}
 % \vfill
  %\centering
  %\begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    %\usebeamerfont{title}\insertsectionhead\par%
 % \end{beamercolorbox}
  %\vfill
  %\end{frame}

% ------Contents below---
%------------------------------------------------------------

\begin{document}
\author[I. Barriola, R. Chaba]{I. Barriola\inst{1} \and R. Chaba\inst{2}}

\institute{
	\inst{1} CRED, Paris Panthéon Assas University, Paris, France
	\and
	\inst{2} LEMMA, Paris Panthéon Assas University, Paris, France
}
\title{Internet and Nation Building in Africa}
\subtitle{Preliminary results}
\date{September 12, 2024}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Motivation}
%\centering\textbf{Nation building needs citizens involvement}\vspace{1em}
    \begin{itemize}\setlength\itemsep{1em}
        \item \textbf{Trust in national institutions} promotes state legitimacy, civic engagement, social cohesion
        \begin{itemize}
            \item Crucial concern in Africa since the post-colonial era
        \end{itemize}
        \item However, the \textbf{nature of trust} is key for expecting favorable outcomes
        \item  \textbf{High levels of trust in institutions can be misleading} if citizens are uninformed or uninterested\\ \vspace{1em}
        $\rightarrow{}$ Such \textbf{default trust} can disrupt accountability mechanisms, weakening the political power of citizens and their relationship with the nation        %\item Information on governance can be acquired through direct experience or communication networks
    \end{itemize}
\end{frame}

\begin{frame}{Motivation}
    \centering\textbf{Most African capitals lie in peripheral areas rather than central locations}\vspace{1em}
    \begin{itemize}\setlength\itemsep{1em}
        \item Large parts of the population live far from their capital city
        \item 80\% of African constitutions feature highly centralized states \textit{(Kuperman, 2015)}
        %\begin{itemize}
         %   \item  Ineffective accountability mechanisms reduce incentives for public investments in remote areas (e.g. McKay et al. 2023, Provenzano 2024)
        %\end{itemize}
        \item Institutions struggle to reach remote areas
        \begin{itemize}\vspace{0.5em}
            \item Lack of state presence in remote areas \textit{(Provenzano, 2024)}\vspace{0.5em}\\
            $\rightarrow{}$ Spatial disparities in state interaction

        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Motivation}
        \begin{itemize}\vspace{0.5em}
            \item Information about governance can be obtained through \textbf{direct experience} or \textbf{communication networks}\vspace{0.5em}
            \item Remote populations:\\
            \begin{itemize}
            \item are less likely to directly encounter governance wrongdoing due to the \textbf{lack of state presence}\vspace{0.5em}
            \item consume news less frequently due to the \textbf{lack of access}\\ \vspace{1em}
            \end{itemize}
            $\rightarrow$ \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Remote populations are more prone to showing default trust in institutions}} 
         \end{itemize}

\end{frame}
\begin{frame}{Motivation}
    \centering\vspace{1em}
    \begin{itemize}\setlength\itemsep{1em}
    %\item Dysfunction of accountability mechanisms reduces incentives for public investments and nation building in remote areas
    \item \textbf{Access to new channels of information} about government activities can \textbf{reshape perceptions} of institutions in remote areas\\ \vspace{0.5em}
    $\rightarrow{}$ \textbf{Expanding internet access} can enhance information consumption and \textbf{reduce spatial disparities} in institutional trust
    \end{itemize}\vspace{3em}
    \centering \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{Replace default trust with critical evaluation to restore accountability mechanisms needed for nation-building}}
\end{frame}

\begin{frame}{Research question}

\centering \textbf{How does the diffusion of mobile internet affect political accountability in remote areas?}
\vspace{15pt}
\begin{itemize}\setlength\itemsep{1em}
    \item Hypothesis:
    \vspace{10pt}
    \begin{itemize}
    \item \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{H1}}: \textbf{Living in remote areas is associated with higher levels of institutional trust}
        \vspace{10pt}
    \item \definecolor{rougeprez}{RGB}{158,27,50}\textcolor{rougeprez}{\textbf{H2}}: \textbf{Expanding internet access mitigates spatial disparities in institutional trust}
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Literature contribution}

\begin{itemize}\setlength\itemsep{1em}
    \item Institutional trust and nation building
    \begin{itemize}
        \item \textit{e.g. Aghion et al. (2010), Algan and Cahuc (2013), McKay et al. (2019)}\\
        $\rightarrow{}$ \textbf{High levels of trust can be misleading for nation building}
    \end{itemize}    
    \item Political economy of the capital city
\begin{itemize}
    \item \textit{e.g.  Mann (1993), Michalopoulos and Papaioannou (2014), Campante et al. (2019), Provenzano (2024)}\\
    $\rightarrow{}$ \textbf{Distance to the capital city shapes institutional perceptions}
\end{itemize}
\item Internet role in accountability and governance information
    \begin{itemize}
        \item \textit{e.g. Manacorda \& Tesei (2020), Guriev et al. (2021), Cariolle et al. (2024)}\\
        $\rightarrow{}$ \textbf{Expanding internet access can enhance accountability mechanisms}
    \end{itemize}

\end{itemize}
\end{frame}

\begin{frame}{Main Data}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}\setlength\itemsep{1em}
\item Afrobarometer surveys accross 20 Sub-Saharan countries: wave 5 to 7 (2011-2018)
\begin{itemize}
    \item Geolocated data, N $\approx$ 85 000
    \item Public attitude survey on democracy, governance, media consumption
    \item Construction of distance variables
    %\item Construction of normalized isolation measure (values between 0 and 1) \\
  % \[
%\frac{\text{distance from the capital city}}{\text{maximal distance from the capital city}}
%\]
\end{itemize}
\item Collins Bartholomew’s Mobile Coverage Explorer: 2G/3G network coverage (2011-2018)
\begin{itemize}
    \item 1×1-kilometer binary grid cells
    \item ADM2 level mean coverage
    \item Weighted by UN-adjusted population density grid
\end{itemize}
%\item Other sources for controls: V-DEM, World Bank, Africa Integrity Indicators...
\end{itemize}

\end{column}
\begin{column}{0.5\textwidth}

\begin{figure}
    \centering
    \caption{Respondents and capital cities}
    \includegraphics[width=6cm]{carte afrique echantillon total.png}
\end{figure}
\end{column}
    \end{columns}

\end{frame}
\begin{frame}{Empirical Strategy - Distance on institutional trust (1)}
    \centering \textbf{Effect of distance to the capital city on institutional trust}\vspace{1em}
    \begin{itemize}
        \item OLS
        \begin{equation}
        trust_{ict} = \beta_{0} + \beta_{1}distance_{ict} + BX_{i} + \mu_{ct} + \varepsilon_{ict}
        \end{equation}
        \begin{itemize}
            \item $trust_{ict}$ : mean of trust measures in parliament, president and electoral commission (values between 0 and 3)\vfill
            \item $distance_{ict}$ : normalized distance measure (values between 0 and 1)\\
            $\rightarrow{}$ \textit{e.g. Michalopoulos and Papaioannou (2014)}\vfill
            \item $X_i$ : set of individual controls\vfill
            \item $\mu_{ct}$ : country $\times$ round fixed effects\vfill
            \item $\epsilon_{ict}$ : error term\vfill
            \item Robust standard errors clustered at the ADM2 x round level
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Empirical Strategy - Distance on institutional trust (2)}
    \begin{itemize}
        \item Border discontinuity design
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}
    \item Similar identification strategy as \textit{Michalopoulos and Papaioannou (2014), de Figueiredo et al. (2023), Provenzano (2024)}\vspace{0.3cm}
    \item We use Murdock's (1959) historical ethnic homeland map and assume that post-colonial African borders were established independently of ethnic regions\vspace{0.3cm}
    \item \textbf{Main assumption:} Two individuals living in the same historical ethnic region share similar unobserved characteristics
\end{itemize}
\end{column}

\begin{column}{0.5\textwidth}
\begin{figure}
    \centering
    \caption{Historical ethnic homeland map}
    \includegraphics[width=4.8cm]{map murdock.png}
\end{figure}
\end{column}

\end{columns}
    \end{itemize}
    \end{frame}

\begin{frame}{Empirical Strategy - Distance on institutional trust (2)}

\begin{itemize}
   \item We limit our sample to individuals living within a 50 km (40km) radius of each side of a border
\end{itemize}

\begin{figure}
    \centering
    \caption{Observations along borders}
    \includegraphics[width=5.5cm]{carte discontinuité (1).png}
\end{figure}

\begin{equation}
trust_{ict}=\beta_{0}+\beta_{1}distance_{ict}+BX_{i}+\textcolor{red}{\mathbf{\nu_{e}}}+\mu_{ct}+\varepsilon_{ict}
\end{equation}

\end{frame}

\begin{frame}{Empirical Strategy - Internet on spatial disparities}

\centering \textbf{Effect of internet use on institutional trust by distance}\vspace{1em}

\begin{itemize}
\item OLS
    \begin{equation}
\begin{split}
trust_{ict} = & \beta_{0} + \beta_{1} distance_{ict} + internet\_use_{ict} + \textcolor{red}{\textbf{distance} \times \textbf{internet\_use}_{ict}} \\
& + BX_{i} + \mu_{ct}+ \varepsilon_{ict}
\end{split}
\end{equation}\vspace{1em}

${internet\_use_{ict}}$ : "how often do you use internet" (values between 0 and 3)\vfill
\item IV
\begin{equation}
\begin{split}
    \textcolor{red}{\textbf{distance} \times \textbf{internet\_use}_{ict}} = & \lambda_{0} + 
    \lambda_{1} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{distance} \times \textbf{internet\_coverage}_{rt}} + BX_{i} \\
    & \quad + \mu_{ct}+ v_{ict}
\end{split}
\end{equation}\\
   $\rightarrow$ Similar to \textit{Guriev et al. (2021)}
\end{itemize}

\end{frame}

\begin{frame}{Distance increases institutional trust}
    \begin{table}[H]
        \sffamily
        \caption{{Effect of distance to the capital on institutional trust}}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        &  \multicolumn{6}{c}{{Trust in institutions}}  \\
        \cmidrule(r){2-7}
        & \multicolumn{2}{c}{{OLS}} & \multicolumn{2}{c}{{BDD: 50km}} & \multicolumn{2}{c}{{BDD: 40km}}\\
            \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            \cmidrule(r){6-7}
            & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} & \multicolumn{1}{c}{{(5)}} & \multicolumn{1}{c}{(6)}\\
         \midrule

         Distance to the capital &       0.224***&       0.322*** & 0.432***&  0.387***& 0.475***&       0.374**\\
         \medskip
         &      (0.03)   &      (0.03)  &  (0.14)   &      (0.14)& (0.14)   &      (0.15)   \\

         \midrule
        Standard controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
        Country X Round FE       & No & Yes& No & Yes& No & Yes\\
        Murdock's area FE & No & No & Yes& Yes& Yes& Yes\\
        Observations      &     83,877   &       83,877  &  18,294   &       18,294 &   16,893   &       16,893\\
        Adjusted-R$^2$        &       0.021   &       0.052  & 0.117   &       0.166 &  0.117   &       0.169  \\

                              \bottomrule
        \multicolumn{7}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the ADM2 x round level  for (1) and (2) and ethnic region for (3-6) are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ADM2 nighttime light.}
        \end{tabular}
        }
        \end{table}

\end{frame}

\begin{frame}{Distance increases institutional trust}

\begin{figure}
    \includegraphics[scale=0.1]{C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/plots/discontinuity/discontinuity.jpg}
    \caption{Border discontinuity - \textit{Based on regression estimates from (4) of Table 1}}
\end{figure}

\end{frame}

\begin{frame}{Internet mitigates spatial disparities}
    \begin{table}[H]
        \sffamily
        \caption{{Effect of internet on institutional trust by distance to the capital}}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Trust in institutions}} & \multicolumn{1}{c}{{Internet use}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet use}} & \multicolumn{1}{c}{{Trust in institutions}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}
            \cmidrule(r){6-6}

            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance to the capital&    0.353*** &&&&0.533***\\
         \smallskip
         &      (0.03)  &&&&  (0.117) \\
    Internet use   &      -0.012** &&&&-0.316\\
    \smallskip   &      (0.01)  &&&&  (0.24) \\

    Distance to the capital $\times$ Internet use&         -0.054*** &&&&-0.437***\\
    \smallskip  &      (0.01) &&&& (0.14)  \\

    Internet coverage && 0.179*** && -0.184*** &  &  \\
    \smallskip&& (0.06) && (0.03) \\
    Distance to the capital city $\times$ Internet coverage&& 0.063 && 0.733*** &  & \\
    \medskip&& (0.10) && (0.07)\\

         \midrule
        SW \emph{F} - Internet coverage &-&-& 16.12&- &-\\
        SW \emph{F} - Distance $\times$ Internet coverage &-&-& 90.80&-&-\\
        Standard controls  & Yes & Yes &&  Yes & Yes  \\
        Country X Round FE       & Yes & Yes& & Yes & Yes \\
        Observations       &       83,877 & 83,877 & & 83,877 & 83,877 \\
        Adjusted-R$^2$    &       0.164 &  0.358 & &   0.262 & - \\
        %Endogeneity test \emph{p}-value & -& - & - & -& 0.00\\

                              \bottomrule
        \multicolumn{6}{p{22cm}}{\fontsize{10}{12}\selectfont % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the ADM2 x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ADM2 nighttime light.}
    \end{tabular}}
        \end{table}

\end{frame}

\begin{frame}{Internet mitigates spatial disparities}

\begin{figure}
    \includegraphics[scale=0.06]{C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/plots/marginal_effect/internet_use.png}
    \caption{Marginal effect of internet use as a function of the distance to the capital}
\end{figure}

\end{frame}

\begin{frame}{Internet mitigates spatial disparities}

    \begin{table}[H]
        \sffamily
        \caption{{Effect of internet on national outcomes by distance to the capital}}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{{2SLS}}\\
        \cmidrule(r){2-5}
        & \multicolumn{3}{c}{{National outcomes}}& \multicolumn{1}{c}{{Placebo}}\\
        \cmidrule(r){2-4}
        \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{Satisfaction in democracy}} & \multicolumn{1}{c}{{Democracy extent}} & \multicolumn{1}{c}{{Trust in ruling party}} & \multicolumn{1}{c}{{Local}} \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}

            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance to the capital&  0.316*** & 0.342*** & 0.444***& 0.295***\\
         \smallskip
         & (0.10)& (0.09) & (0.13)&(0.10) \\
    Internet use     & -0.251 & -0.148 & -0.574**& -0.602***\\
    \smallskip      & (0.19) & (0.17)& (0.26)& (0.22)\\

    Distance to the capital $\times$ Internet use&   -0.229*  & -0.315***  & -0.356**&  -0.111 \\
    \smallskip & (0.12) & (0.11) & (0.16)& (0.12)\\

         \midrule
        Standard controls  & Yes & Yes &Yes&Yes   \\
        Country X Round FE       & Yes & Yes& Yes&Yes  \\
        Observations       &       85,017 & 83,786 & 86,489& 85,953\\
        %Endogeneity test \emph{p}-value & 0.03 & 0.01& 0.00\\

                              \bottomrule
        \multicolumn{5}{p{21cm}}{\fontsize{10}{12}\selectfont % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the ADM2 x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ADM2 nighttime light.}
    \end{tabular}
        }
        \end{table}

\end{frame}

\begin{frame}{Internet enhances corruption perception}

    \begin{table}[H]
        \sffamily
        \caption{{Effect of internet on corruption perception by distance to the capital}}
        \centering
        \resizebox{11cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{{2SLS}}\\
        \cmidrule(r){2-5}
        & \multicolumn{3}{c}{{National outcomes}}& \multicolumn{1}{c}{{Placebo}}\\
        \cmidrule(r){2-4}
        \cmidrule(r){5-5}
            & \multicolumn{1}{c}{{President}} & \multicolumn{1}{c}{{Parliament}} & \multicolumn{1}{c}{{Judiciary}} & \multicolumn{1}{c}{{Local}} \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}

            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}}& \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance to the capital& -0.286***  & -0.302***  & -0.296*** &    -0.202** \\
         \smallskip
         & (0.09)& (0.08) & (0.08) & (0.08) \\
    Internet use   & 0.242 & 0.057  & 0.089&   0.160\\
    \smallskip  & (0.17) & (0.15)& (0.17)& (0.16)  \\

    Distance to the capital $\times$ Internet use& 0.277***   & 0.321***   & 0.336*** &   0.129  \\
    \smallskip  & (0.10) & (0.09) & (0.10)  & (0.09)\\

         \midrule
        Standard controls  & Yes & Yes &Yes& Yes  \\
        Country X Round FE       & Yes & Yes& Yes& Yes \\
        Observations       &       80,370& 81,590 & 81,705 &  79,545  \\
        %Endogeneity test \emph{p}-value & 0.01 & 0.00 & 0.00\\

                              \bottomrule
        \multicolumn{5}{p{14cm}}{\fontsize{9}{11}\selectfont % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the ADM2 x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ADM2 nighttime light.}
    \end{tabular}}
        \end{table}
\end{frame}

\begin{frame}{Stronger effects in autocratic and media-captured countries}
    \begin{table}[H]
        \sffamily
        \caption{{Variations by institution and media freedom}}
        \centering
        %\footnotesize
        \resizebox{11cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{4}{c}{{2SLS}}\\
            \cmidrule(r){2-5}
            & \multicolumn{2}{c}{{Institutions}} & \multicolumn{2}{c}{{Medias}} \\
            \cmidrule(r){2-3}
            \cmidrule(r){4-5}
            & \multicolumn{1}{c}{{Democratic}} & \multicolumn{1}{c}{{Autocratic}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}} \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){4-4}
            \cmidrule(r){5-5}

            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

            \midrule

    Distance to the capital& 0.363 & 0.683*** & 0.364** & 0.719***\\
         \smallskip
         & (0.25)   & (0.15) & (0.17)  & (0.13)   \\
    Internet use & -0.643 & -0.065  & -0.498* & 0.080\\
    \smallskip    & (0.48) & (0.31) & (0.27)& (0.27) \\

    Distance to the capital $\times$ Internet use & -0.217 & -0.638*** & -0.303 & -0.581*** \\
    \smallskip & (0.28) & (0.20)& (0.22) & (0.17) \\

         \midrule
        Standard controls  & Yes & Yes& Yes & Yes\\
        Country X Round FE & Yes & Yes & Yes & Yes\\
        Observations  & 44,434  & 39,443  & 36,872  & 47,005   \\
        %Endogeneity test \emph{p}-value & 0.00 & 0.03 & 0.04 & 0.00 \\

                              \bottomrule
        \multicolumn{5}{p{14cm}}{\fontsize{8}{11}\selectfont % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the ADM2 x round level are in parentheses. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ADM2 nighttime light.}
    \end{tabular}}
        \end{table}
\end{frame}

\begin{frame}{Upcoming research}

    \begin{itemize}
        \item Explore another result:\vspace{0.5em}
        \begin{itemize}
            \item National identification, vote, voter turnout\vspace{0.5em}
            \item Variations in duration of internet exposure\vspace{0.5em}
        \end{itemize}
        \item Explore the role of social medias\vspace{0.5em}
        \item Heterorogeneity: regime type, Sub-Saharan African regions, colonial legacy
    \end{itemize}

\end{frame}

\end{document}

### 2025-02-24 writing/wp/method and results.tex
import folders

--- 2024-11-20 wp/tables.tex
@@
 %\usepackage{longtable}
-\usepackage{adjustbox}
-\usepackage{rotating}
 
@@
 
-\title{Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}
+\title{The Death of Distance: Mobile Internet
+and Political Trust in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}
 
@@
 \maketitle
+\section*{Data}
+Figure 1 displays our sample of 20 Sub-Saharan African countries (in green) and their capital cities (in red).
+Our analysis combines Afrobarometer survey rounds 5-8 (2011-2021), providing geocoded data on public opinion, information access, and demographic characteristics for 98,235 individual respondents across these countries.\footnote{Our sample includes: Benin, Burkina Faso, Botswana, Cameroon, Ivory Coast,
+Ghana, Guinea, Kenya, Liberia, Mali, Malawi, Mozambique, Namibia, Niger, Nigeria, Sierra Leone, Tanzania, Uganda, Zambia, Zimbabwe.
+We exclude islands, countries with multiple capitals, and Northern African countries.
+We also exclude countries with missing data on mobile internet coverage and those not present in all survey rounds.}\footnote{All Afrobarometer surveys were conducted via-in-person, face-to-face interviews.
+The method did not change to computer-assisted interviews, thereby avoiding potential bias toward areas with mobile internet coverage.}
 
-\begin{table}[H]
-    \sffamily
-    \caption{{Effect of distance from the capital on political trust}}
-    \centering
-    %\footnotesize
-    \resizebox{12cm}{!}{
-    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
-    \\
-    \toprule
-    \toprule
-    &  \multicolumn{4}{c}{{OLS}}  \\
-    \cmidrule(r){2-5}
-    &  \multicolumn{4}{c}{{Political trust}}  \\
-    \cmidrule(r){2-5}
-    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
-        \cmidrule(r){2-3}
-        \cmidrule(r){4-5}
-        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
-     \midrule
+To measure political trust and accountability, we focus on three sets of variables from the Afrobarometer surveys.
+First, we construct our main dependent variable \textit{Political Trust} by averaging responses to trust questions about the president and parliament/national assembly, each measured on a 0-3 scale ('Not at all' to 'A lot').\footnote{The specific questions ask: \textit{``How much do you trust each of the following: the president, the parliament/national assembly?''}} Second, we measure electoral accountability through a binary variable indicating willingness to vote against the ruling party in hypothetical next-day elections.\footnote{Based on responses to: \textit{``If [presidential elections] were held tomorrow, which [party's candidate] would you vote for?''}} Third, we capture economic performance assessment through a 1-5 scale rating of economic conditions compared to twelve months prior.\footnote{Based on responses to: \textit{``Looking back, how do you rate economic conditions in this country compared to twelve months ago?''}}
 
-     Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
-     \medskip
-     &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
-     \midrule
-     \smallskip
-    Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
-    \smallskip
-    Country controls & Yes& No& Yes& No\\
-    \smallskip
-    Round FE & Yes & No& Yes & No\\
-    \smallskip
-    Country X Round FE       & No & Yes& No & Yes\\
-    \smallskip
-    Ethnic homeland FE & No & No & Yes& Yes\\
-    \smallskip
-    Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
-    Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\
+To measure remoteness, we calculate each respondent's distance from their national capital using Afrobarometer's geocoded enumeration areas.
+Following Michalopoulos and Papaioannou (2014), we standardize distances by dividing each respondent's distance from the capital by the maximum distance within their country.
+This relative distance measure ranges from 0 (at capital) to 1 (furthest point), enabling meaningful cross-country comparisons.
 
-                          \bottomrule
-    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-    \end{tabular}
-    }
-    \end{table}
-
-    \begin{table}[H]
-        \sffamily
-        \caption{Effect of internet coverage on political trust by distance}
-        \centering
-        %\footnotesize
-        \resizebox{17cm}{!}{
-        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-        \\
-        \toprule
-        \toprule
-        & \multicolumn{5}{c}{{Base sample}}\\
-        \cmidrule(r){2-6}
-        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
-            \cmidrule(r){2-2}
-            \cmidrule(r){3-5}
-            \cmidrule(r){6-6}
-            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
-            \cmidrule(r){2-2}
-            \cmidrule(r){3-3}
-            \cmidrule(r){5-5}    
-            \cmidrule(r){6-6}    
-            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\
-
-            \midrule
-
-    Distance from the capital &0.463***&&&& 1.361***\\      
-    \smallskip
-    &      (0.05)   &&&&     (0.49)   \\
-    Internet coverage     &       0.029   &&&&       1.470**  \\
-    \smallskip
-    & (0.06)   &&&&      (0.64)    \\ 
-    \smallskip
-    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
-    \smallskip  &       (0.10)   &&&               &      (1.09) \\
-
-   Lightning strikes && -0.002*** && -0.000  \\
-    \smallskip&& (0.00) && (0.00) \\
-    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
-    \medskip&& (0.00) && (0.00)\\
-
-         \midrule
-        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-&-\\
-        \smallskip
-        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-&-\\
-        \smallskip
-        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
-        \smallskip
-        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
-        \smallskip
-        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
-        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
-                              \bottomrule
-        \multicolumn{6}{p{27cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
-        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
-        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-    \end{tabular}}
-        \end{table}
-
-        \begin{table}[H]
-            \sffamily
-            \caption{{Other outcomes}}
-            \centering
-            %\footnotesize
-            \resizebox{18cm}{!}{
-            \begin{tabular}{@{\extracolsep{5pt}} l c c}
-            \\
-            \toprule
-            \toprule
-            & \multicolumn{2}{c}{2SLS}\\
-            \cmidrule(r){2-3}
-            &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
-            \cmidrule(r){2-2}
-            \cmidrule(r){3-3}
-            & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
-                \cmidrule(r){2-2}
-                \cmidrule(r){3-3}
-                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
-             \midrule
-
-             Distance from the capital&   -1.306***&       1.560***\\
-             \smallskip
-             &      (0.40)   &      (0.52)   \\
-             Internet coverage     &      -1.370***&       1.565**  \\
-             \smallskip
-             &      (0.47)   &      (0.62)   \\
-             Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
-             \medskip
-             &       (0.92)   &      (1.16)   \\
-             \midrule
-             \smallskip
-            Individual \& regional controls  & Yes & Yes\\
-            \smallskip
-            Country X Round FE       & Yes& Yes\\
-            \smallskip
-            Observations      &       99,414   &       98,512  \\            \bottomrule
-            \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-            includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-            \end{tabular}
-            }
-            \end{table}
-
-            \begin{table}[H]
-              \sffamily
-              \caption{{Media and institutions freedom}}
-              \centering
-              %\footnotesize
-              \resizebox{16cm}{!}{
-              \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
-              \\
-              \toprule
-              \toprule
-              & \multicolumn{4}{c}{2SLS: Political trust}\\
-              \cmidrule(r){2-5}
-              & \multicolumn{4}{c}{{Base sample}}\\
-              \cmidrule(r){2-5}
-              &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
-              \cmidrule(r){2-3}
-                  \cmidrule(r){4-5}
-                  & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
-                  \cmidrule(r){2-2}
-                  \cmidrule(r){3-3}
-                  \cmidrule(r){4-4}
-                  \cmidrule(r){5-5}
-                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
-               \midrule
-
-               Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
-               \smallskip
-               &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
-               Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
-               \smallskip
-               &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
-            Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
-            \medskip
-            &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\
-
-               \midrule
-               \smallskip
-              Individual \& regional controls  & Yes & Yes & Yes & Yes\\
-              \smallskip
-              Country X Round FE       & Yes& Yes & Yes& Yes\\
-              \smallskip
-              Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
-              \bottomrule
-              \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-              \end{tabular}
-              }
-              \end{table}
-
-              \begin{table}[H]
-                \sffamily
-                \caption{{Individual heterogeneity}}
-                \centering
-                %\footnotesize
-                \resizebox{16cm}{!}{
-                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
-                \\
-                \toprule
-                \toprule
-                & \multicolumn{8}{c}{2SLS: Political trust}\\
-                \cmidrule(r){2-9}
-                & \multicolumn{8}{c}{{Base sample}}\\
-                \cmidrule(r){2-9}
-                &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}&  \multicolumn{4}{c}{{Age}}\\
-                \cmidrule(r){2-3}
-                    \cmidrule(r){4-5}
-                    \cmidrule(r){6-9}
-                    & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}} & \multicolumn{1}{c}{{18-25}}& \multicolumn{1}{c}{{26-35}}& \multicolumn{1}{c}{{36-44}}& \multicolumn{1}{c}{{45+}}\\
-                    \cmidrule(r){2-2}
-                    \cmidrule(r){3-3}
-                    \cmidrule(r){4-4}
-                    \cmidrule(r){5-5}
-                    \cmidrule(r){6-6}
-                    \cmidrule(r){7-7}
-                    \cmidrule(r){8-8}
-                    \cmidrule(r){9-9}
-                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
-                 \midrule
-
-                 Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961***&       1.295** &       0.965   &       1.438** &       1.723*** \\
-                 \smallskip
-                 &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)   &      (0.57)   &      (0.63)   &      (0.56)   &      (0.59)   \\
-                 Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***&       1.439*  &       0.982   &       1.236*  &       2.540***\\
-                 \smallskip
-                 &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   &      (0.74)   &      (0.76)   &      (0.72)   &      (0.87)   \\
-                   Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447*  &      -1.994   &      -1.477   &      -2.577** &      -3.103**  \\
-                   \medskip
-                   &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)   &      (1.24)   &      (1.38)   &      (1.28)   &      (1.39)   \\
-                 \midrule
-                 \smallskip
-                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes\\
-                \smallskip
-                Country X Round FE       & Yes& Yes & Yes& Yes & Yes& Yes & Yes& Yes\\
-                \smallskip
-                Observations         &       36,389   &       62,039   &       37,348   &       60,887   &       25,442   &       29,913   &       20,074   &       23,246   \\
-                \bottomrule
-                \multicolumn{9}{p{24cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                \end{tabular}
-                }
-                \end{table}
-
-            \begin{table}[H]
-              \sffamily
-              \caption{{Generalized trust}}
-              \centering
-              %\footnotesize
-              \resizebox{16cm}{!}{
-              \begin{tabular}{@{\extracolsep{5pt}} l c c}
-              \\
-              \toprule
-              \toprule
-              & \multicolumn{2}{c}{2SLS}\\
-              \cmidrule(r){2-3}
-              & \multicolumn{2}{c}{{Base sample: rounds 5 $\&$ 8}}\\
-              \cmidrule(r){2-3}
-                  & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Generalized trust}}\\
-                  \cmidrule(r){2-2}
-                  \cmidrule(r){3-3}
-                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
-               \midrule
-               Distance from the capital&       1.358** &      -0.157   \\
-               \smallskip
-               &      (0.62)   &      (0.17)    \\
-               Internet coverage    &       1.508   &      -0.101    \\
-               \smallskip
-               &      (0.94)   &      (0.23)   \\
-               Distance from the capital $\times$ Internet coverage&      -2.161*  &       0.542   \\
-               \medskip
-               &      (1.22)   &      (0.33)   \\
-
-               \midrule
-               \smallskip
-              Individual \& regional controls  & Yes & Yes\\
-              \smallskip
-              Country X Round FE       & Yes& Yes\\
-              \smallskip
-              Observations         &     49,404   &       49,362\\
-              \bottomrule
-              \multicolumn{3}{p{14cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
-              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-              \end{tabular}
-              }
-              \end{table}
-
-              \begin{table}[H]
-                \sffamily
-                \caption{{Effect of distance from the capital on institutional trust (President, Parliament, Electoral commission)}}
-                \centering
-                %\footnotesize
-                \resizebox{16cm}{!}{
-                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                \\
-                \toprule
-                \toprule
-                &  \multicolumn{6}{c}{{Trust in institutions (President, Parliament, Electoral commission)}}  \\
-                \cmidrule(r){2-7}
-                &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                \cmidrule(r){2-6}
-                \cmidrule(r){7-7}
-                & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                    \cmidrule(r){2-3}
-                    \cmidrule(r){4-5}
-                    \cmidrule(r){6-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                 \midrule
-
-                 Distance from the capital&    0.295***&       0.301***&       0.563***&       0.306 &       0.483***&       1.738***\\
-                 \smallskip
-                 &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20) &      (0.05)   &      (0.58) \\
-                 Internet coverage &&&&&       0.016   &       2.035*** \\
-                 \smallskip
-
-                 &&&&&      (0.06)   &      (0.71)\\
-                 Distance from the capital $\times$ Internet coverage &&&&&      -0.458***&-2.992**\\
-                 \medskip
-                 &&&&&      (0.10) & (1.32)\\
-                 \midrule
-                 \smallskip
-                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                \smallskip
-                Country controls & Yes& No& Yes& No& No& No\\
-                \smallskip
-                Round FE & Yes & No& Yes & No& No& No\\
-                \smallskip
-                Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                \smallskip
-                Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                \smallskip
-                Observations           &   98,499   &       98,499   &        4,202   &        4,202   & 98,499   &       98,499 \\
-                Adjusted-R$^2$        &        0.164   &       0.198   &       0.148   &       0.184  & 0.200   &       - \\
-
-                                      \bottomrule
-                \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                \end{tabular}
-                }
-                \end{table}
-
-                \begin{table}[H]
-                  \sffamily
-                  \caption{{Effect of distance from the capital on trust in president}}
-                  \centering
-                  %\footnotesize
-                  \resizebox{16cm}{!}{
-                  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                  \\
-                  \toprule
-                  \toprule
-                  &  \multicolumn{6}{c}{{Trust in president}}  \\
-                  \cmidrule(r){2-7}
-                  &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                  \cmidrule(r){2-6}
-                  \cmidrule(r){7-7}
-                  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                      \cmidrule(r){2-3}
-                      \cmidrule(r){4-5}
-                      \cmidrule(r){6-6}
-                      \cmidrule(r){7-7}
-                      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                   \midrule
-
-                   Distance from the capital&       0.287***&       0.262***&       0.799***&       0.343   &       0.473***&       1.517**\\
-                   \smallskip
-                   &      (0.05)   &      (0.03)   &      (0.19)   &      (0.25)   &      (0.06)   &      (0.63) \\
-                   Internet coverage &&&&       &       0.047   &       1.659**  \\
-                   \smallskip
-                   &&&&    &      (0.07)   &      (0.81) \\
-                   Distance from the capital $\times$ Internet coverage &&&&&      -0.521***&-2.654*\\
-                   \medskip
-                   &&&&&      (0.12)  & (1.41) \\
-                   \midrule
-                   \smallskip
-                  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                  \smallskip
-                  Country controls & Yes& No& Yes& No& No& No\\
-                  \smallskip
-                  Round FE & Yes & No& Yes & No& No& No\\
-                  \smallskip
-                  Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                  \smallskip
-                  Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                  \smallskip
-                  Observations            &       97,261   &       97,261   &        4,149   &        4,149   &       97,261   &       97,261  \\
-                  Adjusted-R$^2$        &       0.137   &       0.180   &       0.180   &       0.215   &       0.182    &       - \\
-
-                                        \bottomrule
-                  \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                  \end{tabular}
-                  }
-                  \end{table}
-
-                  \begin{table}[H]
-                    \sffamily
-                    \caption{{Effect of distance from the capital on trust in parliament}}
-                    \centering
-                    %\footnotesize
-                    \resizebox{16cm}{!}{
-                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                    \\
-                    \toprule
-                    \toprule
-                    &  \multicolumn{6}{c}{{Trust in parliament}}  \\
-                    \cmidrule(r){2-7}
-                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                    \cmidrule(r){2-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                        \cmidrule(r){2-3}
-                        \cmidrule(r){4-5}
-                        \cmidrule(r){6-6}
-                        \cmidrule(r){7-7}
-                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                     \midrule
-
-                     Distance from the capital&       0.282***&       0.279***&       0.560***&       0.471** &       0.453***&       1.124***\\
-                     \smallskip
-                     &      (0.04)   &      (0.03)   &      (0.17)   &      (0.21)   &      (0.05)   &      (0.39) \\
-                     Internet coverage &&&&       &        0.007   &       1.169**  \\
-                     \smallskip
-                     &&&&    &      (0.06)   &      (0.52)   \\
-                     Distance from the capital $\times$ Internet coverage &&&&&      -0.442***& -1.776**\\
-                     \medskip
-                     &&&&&     (0.10)   &  (0.89) \\
-                     \midrule
-                     \smallskip
-                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                    \smallskip
-                    Country controls & Yes& No& Yes& No& No& No\\
-                    \smallskip
-                    Round FE & Yes & No& Yes & No& No& No\\
-                    \smallskip
-                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                    \smallskip
-                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                    \smallskip
-                    Observations            &      96,182   &       96,182   &        4,111   &        4,111   &       96,182   &       96,182  \\
-                    Adjusted-R$^2$        &        0.130   &       0.160   &       0.102   &       0.127   &       0.161   &       - \\
-
-                                          \bottomrule
-                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                    \end{tabular}
-                    }
-                    \end{table}
-
-                  \begin{table}[H]
-                    \sffamily
-                    \caption{{Effect of distance from the capital on trust in electoral commission}}
-                    \centering
-                    %\footnotesize
-                    \resizebox{16cm}{!}{
-                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
-                    \\
-                    \toprule
-                    \toprule
-                    &  \multicolumn{6}{c}{{Trust in electoral commission}}  \\
-                    \cmidrule(r){2-7}
-                    &  \multicolumn{5}{c}{{OLS}}&  \multicolumn{1}{c}{{2SLS}}  \\
-                    \cmidrule(r){2-6}
-                    \cmidrule(r){7-7}
-                    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}& \multicolumn{1}{c}{{Base sample}}& \multicolumn{1}{c}{{Base sample}}\\
-                        \cmidrule(r){2-3}
-                        \cmidrule(r){4-5}
-                        \cmidrule(r){6-6}
-                        \cmidrule(r){7-7}
-                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}\\
-                     \midrule
-
-                     Distance from the capital&       0.319***&       0.365***&       0.366*  &       0.206   &       0.529***&       2.588***\\
-                     \smallskip
-                     &     (0.04)   &      (0.03)   &      (0.19)   &      (0.23)   &      (0.06)   &      (0.84) \\
-                     Internet coverage &&&&       &        0.003   &       3.252***  \\
-                     \smallskip
-                     &&&&    &      (0.07)   &      (0.95)   \\
-                     Distance from the capital $\times$ Internet coverage &&&&&     -0.418***&  -4.606**\\
-                     \medskip
-                     &&&&&      (0.11)    &  (1.93) \\
-                     \midrule
-                     \smallskip
-                    Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes  \\
-                    \smallskip
-                    Country controls & Yes& No& Yes& No& No& No\\
-                    \smallskip
-                    Round FE & Yes & No& Yes & No& No& No\\
-                    \smallskip
-                    Country X Round FE  & No & Yes& No & Yes& Yes& Yes\\
-                    \smallskip
-                    Ethnic homeland FE & No & No & Yes& Yes& No& No\\
-                    \smallskip
-                    Observations            &      94,926   &       94,926   &        4,035   &        4,035   &       94,926   &       94,926   \\
-                    Adjusted-R$^2$        &         0.118   &       0.144   &       0.094   &       0.137   &       0.145   &       - \\
-
-                                          \bottomrule
-                    \multicolumn{7}{p{20cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-                    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-                    \end{tabular}
-                    }
-                    \end{table}
-
-\begin{table}[H]
-  \sffamily
-  \caption{{Effect of distance from the capital on political trust}}
-  \centering
-  %\footnotesize
-  \resizebox{12cm}{!}{
-  \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
-  \\
-  \toprule
-  \toprule
-  &  \multicolumn{8}{c}{{OLS}}  \\
-  \cmidrule(r){2-9}
-  &  \multicolumn{4}{c}{{Vote against ruling party}}&  \multicolumn{4}{c}{{Country performance}}  \\
-  \cmidrule(r){2-5}
-  \cmidrule(r){6-9}
-  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}  & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
-      \cmidrule(r){2-3}
-      \cmidrule(r){4-5}
-      \cmidrule(r){6-7}
-      \cmidrule(r){8-9}
-      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}&  \multicolumn{1}{c}{{(5)}}&  \multicolumn{1}{c}{{(6)}}&  \multicolumn{1}{c}{{(7)}}&  \multicolumn{1}{c}{{(8)}}\\
-      \midrule
-
-   Distance from the capital&      -0.164***&      -0.101***&      -0.462***&      -0.334***&       0.183***&       0.153***&       0.272*  &      -0.034   \\
-   \medskip
-   &      (0.02)   &      (0.02)   &      (0.09)   &      (0.09)   &      (0.04)   &      (0.03)   &      (0.16)   &      (0.20)   \\
-   \midrule
-   \smallskip
-  Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes  \\
-  \smallskip
-  Country controls & Yes& No& Yes& No& Yes& No& Yes& No\\
-  \smallskip
-  Round FE & Yes & No& Yes & No& Yes & No& Yes & No\\
-  \smallskip
-  Country X Round FE       & No & Yes& No & Yes& No & Yes& No & Yes\\
-  \smallskip
-  Ethnic homeland FE & No & No & Yes& Yes& No & No & Yes& Yes\\
-  \smallskip
-  Observations           &       99,414   &       99,414   &        4,247   &        4,247   &       98,512   &       98,512   &        4,203   &        4,203   \\
-  Adjusted-R$^2$         &       0.082   &       0.147   &       0.167   &       0.249   &       0.140   &       0.161   &       0.166   &       0.184   \\
-                        \bottomrule
-  \multicolumn{9}{p{21cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959).
-Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses.
-The set of individual controls
-  includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
-  education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption.
-The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
-The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin.
-*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
-  \end{tabular}
-  }
-  \end{table}
+We combine our Afrobarometer data with GSMA's digital maps of mobile internet coverage, providing 1x1-kilometer grid cell resolution data from mobile network providers.
+For regional coverage measurement, following Guriev et al.
+(2021) we overlay mobile coverage maps with population density data and calculate weighted averages of internet availability by region and year, using normalized population density weights.
+This approach ensures comparable coverage measures across regions of different sizes and population distributions.\\
+The second part of our empirical strategy addresses how mobile internet expansion affects spatial disparities in political trust.
+To address potential omitted variable bias - arising from non-random internet infrastructure placement and the correlation between economic development and internet access - we instrument internet coverage using regional lightning strike patterns, following recent literature (Manacorda and Tesei, 2020; Guriev et al., 2021; Cariolle and Carolle, 2024).
+This identification strategy exploits the fact that areas with frequent lightning strikes face higher infrastructure deployment and maintenance costs, while these weather patterns are plausibly exogenous to political trust.
+Following Guriev et al.
+(2021) and Cariolle and Carolle (2024), we construct our instrument by calculating the average daily lightning strikes at the regional level using VHRFC data over 1998-2013, weighted by regional population density in 2011.
+This weighting accounts for two offsetting forces: while lightning strikes increase infrastructure costs, population density reduces per-capita costs by spreading infrastructure investments across more users in high-risk areas.
+This instrument provides plausibly exogenous variation in internet access across varying distance from the capital city.
 

### 2025-02-24 writing/wp/tables.tex
import folders

--- 2024-11-20 wp/tables.tex
@@
 
+  \begin{table}[H]
+    \sffamily
+    \caption{BDD IV : Effect of internet coverage on political trust by distance}
+    \centering
+    %\footnotesize
+    \resizebox{17cm}{!}{
+    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
+    \\
+    \toprule
+    \toprule
+    & \multicolumn{5}{c}{{Border sample}}\\
+    \cmidrule(r){2-6}
+    & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
+        \cmidrule(r){2-2}
+        \cmidrule(r){3-5}
+        \cmidrule(r){6-6}
+        & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
+        \cmidrule(r){2-2}
+        \cmidrule(r){3-3}
+        \cmidrule(r){5-5}    
+        \cmidrule(r){6-6}    
+        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\
+
+        \midrule
+
+Distance from the capital & 0.640**&&&&  1.214***\\      
+\smallskip
+&      (0.26)   &&&&     (0.42)   \\
+Internet coverage     &      0.620** &&&&       0.809  \\
+\smallskip
+&  (0.30)   &&&&      (1.02)    \\ 
+\smallskip
+Distance from the capital $\times$ Internet coverage&      -0.535&&&&       -2.559**\\
+\smallskip  &       (0.46)    &&&&      (1.18) \\
+
+Lightning strikes && 0.002 && 0.003***  \\
+\smallskip&& (0.00) && (0.00) \\
+Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.003***\\
+\medskip&& (0.00) && (0.00)\\
+
+     \midrule
+    SW \emph{F} - Lightning strikes &-&-& 12.45 &- &-\\
+    \smallskip
+    SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 16.25 &-&-\\
+    \smallskip
+    Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
+    \smallskip
+    Country X Round FE       & Yes & Yes&- & Yes & Yes \\
+    \smallskip
+    Ethnic homeland FE& Yes & Yes&- & Yes & Yes \\
+    \smallskip
+    Observations       &       4,189    &4,247 && 4,247&      4,189  \\
+    Adjusted-R$^2$    &       0.190    &-&-&-&  \\
+                          \bottomrule
+    \multicolumn{6}{p{20.7cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
+    \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
+    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
+    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption.
+The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy.
+*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
+\end{tabular}}
+    \end{table}
+
 \end{document}

### 2025-02-24 writing/wp/tex.tex
import folders

\documentclass[11pt]{article}
\usepackage{amsmath}

\title{Essai}
\begin{document}
\maketitle

\tableofcontents
\clearpage

\section{The political consequences of Africa’s mobile revolution - Yeandle, 2023, WP}

\subsection{Abstract}
\begin{itemize}
    \item \textbf{QR}: How mobile technology shapes public opinion in geographically isolated areas ?
    \item \textbf{TH}: Mobile devices increase contact with physically distant social networks
    \\
    $\Rightarrow$ Rising urban contact provides exposure to opposition-aligned political contexts, which reduce government support and political trust
    \item \textbf{ES}: \begin{itemize}
        \item Afrobarometer, Staggered DiD, continent-wide
        \item Household panel, OLS ?, Ghana
    \end{itemize}
    \item \textbf{L}: social contract, accountability, technological change
\end{itemize}

\subsection{Notes}
\subsubsection*{Results}
\begin{itemize}
    \item The arrival of mobile coverage reduces both trust in President and evalutation of government performancen a dynamic effect that continues several years after en area enters reception
    \item Evidence that coverage is not targeted by governments, nor that its future provision has anticipatory effects
    \item The arrival of moblile coverage drives a decline in trust and apparaisal of national but not local politicians
    \begin{itemize}
        \item Rural residents are likely better-informed about local political actors before the arrival of coverage, so it is national figures and insitutions which are subject to change
    \end{itemize}
    \item Negative effects are driven by respondents in the most isolated, distant, rural areas
    \begin{itemize}
        \item Compare individuals living less than 273km away from their capital (the median distance) with those living furhter away than this
    \end{itemize}
    \item Mobile coverage has much smaller informational impacts on urban respondents, and are more exposed to other forms of mass media and direct forms of opposition moblilisation, like protests
\end{itemize}
\subsubsection*{Data}
\begin{itemize}
    \item Coverage is a strong proxy for individual-level, allows to look further back in time, before usage questions were common in social surveys
    \item Afrobarometer rounds 1-6: 1999 to 2015
    \item Respondents are classified as in or outside coverage based on the coordinates of their enumeration area
\end{itemize}
\subsubsection*{Specification}
\begin{itemize}
    \item 1st concern: Expansions are staggered, both within and across countries: locally defined areas receive coverage at different periods in time
    \begin{itemize}
\item Living inside coverage is a dynamic treatment, as it takes time for local residents in newly covered areas to start personnaly using mobile devices, and thus for urban contact and trust effects to ensue
    \\
    $\Rightarrow$: TWFE might draw erroneous comparisons between groups: treatment "turns on" in different periods and has effects that vary over time. This might contaminate the control group under TWFE and lead to "forbidden comparisons" (Goodman-Bacon 2018; Dube et al. 2023)
    \item Run event-study specifications using the Sun and Abraham (2021) estimator: designed for staggered treatments with dynamic effectsn, estimating a series of cohort-by-period interactions which can then be aggregated to produce an overall ATT
\end{itemize}
\end{itemize}
\begin{itemize}
    \item Use never-treated units as the central comparison group (11\% of the full sample), represent en "clean" counterfactual (Dube et al. 2023)
    \item 2nd concern: the outcome data stems from repeated cross-sections surveys of the same population buth with different individuals sampled in each rounds
    \begin{itemize}
    \item As respondents are selected trough randomisation, we can assume the rising probability of living inside coverage in later rounds is driven by the gradual expansion of coverage itself
\end{itemize}
    \item Country and year fixed effects; EA clustering
\end{itemize}

\subsection*{Threats to inference}
\subsubsection*{SUTVA}
\begin{itemize}
    \item "Individuals living inside coverage are affected by it, and those living outside are not"
    \item Spatial nature of the context increases risks of spillovers
    \item 3 solutions:
    \begin{itemize}
        \item Spillovers are likely to bias against finding significant effects, since the negative impact of coverage would be indirectly shaping opinion in control group observations
        \item Spillovers between EAs are unlikely; rural EAs are often physically far from one another due to low population density
        \item Conley SE 50km radius
    \end{itemize}
\end{itemize}
\subsubsection*{Parallel trends}
\begin{itemize}
    \item "If those in the treatment group did not receive coverage, changes in behaviour would not diverge from those under control"
    \item Concerns that treated areas are different in other ways besides coverage, or that coverage might be targeted by governmentrs seeking to change political behaviour
    \item Allowing for country trends help relax this assumption by allowing each country to follow its own path
\end{itemize}
\subsubsection*{No (relevant) anticipation effects}
\begin{itemize}
    \item "Respondents do not condition their behavior on when they will receive coverage in the future"
    \item Seems unlikely: decisions about the future allocation of coverage are taken commercially, in either country capitals or overseas, and it is difficult ti see how rural residenst living outside of coverage would come to know about these
    \item Examining pre-trends, there is no evidence that public opinion shifts in periods just prior to receiving treatment
\end{itemize}
\subsubsection*{Discussion}
\begin{itemize}
    \item Mobile technology appears to exhibit one way negative effects, undercutting previous pro-incumbent bias. It is not clear that rural opinion is reponding to the true quality of politicians, more than it is responding to the homogeneous, and perhaps biased, information they are given by urban relaives
    \item It is an open question whether represents a better or worse state of rural accountability, or whether this shift is normatively desirable
    \item Further work should consider how mobile internet, and related exposure to social media platforms, differs, from basic forms of mobile telephony that this paper investigates
\end{itemize}
\clearpage
\section{Mobile internet and national identity in sub-saharan Africa, Choi, Laughlin, Schultz, 2023, WP}

\subsection{Abstract}
\begin{itemize}
    \item \textbf{QR}: How the expansion of mobile internet infrastructure affects national identity in sub-Saharan Africa ?
    \item \textbf{TH}: Access to mobile internet in diverse society undermines national identity because it facilitates voter exposure to the polarizing tendencies of internet-based social media and communication platforms
    \item \textbf{ES}: \begin{itemize}
        \item DiD; Afrobarometer: internet on identification
        \item As if random variation in the timing of individuals' survey interview relative to presidential elections
    \end{itemize}
    \item \textbf{L}: How technological innovations can inhibit the process of state-building in diverse societies
\end{itemize}

\subsection{Notes}
\subsubsection*{Theory}
\begin{itemize}
    \item Mobile internet can undermine national identification by exposing citizens to internet-based social media platforms which provide two interacting pathways to polarization
    \begin{enumerate}
        \item An elite-driven pathway whereby citizens come into contact with the polarizing rhetoric peddled by political parties and politicians that capitalize on the opportunities provided by these new social media platforms during elections
        \item A mass-driven pathway whereby citizens not only consume or disseminate polarizing mis-disinformation from politicians but also themselves take part in the productuon and reproduction of such mis/disinformation
    \end{enumerate}
\end{itemize}
\subsubsection*{Results}
\begin{itemize}
    \item Expanded access leads to a decrease in individual's propensity to identity with the nation over their ethnocommunal group
    \item Proximity to presidential elections amplifies the polarizing effects of the mobile internet coverage
\\
$\Rightarrow$ Do not intend to adjucate whether polarization through increased mobile access is more an elite-driven or mass-driven process

\end{itemize}
\subsubsection*{Specification}
\begin{itemize}
    \item Afrobarometer: rounds 3-7; 2005-2018; 27 countries
    \item Combining survey responses with mobile coverage spatial polygons allows to locate whether respondents fall within or outside of mobile coverage boundaries
    \item DiD using repeated cross-sections
    \begin{itemize}
    \item 1st difference: whether an individual lives in an area in which, during the period of study, mobile internet coverage becomes available
    \item 2nd difference: whether an individual is surveyed in the pre-mobile coverage or post-mobile coverage period
    \item Compare treated units to "not-yet treated units": period study of 13 years during an era of rapid mobile internet expansion, so individuals who are still left without mobile internet coverage at the end of the period may be fundamentally different
    \end{itemize}

    \item Country/district 
    \begin{itemize}
     \item        \begin{equation*}
        \text{y}_{ijt} = \alpha + \beta \text{Covered}_{ijt} + \gamma \text{EverCovered}_{i} + \delta_j + \zeta_t + \theta \text{X}_{it} + \epsilon_{ijt}
        \end{equation*}
    \item Geographical area (country or district); clustered by locality (robustness with Conley 500km)
\end{itemize}

    \item Grid
    \begin{itemize}
        \item Aggragate the treatment to 55x55km
        \item Round and grid-cell FE
        \item Individuals are treated if the majority of respondents in the grid cell during a round have mobile coverage
        \item Clustered by grid-cell
        \item Staggered problems, not shown in the WP
    \end{itemize}

\end{itemize}

\subsubsection*{Alternative explanations}
\begin{itemize}
    \item Access to mobile internet may have increased individual repsondents' wealth
    \\
    $\Rightarrow$ Controls measures of wealth
    \item Results driven by the selective expansion of mobile internet coverage into affluent areas
    \\
    $\Rightarrow$ Controls for time-varying measure of population density; distance from a road network
    \item Increased coverage may accompany a broader modernization process
    \\
    $\Rightarrow$ Time varying controls for nighttime light density
    \item Result do not emerge through electoral mechanism but by increased access to information that shapes citizens evaluation (approval or trust) of the government and insitutions
    \\
    $\Rightarrow$ Control for measures of trust; no effect of increased mobile internet on trust
    \item Basic mobile internet specifications
\end{itemize}
\end{document}

### 2025-02-24 writing/wp/wp - Copy.tex
import folders

--- 2024-11-20 wp/method and results.tex
@@
 \and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
+% \textbf{Paul Maarek}\thanks{\emph{Corresponding author}. LEMMA, Universit\'{e} Panth\'{e}on-Assas (Paris II), France; \texttt{Paul.Maarek@u-paris2.fr}.}   \\ LEMMA -- Paris II  \\
+%   \and \textbf{Victor Hiller} \\ LEMMA -- Paris II \\ 
+% \and \textbf{Michael T. Dorsch}
+%  \\ CEU -- Vienna 
+% \and
+% \and \textbf{R\'{e}dha Chaba} \\ LEMMA -- Paris II  \\
 }
@@
 \maketitle
-\section*{Data}
-We use Afrobarometer surveys to leverage geocoded information on public opinion, information-gathering and demographic characteristics across African countries at the individual level.\footnote{All Afrobarometer surveys were conducted via-in-person, face-to-face interviews.
-The method did not change to computer-assisted interviews, thereby avoiding potential bias toward areas with mobile internet coverage.} We rely on rounds 5 to 8, covering the period from 2011 to 2021, to construct our sample of 98,235 individual respondents across 20 Sub-Saharan African countries.\footnote{Our sample includes: Benin, Burkina Faso, Botswana, Cameroon, Ivory Coast,
-Ghana, Guinea, Kenya, Liberia, Mali, Malawi, Mozambique, Namibia, Niger, Nigeria, Sierra Leone, Tanzania, Uganda, Zambia, Zimbabwe.}\footnote{We exclude islands, countries with multiple capitals, and Northern African countries.
-We also exclude Burundi, Gabon, Gambia, and Senegal due to missing data on mobile internet coverage.}
-We measure political accountability by focusing on two key sets of variables from the Afrobarometer.
-First, we measure trust in institutions through the following questions:
-\textit{‘‘How much do you trust each of the following: the president, the parliament/national assembly?’’}.
-Each question is measured on a scale from 0 ('Not at all') to 3 ('A lot').
-We construct our main dependent variable \textit{Institutional Trust} by averaging the responses to these two questions.\footnote{In Table X we report the results of the replication using the variables analyzed individually.}
-Second, we measure the willingness to sanction the ruling party through the following question:
-\textit{‘‘If [presidential elections] were held tomorrow, which [party’s candidate] would you vote for?’’}.
-We create a binary variable that equals 1 if the respondent indicates they would vote for any party other than the ruling party, and 0 if they would vote for the ruling party.\\
 
-The geographic spread of our sample, ranging from urban centers to remote rural areas, allows us to effectively examine how the impact of mobile internet on political accountability varies with distance from political centers.
-We leverage the precise geocoding of Afrobarometer survey enumeration areas to calculate the distance of each survey respondent from their country's capital city.
-Similar to Michalopoulos and Papaioannou (2014), to account for varying country sizes in our sample, we construct a relative distance measure as our main independent variable instead of using absolute distance from the capital city.
-For each respondent, we calculate the relative distance by dividing the respondent's distance from the capital by the maximum distance to the capital within the country.
-This standardization allows for meaningful comparisons across countries of different sizes.
-The resulting values range from 0 (at the capital) to 1 (at the furthest point from the capital), providing an intuitive scale of remoteness that is comparable across all countries in our sample.\\
+\section*{Research question}
 
-We combine Afrobarometer geocoded individual level data with detailed digital maps of mobile internet coverage provided by the Global System for Mobile Communications Association (GSMA).
-These maps compile coverage data from mobile network providers to measure coverage availability at a reliable signal strength with a 1x1-kilometer grid cell resolution.
-To integrate mobile network coverage data with the Afrobarometer surveys, we calculate regional mobile internet coverage for each region and year.
-This process involves overlaying the mobile internet coverage map with population density data at the grid-cell level.
-We then compute a weighted average of mobile internet availability for each region, using population density as weights.
-These weights are normalized to sum to one, ensuring comparability across regions of different sizes and population distributions.
+How does the diffusion of mobile internet affect political accountability in remote areas ?
+\section*{Hypothesis}
+\begin{enumerate}
+  \item Living in remote areas is associated with higher levels of institutional trust.
+  \item Increased internet access mitigates the spatial disparities in the levels of institutional trust.
+  \item Increased internet access strengthens ethnic over national identity in remote areas
+\end{enumerate}
 
-\section*{IV method}
+Trust in national institutions promotes state legitimacy, civic engagement, and social cohesion, all essential for nation-building.
+However, the nature of this trust is crucial for ensuring favorable outcomes.
+Trust in instituions can be misleading if citizens lack information or interest.
+Such default trust can disrupt accountability mechanisms and undermine incentives for public investments.\\
 
-Specifically, our main treatment of interest is the interaction between internet coverage at the regional level and distance from the capital city.
-This approach allows us to capture potential heterogeneity in the effect of internet news exposure across different geographic contexts.\\
+Most African capitals lie in peripheral areas, with large parts of the population living at significant distances from the capital city.
+This geographic distribution hinders national institutions from reaching remote areas, causing a shortage of state presence and a dual institutional framework within countries.
+The limited state presence and restricted access to information make remote populations less likely to experience governance issues, fostering a default trust in institutions.\\
 
-Several econometric challenges necessitate an instrumental variable (IV) approach.
-Reverse causality is a concern, as trust in political institutions may influence internet news consumption patterns, creating a bidirectional relationship that complicates causal inference.
-Omitted variable bias poses a threat, as unobservable factors such as political interest, media literacy, or cultural attitudes may affect both news consumption and institutional trust, potentially biasing our estimates.
-Furthermore, measurement error in self-reported internet news consumption could lead to attenuation bias.
-These issues are compounded when considering the interaction term, as any endogeneity in the component variables carries over and potentially amplifies in the interaction.\\
+Expanding internet coverage can replace default trust with a refined perception of institutions to restore accountability mechanims essential for nation-building.\\
 
-To address these challenges, we propose using the interaction between mobile internet coverage and distance from the capital city as our instrument.
-This choice is motivated by several factors.
-Higher mobile internet coverage directly increases the potential for internet news consumption, ensuring relevance.
-The rollout of internet infrastructure is primarily driven by commercial and technical factors rather than political considerations, enhancing the likelihood of satisfying the exclusion restriction.
-Moreover, mobile internet coverage and its impact likely vary with distance from the capital city, providing a strong first-stage relationship with our treatment of interest.
-The interaction term in our instrument captures how the availability of mobile internet coverage changes with distance from the capital city, which in turn affects the likelihood of internet news consumption across different regions.
-This approach allows us to estimate how the influence of internet news consumption on trust varies depending on geographic proximity to the center of political power, using only the variation in news consumption driven by exogenous factors related to internet infrastructure development.\\
+\textbf{Capital location}\\
 
-While our instrument choice is theoretically justified, we acknowledge potential criticisms.
-In some contexts, governments may influence internet infrastructure deployment for political reasons, potentially violating the exclusion restriction.
-Additionally, uneven internet development could reflect broader patterns of regional inequality, which might independently affect trust in institutions.
-The interaction with distance from the capital could exacerbate these concerns if there are systematic differences in how mobile internet infrastructure is rolled out about proximity to the political center.\\
+Some leaders have shifted the location of their capital in order to make governments more central and closer to their citizens. (Sow, 2023)\\
+How trust is spatially distributed matters for how polities are governed, and is consequential for electoral behaviour, trends and outcomes (McKay, 2023)\\
+Presence of the state: To what degree do state penetrates their societies?\\
+Mann (1993): Infrastructural power comes from increasing the level and quality of contact citizens have with state.
+Organizational capacity is partly conditioned by productive interactions that take place throughout a country's territory.\\
 
-To address these concerns, we argue that economic and technical determinants are the primary drivers of the expansion of mobile internet coverage, rather than political incentives.
-Investment decisions made by telecom providers — often international firms – are made on the basis of their economic viability and expected returns.
-This emphasis on financial incentives diminishes the probability of politically motivated deployment strategies.
-Additionally, variations in mobile internet coverage across regions often arise due to technical and geographical limitations.
-Terrain, population density and the availability of supporting infrastructure all define the feasibility and cost of network deployment.
-These technical considerations often override any potential political motivation in infrastructure development decisions.
-We capture the nuanced interplay of these economic and technical factors across diverse geographic contexts by using an instrument that interacts mobile internet coverage and distance to the capital.\\
+State are not sumply about order and growth; they fundamentally depend on the construction, maintenance, and allegiance of a political community (voir les ref p.20 du livre Unpacking States in the DevelopingWorld: Capacity, Performance, and Politics - Centeno, Kohli,
+Yashar).
+State must have mechanims for structuring and ingraining social inclusion.
+By social inclusion we mean the ability of the state to incorporate the entire population, to promote social wellbeing, and to establish itself as the property of no particular group or sector.\\
+
+African presidents have historically controlled politics on the continent through highly centralised states, a situation that is enrished in around 80 per cent of African constitutions (Kuperman 2015, from Dyzenhaus)\\
+Number of factors that shape the quality of accountability in devloved system, such as the strengh of citizens and civil society (Sisk 2001).\\
 

### 2025-02-24 writing/wp/wp.tex
import folders

%l !Rnw weave = knitr

\documentclass[11pt]{article}

\usepackage[]{graphicx} % omit 'demo' option in real doc.
\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\usepackage{epstopdf}
\usepackage{float}
\epstopdfDeclareGraphicsRule{.tif}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tif}

\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage{hyperref}
\hypersetup{
        colorlinks=true,
        breaklinks,
        allcolors=[RGB]{128,0,0}
}

\let\oldFootnote\footnote
\newcommand\nextToken\relax

\renewcommand\footnote[1]{%
    \oldFootnote{#1}\futurelet\nextToken\isFootnote}

\newcommand\isFootnote{%
    \ifx\footnote\nextToken\textsuperscript{,}\fi}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{crimson}

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}

\usepackage{bbding} % checkmark symbol
\usepackage{comment} % checkmark symbol

\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\floatpagefraction}{0.75}

%Bibliography
\usepackage{natbib}
%\usepackage[autostyle]{csquotes}
%\usepackage[backend=bibtex, style=authoryear, natbib=true]{biblatex}
%\addbibresource{CCH.bib}

%%For Hypotheses and Subhypotheses
%\usepackage{ntheorem}
\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp}
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
}
\makeatother
%%%

\setcounter{MaxMatrixCols}{10}

\theoremstyle{plain}
\newtheorem{prop}{\protect\propositionname}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\makeatother
\providecommand{\examplename}{Example}
\providecommand{\propositionname}{Proposition}
\providecommand{\theoremname}{Theorem}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bb}{\begin{block}}
\newcommand{\eb}{\end{block}}
\newcommand{\bmath}{\begin{eqnarray}}
\newcommand{\emath}{\end{eqnarray}}
\newcommand{\bmathnn}{\begin{eqnarray*}}
\newcommand{\emathnn}{\end{eqnarray*}}
\newtheorem{theorem}{{Theorem}}%[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{prediction}{Prediction}
\newtheorem{open_question}{Open question}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{claim}[theorem]{{Claim}}
\newtheorem{example}[theorem]{{Example}}
\newtheorem{corollary}[theorem]{{Corollary}}
\newtheorem{remark}[theorem]{{Remark}}
\newtheorem{assumptions}[theorem]{{Assumptions}}
\newtheorem*{thm1star}{{Theorem $\mathbf{1^*}$}}
\newtheorem*{thm2star}{{Theorem $\mathbf{2^*}$}}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}

%For nice tables
\usepackage{booktabs}
\usepackage{array}
\usepackage{threeparttable}
\usepackage{tabulary}
\newcolumntype{M}[1]{{\centering\arraybackslash}m{#1}}

%Expectation opperator
\newcommand{\Expect}{{\rm I\kern-.3em E}}

%Significance commands
\newcommand*{\SuperScriptSameStyle}[1]{%
  \ensuremath{%
    \mathchoice
      {{}^{\displaystyle #1}}%
      {{}^{\textstyle #1}}%
      {{}^{\scriptstyle #1}}%
      {{}^{\scriptscriptstyle #1}}%
  }%
}

\newcommand*{\oneS}{\SuperScriptSameStyle{*}}
\newcommand*{\twoS}{\SuperScriptSameStyle{**}}
\newcommand*{\threeS}{\SuperScriptSameStyle{*{*}*}}
\newcommand{\vh}[1]{\textcolor{red}{(VH: #1)}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\title{Mobile Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

\vspace{1cm}

\author{
\textbf{Illan Barriola} \\ CRED -- Paris II \\
\and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
% \textbf{Paul Maarek}\thanks{\emph{Corresponding author}. LEMMA, Universit\'{e} Panth\'{e}on-Assas (Paris II), France; \texttt{Paul.Maarek@u-paris2.fr}.}   \\ LEMMA -- Paris II  \\
%   \and \textbf{Victor Hiller} \\ LEMMA -- Paris II \\ 
% \and \textbf{Michael T. Dorsch}
%  \\ CEU -- Vienna 
% \and
% \and \textbf{R\'{e}dha Chaba} \\ LEMMA -- Paris II  \\
}

\date{ \today}

\maketitle

\section*{Research question}

How does the diffusion of mobile internet affect political accountability in remote areas ?
\section*{Hypothesis}
\begin{enumerate}
  \item Living in remote areas is associated with higher levels of institutional trust.
  \item Increased internet access mitigates the spatial disparities in the levels of institutional trust.
\end{enumerate}

\section*{Presentation}
\textbf{Many African capital cities are located close to the coast} 
  \begin{itemize}
    \item Constrain the penetration of institutions in the hinterland\\
    $\Rightarrow$ Coexistence of a dual institutional framework within countries (Lewis 1954; Migdal 1988, Michalopoulos and Papaioannou 2014)\\
    $\Rightarrow$ Concentration of the economic activity around capital cities (Pinkovskiy 2013, Provenzano 2024)

  \end{itemize}
\clearpage

\textbf{State of Art}\\

The identity of sovereign states and their perceived ligitimacy have dimensions both objective and subjective.
Discrepancies between these two dimensions may appear during processes of democratization because the participatory aspirations of citizens
 and their respective identites will not necessarily coincide with the existing political boundaries and the institutional framework.\\

This may lead to a more or less peaceful redrawing of boundaries ands attempts of internal democratic reforms.
These processes and possible conflicts cannot be resolved by democratic standards and procedures because the rule of law pre-supposes an existing poltical unit, and procedures such as majority decisions may exclude and possibly suppress important segments of the population.
If democracy means "rule of the people", it first has to be decided who the people are and which boundaries should be respected.
In this sens, state formation and nation-building must be considered as prerequisites of any meaningful democratization.\\

\textbf{Sow, 2023}\\

The post-colonial era in Africa saw a wave of nation building initiatives aiming to construct a sens of national identity.
The rational for nation building stems from the importance of having a united population for the sake of conflict prevention and long-term political stability.
On key component of nation building is constructing a sense of belonging to one nation and having a strong sense of national identity.
In African countries where ethnic identities remain salient, ethnic ties can be formed at the detriment of national identity. In contexts where ethnic identities are strong and present, individual may feel closer to their ethnic group than their nation, as a whole.\\

The instrumentalist theory defines identity as a malleable social construct, which changes due to a myriad of factors (\textcolor{blue}{\textbf{Williams, 2015}}).\\

Improvements in ICT, leads to an improved access to information.
This improved access to information could heighten the perception of corruption.
Moroever, improved ICT leads to the strenghterning of social networks along digital lines, thus bringing co-ethnics together in the digital world.\\

Nation building is defined as the process of creating and maintaining a shared national identity.\\
Despite the existence of differences - stemming from a different histrorical background, ethnic diversity, a colonial divide and conquer legacy, etc
- among groups, nation building strives to build collective capacity and create a shared vision of the future (\textcolor{blue}{\textbf{Bourgon, 2010}}).\\
Many identify with both their nation and their ethnic group. The position of one's ethnic group, in society, can determine the level of national identity.
\textcolor{blue}{\textbf{Green (2020)}} argues that certain nations have "core" ethnic groups and when the core group is in power, members of the group tend to identify more with the nation.\\

The modernist view states that national identity is a product of modernity, through mechanisms related to industrialization and mass education (\textcolor{blue}{\textbf{Storm, 2018}}).
As countries develop, residents starts to trade in other forms of identity for a more solid national identity. Richer areas tend to identify more with the nation - over their ethnic group - 
due to a lower reliance on ethnic networks (\textcolor{blue}{\textbf{Ahlerup, Baskaran and Bigsten, 2017}}).\\

Centralized political systems encourage citizens to pool their demands into one that suits the wider group of citizens, and abandon demands rooted in provincial origins (\textcolor{blue}{\textbf{Acemoglu, Robinson and Torvik, 2020}}).\\

In Africa notably, geographic features have affected state-building \textcolor{blue}{\textbf{(Herbst, 2000})}. Countries use spatial tools to create or improve national identity.\\
Placement of strategic cities within the nation. Some leaders have shifted the location of their capital in order to make governments more central and closer to their citizens. In 1976, Nigeria moved the capital from Lagos to Abuja.\\

Ethnic identification refers to "a person's use of racial, national or religious terms to identify himself, and thereby, to relate himself to others." (\textcolor{blue}{\textbf{Glaser, 1958}}).
Instrumentalism defines ethnicity as a tool used by individuals of the group to unify and mobilize each other in the aim to achieve a common goal.
Ethnic identities are socially constructed and can be formed through differents channels (\textcolor{blue}{\textbf{Wimmer, 2008}}), such as economic, political, security, and nation building.\\

Research papers using Afrobarometer surveys in Uganda (\textcolor{blue}{\textbf{Green, 2020}}) and Benin (\textcolor{blue}{\textbf{Koter, 2019}}) find that ethnic identification is affected by whether
 or not the president is part of a respondent's ethnic group.
 Perceived exclusion of an ethnic group from power strengthens ethnic identification. Politicians engage in ethnically targeted outreach, which can lead to stronger ethnic identification in both the in-groups who see their ethnic groups catered to and the out-group
  who can perceive a threat through the exclusion (\textcolor{blue}{\textbf{Higashijima and Nakai, 2015}}).\\

Suspect corruption to play a role in poor confidence in government and the subsequent decline in national identification. News consumption and internet access. Also, 
¨possible stronger ethnic connections in the digital world.\\

Nation building is one key pillar of a country's political stability. A lack of thereof can hinder long term economic development by preventing the influx of investment.\\
One key element of nation building is creating a nation of people who feel strong ties to their countries and identify with their nation to some extent. Africa is home to nearly 3000 ethnic groups.
The salience of ethnic identities can take away from national identity and hinder long term nation builiding efforts.\\

\textbf{McKay, 2023}

How trust is spatially distributed matters for how polities are governed, and is consequential for electoral behaviour, trends and outcomes.\\

\textbf{Dellmuth, 2023}

Future research could usefully theorise and examine how the effect of regional inequalities on political attitudes might be conditioned by democracy.\\

\textbf{States in the Developing World, Centeno, Kohli, Yashar, Mistree}\\

- \textbf{Unpacking States in the Developing World: Capacity, Performance, and Politics - Centeno, Kohli, Yashar}

In its simplest terms, state capacity involves the bureaucratic, managerial, and organizational ability to process information, implement policies, and maintain governing systems. State capacity is thus a function of the organizational skills and institutions required for carrying out relevant tasks. In particular, we identify organizational capacity in terms of the following factors:\\
- Presence of the state: To what degree do state penetrates their societies? Mann(1993) highlighted the importance of the infrastructural reach of the state. Mann's critical insight came from recognizing that infrastructural power comes from increasing the level and quality of contact citizens have with state. Organizational capacity is partly conditioned by productive interactions that take place throughout a country's territory.\\

States are not simply about order and growth; they fundamentally depend on the construction, maintenance, and allegiance (sometimes coerced) of a political community (voir les ref, p.20 du livre). States must have mechanisms for structuring and ingraining social inclusion. By social inclusion we mean the ability of the state to incorporate the entire population, to promote social wellbeing, and to establish itself as the property of no particular group or sector.\\

Even where polities have clearly and expansively defined the rules of membership, the question is whether the state can uphold those terms. Can they identify, count, and regulate the citizens of their country. It entails meaningful state capacity throughout a territory and across social cleavages to administer censuses, provide passports, construct participatory institutions, and externd social services. In this regard, social inclusion requires defining citizenship membership and boundaries alongside policies that seek to equalize further political, social, and/or economic rights (Marshall 1963). As should be clear, social inclusion can be used for both democratic and authoritatian ends.\\

-\textbf{State Capacity, History, Structure, and Political Contestation in Africa - Mkandawire}

Concern over state capacity and its deployment in Africa has changed over the years. In the immediate postcolonial era, the concerns revolved around three issues. [...]\\
The second was about "nation building" including especially the capacity to hold together the new nation. This required capcities to inculcate new values of nationalism in the populace, to legitimize the poltical and economic order (Deutsch 1978), and to exercise "infrastructural power" (Mann 1984) that would obviate or diminish the constant recourse to repression.\\

A widespread view was that in the special conditions of Africa, the task of acquiring legitimacy was inherently more complex than in other societies - what with the artificiality if national borders, the multiplicity of ethnic groups, and a populist streak in African politics -  a populism has something to do with the peculiarities of the African agrarian structures and the varied social origins of the "founders" of the new nation.\\

Improve the welfare of the citizenry and thereby enhance its own legitimacy. Similarly, legitimacy can facilitate the extractive capacity of the state through the "quasi-voluntary compliance" it induces among taxpayers (Levi 1988).\\

\textbf{Institutions and Democracy in Africa - Nic Cheeseman}\\
- \textbf{Decentralisation - Accountability in Local Government - Alex Dyzenhaus}\\

African presidents have historically controlled politics on the continent through highly centralised states, a situation that is enrishned in around 80 per cent of African constitutions (Kuperman 2015).\\
The existing literature highlights a number of factors that shape the quality of accountability in devolved systems, such as the strengh of citizens and civil society (Sisk 2001).\\

\textbf{Politics in the Developing World - Burnell, Rakner, Randall}\\
- \textbf{Ethnopolitics and Nationalism - Scarritt, Birnir}\\

National identities are inherntly political, emphasizing the autonomy and unity of the nation as an actual or potential political unit (Hutchinson and Smith 1994). Civic national identities involve unity among citizens of an autonomous state. [...] Very few natioanl identities in the developing world are purely civic, but a substantial majority of them contain civic or multi-ethnic aspects, so that they do not identify the nation with a single ethnic group. Since nationalism is a constructed identity, the significant variations in the specific nature of nations in the developing world are not surprising. The boundaries of the vast majority of developing states were determined by colonial rulers, and the varieties of nationalism are products of the interaction between the states that rule within these boundaries and the morphology of ethnopolitical identities, the tactics of ethnopolitical groups, and the presence of alternative identities within the same boundaries. "The normative model of the contemporary polity calls for the coincidence of nation and state" (Young 1976).\\

Sub-Saharan Africa is where multi-ethnic nationalism is most common, although ethno-nationalism is by no means absent there. The predominence of ethnopolitical cleavages, their complex multilevel morphology, the absence of large cultural differences in most African countries except those divided by religion, and the politics of communal contention combine to produce multi-ethnic national identities  the most effectively integrate national and ethnopolitical identities in this context.\\

National identities: Inherently political, emphasizing the autonomy and unity of nation as an actual or potential political unit.\\
Nation-building: Referring to building a sense of national belonging and unity.\\

\textbf{Trust but verify? Examining the role of trust in institutions in the spread of unverified information on social media - Zoonen et al. 2024}\\

Trust in institutions is associated with reasons for sharing unverified information and reduces individual's motivation to authenticate information.\\

\end{document}

### 2025-02-24 script/r/discontinuity_plot.Rmd
keep essential scripts

```{r}
setwd("~/working_paper/trust/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(estimatr)
library(ggplot2)
library(extrafont)
library(ggtext)
```

```{r}
df_40 <- read_dta("data/data_dta/df_40_2.dta")

df_40 <- na.omit(subset(df_40, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num")))

reg3_40 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num), clusters = cluster_bdd, data = df_40)

library(lfe)

reg3_40 <- felm(pol_trust ~ dist_cap_max_norm + dist_sndncap_max_norm + age + age_2 + factor(sex) + factor(educ_sec) + 
              factor(bin_rural) + factor(bin_conditions_eco) + factor(bin_conditions_country) + factor(bin_emp) + disc_pol_a + 
              tele_news + paper_news + radio_news + night_region_log + pop_region_log + area_region_log | 
              country_round + murdock_names | 0 | cluster_bdd, data = df_40)
summary(reg3_40)

df_40$ft_values <- fitted(reg3_40)

```

```{r}
#Pour les gens près de la capitale (sous la médiane), on rend la distance à la frontière négative (cf. on multiplie par -1)
df_40$distance_border <- ifelse(df_40$dist_cap_max_norm<median(df_40$dist_cap_max_norm),
                                       -df_40$distance_border,df_40$distance_border)

#On crée une base avec les gens près et une avec les gens loin
df_40_pres <- subset(df_40, df_40$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
df_40_loin <- subset(df_40, df_40$distance_border>0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)

#On définit 10 intervalles
nb_intervals <- 10

#On découpe les deux bases en 10 intervalles
intervals_dist_border_pres <- cut(df_40_pres$distance_border, breaks = nb_intervals)
intervals_dist_border_loin <- cut(df_40_loin$distance_border, breaks = nb_intervals)

#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base près
mean_dist_border_intervals_pres <- data.frame(tapply(df_40_pres$distance_border, intervals_dist_border_pres, mean))
mean_trust_intervals_pres <- data.frame(tapply(df_40_pres$ft_values, intervals_dist_border_pres, mean))

#On renomme les colonnes
colnames(mean_dist_border_intervals_pres) <- "mean_dist_border_intervals"
colnames(mean_trust_intervals_pres) <- "mean_trust_intervals"

#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base loin
mean_dist_border_intervals_loin <- data.frame(tapply(df_40_loin$distance_border, intervals_dist_border_loin, mean))
mean_trust_intervals_loin <- data.frame(tapply(df_40_loin$ft_values, intervals_dist_border_loin, mean))

#On renomme les colonnes
colnames(mean_dist_border_intervals_loin) <- "mean_dist_border_intervals"
colnames(mean_trust_intervals_loin) <- "mean_trust_intervals"

#On fussionne les bases près et loin
mean_dist_border_intervals <- rbind(mean_dist_border_intervals_pres,mean_dist_border_intervals_loin)
mean_trust_intervals <- rbind(mean_trust_intervals_pres,mean_trust_intervals_loin)

data_intervals <- cbind(mean_dist_border_intervals,mean_trust_intervals)

#Les intervalles de confiance pour le trust
lower_distance_fun <- function(x) {
  mean_val <- mean(x)
  conf_int <- t.test(x)$conf.int
  ic95_ <- abs(conf_int[1] - mean_val)
  ic95_
}

#On fait les intervalles de confiance pour chaque intervalle (40 en tout, 10 près + 10 loin)
mean_trust_intervals_pres_ic <- data.frame(tapply(df_40_pres$ft_values, intervals_dist_border_pres, lower_distance_fun))
mean_trust_intervals_loin_ic <- data.frame(tapply(df_40_loin$ft_values, intervals_dist_border_loin, lower_distance_fun))
colnames(mean_trust_intervals_pres_ic) <- "ic_trust"
colnames(mean_trust_intervals_loin_ic) <- "ic_trust"

#On met toutes les intervalles dans la même base
mean_trust_intervals_ic <- rbind(mean_trust_intervals_pres_ic,mean_trust_intervals_loin_ic)

data_intervals_ic <- cbind(data_intervals,mean_trust_intervals_ic)

#Les moyenne près/loin pour les lignes sur le graph
moy_trust_pres <- mean(df_40_pres$ft_values)
moy_trust_loin <- mean(df_40_loin$ft_values)

```

```{r}
theme_set(theme_minimal(base_family = "Arial"))

ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  scale_color_manual(values = c("blue", "red"), 
                     name = "Legend",
                     labels = c("Close to the capital","Far to the capital")) + 
  labs(x = "Distance from the Border (in km)",
       y = "Political Trust") +
  scale_x_continuous(labels = function(x) x / 1000) +

  theme_minimal() +

  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +

    geom_point(aes(color = mean_dist_border_intervals > 0), size=3, show.legend = FALSE) +

  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
              method = "lm", formula = y ~ poly(x, 2), color = "darkblue", size = 1, se = TRUE,
    level = 0.90, show.legend = FALSE) +

  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
              method = "lm", formula = y ~ poly(x, 2), color = "darkred", size = 1, se = TRUE,
    level = 0.90,
show.legend = FALSE) +

  geom_segment(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)), 
                   xend = 0, 
                   y = moy_trust_pres, 
                   yend = moy_trust_pres, 
                   linetype = "mean_near"),
               color = "darkblue", size = 1.5) +

  geom_segment(aes(x = 0, 
                   xend = max(abs(data_intervals$mean_dist_border_intervals)), 
                   y = moy_trust_loin, 
                   yend = moy_trust_loin, 
                   linetype = "mean_far"),
               color = "darkred", size = 1.5) +

scale_linetype_manual(name = NULL, 
                        values = c("mean_near" = "solid", 
                                   "mean_far" = "solid"),
                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), max(abs(data_intervals$mean_dist_border_intervals))))+

ggtext::geom_richtext(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Close to the Capital"),
                        vjust = 2, hjust = 0.6, size = 5, fill = "white", color = "black", fontface = "bold", 
                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) + 
  ggtext::geom_richtext(aes(x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Far from the Capital"),
                        vjust = 2, hjust = 0.4, size = 5, fill = "white", color = "black", fontface = "bold", 
                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) +

  theme(plot.title = element_text(size = 20, hjust = 0.5),  
        axis.title = element_text(size = 15), 
        legend.text = element_text(size = 12),
        legend.position = c(0.85, 0.2), # Position de la légende
        legend.background = element_rect(fill = alpha('white', 1)))

ggsave("plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)

```

```{r}
# Set the base theme
theme_set(theme_minimal(base_family = "Arial"))

# Create the plot
ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
  # Add color scale
  scale_color_manual(
    values = c("blue", "red"), 
    name = "Legend",
    labels = c("Close to the capital", "Far to the capital")
  ) +

  # Add labels and scales
  labs(
    x = "Distance from the Border (in km)",
    y = "Political trust"
  ) +
  scale_x_continuous(labels = function(x) x / 1000) +
  theme_minimal() +

  # Add vertical line at x=0
  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +

  # Add points
  geom_point(
    aes(color = mean_dist_border_intervals > 0), 
    size = 3, 
    show.legend = FALSE
  ) +

  # Add smooth lines for both sides
  geom_smooth(
    data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
    method = "lm", 
    formula = y ~ poly(x, 2), 
    color = "darkblue", 
    size = 1,
    show.legend = FALSE
  ) +
  geom_smooth(
    data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
    method = "lm", 
    formula = y ~ poly(x, 2), 
    color = "darkred", 
    size = 1,
    se = TRUE,
    level = 0.90,
    show.legend = FALSE
  ) +

  # Add mean lines
  geom_segment(
    aes(
      x = -max(abs(data_intervals$mean_dist_border_intervals)), 
      xend = 0, 
      y = moy_trust_pres, 
      yend = moy_trust_pres, 
      linetype = "mean_near"
    ),
    color = "darkblue", 
    size = 1.5
  ) + 
  geom_segment(
    aes(
      x = 0, 
      xend = max(abs(data_intervals$mean_dist_border_intervals)), 
      y = moy_trust_loin, 
      yend = moy_trust_loin, 
      linetype = "mean_far"
    ),
    color = "darkred", 
    size = 1.5
  ) +

  # Add line type scale
  scale_linetype_manual(
    name = NULL, 
    values = c("mean_near" = "solid", "mean_far" = "solid"),
    labels = c(expression(bar(y)[far]), expression(bar(y)[close]))
  ) +

  # Set coordinate limits
  coord_cartesian(
    xlim = c(
      -max(abs(data_intervals$mean_dist_border_intervals)), 
      max(abs(data_intervals$mean_dist_border_intervals))
    )
  ) +

  # Add text labels
  ggtext::geom_richtext(
    aes(
      x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
      y = Inf, 
      label = "Close to the Capital"
    ),
    vjust = 2, 
    hjust = 0.6, 
    size = 5, 
    fill = "white", 
    color = "black", 
    fontface = "bold", 
    label.color = "black", 
    box.padding = unit(0.5, "lines"), 
    label.size = 1
  ) + 
  ggtext::geom_richtext(
    aes(
      x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
      y = Inf, 
      label = "Far from the Capital"
    ),
    vjust = 2, 
    hjust = 0.4, 
    size = 5, 
    fill = "white", 
    color = "black", 
    fontface = "bold", 
    label.color = "black", 
    box.padding = unit(0.5, "lines"), 
    label.size = 1
  ) +

  # Theme customization
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title = element_text(size = 15),
    legend.text = element_text(size = 12),
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(fill = alpha('white', 1))
  )
```

```{r}
# Check sample sizes
n_far <- nrow(df_40_loin)
n_close <- nrow(df_40_pres)
cat("Sample sizes:\nFar from capital:", n_far, "\nClose to capital:", n_close, "\n")

# Check variance in trust values
var_far <- var(df_40_loin$ft_values)
var_close <- var(df_40_pres$ft_values)
cat("\nVariance in trust values:\nFar from capital:", round(var_far, 4), 
    "\nClose to capital:", round(var_close, 4))

# Check mean number of observations per interval
mean_obs_per_interval_far <- mean(table(intervals_dist_border_loin))
mean_obs_per_interval_close <- mean(table(intervals_dist_border_pres))
cat("\n\nMean observations per interval:\nFar from capital:", 
    round(mean_obs_per_interval_far, 2),
    "\nClose to capital:", round(mean_obs_per_interval_close, 2))
```

### 2025-02-24 script/r/draft.Rmd
keep essential scripts

```{r}
library(ggplot2)
library(dplyr)
library(maps)

# Mapping of ISO codes to country names
iso_to_country <- data.frame(
  iso = c("AGO", "BDI", "BEN", "BFA", "BWA", "CIV", "CMR", "CPV", "DZA", "EGY", 
          "ETH", "GAB", "GHA", "GIN", "GMB", "KEN", "LBR", "LSO", "MAR", "MDG", 
          "MLI", "MOZ", "MUS", "MWI", "NAM", "NER", "NGA", "SDN", "SEN", "SLE", 
          "STP", "SWZ", "TGO", "TUN", "TZA", "UGA", "ZAF", "ZMB", "ZWE"),
  country = c("Angola", "Burundi", "Benin", "Burkina Faso", "Botswana", "Ivory Coast", 
              "Cameroon", "Cape Verde", "Algeria", "Egypt", "Ethiopia", "Gabon", 
              "Ghana", "Guinea", "Gambia", "Kenya", "Liberia", "Lesotho", "Morocco", 
              "Madagascar", "Mali", "Mozambique", "Mauritius", "Malawi", "Namibia", 
              "Niger", "Nigeria", "Sudan", "Senegal", "Sierra Leone", "Sao Tome and Principe", 
              "Eswatini", "Togo", "Tunisia", "Tanzania", "Uganda", "South Africa", 
              "Zambia", "Zimbabwe")
)

# Count observations for each country based on ISO codes
country_counts <- data_final_adm %>%
  group_by(iso) %>%
  summarize(observation_count = n())

# Filter countries with at least 1000 observations and match with ISO codes
highlight_countries <- country_counts %>%
  filter(observation_count >= 1000, iso %in% iso_to_country$iso) %>%
  pull(iso)

cty <- iso_to_country%>%
  pull(country)

# Get the world map data
africa_map <- map_data("world")%>%
  filter(region%in%cty)

# Add a column for highlighting based on country names
africa_map <- africa_map %>%
  left_join(iso_to_country, by = c("region" = "country")) %>%
  mutate(highlight = ifelse(iso %in% highlight_countries, "Yes", "No"))

# Plot
ggplot() +
  geom_polygon(data = africa_map, aes(x = long, y = lat, group = group, fill = highlight), 
               color = "black") +
  scale_fill_manual(values = c("Yes" = "lightblue", "No" = "gray"), guide = "none") +
  labs(title = "Map of Africa: Countries with At Least 1000 Observations Highlighted") +
  theme_minimal()

```

```{r}

afro_diff <- anti_join(afro_stack, data_final)

afro_diff%>%
  distinct(iso)

afro_diff %>%
  select(latitude, longitude)%>%
  View()

data_final%>%
  select(dist_cap_log, dist_ncap_log, dist_sndncap_log)%>%
  summary()

```

```{r}
gov_index <- read_excel("data/data_raw/gov_index.xlsx")%>%
  rename(iso=ISO)
polstab_index <- read_excel("data/data_raw/polstab_index.xlsx")%>%
  rename(iso=ISO)
reg_index <- read_excel("data/data_raw/reg_index.xlsx")%>%
  rename(iso=ISO)
rule_index <- read_excel("data/data_raw/rule_index.xlsx")%>%
  rename(iso=ISO)
voiceac_index <- read_excel("data/data_raw/voiceac_index.xlsx")%>%
  rename(iso=ISO)

vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")

```

```{r}
data_final_adm%>% filter(iso=="BEN") %>% select(pop_adm1, pop_adm2, pop_adm3)%>%summary()

data_final_adm %>% select(gg_adm1_pot, round)%>%filter(round==6)%>%summary()

data_final_adm%>%filter(iso=="BEN")%>%select(iso, round, gg_adm1_pot, NAME_1)%>%View()
```

```{r}
ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")

ggg_cty<-ggg_stack%>%distinct(iso)%>%pull(iso)

all_rounds <- seq(min(ggg_stack$round, na.rm = TRUE), max(ggg_stack$round, na.rm = TRUE), by = 1)

for (country in ggg_cty) {
  ggg_stack %>%
    filter(iso == country) %>%
    group_by(round) %>%
    summarize(
      ggg_adm1_mean = mean(ggg_adm1_pot, na.rm = TRUE),
      ggg_adm2_mean = mean(ggg_adm2_pot, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    complete(round = all_rounds, fill = list(ggg_adm1_mean = NA, ggg_adm2_mean = NA)) %>%  # Fill missing rounds with NA
    ggplot(aes(x = round)) +
    geom_line(aes(y = ggg_adm1_mean), size = 1, color = "blue") +
    geom_point(aes(y = ggg_adm1_mean), size = 2, color = "blue") +
    geom_line(aes(y = ggg_adm2_mean), size = 1, color = "red") +
    geom_point(aes(y = ggg_adm2_mean), size = 2, color = "red") +
    labs(
      title = paste("Evolution of ggg_adm1_pot and ggg_adm2_pot Across Rounds for", country),
      x = "Round",
      y = "Mean Values"
    ) +
    scale_y_continuous(limits = c(0, 1)) +  # Fixed y-axis scale between 0 and 1
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 16),
      axis.title = element_text(size = 14),
      legend.position = "none"
    ) -> p
  print(p)
}
```

```{r}
setwd("~/working_paper/trust/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(sf)
```

```{r}
countries <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

data_final <- readRDS("data/data_rds/data_final.rds")

data_final_sf <- subset(data_final, select = c("id_unique","iso","latitude","longitude"))

data_final_sf <- st_as_sf(data_final_sf, coords = c("longitude", "latitude"), crs = 4326)

result <- list()

for (country in countries) {
  shapefile <- file.path("C:/Users/Redha CHABA/Documents/working_paper/trust/data/data_raw/road_shp", paste0("routes_", country, ".shp"))

  if (file.exists(shapefile)) {
    roads_sf <- st_read(shapefile)
    roads_sf <- st_transform(roads_sf, st_crs(data_final_sf))

    data_final_sf$distance_to_road <- st_distance(data_final_sf, roads_sf) %>% apply(1, min)

    country_data_result <- as.data.frame(data_final_sf)
    country_data_result <- country_data_result %>%
      select(id_unique, distance_to_road)

    result[[country]] <- country_data_result
  } else {
    warning(paste("Shapefile not found for country:", country))
  }
}

# Combine results into a single data frame
result_combined <- do.call(rbind, lapply(names(result), function(country) {
  cbind(result[[country]], country = country)
}))

final_result_road <- do.call(rbind, result)

final_df6 <- merge(final_df6,final_result_road, by="id_unique")

remove(bdd, country_data, country_data_result, country_data_sf, result, roads_sf, countries, ISO, shapefile)

```

```{r}
tiff_file <- "C:/Users/Redha CHABA/Desktop/temp/desert.tif"

desert_wgs84 <- rast(tiff_file)

print(desert_wgs84)

binary_raster <- ifel(!is.na(desert_wgs84), 1, 0)

print(binary_raster)

freq(binary_raster)

plot(binary_raster, main = "Desert Map", col = terrain.colors(100))

desert_r5_adm1 <- data.frame()

for (country in cty_adm1) {

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
  regions <- st_read(shapefile) %>% st_make_valid()

  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
  country_shp <- vect(shapefile_path)

  if (!identical(crs(binary_raster), crs(country_shp))) {
    country_shp <- project(country_shp, crs(binary_raster))
  }

  binary_raster_cropped <- crop(binary_raster, country_shp)
  binary_raster_masked <- mask(binary_raster_cropped, country_shp)

  desert_adm1 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')

  regions$desert_adm1 <- desert_adm1
  regions_df <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, desert_adm1) %>%
    mutate(round = 5)

  desert_r5_adm1 <- rbind(desert_r5_adm1, regions_df)
}

desert_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(desert_r5_adm1))

saveRDS(desert_r5_adm1, file="data/data_rds/geo_ctrl/desert_r5_adm1.rds")

desert_r5_adm2 <- data.frame()

for (country in cty_adm2) {

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
  regions <- st_read(shapefile) %>% st_make_valid()

  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
  country_shp <- vect(shapefile_path)

  if (!identical(crs(binary_raster), crs(country_shp))) {
    country_shp <- project(country_shp, crs(binary_raster))
  }

  binary_raster_cropped <- crop(binary_raster, country_shp)
  binary_raster_masked <- mask(binary_raster_cropped, country_shp)

  desert_adm2 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')

  regions$desert_adm2 <- desert_adm2
  regions_df <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, desert_adm2) %>%
    mutate(round = 5)

  desert_r5_adm2 <- rbind(desert_r5_adm2, regions_df)
}

desert_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(desert_r5_adm2))

saveRDS(desert_r5_adm2, file="data/data_rds/geo_ctrl/desert_r5_adm2.rds")
```

```{r}
library(ggplot2)

ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a)), aes(x = factor(neig_eth_a))) +
  geom_bar(fill = "steelblue") +
  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
       y = "Count",
       x=NULL) +
  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
  theme_minimal()

ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a), spl==1), aes(x = factor(neig_eth_a))) +
  geom_bar(fill = "steelblue") +
  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
       y = "Count",
       x=NULL) +
  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
  theme_minimal()
```

### 2025-02-24 script/r/rbci_data.Rmd
keep essential scripts

```{r}
setwd("~/working_paper/trust/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(stringr)
library(geosphere)
library(purrr)
library(kableExtra)
library(tidyr)
library(readxl)
library(sf)
library(exactextractr)
library(raster)
library(rgdal)
library(ncdf4)
```

#Afrobarometer & capital cities

```{r}
afro_stack <- readRDS("data/data_rds/afro_stack.rds")
glimpse(afro_stack)

cities <- read_excel("data/data_raw/cities.xlsx")

cities %<>%
  rename(iso=ISO)

data_final <- left_join(afro_stack, cities, by = "iso")%>%
  select(-cname.y)%>%
  rename(cname=cname.x)
```

#Calculate distances

```{r}
calculate_distances <- function(df) {
  df %>%
    mutate(
      dist_cap = if_all(c(longitude, latitude, caplong, caplat), ~!is.na(.)) %>% 
        {if_else(., distGeo(cbind(longitude, latitude), cbind(caplong, caplat)) / 1000, NA_real_)},

      dist_ncap = if_all(c(longitude, latitude, ncaplong, ncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(longitude, latitude), cbind(ncaplong, ncaplat)) / 1000, NA_real_)},

      dist_sndncap = if_all(c(longitude, latitude, sndncaplong, sndncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(longitude, latitude), cbind(sndncaplong, sndncaplat)) / 1000, NA_real_)},

      dist_cap_ncap = if_all(c(caplong, caplat, ncaplong, ncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(caplong, caplat), cbind(ncaplong, ncaplat)) / 1000, NA_real_)},

      dist_cap_sndncap = if_all(c(caplong, caplat, sndncaplong, sndncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(caplong, caplat), cbind(sndncaplong, sndncaplat)) / 1000, NA_real_)}
    )
}

calculate_stats <- function(df, dist_cols) {
  for(col in dist_cols) {
    log_col <- paste0(col, "_log")
    df <- df %>%
      mutate(!!log_col := log(!!sym(col)))

    df <- df %>%
      group_by(cname) %>%
      mutate(
        !!paste0(col, "_max") := max(!!sym(col), na.rm = TRUE),
        !!paste0(col, "_max95") := quantile(!!sym(col), probs = 0.95, na.rm = TRUE),
        !!paste0(col, "_mean") := mean(!!sym(col), na.rm = TRUE)
      ) %>%
      ungroup()

    df <- df %>%
      mutate(
        !!paste0(col, "_max_norm") := !!sym(col) / !!sym(paste0(col, "_max")),
        !!paste0(col, "_max_norm95") := if_else(!!sym(col) <= !!sym(paste0(col, "_max95")), 
                                               !!sym(col) / !!sym(paste0(col, "_max95")), 
                                               NA_real_),
        !!paste0(col, "_mean_norm") := !!sym(col) / !!sym(paste0(col, "_mean"))
      )

    df <- df %>%
      mutate(
        !!paste0(col, "_max_all") := max(!!sym(col), na.rm = TRUE),
        !!paste0(col, "_max95_all") := quantile(!!sym(col), probs = 0.95, na.rm = TRUE),
        !!paste0(col, "_mean_all") := mean(!!sym(col), na.rm = TRUE)
      )

    for(breaks in c(5, 10)) {
      suffix <- if(breaks == 5) "quint" else "dec"

      df <- df %>%
        group_by(iso) %>%
        mutate(
          !!paste0(col, "_", suffix) := ntile(!!sym(col), breaks),
          !!paste0(col, "_", suffix, "_log") := ntile(!!sym(log_col), breaks),
          !!paste0(col, "_", suffix, "_max_norm") := ntile(!!sym(paste0(col, "_max_norm")), breaks),
          !!paste0(col, "_", suffix, "_mean_norm") := ntile(!!sym(paste0(col, "_mean_norm")), breaks)
        ) %>%
        ungroup()

      df <- df %>%
        mutate(
          !!paste0(col, "_", suffix, "_all") := ntile(!!sym(col), breaks),
          !!paste0(col, "_", suffix, "_log_all") := ntile(!!sym(log_col), breaks),
          !!paste0(col, "_", suffix, "_max_norm_all") := ntile(!!sym(paste0(col, "_max_norm")), breaks),
          !!paste0(col, "_", suffix, "_mean_norm_all") := ntile(!!sym(paste0(col, "_mean_norm")), breaks)
        )
    }
  }
  return(df)
}

data_final %<>%
  calculate_distances() %>%
  calculate_stats(c("dist_cap", "dist_ncap", "dist_sndncap", "dist_cap_ncap", "dist_cap_sndncap"))

saveRDS(data_final, file="data/data_rds/data_final.rds")
```

#Levels

```{r}
folder_path <- "data/data_raw/gadm"

files <- list.files(folder_path, full.names = TRUE)

levels <- data.frame(file = files) %>%
  mutate(country = str_extract(file, "(?<=_)[A-Z]{3}(?=_\\d)"),
         level = as.integer(str_extract(file, "(?<=_)[0-9]+(?=\\.shp$)"))) %>%
  arrange(country, desc(level)) %>%
  distinct(country, .keep_all = TRUE)

levels %<>%
  group_by(country) %>%
  summarise(levels_nb = first(level))

print(levels, n=40)
```

#Administrative boundaries

```{r}
process_admin_level <- function(data, country_code, admin_level) {
  shp_path <- file.path(folder_path, sprintf("gadm41_%s_%d.shp", country_code, admin_level))

  panel_sf <- data %>%
    filter(!is.na(latitude) & !is.na(longitude)) %>%
    filter(iso == country_code) %>%
    select(id_unique, latitude, longitude)

  regions <- st_read(shp_path, quiet = TRUE)
  regions_valid <- st_make_valid(regions)

  panel_sf <- st_as_sf(panel_sf, 
                       coords = c("longitude", "latitude"), 
                       crs = st_crs(regions_valid))

  result <- st_join(panel_sf, regions_valid, join = st_intersects) %>%
    as.data.frame() %>%
    select(id_unique, paste0("NAME_", admin_level))

  return(result)
}

data_final_adm <- as.data.frame(data_final)

for(i in 1:nrow(levels)) {
  country <- levels$country[i]
  max_level <- levels$levels_nb[i]
  print(paste("Processing country:", country))

  for(level in 1:max_level) {
    print(paste("  Level:", level))
    result <- process_admin_level(data_final_adm, country, level)
    data_final_adm <- left_join(data_final_adm, result, by = "id_unique")
  }
}

data_final_adm %<>%
  mutate(NAME_1 = coalesce(!!!select(., matches("NAME_1")))) %>%
  mutate(NAME_2 = coalesce(!!!select(., matches("NAME_2")))) %>%
  mutate(NAME_3 = coalesce(!!!select(., matches("NAME_3")))) %>%
  mutate(NAME_4 = coalesce(!!!select(., matches("NAME_4")))) %>%
  select(-matches("NAME_\\d+\\.[xy](\\.?[xy])*$")) %>%
  select(everything(), NAME_1, NAME_2, NAME_3, NAME_4)

rm(list = setdiff(ls(), c("data_final_adm", "select", "levels")))

data_final_adm %>%
 filter(is.na(NAME_1)) %>%
 group_by(iso) %>%
 count() %>%
 arrange(desc(n))%>%
  print(n=40)

saveRDS(data_final_adm, file="data/data_rds/data_final_adm.rds")
```

#Adm setup

```{r}
cty_adm1 <- levels%>%
  filter(levels_nb>=1)%>%
  pull(country)

cty_adm2 <- levels%>%
  filter(levels_nb>=2)%>%
  pull(country)

cty_adm3 <- levels%>%
  filter(levels_nb>=3)%>%
  pull(country)

cty_adm4 <- levels%>%
  filter(levels_nb>=4)%>%
  pull(country)
```

#Raster function

```{r}
rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}
```

#3G

##Round 5 (2012)

###adm1

```{r}
ggg_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 5)

    ggg_r5_adm1 <- rbind(ggg_r5_adm1, regions)

}

ggg_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm1))

saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1_bis.rds")
```

###adm2

```{r}
ggg_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 5)

    ggg_r5_adm2 <- rbind(ggg_r5_adm2, regions)

}

ggg_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm2))

saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2_bis.rds")
```

###adm3

```{r}
ggg_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 5)

    ggg_r5_adm3 <- rbind(ggg_r5_adm3, regions)

}

ggg_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm3))

saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3_bis.rds")
```

###adm_merge

```{r}
ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1_bis.rds")
ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2_bis.rds")
ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3_bis.rds")

ggg_r5 <- merge(ggg_r5_adm1, ggg_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r5 <- merge(ggg_r5, ggg_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r5, file="data/data_rds/ggg_r5_bis.rds")
```

##Round 6 (2015)

###adm1

```{r}
ggg_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 6)

    ggg_r6_adm1 <- rbind(ggg_r6_adm1, regions)

}

ggg_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm1))

saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1_bis.rds")
```

###adm2

```{r}
ggg_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 6)

    ggg_r6_adm2 <- rbind(ggg_r6_adm2, regions)

}

ggg_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm2))

saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2_bis.rds")

```

###adm3

```{r}
ggg_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 6)

    ggg_r6_adm3 <- rbind(ggg_r6_adm3, regions)

}

ggg_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm3))

saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3_bis.rds")
```

###adm_merge

```{r}
ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1_bis.rds")
ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2_bis.rds")
ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3_bis.rds")

ggg_r6 <- merge(ggg_r6_adm1, ggg_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r6 <- merge(ggg_r6, ggg_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r6, file="data/data_rds/ggg_r6_bis.rds")
```

##Round 7 (2017)

###adm1

```{r}
ggg_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 7)

    ggg_r7_adm1 <- rbind(ggg_r7_adm1, regions)

}

ggg_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm1))

saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1_bis.rds")
```

###adm2

```{r}
ggg_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 7)

    ggg_r7_adm2 <- rbind(ggg_r7_adm2, regions)

}

ggg_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm2))

saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2_bis.rds")
```

###adm3

```{r}
ggg_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 7)

    ggg_r7_adm3 <- rbind(ggg_r7_adm3, regions)

}

ggg_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm3))

saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3_bis.rds")
```

###adm_merge

```{r}
ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1_bis.rds")
ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2_bis.rds")
ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3_bis.rds")

ggg_r7 <- merge(ggg_r7_adm1, ggg_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r7 <- merge(ggg_r7, ggg_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r7, file="data/data_rds/ggg_r7_bis.rds")
```

##Round 8 (2020)

###adm1

```{r}
ggg_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 8)

    ggg_r8_adm1 <- rbind(ggg_r8_adm1, regions)

}

ggg_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm1))

saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1_bis.rds")
```

###adm2

```{r}
ggg_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 8)

    ggg_r8_adm2 <- rbind(ggg_r8_adm2, regions)

}

ggg_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm2))

saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2_bis.rds")
```

###adm3

```{r}
ggg_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 8)

    ggg_r8_adm3 <- rbind(ggg_r8_adm3, regions)

}

ggg_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm3))

saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3_bis.rds")
```

###adm_merge

```{r}
ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1_bis.rds")
ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2_bis.rds")
ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3_bis.rds")

ggg_r8 <- merge(ggg_r8_adm1, ggg_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r8 <- merge(ggg_r8, ggg_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r8, file="data/data_rds/ggg_r8_bis.rds")
```

```{r}
ggg_r5 <- readRDS("data/data_rds/ggg_r5_bis.rds")
ggg_r6 <- readRDS("data/data_rds/ggg_r6_bis.rds")
ggg_r7 <- readRDS("data/data_rds/ggg_r7_bis.rds")
ggg_r8 <- readRDS("data/data_rds/ggg_r8_bis.rds")

ggg_rounds <- list(ggg_r5, ggg_r6, ggg_r7, ggg_r8)

ggg_stack <- bind_rows(ggg_rounds)

saveRDS(ggg_stack, file="data/data_rds/ggg_stack_bis.rds")
```

#2G

##Round 5 (2012)

###adm1

```{r}
gg_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 5)

    gg_r5_adm1 <- rbind(gg_r5_adm1, regions)

}

gg_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm1))

saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1_bis.rds")
```

###adm2

```{r}
gg_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 5)

    gg_r5_adm2 <- rbind(gg_r5_adm2, regions)

}

gg_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm2))

saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2_bis.rds")
```

###adm3

```{r}
gg_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 5)

    gg_r5_adm3 <- rbind(gg_r5_adm3, regions)
}

gg_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm3))

saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3_bis.rds")
```

###adm_merge

```{r}
gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1_bis.rds")
gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2_bis.rds")
gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3_bis.rds")

gg_r5 <- merge(gg_r5_adm1, gg_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r5 <- merge(gg_r5, gg_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r5, file="data/data_rds/gg_r5_bis.rds")
```

##Round 6 (2015)

###adm1

```{r}
gg_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 6)

    gg_r6_adm1 <- rbind(gg_r6_adm1, regions)

}

gg_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm1))

saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1_bis.rds")
```

###adm2

```{r}
gg_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 6)

    gg_r6_adm2 <- rbind(gg_r6_adm2, regions)

}

gg_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm2))

saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2_bis.rds")
```

###adm3

```{r}
gg_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 6)

    gg_r6_adm3 <- rbind(gg_r6_adm3, regions)

}

gg_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm3))

saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3_bis.rds")
```

###adm_merge

```{r}
gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1_bis.rds")
gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2_bis.rds")
gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3_bis.rds")

gg_r6 <- merge(gg_r6_adm1, gg_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r6 <- merge(gg_r6, gg_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r6, file="data/data_rds/gg_r6_bis.rds")

```

##Round 7 (2017)

###adm1

```{r}
gg_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 7)

    gg_r7_adm1 <- rbind(gg_r7_adm1, regions)
}

gg_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm1))

saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1_bis.rds")
```

###adm2

```{r}
gg_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 7)

    gg_r7_adm2 <- rbind(gg_r7_adm2, regions)

}

gg_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm2))

saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2_bis.rds")
```

###adm3

```{r}
gg_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 7)

    gg_r7_adm3 <- rbind(gg_r7_adm3, regions)
}

gg_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm3))

saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3_bis.rds")
```

###adm_merge

```{r}
gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1_bis.rds")
gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2_bis.rds")
gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3_bis.rds")

gg_r7 <- merge(gg_r7_adm1, gg_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r7 <- merge(gg_r7, gg_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r7, file="data/data_rds/gg_r7_bis.rds")
```

##Round 8 (2020)

###adm1

```{r}
gg_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1

#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 8)

    gg_r8_adm1 <- rbind(gg_r8_adm1, regions)
}

gg_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm1))

saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1_bis.rds")
```

###adm2

```{r}
gg_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2

#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 8)

    gg_r8_adm2 <- rbind(gg_r8_adm2, regions)

}

gg_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm2))

saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2_bis.rds")
```

###adm3

```{r}
gg_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled

#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3

#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 8)

    gg_r8_adm3 <- rbind(gg_r8_adm3, regions)
}

gg_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm3))

saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3_bis.rds")
```

###adm_merge

```{r}
gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1_bis.rds")
gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2_bis.rds")
gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3_bis.rds")

gg_r8 <- merge(gg_r8_adm1, gg_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r8 <- merge(gg_r8, gg_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r8, file="data/data_rds/gg_r8_bis.rds")
```

```{r}
gg_r5 <- readRDS("data/data_rds/gg_r5_bis.rds")
gg_r6 <- readRDS("data/data_rds/gg_r6_bis.rds")
gg_r7 <- readRDS("data/data_rds/gg_r7_bis.rds")
gg_r8 <- readRDS("data/data_rds/gg_r8_bis.rds")

gg_rounds <- list(gg_r5, gg_r6, gg_r7, gg_r8)

gg_stack <- bind_rows(gg_rounds)

saveRDS(gg_stack, file="data/data_rds/gg_stack_bis.rds")
```

##Merge internet

```{r}
gg_stack <- readRDS("data/data_rds/gg_stack_bis.rds")
ggg_stack <- readRDS("data/data_rds/ggg_stack_bis.rds")

int_stack_bis <- gg_stack %>%
  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

saveRDS(int_stack_bis, file="data/data_rds/int_stack_bis.rds")

int_stack_bis <- readRDS("data/data_rds/int_stack_bis.rds")

int_stack_bis%<>%
  mutate(pop_adm1= coalesce(pop_adm1.x, pop_adm1.y))%>%
  mutate(pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y))%>%
  mutate(pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y))

int_stack_bis%<>%
  select(-ends_with(".x"), -ends_with(".y"))

data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp.rds")

data_final_nlp_bis%<>%
  select(-c("gg_pop_adm1","gg_adm1","gg_adm1_pot","gg_pop_adm2","gg_adm2","gg_adm2_pot","gg_pop_adm3","gg_adm3","gg_adm3_pot","ggg_pop_adm1","ggg_adm1","ggg_adm1_pot","ggg_pop_adm2","ggg_adm2","ggg_adm2_pot","ggg_pop_adm3","ggg_adm3","ggg_adm3_pot","pop_adm1","pop_adm2","pop_adm3", "gg_region_pot", "ggg_region_pot", "cvg_region_pot", "cvg_region_pot_2"))

data_final_nlp_bis %<>%
  left_join(int_stack_bis, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

data_final_nlp_bis%<>%
mutate(gg_region_pot = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ gg_adm1_pot,
    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ gg_adm2_pot, 
    TRUE ~ NA_integer_
  ))%>%
mutate(ggg_region_pot = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ ggg_adm1_pot,
    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ ggg_adm2_pot, 
    TRUE ~ NA_integer_))%>%
  mutate(cvg_region_pot=ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))

data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp_bis.rds")

data_final_nlp_bis%<>%
mutate(pop_region = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ pop_adm1,
    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ pop_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(pop_region_log=log(pop_region+1))

data_final_nlp_bis2%<>%
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id())%>%
  ungroup()%>%
  mutate(adm1_time = case_when(
    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm1_time = as.integer(as.factor(adm1_time)))%>%
mutate(adm2_time = case_when(
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm2_time = as.integer(as.factor(adm2_time)))

  data_final_nlp_bis2%<>%
  mutate(country_round=as.numeric(paste0(round,ccode)))%>%
  mutate(region_time = case_when(
    iso %in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name2_id * 10000 + round, 
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
  mutate(region_time = as.integer(as.factor(region_time)))

saveRDS(data_final_nlp_bis, file="data/data_rds/data_final_nlp_bis.rds")
write_dta(data_final_nlp_bis, "data/data_dta/data.dta")
```

#Nightlight

##Round 5 (2012)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 5)

    night_r5_adm1 <- rbind(night_r5_adm1, regions)
}

night_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm1))

saveRDS(night_r5_adm1, file="data/data_rds/night_r5_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 5)

    night_r5_adm2 <- rbind(night_r5_adm2, regions)
}

night_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm2))

saveRDS(night_r5_adm2, file="data/data_rds/night_r5_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 5)

    night_r5_adm3 <- rbind(night_r5_adm3, regions)
}

night_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm3))

saveRDS(night_r5_adm3, file="data/data_rds/night_r5_adm3.rds")
```

###adm_merge

```{r}
night_r5_adm1 <- readRDS("data/data_rds/night_r5_adm1.rds")
night_r5_adm2 <- readRDS("data/data_rds/night_r5_adm2.rds")
night_r5_adm3 <- readRDS("data/data_rds/night_r5_adm3.rds")

night_r5 <- merge(night_r5_adm1, night_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r5 <- merge(night_r5, night_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r5, file="data/data_rds/night_r5.rds")
```

##Round 6 (2015)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 6)

    night_r6_adm1 <- rbind(night_r6_adm1, regions)
}

night_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm1))

saveRDS(night_r6_adm1, file="data/data_rds/night_r6_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 6)

    night_r6_adm2 <- rbind(night_r6_adm2, regions)
}

night_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm2))

saveRDS(night_r6_adm2, file="data/data_rds/night_r6_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 6)

    night_r6_adm3 <- rbind(night_r6_adm3, regions)
}

night_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm3))

saveRDS(night_r6_adm3, file="data/data_rds/night_r6_adm3.rds")
```

###adm_merge

```{r}
night_r6_adm1 <- readRDS("data/data_rds/night_r6_adm1.rds")
night_r6_adm2 <- readRDS("data/data_rds/night_r6_adm2.rds")
night_r6_adm3 <- readRDS("data/data_rds/night_r6_adm3.rds")

night_r6 <- merge(night_r6_adm1, night_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r6 <- merge(night_r6, night_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r6, file="data/data_rds/night_r6.rds")
```

##Round 7 (2017)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 7)

    night_r7_adm1 <- rbind(night_r7_adm1, regions)
}

night_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm1))

saveRDS(night_r7_adm1, file="data/data_rds/night_r7_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 7)

    night_r7_adm2 <- rbind(night_r7_adm2, regions)
}

night_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm2))

saveRDS(night_r7_adm2, file="data/data_rds/night_r7_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 7)

    night_r7_adm3 <- rbind(night_r7_adm3, regions)
}

night_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm3))

saveRDS(night_r7_adm3, file="data/data_rds/night_r7_adm3.rds")
```

###adm_merge

```{r}
night_r7_adm1 <- readRDS("data/data_rds/night_r7_adm1.rds")
night_r7_adm2 <- readRDS("data/data_rds/night_r7_adm2.rds")
night_r7_adm3 <- readRDS("data/data_rds/night_r7_adm3.rds")

night_r7 <- merge(night_r7_adm1, night_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r7 <- merge(night_r7, night_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r7, file="data/data_rds/night_r7.rds")
```
##Round 8 (2020)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm1 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 8)

    night_r8_adm1 <- rbind(night_r8_adm1, regions)
}

night_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm1))

saveRDS(night_r8_adm1, file="data/data_rds/night_r8_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm2 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 8)

    night_r8_adm2 <- rbind(night_r8_adm2, regions)
}

night_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm2))

saveRDS(night_r8_adm2, file="data/data_rds/night_r8_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm3 <- data.frame()
success_countries <- c()
failed_countries <- c()

for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 8)

    night_r8_adm3 <- rbind(night_r8_adm3, regions)
}

night_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm3))

saveRDS(night_r8_adm3, file="data/data_rds/night_r8_adm3.rds")
```

###adm_merge

```{r}
night_r8_adm1 <- readRDS("data/data_rds/night_r8_adm1.rds")
night_r8_adm2 <- readRDS("data/data_rds/night_r8_adm2.rds")
night_r8_adm3 <- readRDS("data/data_rds/night_r8_adm3.rds")

night_r8 <- merge(night_r8_adm1, night_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r8 <- merge(night_r8, night_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r8, file="data/data_rds/night_r8.rds")
```

##Nightlight stack

```{r}
night_r5 <- readRDS("data/data_rds/night_r5.rds")
night_r6 <- readRDS("data/data_rds/night_r6.rds")
night_r7 <- readRDS("data/data_rds/night_r7.rds")
night_r8 <- readRDS("data/data_rds/night_r8.rds")

night_rounds <- list(night_r5, night_r6, night_r7, night_r8)

night_stack <- bind_rows(night_rounds)

saveRDS(night_stack, file="data/data_rds/night_stack.rds")
```

##Merge nightlight

```{r}
data_final_int <- readRDS("data/data_rds/data_final_nlp_bis.rds")
night_stack <- readRDS("data/data_rds/night_stack.rds")

data_final_int%<>%
  select(-c("night_adm1", "night_adm2", "night_adm3"))

data_final_int_n<- data_final_int %>%
  left_join(night_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

saveRDS(data_final_int_n, file="data/data_rds/data_final_int_n.rds")
```

#Lightning strikes

```{r}
ncpath <- "data/data_raw/"
ncname <- "VHRFC"  
ncfname <- paste(ncpath, ncname, ".nc", sep="")
ncin <- nc_open(ncfname)
print(ncin)

FRD <- ncvar_get(ncin, "VHRFC_LIS_FRD")
dim(FRD)

lon <- ncvar_get(ncin, "Longitude")
lat <- ncvar_get(ncin, "Latitude")

r_FRD <- raster(t(FRD), 
                xmn=min(lon), xmx=max(lon), 
                ymn=min(lat), ymx=max(lat),
                crs=CRS("+proj=longlat +datum=WGS84"))

r_FRD <- flip(r_FRD, direction = "y")

nc_close(ncin)
```

##adm1

```{r}
lis_r_adm1 <- data.frame()

for (country in cty_adm1) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled

    lis_pop_adm1 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm1 <- lis_pop_adm1

    lis_adm1 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm1 <- lis_adm1

    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1

    regions$lis_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, lis_pop_adm1 / pop_adm1)

regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, lis_adm1, lis_pop_adm1, lis_adm1_pot)

lis_r_adm1 <- rbind(lis_r_adm1, regions)
}

lis_r_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm1))

saveRDS(lis_r_adm1, file="data/data_rds/lis_r_adm1.rds")
```

##adm2

```{r}
lis_r_adm2 <- data.frame()

for (country in cty_adm2) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
        pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled

    lis_pop_adm2 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm2 <- lis_pop_adm2

    lis_adm2 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm2 <- lis_adm2

    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2

    regions$lis_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, lis_pop_adm2 / pop_adm2)

regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, NAME_2, lis_adm2, lis_pop_adm2, lis_adm2_pot)

lis_r_adm2 <- rbind(lis_r_adm2, regions)
}

lis_r_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm2))

saveRDS(lis_r_adm2, file="data/data_rds/lis_r_adm2.rds")
```

##adm3

```{r}
lis_r_adm3 <- data.frame()

for (country in cty_adm3) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
        pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled

    lis_pop_adm3 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm3 <- lis_pop_adm3

    lis_adm3 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm3 <- lis_adm3

    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3

    regions$lis_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, lis_pop_adm3 / pop_adm3)

regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, NAME_2, NAME_3, lis_adm3, lis_pop_adm3, lis_adm3_pot)

lis_r_adm3 <- rbind(lis_r_adm3, regions)
}

lis_r_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm3))

saveRDS(lis_r_adm3, file="data/data_rds/lis_r_adm3.rds")
```

##Lightning stack

```{r}
lis_r_adm1 <- readRDS("data/data_rds/lis_r_adm1.rds")
lis_r_adm2 <- readRDS("data/data_rds/lis_r_adm2.rds")
lis_r_adm3 <- readRDS("data/data_rds/lis_r_adm3.rds")

lis_r <- merge(lis_r_adm1, lis_r_adm2, by = c("iso", "NAME_1"), all = TRUE)
lis_r <- merge(lis_r, lis_r_adm3, by = c("iso", "NAME_1", "NAME_2"), all = TRUE)

saveRDS(lis_r, file="data/data_rds/lis_r.rds")
```

##Merge lightning

```{r}
data_final_int_n <- readRDS("data/data_rds/data_final_int_n.rds")

data_final_int_n%<>%
  select(-c("lis_adm1", "lis_pop_adm1", "lis_adm1_pot","lis_adm2","lis_pop_adm2","lis_adm2_pot", "lis_adm3", "lis_pop_adm3", "lis_adm3_pot", "tv"))

lis_r <- readRDS("data/data_rds/lis_r.rds")

rounds <- data.frame(round = rep(5:8, each = nrow(lis_r)))

expanded_data <- lis_r[rep(1:nrow(lis_r), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, NAME_3, round, .keep_all = TRUE)

data_final_int_n_l <- left_join(data_final_int_n, expanded_data, by=c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

data_final_int_n_l%<>%
  mutate(tv=case_when(
    round==5 ~ 1,
    round==6 ~ 2,
    round==7 ~ 3,
    round==8 ~ 4,
  ))

glimpse(data_final_int_n_l)

saveRDS(data_final_int_n_l, file="data/data_rds/data_final_int_n_l.rds")
```

#Region area

```{r}
data_final_nlp_bis <- readRDS("data/data_rds/data_final_int_n_l.rds")

countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

data_keep <- subset(data_final_nlp_bis, select = c("id_unique", "latitude", "longitude")) %>%
  filter(!is.na(latitude) & !is.na(longitude))

data_keep_sf <- st_as_sf(data_keep, coords = c("longitude", "latitude"), crs = 4326)

remove(data_keep)

all_regions_0 <- list()

for (country in countries) {
  shapefile_0 <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    if (file.exists(shapefile_0)) {
      regions_0 <- st_read(shapefile_0, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_0))) {
        regions_0 <- st_set_crs(regions_0, 4326)
      }
      regions_0$iso <- country
      regions_0$area_0_km2 <- as.numeric(st_area(regions_0)) / 10^6
      all_regions_0[[country]] <- regions_0
}}

df_regions_0 <- do.call(rbind, all_regions_0) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_0 <- st_join(data_keep_sf, df_regions_0 %>% select(iso, area_0_km2), join = st_intersects)

data_keep_sf_0 %<>%
  filter(!is.na(iso) | !is.na(area_0_km2))

#adm1

all_regions_1 <- list()

for (country in countries) {
  shapefile_1 <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    if (file.exists(shapefile_1)) {
      regions_1 <- st_read(shapefile_1, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_1))) {
        regions_1 <- st_set_crs(regions_1, 4326)
      }
      regions_1$iso <- country
      regions_1$area_1_km2 <- as.numeric(st_area(regions_1)) / 10^6
      all_regions_1[[country]] <- regions_1
    }}

df_regions_1 <- do.call(rbind, all_regions_1) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_1 <- st_join(data_keep_sf_0, df_regions_1 %>% select(iso, NAME_1, area_1_km2), join = st_intersects)

data_keep_sf_1 %<>%
rename(iso = iso.x) %>%
  select(-iso.y)

#adm2

all_regions_2 <- list()

for (country in countries) {
  shapefile_2 <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    if (file.exists(shapefile_2)) {
      regions_2 <- st_read(shapefile_2, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_2))) {
        regions_2 <- st_set_crs(regions_2, 4326)
      }
      regions_2$iso <- country
      regions_2$area_2_km2 <- as.numeric(st_area(regions_2)) / 10^6
      all_regions_2[[country]] <- regions_2
    }}

df_regions_2 <- do.call(rbind, all_regions_2) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_2 <- st_join(data_keep_sf_1, df_regions_2 %>% select(iso, NAME_1, NAME_2, area_2_km2), join = st_intersects)

data_keep_sf_2 %<>%
rename(iso = iso.x,
       NAME_1=NAME_1.x) %>%
  select(-c("iso.y", "NAME_1.y"))

#adm3

countries_adm3 <-  countries[countries %in%cty_adm3]

all_regions_3 <- list()

for (country in countries_adm3) {
  shapefile_3 <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    if (file.exists(shapefile_3)) {
      regions_3 <- st_read(shapefile_3, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_3))) {
        regions_3 <- st_set_crs(regions_3, 4326)
      }
      regions_3$iso <- country
      regions_3$area_3_km2 <- as.numeric(st_area(regions_3)) / 10^6
      all_regions_3[[country]] <- regions_3
    }}

df_regions_3 <- do.call(rbind, all_regions_3) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_3 <- st_join(data_keep_sf_2, df_regions_3 %>% select(iso, NAME_1, NAME_2, NAME_3, area_3_km2), join = st_intersects)

data_keep_sf_3 %<>%
rename(iso = iso.x,
       NAME_1=NAME_1.x,
       NAME_2 = NAME_2.x) %>%
  select(-c("iso.y", "NAME_1.y", "NAME_2.y"))

data_area_region <- as.data.frame(data_keep_sf_3)%>%select(-c("geometry", "id_unique"))

saveRDS(data_area_region, file="data/data_rds/data_area_region.rds")

data_final_nlp_bis2%<>%
  select(-c( "area_0_km2", "area_1_km2", "area_2_km2", "area_3_km2"))

data_final_nlp_bis2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
  distinct(id_unique, .keep_all = TRUE)

saveRDS(data_final_nlp_bis2, file="data/data_rds/data_final_nlp_bis2.rds")
```

#Various variable creation

```{r}
data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")

#remove too long variables for stata
data_final_nlp_bis2%<>%
  select(-c(dist_cap_ncap_quint_mean_norm_all, dist_cap_sndncap_quint_max_norm_all, dist_cap_sndncap_quint_mean_norm_all, dist_cap_sndncap_dec_max_norm_all, dist_cap_sndncap_dec_mean_norm_all))

#region variables
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

data_final_nlp_bis2%<>%
  select(-c("lis_region", "pop_region", "night_region", "lis_region_pot", "lis_region_log", "pop_region_log", "night_region_log"))

data_final_nlp_bis2 %<>%
mutate(lis_region = case_when(
    iso %in% countries_adm1 ~ lis_adm1,
    iso %in% countries_adm2 ~ lis_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(pop_region = case_when(
    iso %in% countries_adm1 ~ pop_adm1,
    iso %in% countries_adm2 ~ pop_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(night_region = case_when(
    iso %in% countries_adm1 ~ night_adm1,
    iso %in% countries_adm2 ~ night_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(lis_region_log=log(lis_region+1))%>%
  mutate(pop_region_log=log(pop_region+1))%>%
  mutate(night_region_log=log(night_region+1))

data_final_nlp_bis2%<>%
  mutate(lis_region_pot = case_when(
    iso %in% countries_adm1 ~ lis_adm1_pot,
    iso %in% countries_adm2 ~ lis_adm2_pot, 
    TRUE ~ NA_integer_
  ))

##add president birthplace (region)
data_president <- read_xlsx("data/data_raw/data_president.xlsx")
data_president%<>%
  filter(!is.na(date_of_election))

unique_combinations <- data_president %>%
  distinct(iso, round)

#countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

results <- data.frame()

for (i in 1:nrow(unique_combinations)) {

  iso <- unique_combinations$iso[i]
  round <- unique_combinations$round[i]

  data_filtered <- data_president %>%
    filter(iso == !!iso, round == !!round)

  if (nrow(data_filtered) == 0) {
    warning(paste("Pas de données pour le pays", iso, "et la période", round))
    next
  }

  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", iso, "_1.shp")

  if (file.exists(shapefile_path)) {
    regions_sf <- st_read(shapefile_path)
    regions_sf <- st_make_valid(regions_sf)

    presidents_sf <- st_as_sf(data_filtered, coords = c("long_nais", "lat_nais"), crs = 4326)

    presidents_with_region <- st_join(presidents_sf, regions_sf, join = st_within)

    presidents_with_region$iso <- iso
    presidents_with_region$round <- round

    results <- rbind(results, presidents_with_region)

  } else {
    warning(paste("Shapefile pour le pays", iso, "n'existe pas dans le chemin spécifié."))
  }
}

results%<>%
  select(iso, round, NAME_1)

results%<>%
  select(-geometry)

results%<>%
  rename(NAME_1_pres=NAME_1)

data_final_nlp_bis2%<>%
  select(-c("pres_adm1", "pres_adm2"))

data_final_nlp_bis2 %<>% left_join(results, by=c("iso", "round"))

data_final_nlp_bis2 %<>%
  mutate(pres_adm1=ifelse(NAME_1_pres==NAME_1, 1, 0))

data_final_nlp_bis2%<>%
  select(-geometry)

#individual variables
data_final_nlp_bis2 %<>%
mutate(age = na_if(age, -1) %>% na_if(998) %>% na_if(999))%>%
mutate(age_2=age*age)%>%
mutate(educ_sec=case_when(
    educ %in% c(5, 6,7,8,9) ~ 1,
    educ %in% c(0,1,2, 3, 4) ~0,
    TRUE ~ NA_integer_))%>%
mutate(conditions_country = if_else(conditions_country %in% c(1, 2, 3, 4, 5), conditions_country, NA_integer_))%>%
mutate(bin_conditions_country=ifelse(conditions_country>=3, 1, 0))%>%
mutate(conditions_eco = if_else(conditions_eco %in% c(1, 2, 3, 4, 5), conditions_eco, NA_integer_))%>%
mutate(bin_conditions_eco = if_else(is.na(conditions_eco), NA_integer_, if_else(conditions_eco >= 3, 1L, 0L)))%>%
mutate(emp = if_else(emp %in% c(0, 1, 2, 3), emp, NA_integer_))%>%
mutate(bin_emp = case_when(emp %in% c(0, 1) ~ 0,
                           emp %in% c(2, 3) ~ 1,
                           TRUE ~ NA_integer_))%>%
mutate(tele_news = if_else(tele_news %in% c(0, 1, 2, 3, 4), tele_news, NA_integer_))%>%
mutate(paper_news = if_else(paper_news %in% c(0, 1, 2, 3, 4), paper_news, NA_integer_))%>%
mutate(radio_news = if_else(radio_news %in% c(0, 1, 2, 3, 4), radio_news, NA_integer_))%>%
mutate(internet_news = if_else(internet_news %in% c(0, 1, 2, 3, 4), internet_news, NA_integer_))%>%
mutate(sm_news = if_else(sm_news %in% c(0, 1, 2, 3, 4), sm_news, NA_integer_))%>%
mutate(internet_use = if_else(internet_use %in% c(0, 1, 2, 3, 4), internet_use, NA_integer_))%>%
mutate(feelnat = if_else(feelnat %in% c(1, 2, 3, 4, 5), feelnat, NA_integer_))%>%
mutate(trust_parl_a = if_else(trust_parl %in% c(0, 1, 2, 3), trust_parl, NA_integer_))%>%
mutate(trust_pres_a = if_else(trust_pres %in% c(0, 1, 2, 3), trust_pres, NA_integer_))%>%
mutate(trust_elec_a = if_else(trust_elec %in% c(0, 1, 2, 3), trust_elec, NA_integer_))%>%
mutate(unfair_eth = if_else(conditions_eco %in% c(0, 1, 2, 3), unfair_eth, NA_integer_))%>%
mutate(bin_unfair_eth = case_when(unfair_eth %in% c(0, 1) ~ 0,
                           unfair_eth %in% c(2, 3) ~ 1,
                           TRUE ~ NA_integer_))%>%
mutate(unfair_eth = as.numeric(unfair_eth)) %>%
 mutate(bin_unfair_eth = case_when(
    unfair_eth == 0 ~ 0,  # Never -> 0
    unfair_eth == 1 ~ 0,  # Sometimes -> 0
    unfair_eth == 2 ~ 1,  # Often -> 1
    unfair_eth == 3 ~ 1,  # Always -> 1
    TRUE ~ NA_real_       # All other cases -> NA
  )) %>%
  mutate(disc_pol_a=if_else(disc_pol %in% c(0, 1, 2), disc_pol, NA_integer_))

data_final_nlp_bis2 %<>%
 group_by(id_unique)%>%
  mutate(pol_trust = ifelse(all(is.na(c(trust_pres_a, trust_parl_a))), NA, weighted.mean(c(trust_pres_a, trust_parl_a), na.rm = TRUE)))%>%
  ungroup()

#cluster variables
data_final_nlp_bis2 %<>%
mutate(country_round=as.numeric(paste0(round,ccode)))

cty_sample <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

data_final_nlp_bis2%<>%
  mutate(spl=if_else(iso%in%cty_sample, 1, 0))
```

#Country variables

```{r}
##correction: add colonial origin
data_color <- read_xlsx("data/data_raw/color.xlsx")

data_final_nlp_bis2 %<>% left_join(data_color, by="iso")
rm(data_color)

juriglobe <- read_excel("data/data_raw/FR_index.xlsx")

juriglobe %<>%
  rename(gov_type = "Forme\r\nde gouvernement") %>%
  mutate(
    gov_type = case_when(
      gov_type == "Présidentiel" ~ "presidential",
      gov_type == "Parlementaire" ~ "parliamentarian",
      gov_type == "Semi-présidentiel" ~ "semi_presidential",
      gov_type == "Monarchique" ~ "monarchical",
      TRUE ~ NA_character_
    ),
    presidential = as.numeric(gov_type == "presidential"),
    parlementarian = as.numeric(gov_type == "parliamentarian"),
    semi_presidential = as.numeric(gov_type == "semi_presidential"),
    monarchical = as.numeric(gov_type == "monarchical")
  ) %>%
  select(iso, presidential, parlementarian, semi_presidential, monarchical, gov_type)

data_final_nlp_bis2 %<>% left_join(juriglobe, by="iso")

rm(juriglobe)

data_final_nlp_bis2%<>%
  select(-geometry)

gdppc <- read_excel("data/data_raw/gdppc.xls")%>%
  rename(iso=ISO)%>%
  select(iso, gdpcap_2012, gdpcap_2015, gdpcap_2017, gdpcap_2020)
pop <- read_excel("data/data_raw/pop.xls")%>%
  rename(iso=ISO)%>%
  select(iso, pop_2012, pop_2015, pop_2017, pop_2020)
area <- read_excel("data/data_raw/area.xls")%>%
  select(iso, area_2012, area_2015, area_2017, area_2020)
cor_index <- read_excel("data/data_raw/cor_index.xlsx")%>%
  rename(iso=ISO)%>%
  select(iso, cor_2012, cor_2015, cor_2017, cor_2020)

data_cty <- list(
  cor_index,
  gdppc,
  pop,
  area
)

var_cty <- reduce(data_cty, inner_join, by = "iso")

var_cty %<>%
  mutate(across(-iso, as.numeric))

glimpse(var_cty)

data_final_nlp_bis2%<>%
  select(-c("gdppc", "gdppc_log", "cor_index", "area", "area_log", "pop"))

data_final_nlp_bis2 %<>% left_join(var_cty, by = "iso")

data_final_nlp_bis2 %<>%
mutate(cor_index = case_when(
    round == 5 ~ cor_2012,
    round == 6 ~ cor_2015,
    round == 7 ~ cor_2017,
    round == 8 ~ cor_2020,
    TRUE ~ NA
  ))

data_final_nlp_bis2 %<>%
mutate(gdppc = case_when(
    round == 5 ~ gdpcap_2012,
    round == 6 ~ gdpcap_2015,
    round == 7 ~ gdpcap_2017,
    round == 8 ~ gdpcap_2020,
    TRUE ~ NA
  ))

data_final_nlp_bis2 %<>%
mutate(pop = case_when(
    round == 5 ~ pop_2012,
    round == 6 ~ pop_2015,
    round == 7 ~ pop_2017,
    round == 8 ~ pop_2020,
    TRUE ~ NA
  ))

data_final_nlp_bis2 %<>%
mutate(area = case_when(
    round == 5 ~ area_2012,
    round == 6 ~ area_2015,
    round == 7 ~ area_2017,
    round == 8 ~ area_2020,
    TRUE ~ NA
  ))

data_final_nlp_bis2%<>%
  select(-c(cor_2012, cor_2015, cor_2017, cor_2020, gdpcap_2012, gdpcap_2015, gdpcap_2017, gdpcap_2020, pop_2012, pop_2015, pop_2017, pop_2020, area_2012, area_2015, area_2017, area_2020))

data_final_nlp_bis2%<>%
  mutate(gdppc_log=log(gdppc+1))%>%
  mutate(area_log=log(area+1))

qog <- read.csv("data/data_raw/qog_std_ts_jan24.csv")

countries <- unique(data_final_nlp_bis2$iso)

qog%<>%
  filter(ccodealp %in% countries)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, fhp_mcpp5, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(iso=ccodealp, fh_med_index=fhp_mcpp5, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)

qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2012 ~ 5,
                   round==2015 ~ 6,
                   round==2017 ~ 7,
                   round==2020 ~ 8))

data_final_nlp_bis2%<>%
  select(-c( "med_self_censor", "citiz_self_censor", "fh_med_index", "vdem_med_corrupt", "vdem_polyarchy"))

data_final_nlp_bis2 %<>% left_join(qog, by=c("iso", "round"))

data_final_nlp_bis2%<>%
  mutate(color_num = as.numeric(factor(color)))

data_final_nlp_bis2%<>%
  mutate(gov_num = as.numeric(factor(gov_type)))
```

#Individual variables

```{r}
#Correction sex
afro_stack <- readRDS("data/data_rds/afro_stack.rds")

data_final_nlp_bis2%<>%select(-sex)

afro_stack %<>%
  mutate(sex = as.numeric(sex)) %>%
  mutate(sex = case_when(
    sex == 1 ~ 0,  # Male -> 0
    sex == 2 ~ 1,  # Female -> 1
    TRUE ~ NA_integer_
  ))%>%
  select(id_unique, sex)

data_final_nlp_bis2%<>%
  left_join(afro_stack, by="id_unique")

#Correction rural

data_final_nlp_bis2%<>%select(-c("rural", "bin_rural"))

afro_stack <- readRDS("data/data_rds/afro_stack.rds")

afro_stack %<>%
  mutate(bin_rural = case_when(
    round == 5 & rural == 1 ~ 0,  # Urban in round 5 -> 0
    round == 5 & rural == 2 ~ 1,  # Rural in round 5 -> 1
    round == 6 & rural == 1 ~ 0,  # Urban in round 6 -> 0
    round == 6 & rural == 2 ~ 1,  # Rural in round 6 -> 1
    round == 7 & rural %in% c(1, 3, 460) ~ 0,  # Urban, Semi-Urban, Peri-Urban
    round== 7 & rural == 2 ~ 1, # Rural in round 7 -> 1
    round == 8 & rural %in% c(1, 3) ~ 0,  # Urban, Semi-Urban, Peri-Urban in round 8 -> 0
    round == 8 & rural == 2 ~ 1,  # Rural in round 8 -> 1
    TRUE ~ NA_integer_  # NA for all other cases
  ))

afro_stack%<>%
  select(id_unique, rural, bin_rural)

data_final_nlp_bis2%<>%
  left_join(afro_stack, by="id_unique")
```

```{r}
#vote_oppo

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

data_final_nlp_bis2%<>%
  select(-c("vote_party", "vote_oppo"))

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(vote_party = case_when(
    round == 7 ~ vote_party.y,
    round == 8 ~ vote_party.x))

data_final_nlp_bis2%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w7)

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(vote_party = case_when(
    round == 6 ~ vote_party.y,
    round %in% c(7,8) ~ vote_party.x))

data_final_nlp_bis2%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w6)

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(vote_party = case_when(
    round == 5 ~ vote_party.y,
    round %in% c(6,7,8) ~ vote_party.x))

data_final_nlp_bis2%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w5)

data_final_nlp_bis2%<>%
mutate(vote_party = case_when(
  vote_party %in% c(9995, 9997, 9998, 9999, -1) ~ NA_real_,
  TRUE ~ vote_party
))

data_final_nlp_bis2%<>%
  select(-c("year_of_election", "date_of_election", "winner"))

data_elections_R <- na.omit(read_excel("data/data_raw/data_elections_R.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "date", "numeric")))

data_final_nlp_bis2 %<>% left_join(data_elections_R, by=c("iso","round"))

data_final_nlp_bis2$vote_party <- as.numeric(zap_labels(data_final_nlp_bis2$vote_party))

data_final_nlp_bis2$vote_oppo <- ifelse(data_final_nlp_bis2$winner!=data_final_nlp_bis2$vote_party, 1,0)
```

```{r}
#growth_country

data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q6A)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q6A)%>%
  rename(growth_country=Q6A)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q6)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q6)%>%
  rename(growth_country=Q6)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(growth_country = case_when(
    round == 7 ~ growth_country.y,
    round == 8 ~ growth_country.x))

data_final_nlp_bis2%<>%
  select(-c(growth_country.y, growth_country.x))

rm(afro_w7)

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q6)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q6)%>%
  rename(growth_country=q6)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(growth_country = case_when(
    round == 6 ~ growth_country.y,
    round %in% c(7,8) ~ growth_country.x))

data_final_nlp_bis2%<>%
  select(-c(growth_country.y, growth_country.x))

rm(afro_w6)

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q5a)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q5a)%>%
  rename(growth_country=q5a)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(growth_country = case_when(
    round == 5 ~ growth_country.y,
    round %in% c(6,7,8) ~ growth_country.x))

data_final_nlp_bis2%<>%
  select(-c(growth_country.y, growth_country.x))

rm(afro_w5)

data_final_nlp_bis2%<>%
mutate(growth_country = if_else(growth_country %in% c(1, 2, 3, 4, 5), growth_country, NA_integer_))

data_final_nlp_bis2 %<>%
  mutate(across(
    .cols = c(perf_corr, perf_crime, perf_eco, perf_educ, perf_elect, perf_health, 
              perf_ineq, perf_job, perf_local, perf_parl, perf_pres, perf_price, 
              perf_road, perf_water, perf_trad),
    .fns = ~ if_else(. %in% c(1, 2, 3, 4), ., NA_integer_)
  ))

data_final_nlp_bis2%<>%
   group_by(id_unique)%>%
  mutate(perf_mean=mean(c(perf_eco, perf_job, perf_poor, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect), na.rm = TRUE))%>%
  ungroup()

data_final_nlp_bis2%<>%
mutate(corr_level = if_else(corr_level %in% c(1, 2, 3, 4, 5), corr_level, NA_integer_))

data_final_nlp_bis2%<>%
mutate(corr_parl_a = if_else(corr_parl %in% c(0, 1, 2, 3), corr_parl, NA_integer_))%>%
mutate(corr_pres_a = if_else(corr_pres %in% c(0, 1, 2, 3), corr_pres, NA_integer_))%>%
mutate(corr_local_a = if_else(corr_local %in% c(0, 1, 2, 3), corr_local, NA_integer_))%>%
mutate(corr_trad_a = if_else(corr_trad %in% c(0, 1, 2, 3), corr_trad, NA_integer_))%>%
mutate(corr_judge_a = if_else(corr_judge %in% c(0, 1, 2, 3), corr_judge, NA_integer_))

data_final_nlp_bis2%<>%
  group_by(id_unique)%>%
  mutate(pol_corr = ifelse(all(is.na(c(corr_pres_a, corr_parl_a))), NA, weighted.mean(c(corr_pres_a, corr_parl_a), na.rm = TRUE)))%>%
  ungroup()
```

```{r}
#perf_poor

data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q50B)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q50B)%>%
  rename(perf_poor=Q50B)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q56B)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q56B)%>%
  rename(perf_poor=Q56B)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(perf_poor = case_when(
    round == 7 ~ perf_poor.y,
    round == 8 ~ perf_poor.x))

data_final_nlp_bis2%<>%
  select(-c(perf_poor.y, perf_poor.x))

rm(afro_w7)

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q66b)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q66b)%>%
  rename(perf_poor=q66b)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(perf_poor = case_when(
    round == 6 ~ perf_poor.y,
    round %in% c(7,8) ~ perf_poor.x))

data_final_nlp_bis2%<>%
  select(-c(perf_poor.y, perf_poor.x))

rm(afro_w6)

afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q65b)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q65b)%>%
  rename(perf_poor=q65b)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(perf_poor = case_when(
    round == 5 ~ perf_poor.y,
    round %in% c(6,7,8) ~ perf_poor.x))

data_final_nlp_bis2%<>%
  select(-c(perf_poor.y, perf_poor.x))

rm(afro_w5)

data_final_nlp_bis2%<>%
mutate(perf_poor = if_else(perf_poor %in% c(1, 2, 3, 4), perf_poor, NA_integer_))
```

```{r}
data_final_nlp_bis2%<>%
  mutate(bin_feelnat = case_when(
      !is.na(feelnat) & feelnat %in% c(4, 5) ~ 1,
      !is.na(feelnat) & feelnat %in% c(1, 2, 3) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(check_citiz_a = if_else(check_citiz %in% c(1, 2, 3, 4, 5), check_citiz, NA_integer_))%>%
  mutate(check_parl_a = if_else(check_parl %in% c(1, 2, 3, 4, 5), check_citiz, NA_integer_))

data_final_nlp_bis2 %<>%
  mutate(bin_check_citiz = case_when(
    !is.na(check_citiz_a) & check_citiz_a %in% c(1, 2, 5) ~ 0,
    !is.na(check_citiz_a) & check_citiz_a %in% c(3, 4) ~ 1,
    TRUE ~ NA_integer_
  ))

data_final_nlp_bis2 %<>%
  mutate(bin_check_parl = case_when(
    !is.na(check_parl_a) & check_parl_a %in% c(1, 2, 5) ~ 0,
    !is.na(check_parl_a) & check_parl_a %in% c(3, 4) ~ 1,
    TRUE ~ NA_integer_
  ))

data_final_nlp_bis2%<>%
  mutate(assoc_a = if_else(assoc %in% c(0, 1, 2, 3), assoc, NA_integer_))%>%
  mutate(commu_a = if_else(commu %in% c(0, 1, 2, 3, 4), commu, NA_integer_))%>%
  mutate(prob_a = if_else(prob %in% c(0, 1, 2, 3, 4), prob, NA_integer_))

data_final_nlp_bis2%<>%
  mutate(elec_fair_a = if_else(elec_fair %in% c(1, 2, 3, 4), elec_fair, NA_integer_))%>%
  mutate(pref_demo_a = if_else(pref_demo %in% c(1, 2, 3), pref_demo, NA_integer_))%>%
  mutate(protest_a = if_else(protest %in% c(0, 1, 2, 3, 4), protest, NA_integer_))%>%
  mutate(vote_a = if_else(vote %in% c(0, 1, 2, 3, 4, 5 ,6 , 7), vote , NA_integer_))%>%
  mutate(bin_vote = case_when(
    !is.na(vote_a) & vote_a %in% c(0, 2, 3, 4, 5 ,6 , 7) ~ 0,
    !is.na(vote_a) & vote_a == 1 ~ 1,
    TRUE ~ NA_integer_
  ))

data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")

data_final_nlp_bis2%<>%
  mutate(trust_gen_a=if_else(trust_gen%in%c(0,1), trust_gen, NA_integer_))

data_final_nlp_bis2%<>%
  mutate(extent_a = if_else(extent %in% c(1, 2, 3, 4), extent, NA_integer_))%>%
  mutate(satis_demo_a = if_else(satis_demo %in% c(0, 1, 2, 3, 4), satis_demo, NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_corr_parl_a = case_when(
      !is.na(corr_parl_a) & corr_parl_a %in% c(2, 3) ~ 1,
      !is.na(corr_parl_a) & corr_parl_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_corr_pres_a = case_when(
      !is.na(corr_pres_a) & corr_pres_a %in% c(2, 3) ~ 1,
      !is.na(corr_pres_a) & corr_pres_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_trust_parl_a = case_when(
      !is.na(trust_parl_a) & trust_parl_a %in% c(2, 3) ~ 1,
      !is.na(trust_parl_a) & trust_parl_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_trust_pres_a = case_when(
      !is.na(trust_pres_a) & trust_pres_a %in% c(2, 3) ~ 1,
      !is.na(trust_pres_a) & trust_pres_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2 %<>%
 group_by(id_unique)%>%
  mutate(bin_pol_trust = ifelse(all(is.na(c(bin_trust_pres_a, bin_trust_parl_a))), NA_integer_, weighted.mean(c(bin_trust_pres_a, bin_trust_parl_a), na.rm = TRUE)))%>%
  ungroup()

data_final_nlp_bis2 %<>%
 group_by(id_unique)%>%
  mutate(bin_pol_corr = ifelse(all(is.na(c(bin_corr_pres_a, bin_corr_parl_a))), NA_integer_, weighted.mean(c(bin_corr_pres_a, bin_corr_parl_a), na.rm = TRUE)))%>%
  ungroup()

data_final_nlp_bis2%<>%
  mutate(bin_pol_trust_2 = case_when(
      !is.na(bin_pol_trust) & bin_pol_trust %in% c(0.5, 1) ~ 1,
      !is.na(bin_pol_trust) & bin_pol_trust == 0 ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_pol_corr_2 = case_when(
      !is.na(bin_pol_corr) & bin_pol_corr %in% c(0.5, 1) ~ 1,
      !is.na(bin_pol_corr) & bin_pol_corr == 0 ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  group_by(latitude, longitude)%>%
  mutate(ea_id = cur_group_id()) %>%
  mutate(ea_round=as.numeric(paste0(ea_id,round)))%>%
  ungroup()

data_final_nlp_bis2%<>%
  mutate(region = case_when(
    iso %in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name2_id, 
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name1_id,
    TRUE ~ NA_integer_
  ))

data_final_nlp_bis2%<>%
  mutate(bin_growth_country = case_when(
      !is.na(growth_country) & growth_country %in% c(3, 4, 5) ~ 1,
      !is.na(growth_country) & growth_country %in% c(1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_internet_news = case_when(
      !is.na(internet_news) & internet_news %in% c(3, 4, 5) ~ 1,
      !is.na(internet_news) & internet_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_paper_news = case_when(
      !is.na(paper_news) & paper_news %in% c(3, 4, 5) ~ 1,
      !is.na(paper_news) & paper_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_radio_news = case_when(
      !is.na(radio_news) & radio_news %in% c(3, 4, 5) ~ 1,
      !is.na(radio_news) & radio_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_tele_news = case_when(
      !is.na(tele_news) & tele_news %in% c(3, 4, 5) ~ 1,
      !is.na(tele_news) & tele_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_sm_news = case_when(
      !is.na(sm_news) & sm_news %in% c(3, 4, 5) ~ 1,
      !is.na(sm_news) & sm_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_internet_use = case_when(
      !is.na(internet_use) & internet_use %in% c(3, 4, 5) ~ 1,
      !is.na(internet_use) & internet_use %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp_bis2%<>%
  mutate(bin_disc_pol_a = case_when(
      !is.na(disc_pol_a) & disc_pol_a %in% c(1, 2) ~ 1,
      !is.na(disc_pol_a) & disc_pol_a == 0 ~ 0,
      TRUE ~ NA_integer_))

```

```{r}
data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q86B)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q86B)%>%
  rename(neig_eth=Q86B)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w8, by="id_unique")

rm(afro_w8)

afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w7%<>%
  select(RESPNO, Q87B)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q87B)%>%
  rename(neig_eth=Q87B)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(neig_eth = case_when(
    round == 7 ~ neig_eth.y,
    round == 8 ~ neig_eth.x))

data_final_nlp_bis2%<>%
  select(-c(neig_eth.y, neig_eth.x))

rm(afro_w7)

afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q89b)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q89b)%>%
  rename(neig_eth=q89b)

data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")

data_final_nlp_bis2%<>%
  mutate(neig_eth = case_when(
    round == 6 ~ neig_eth.y,
    round %in% c(7,8) ~ neig_eth.x))

data_final_nlp_bis2%<>%
  select(-c(neig_eth.y, neig_eth.x))

rm(afro_w6)

data_final_nlp_bis2%<>%
  mutate(neig_eth_a = if_else(neig_eth %in% c(1, 2, 3, 4, 5), neig_eth, NA_integer_))
```

```{r}
data_final_nlp_bis2%<>%
  mutate(dist_cap_10=dist_cap/10,
         dist_ncap_10=dist_ncap/10,
         dist_sndncap_10=dist_sndncap/10,
         dist_cap_max_norm_2=dist_cap_max_norm*dist_cap_max_norm,
         dist_cap_max_norm_3=dist_cap_max_norm*dist_cap_max_norm*dist_cap_max_norm,
         dist_ncap_max_norm_2=dist_ncap_max_norm*dist_ncap_max_norm,
         dist_ncap_max_norm_3=dist_ncap_max_norm*dist_ncap_max_norm*dist_ncap_max_norm,
         dist_sndncap_max_norm_2=dist_sndncap_max_norm*dist_sndncap_max_norm,
         dist_sndncap_max_norm_3=dist_sndncap_max_norm*dist_sndncap_max_norm*dist_sndncap_max_norm
         )
```

```{r}
data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")

data_final_nlp_bis2%<>%
  group_by(NAME_2, round)%>%
  mutate(internet_news_adm2=mean(internet_news),
         sm_news_adm2=mean(sm_news),
         internet_use_adm2=mean(internet_use))

```

```{r}
table(data_final_nlp_bis2$neig_eth_a)
hist(data_final_nlp_bis2$neig_eth_a)
```

#Export Stata

```{r}
saveRDS(data_final_nlp_bis2, file="data/data_rds/data_final_r.rds")

write_dta(data_final_nlp_bis2, "data/data_dta/data_final_r.dta")
```

### 2025-02-24 script/r/draft.Rmd
draft: desert control rds

@@
 ```{r}
-tiff_file <- "C:/Users/Redha CHABA/Desktop/temp/desert.tif"
+library(terra)
+
+tiff_file <- "data/data_raw/geography/desert/desert.tif"
 
@@
 
-freq(binary_raster)
-
-plot(binary_raster, main = "Desert Map", col = terrain.colors(100))
+plot(binary_raster, main = "Desert Map", col = rev(heat.colors(100)))
 
@@
 ```
-
-```{r}
-library(ggplot2)
-
-ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a)), aes(x = factor(neig_eth_a))) +
-  geom_bar(fill = "steelblue") +
-  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
-       y = "Count",
-       x=NULL) +
-  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
-  theme_minimal()
-
-ggplot(data_final_nlp_bis2%>%filter(!is.na(neig_eth_a), spl==1), aes(x = factor(neig_eth_a))) +
-  geom_bar(fill = "steelblue") +
-  labs(title = "Willingness to Have Neighbors of Different Ethnicities - Waves 6-8",
-       y = "Count",
-       x=NULL) +
-  scale_x_discrete(labels = c("Strongly dislike", "Somewhat dislike","Would not care", "Somewhat like", "Strongly like")) +
-  theme_minimal()
-```

### 2025-02-25 script/r/draft.Rmd
elevation code

@@
+```{r}
+setwd("~/working_paper/trust/")
+getwd()
+```
+
+```{r packages, echo=FALSE, }
+library(haven)
+library(dplyr)
+select <- dplyr::select
+library(magrittr)
+library(stringr)
+library(geosphere)
+library(purrr)
+library(kableExtra)
+library(tidyr)
+library(readxl)
+library(sf)
+library(exactextractr)
+library(raster)
+library(rgdal)
+library(ncdf4)
+library(terra)
+```
+
+#Levels
+
+```{r}
+folder_path <- "data/data_raw/gadm"
+
+files <- list.files(folder_path, full.names = TRUE)
+
+levels <- data.frame(file = files) %>%
+  mutate(country = str_extract(file, "(?<=_)[A-Z]{3}(?=_\\d)"),
+         level = as.integer(str_extract(file, "(?<=_)[0-9]+(?=\\.shp$)"))) %>%
+  arrange(country, desc(level)) %>%
+  distinct(country, .keep_all = TRUE)
+
+levels %<>%
+  group_by(country) %>%
+  summarise(levels_nb = first(level))
+
+print(levels, n=40)
+```
+
+#Adm setup
+
+```{r}
+cty_adm1 <- levels%>%
+  filter(levels_nb>=1)%>%
+  pull(country)
+
+cty_adm2 <- levels%>%
+  filter(levels_nb>=2)%>%
+  pull(country)
+
+cty_adm3 <- levels%>%
+  filter(levels_nb>=3)%>%
+  pull(country)
+
+cty_adm4 <- levels%>%
+  filter(levels_nb>=4)%>%
+  pull(country)
+```
+
 ```{r}
@@
 ```{r}
-library(terra)
 
@@
 ```
+
+```{r}
+tiff_file <- "data/data_raw/geography/elevation/elevation.tif"
+
+elevation_wgs84 <- rast(tiff_file)
+
+print(elevation_wgs84)
+
+plot(elevation_wgs84, main = "Elevation Map", col = terrain.colors(100), breaks = seq(-1000, 3000, by = 100))
+
+elevation_r5_adm1 <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(elevation_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(elevation_wgs84))
+  }
+
+  elevation_wgs84_cropped <- crop(elevation_wgs84, country_shp)
+  elevation_wgs84_masked <- mask(elevation_wgs84_cropped, country_shp)
+
+  elevation_adm1 <- exactextractr::exact_extract(elevation_wgs84_masked, regions, 'mean')
+
+  regions$elevation_adm1 <- elevation_adm1
+  regions_df <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, elevation_adm1) %>%
+    mutate(round = 5)
+
+  elevation_r5_adm1 <- rbind(elevation_r5_adm1, regions_df)
+}
+
+elevation_r5_adm1 %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(elevation_r5_adm1))
+
+saveRDS(elevation_r5_adm1, file="data/data_rds/geo_ctrl/elevation_r5_adm1.rds")
+
+elevation_r5_adm2 <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(elevation_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(elevation_wgs84))
+  }
+
+  elevation_wgs84_cropped <- crop(elevation_wgs84, country_shp)
+  elevation_wgs84_masked <- mask(elevation_wgs84_cropped, country_shp)
+
+  elevation_adm2 <- exactextractr::exact_extract(elevation_wgs84_masked, regions, 'mean')
+
+  regions$elevation_adm2 <- elevation_adm2
+  regions_df <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, elevation_adm2) %>%
+    mutate(round = 5)
+
+  elevation_r5_adm2 <- rbind(elevation_r5_adm2, regions_df)
+}
+
+elevation_r5_adm2 %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(elevation_r5_adm2))
+
+saveRDS(elevation_r5_adm2, file="data/data_rds/geo_ctrl/elevation_r5_adm2.rds")
+```

### 2025-02-25 script/r/draft.Rmd
Add script precipitation, temperature (mean, max, min) + improved loops

@@
 print(levels, n=40)
-```
 
-#Adm setup
-
-```{r}
 cty_adm1 <- levels%>%
@@
 ```{r}
-
 tiff_file <- "data/data_raw/geography/desert/desert.tif"
@@
 
-desert_r5_adm1 <- data.frame()
+desert_adm1_df <- data.frame()
 
@@
   regions$desert_adm1 <- desert_adm1
-  regions_df <- regions %>%
+
+  country_results <- regions %>%
     as.data.frame() %>%
     rename(iso = GID_0) %>%
-    select(iso, NAME_1, desert_adm1) %>%
-    mutate(round = 5)
+    select(iso, NAME_1, desert_adm1)
 
-  desert_r5_adm1 <- rbind(desert_r5_adm1, regions_df)
+  desert_adm1_df <- rbind(desert_adm1_df, country_results)
 }
 
-desert_r5_adm1 %<>%
+desert_adm1_df %<>%
   mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
 
-print(glimpse(desert_r5_adm1))
+print(glimpse(desert_adm1_df))
 
-saveRDS(desert_r5_adm1, file="data/data_rds/geo_ctrl/desert_r5_adm1.rds")
+saveRDS(desert_adm1_df, file="data/data_rds/geo_ctrl/desert_adm1.rds")
 
-desert_r5_adm2 <- data.frame()
+desert_adm2_df <- data.frame()
 
@@
   regions$desert_adm2 <- desert_adm2
-  regions_df <- regions %>%
+
+  country_results <- regions %>%
     as.data.frame() %>%
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, desert_adm2) %>%
-    mutate(round = 5)
+    select(iso, NAME_2, desert_adm2)
 
-  desert_r5_adm2 <- rbind(desert_r5_adm2, regions_df)
+  desert_adm2_df <- rbind(desert_adm2_df, country_results)
 }
 
-desert_r5_adm2 %<>%
+desert_adm2_df %<>%
   mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
 
-print(glimpse(desert_r5_adm2))
+print(glimpse(desert_adm2_df))
 
-saveRDS(desert_r5_adm2, file="data/data_rds/geo_ctrl/desert_r5_adm2.rds")
+saveRDS(desert_adm2_df, file="data/data_rds/geo_ctrl/desert_adm2.rds")
 ```
@@
 
-elevation_r5_adm1 <- data.frame()
+elevation_adm1_df <- data.frame()
 
@@
   regions$elevation_adm1 <- elevation_adm1
-  regions_df <- regions %>%
+
+  country_results <- regions %>%
     as.data.frame() %>%
     rename(iso = GID_0) %>%
-    select(iso, NAME_1, elevation_adm1) %>%
-    mutate(round = 5)
+    select(iso, NAME_1, elevation_adm1)
 
-  elevation_r5_adm1 <- rbind(elevation_r5_adm1, regions_df)
+  elevation_adm1_df <- rbind(elevation_adm1_df, country_results)
 }
 
-elevation_r5_adm1 %<>%
+elevation_adm1_df %<>%
   mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
 
-print(glimpse(elevation_r5_adm1))
+print(glimpse(elevation_adm1_df))
 
-saveRDS(elevation_r5_adm1, file="data/data_rds/geo_ctrl/elevation_r5_adm1.rds")
+saveRDS(elevation_adm1_df, file="data/data_rds/geo_ctrl/elevation_adm1.rds")
 
-elevation_r5_adm2 <- data.frame()
+elevation_adm2_df <- data.frame()
 
@@
   regions$elevation_adm2 <- elevation_adm2
-  regions_df <- regions %>%
+
+  country_results <- regions %>%
     as.data.frame() %>%
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, elevation_adm2) %>%
-    mutate(round = 5)
+    select(iso, NAME_2, elevation_adm2)
 
-  elevation_r5_adm2 <- rbind(elevation_r5_adm2, regions_df)
+  elevation_adm2_df <- rbind(elevation_adm2_df, country_results)
 }
 
-elevation_r5_adm2 %<>%
+elevation_adm2_df %<>%
   mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
 
-print(glimpse(elevation_r5_adm2))
+print(glimpse(elevation_adm2_df))
 
-saveRDS(elevation_r5_adm2, file="data/data_rds/geo_ctrl/elevation_r5_adm2.rds")
+saveRDS(elevation_adm2_df, file="data/data_rds/geo_ctrl/elevation_adm2.rds")
 ```
+
+```{r}
+library(viridis)
+
+tiff_file <- "data/data_raw/geography/precipitation/CHELSA_bio12_1981-2010_V.2.1.tif"
+
+precipitation_wgs84 <- rast(tiff_file)
+
+print(precipitation_wgs84)
+
+africa_extent <- ext(-20, 60, -40, 40)
+
+precipitation_africa <- crop(precipitation_wgs84, africa_extent)
+
+plot(precipitation_africa, main = "Precipitation Map of Africa", col = viridis(100), breaks = seq(0, 3000, by = 100))
+
+precipitation_adm1_df <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(precipitation_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(precipitation_wgs84))
+  }
+
+  precipitation_wgs84_cropped <- crop(precipitation_wgs84, country_shp)
+  precipitation_wgs84_masked <- mask(precipitation_wgs84_cropped, country_shp)
+
+  precipitation_adm1 <- exactextractr::exact_extract(precipitation_wgs84_masked, regions, 'mean')
+
+  regions$precipitation_adm1 <- precipitation_adm1
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, precipitation_adm1)
+
+  precipitation_adm1_df <- rbind(precipitation_adm1_df, country_results)
+}
+
+precipitation_adm1_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(precipitation_adm1_df))
+
+saveRDS(precipitation_adm1_df, file="data/data_rds/geo_ctrl/precipitation_adm1.rds")
+
+precipitation_adm2_df <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(precipitation_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(precipitation_wgs84))
+  }
+
+  precipitation_wgs84_cropped <- crop(precipitation_wgs84, country_shp)
+  precipitation_wgs84_masked <- mask(precipitation_wgs84_cropped, country_shp)
+
+  precipitation_adm2 <- exactextractr::exact_extract(precipitation_wgs84_masked, regions, 'mean')
+
+  regions$precipitation_adm2 <- precipitation_adm2
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, precipitation_adm2)
+
+  precipitation_adm2_df <- rbind(precipitation_adm2_df, country_results)
+}
+
+precipitation_adm2_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(precipitation_adm2_df))
+
+saveRDS(precipitation_adm2_df, file="data/data_rds/geo_ctrl/precipitation_adm2.rds")
+```
+
+```{r}
+shapefile_directory <- "data/data_raw/gadm/"
+
+shapefile_names <- list.files(shapefile_directory, pattern = "*_2.shp", full.names = TRUE)
+
+adm2_shapefiles <- lapply(shapefile_names, st_read)
+adm2_combined <- do.call(rbind, adm2_shapefiles)
+
+adm2_combined_merged <- merge(adm2_combined, precipitation_adm2, by.x = "NAME_2", by.y = "NAME_2", all.x = TRUE)
+
+library(ggplot2)
+
+ggplot() +
+  geom_sf(data = adm2_combined_merged, aes(fill = precipitation_adm2), color = "black", size = 0.25) +
+  scale_fill_viridis(name = "Precipitation (mm)", option = "plasma", na.value = "grey") +
+  labs(title = "Precipitation Map of Africa",
+       subtitle = "Regional Precipitation Values") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
+    plot.subtitle = element_text(hjust = 0.5, size = 12),
+    legend.position = "bottom"
+  )
+
+```
+
+```{r}
+tiff_file <- "data/data_raw/geography/temperature/CHELSA_bio1_1981-2010_V.2.1.tif"
+
+temp_mean_wgs84 <- rast(tiff_file)
+
+print(temp_mean_wgs84)
+
+africa_extent <- ext(-20, 60, -40, 40)
+
+temp_mean_africa <- crop(temp_mean_wgs84, africa_extent)
+
+plot(temp_mean_africa, main = "temp_mean Map of Africa", col = rev(heat.colors(100)), breaks = seq(0, 50, by = 1))
+
+temp_mean_adm1_df <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_mean_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_mean_wgs84))
+  }
+
+  temp_mean_wgs84_cropped <- crop(temp_mean_wgs84, country_shp)
+  temp_mean_wgs84_masked <- mask(temp_mean_wgs84_cropped, country_shp)
+
+  temp_mean_adm1 <- exactextractr::exact_extract(temp_mean_wgs84_masked, regions, 'mean')
+
+  regions$temp_mean_adm1 <- temp_mean_adm1
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, temp_mean_adm1)
+
+  temp_mean_adm1_df <- rbind(temp_mean_adm1_df, country_results)
+}
+
+temp_mean_adm1_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_mean_adm1_df))
+
+saveRDS(temp_mean_adm1_df, file="data/data_rds/geo_ctrl/temp_mean_adm1.rds")
+
+temp_mean_adm2_df <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_mean_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_mean_wgs84))
+  }
+
+  temp_mean_wgs84_cropped <- crop(temp_mean_wgs84, country_shp)
+  temp_mean_wgs84_masked <- mask(temp_mean_wgs84_cropped, country_shp)
+
+  temp_mean_adm2 <- exactextractr::exact_extract(temp_mean_wgs84_masked, regions, 'mean')
+
+  regions$temp_mean_adm2 <- temp_mean_adm2
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, temp_mean_adm2)
+
+  temp_mean_adm2_df <- rbind(temp_mean_adm2_df, country_results)
+}
+
+temp_mean_adm2_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_mean_adm2_df))
+
+saveRDS(temp_mean_adm2_df, file="data/data_rds/geo_ctrl/temp_mean_adm2.rds")
+```
+
+```{r}
+tiff_file <- "data/data_raw/geography/temperature/CHELSA_bio5_1981-2010_V.2.1.tif"
+
+temp_max_wgs84 <- rast(tiff_file)
+
+print(temp_max_wgs84)
+
+africa_extent <- ext(-20, 60, -40, 40)
+
+temp_max_africa <- crop(temp_max_wgs84, africa_extent)
+
+plot(temp_max_africa, main = "temp_max Map of Africa", col = rev(heat.colors(100)), breaks = seq(0, 50, by = 1))
+
+temp_max_adm1_df <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_max_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_max_wgs84))
+  }
+
+  temp_max_wgs84_cropped <- crop(temp_max_wgs84, country_shp)
+  temp_max_wgs84_masked <- mask(temp_max_wgs84_cropped, country_shp)
+
+  temp_max_adm1 <- exactextractr::exact_extract(temp_max_wgs84_masked, regions, 'mean')
+
+  regions$temp_max_adm1 <- temp_max_adm1
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, temp_max_adm1)
+
+  temp_max_adm1_df <- rbind(temp_max_adm1_df, country_results)
+}
+
+temp_max_adm1_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_max_adm1_df))
+
+saveRDS(temp_max_adm1_df, file="data/data_rds/geo_ctrl/temp_max_adm1.rds")
+
+temp_max_adm2_df <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_max_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_max_wgs84))
+  }
+
+  temp_max_wgs84_cropped <- crop(temp_max_wgs84, country_shp)
+  temp_max_wgs84_masked <- mask(temp_max_wgs84_cropped, country_shp)
+
+  temp_max_adm2 <- exactextractr::exact_extract(temp_max_wgs84_masked, regions, 'mean')
+
+  regions$temp_max_adm2 <- temp_max_adm2
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, temp_max_adm2)
+
+  temp_max_adm2_df <- rbind(temp_max_adm2_df, country_results)
+}
+
+temp_max_adm2_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_max_adm2_df))
+
+saveRDS(temp_max_adm2_df, file="data/data_rds/geo_ctrl/temp_max_adm2.rds")
+```
+
+```{r}
+tiff_file <- "data/data_raw/geography/temperature/CHELSA_bio6_1981-2010_V.2.1.tif"
+
+temp_min_wgs84 <- rast(tiff_file)
+
+print(temp_min_wgs84)
+
+africa_extent <- ext(-20, 60, -40, 40)
+
+temp_min_africa <- crop(temp_min_wgs84, africa_extent)
+
+plot(temp_min_africa, main = "temp_min Map of Africa", col = viridis(100), breaks = seq(-20, 30, by = 1))
+
+temp_min_adm1_df <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_min_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_min_wgs84))
+  }
+
+  temp_min_wgs84_cropped <- crop(temp_min_wgs84, country_shp)
+  temp_min_wgs84_masked <- mask(temp_min_wgs84_cropped, country_shp)
+
+  temp_min_adm1 <- exactextractr::exact_extract(temp_min_wgs84_masked, regions, 'mean')
+
+  regions$temp_min_adm1 <- temp_min_adm1
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, temp_min_adm1)
+
+  temp_min_adm1_df <- rbind(temp_min_adm1_df, country_results)
+}
+
+temp_min_adm1_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_min_adm1_df))
+
+saveRDS(temp_min_adm1_df, file="data/data_rds/geo_ctrl/temp_min_adm1.rds")
+
+temp_min_adm2_df <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(temp_min_wgs84), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(temp_min_wgs84))
+  }
+
+  temp_min_wgs84_cropped <- crop(temp_min_wgs84, country_shp)
+  temp_min_wgs84_masked <- mask(temp_min_wgs84_cropped, country_shp)
+
+  temp_min_adm2 <- exactextractr::exact_extract(temp_min_wgs84_masked, regions, 'mean')
+
+  regions$temp_min_adm2 <- temp_min_adm2
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, temp_min_adm2)
+
+  temp_min_adm2_df <- rbind(temp_min_adm2_df, country_results)
+}
+
+temp_min_adm2_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(temp_min_adm2_df))
+
+saveRDS(temp_min_adm2_df, file="data/data_rds/geo_ctrl/temp_min_adm2.rds")
+```

### 2025-02-25 script/r/draft.Rmd
Add mountains. Geo ctrls script done

@@
 
-binary_raster <- ifel(!is.na(desert_wgs84), 1, 0)
+africa_extent <- ext(-30, 60, -40, 40)
+
+destert_africa <- crop(desert_wgs84, africa_extent)
+
+binary_raster <- ifel(!is.na(desert_africa), 1, 0)
 
@@
 
-africa_extent <- ext(-20, 60, -40, 40)
+africa_extent <- ext(-30, 60, -40, 40)
 
@@
 ```
+
+```{r}
+tiff_file <- "data/data_raw/geography/mountain/k3binary.tif"
+
+mountain_wgs84 <- rast(tiff_file)
+
+print(mountain_wgs84)
+
+africa_extent <- ext(-30, 60, -40, 40)
+
+mountain_africa <- crop(mountain_wgs84, africa_extent)
+
+binary_raster <- ifel(!is.na(mountain_africa), 1, 0)
+
+plot(binary_raster, main = "mountain Map of Africa", col = viridis(100))
+
+mountain_adm1_df <- data.frame()
+
+for (country in cty_adm1) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(binary_raster), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(binary_raster))
+  }
+
+  binary_raster_cropped <- crop(binary_raster, country_shp)
+  binary_raster_masked <- mask(binary_raster_cropped, country_shp)
+
+  mountain_adm1 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')
+
+  regions$mountain_adm1 <- mountain_adm1
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_1, mountain_adm1)
+
+  mountain_adm1_df <- rbind(mountain_adm1_df, country_results)
+}
+
+mountain_adm1_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(mountain_adm1_df))
+
+saveRDS(mountain_adm1_df, file="data/data_rds/geo_ctrl/mountain_adm1.rds")
+
+mountain_adm2_df <- data.frame()
+
+for (country in cty_adm2) {
+
+  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
+  regions <- st_read(shapefile) %>% st_make_valid()
+
+  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
+  country_shp <- vect(shapefile_path)
+
+  if (!identical(crs(binary_raster), crs(country_shp))) {
+    country_shp <- project(country_shp, crs(binary_raster))
+  }
+
+  binary_raster_cropped <- crop(binary_raster, country_shp)
+  binary_raster_masked <- mask(binary_raster_cropped, country_shp)
+
+  mountain_adm2 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')
+
+  regions$mountain_adm2 <- mountain_adm2
+
+  country_results <- regions %>%
+    as.data.frame() %>%
+    rename(iso = GID_0) %>%
+    select(iso, NAME_2, mountain_adm2)
+
+  mountain_adm2_df <- rbind(mountain_adm2_df, country_results)
+}
+
+mountain_adm2_df %<>%
+  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))
+
+print(glimpse(mountain_adm2_df))
+
+saveRDS(mountain_adm2_df, file="data/data_rds/geo_ctrl/mountain_adm2.rds")
+```

### 2025-02-27 script/r/draft.Rmd
merge geo controls

@@
 
-destert_africa <- crop(desert_wgs84, africa_extent)
+desert_africa <- crop(desert_wgs84, africa_extent)
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, desert_adm2)
+    select(iso, NAME_1, NAME_2, desert_adm2)
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, elevation_adm2)
+    select(iso, NAME_1, NAME_2, elevation_adm2)
 
@@
 
-plot(precipitation_africa, main = "Precipitation Map of Africa", col = viridis(100), breaks = seq(0, 3000, by = 100))
+plot(precipitation_africa, main = "Precipitation Map of Africa", col = rev(viridis(100)))
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, precipitation_adm2)
+    select(iso, NAME_1, NAME_2, precipitation_adm2)
 
@@
 
-plot(temp_mean_africa, main = "temp_mean Map of Africa", col = rev(heat.colors(100)), breaks = seq(0, 50, by = 1))
+plot(temp_mean_africa, main = "temp_mean Map of Africa", col = rev(heat.colors(100)))
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, temp_mean_adm2)
+    select(iso, NAME_1, NAME_2, temp_mean_adm2)
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, temp_max_adm2)
+    select(iso, NAME_1, NAME_2, temp_max_adm2)
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, temp_min_adm2)
+    select(iso, NAME_1, NAME_2, temp_min_adm2)
 
@@
     rename(iso = GID_0) %>%
-    select(iso, NAME_2, mountain_adm2)
+    select(iso, NAME_1, NAME_2, mountain_adm2)
 
@@
 ```
+
+```{r}
+data_final_r <- readRDS("data/data_rds/data_final_r.rds")
+
+desert_adm1 <- readRDS("data/data_rds/geo_ctrl/desert_adm1.rds")
+desert_adm2 <- readRDS("data/data_rds/geo_ctrl/desert_adm2.rds")
+
+desert <- merge(desert_adm1, desert_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(desert_adm1, desert_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(desert)))
+
+expanded_data <- desert[rep(1:nrow(desert), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo <- expanded_data
+
+rm(desert)
+
+elevation_adm1 <- readRDS("data/data_rds/geo_ctrl/elevation_adm1.rds")
+elevation_adm2 <- readRDS("data/data_rds/geo_ctrl/elevation_adm2.rds")
+
+elevation <- merge(elevation_adm1, elevation_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(elevation_adm1, elevation_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(elevation)))
+
+expanded_data <- elevation[rep(1:nrow(elevation), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(elevation)
+
+mountain_adm1 <- readRDS("data/data_rds/geo_ctrl/mountain_adm1.rds")
+mountain_adm2 <- readRDS("data/data_rds/geo_ctrl/mountain_adm2.rds")
+
+mountain <- merge(mountain_adm1, mountain_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(mountain_adm1, mountain_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(mountain)))
+
+expanded_data <- mountain[rep(1:nrow(mountain), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(mountain)
+
+precipitation_adm1 <- readRDS("data/data_rds/geo_ctrl/precipitation_adm1.rds")
+precipitation_adm2 <- readRDS("data/data_rds/geo_ctrl/precipitation_adm2.rds")
+
+precipitation <- merge(precipitation_adm1, precipitation_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(precipitation_adm1, precipitation_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(precipitation)))
+
+expanded_data <- precipitation[rep(1:nrow(precipitation), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(precipitation)
+
+temp_max_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_max_adm1.rds")
+temp_max_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_max_adm2.rds")
+
+temp_max <- merge(temp_max_adm1, temp_max_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(temp_max_adm1, temp_max_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(temp_max)))
+
+expanded_data <- temp_max[rep(1:nrow(temp_max), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(temp_max)
+
+temp_min_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_min_adm1.rds")
+temp_min_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_min_adm2.rds")
+
+temp_min <- merge(temp_min_adm1, temp_min_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(temp_min_adm1, temp_min_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(temp_min)))
+
+expanded_data <- temp_min[rep(1:nrow(temp_min), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(temp_min)
+
+temp_mean_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_mean_adm1.rds")
+temp_mean_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_mean_adm2.rds")
+
+temp_mean <- merge(temp_mean_adm1, temp_mean_adm2, by = c("iso", "NAME_1"), all = TRUE)
+
+rm(temp_mean_adm1, temp_mean_adm2)
+
+rounds <- data.frame(round = rep(5:8, each = nrow(temp_mean)))
+
+expanded_data <- temp_mean[rep(1:nrow(temp_mean), times = 4), ]
+
+expanded_data$round <- rounds$round
+
+expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)
+
+data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+rm(temp_mean)
+
+data_final_r %<>% left_join(data_geo, by=c("iso", "NAME_1", "NAME_2", "round"))
+
+saveRDS(data_final_r, file="data/data_rds/data_27_05_25.rds")
+
+write_dta(data_final_r, "data/data_dta/data_27_05_25.dta")
+```

### 2025-02-27 script/r/draft.Rmd
add adm harmonization for geo controls

@@
 ```{r}
-data_final_r <- readRDS("data/data_rds/data_final_r.rds")
-
 desert_adm1 <- readRDS("data/data_rds/geo_ctrl/desert_adm1.rds")
@@
 
+data_final_r <- readRDS("data/data_rds/data_final_r.rds")
+
 data_final_r %<>% left_join(data_geo, by=c("iso", "NAME_1", "NAME_2", "round"))
 
-saveRDS(data_final_r, file="data/data_rds/data_27_05_25.rds")
-
-write_dta(data_final_r, "data/data_dta/data_27_05_25.dta")
-```
+countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+
+data_final_r %<>%
+mutate(desert_region = case_when(
+    iso %in% countries_adm1 ~ desert_adm1,
+    iso %in% countries_adm2 ~ desert_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(elevation_region = case_when(
+    iso %in% countries_adm1 ~ elevation_adm1,
+    iso %in% countries_adm2 ~ elevation_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(mountain_region = case_when(
+    iso %in% countries_adm1 ~ mountain_adm1,
+    iso %in% countries_adm2 ~ mountain_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(precipitation_region = case_when(
+    iso %in% countries_adm1 ~ precipitation_adm1,
+    iso %in% countries_adm2 ~ precipitation_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(temp_max_region = case_when(
+    iso %in% countries_adm1 ~ temp_max_adm1,
+    iso %in% countries_adm2 ~ temp_max_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(temp_min_region = case_when(
+    iso %in% countries_adm1 ~ temp_min_adm1,
+    iso %in% countries_adm2 ~ temp_min_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(temp_mean_region = case_when(
+    iso %in% countries_adm1 ~ temp_mean_adm1,
+    iso %in% countries_adm2 ~ temp_mean_adm2, 
+    TRUE ~ NA_integer_
+  ))
+
+saveRDS(data_final_r, file="data/data_rds/data_27_02_25.rds")
+
+write_dta(data_final_r, "data/data_dta/data_27_02_25.dta")
+```

### 2025-03-14 script/r/discontinuity_plot.Rmd
maj discontinuity plot

@@
 ```{r}
-df_40 <- read_dta("data/data_dta/df_40_2.dta")
+df_40 <- read_dta("data/data_dta/df_40.dta")
 
-df_40 <- na.omit(subset(df_40, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num")))
+df_40%<>%
+  group_by(id_unique)%>%
+  mutate(mountain_region_tv=mountain_region*tv,
+         desert_region_tv=desert_region*tv) %>%
+  ungroup()
+
+df_40 <- na.omit(subset(df_40, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))
 
 reg3_40 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
-                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num), clusters = cluster_bdd, data = df_40)
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv, clusters = cluster_bdd, data = df_40)
 
-library(lfe)
-
-reg3_40 <- felm(pol_trust ~ dist_cap_max_norm + dist_sndncap_max_norm + age + age_2 + factor(sex) + factor(educ_sec) + 
-              factor(bin_rural) + factor(bin_conditions_eco) + factor(bin_conditions_country) + factor(bin_emp) + disc_pol_a + 
-              tele_news + paper_news + radio_news + night_region_log + pop_region_log + area_region_log | 
-              country_round + murdock_names | 0 | cluster_bdd, data = df_40)
 summary(reg3_40)
@@
 df_40$ft_values <- fitted(reg3_40)
-
 ```
@@
 df_40_pres <- subset(df_40, df_40$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
-df_40_loin <- subset(df_40, df_40$distance_border>0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
+df_40_loin <- subset(df_40, df_40$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
 
 #On définit 10 intervalles
-nb_intervals <- 10
+nb_intervals <- 40
 
@@
 ```{r}
-theme_set(theme_minimal(base_family = "Arial"))
+# Create modified datasets with points at the boundary and extremes
+data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
+data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)
 
-ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
-  scale_color_manual(values = c("blue", "red"), 
-                     name = "Legend",
-                     labels = c("Close to the capital","Far to the capital")) + 
-  labs(x = "Distance from the Border (in km)",
-       y = "Political Trust") +
-  scale_x_continuous(labels = function(x) x / 1000) +
+# Find the min and max values in your x range
+x_min <- -40000  # -40 km in your units
+x_max <- 40000   # 40 km in your units
 
-  theme_minimal() +
+# Find the predicted values at x=0, x_min, and x_max for each curve
+left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
+right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)
 
-  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +
+y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))
 
-    geom_point(aes(color = mean_dist_border_intervals > 0), size=3, show.legend = FALSE) +
+y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))
 
-  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
-              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
-              method = "lm", formula = y ~ poly(x, 2), color = "darkblue", size = 1, se = TRUE,
-    level = 0.90, show.legend = FALSE) +
+# Average confidence interval for the added points
+avg_ic_left <- mean(data_left$ic_trust)
+avg_ic_right <- mean(data_right$ic_trust)
 
-  geom_smooth(data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
-              aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
-              method = "lm", formula = y ~ poly(x, 2), color = "darkred", size = 1, se = TRUE,
-    level = 0.90,
-show.legend = FALSE) +
+# Add points at x=0 and x=x_min to left dataset
+data_left_plus <- rbind(data_left, 
+                        data.frame(
+                          mean_dist_border_intervals = 0,
+                          mean_trust_intervals = y_at_zero_left,
+                          ic_trust = avg_ic_left
+                        ),
+                        data.frame(
+                          mean_dist_border_intervals = x_min,
+                          mean_trust_intervals = y_at_min,
+                          ic_trust = avg_ic_left
+                        ))
 
-  geom_segment(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)), 
-                   xend = 0, 
-                   y = moy_trust_pres, 
-                   yend = moy_trust_pres, 
-                   linetype = "mean_near"),
-               color = "darkblue", size = 1.5) +
-
-  geom_segment(aes(x = 0, 
-                   xend = max(abs(data_intervals$mean_dist_border_intervals)), 
-                   y = moy_trust_loin, 
-                   yend = moy_trust_loin, 
-                   linetype = "mean_far"),
-               color = "darkred", size = 1.5) +
-
-scale_linetype_manual(name = NULL, 
-                        values = c("mean_near" = "solid", 
-                                   "mean_far" = "solid"),
-                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
-  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), max(abs(data_intervals$mean_dist_border_intervals))))+
-
-ggtext::geom_richtext(aes(x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Close to the Capital"),
-                        vjust = 2, hjust = 0.6, size = 5, fill = "white", color = "black", fontface = "bold", 
-                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) + 
-  ggtext::geom_richtext(aes(x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, y = Inf, label = "Far from the Capital"),
-                        vjust = 2, hjust = 0.4, size = 5, fill = "white", color = "black", fontface = "bold", 
-                        label.color = "black", box.padding = unit(0.5, "lines"), label.size = 1) +
-
-  theme(plot.title = element_text(size = 20, hjust = 0.5),  
-        axis.title = element_text(size = 15), 
-        legend.text = element_text(size = 12),
-        legend.position = c(0.85, 0.2), # Position de la légende
-        legend.background = element_rect(fill = alpha('white', 1)))
-
-ggsave("plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
-
+# Add points at x=0 and x=x_max to right dataset
+data_right_plus <- rbind(data_right, 
+                         data.frame(
+                           mean_dist_border_intervals = 0,
+                           mean_trust_intervals = y_at_zero_right,
+                           ic_trust = avg_ic_right
+                         ),
+                         data.frame(
+                           mean_dist_border_intervals = x_max,
+                           mean_trust_intervals = y_at_max,
+                           ic_trust = avg_ic_right
+                         ))
 ```
@@
 ```{r}
-# Set the base theme
-theme_set(theme_minimal(base_family = "Arial"))
+ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
+  # Add vertical line at border
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.8) +
 
-# Create the plot
-ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
-  # Add color scale
-  scale_color_manual(
-    values = c("blue", "red"), 
-    name = "Legend",
-    labels = c("Close to the capital", "Far to the capital")
-  ) +
+  # Left side smooth curve (Close to Capital)
+# Left side smooth curve (Close to Capital)
+geom_smooth(data = data_left_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "navy", size = 1.2, se = TRUE,
+            fill="navy",
+            alpha=0.1,
+            level = 0.90, show.legend = FALSE) +
 
-  # Add labels and scales
-  labs(
-    x = "Distance from the Border (in km)",
-    y = "Political trust"
-  ) +
-  scale_x_continuous(labels = function(x) x / 1000) +
-  theme_minimal() +
+# Right side smooth curve (Far from Capital)
+geom_smooth(data = data_right_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill = "firebrick",
+            alpha = 0.1,
+            level = 0.90, show.legend = FALSE)+
 
-  # Add vertical line at x=0
-  geom_vline(xintercept = 0, linetype = "dashed", color = "lightblue") +
-
-  # Add points
-  geom_point(
-    aes(color = mean_dist_border_intervals > 0), 
-    size = 3, 
-    show.legend = FALSE
-  ) +
-
-  # Add smooth lines for both sides
-  geom_smooth(
-    data = subset(data_intervals_ic, mean_dist_border_intervals <= 0),
-    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
-    method = "lm", 
-    formula = y ~ poly(x, 2), 
-    color = "darkblue", 
-    size = 1,
-    show.legend = FALSE
-  ) +
-  geom_smooth(
-    data = subset(data_intervals_ic, mean_dist_border_intervals > 0),
-    aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
-    method = "lm", 
-    formula = y ~ poly(x, 2), 
-    color = "darkred", 
-    size = 1,
-    se = TRUE,
-    level = 0.90,
-    show.legend = FALSE
-  ) +
-
-  # Add mean lines
-  geom_segment(
-    aes(
-      x = -max(abs(data_intervals$mean_dist_border_intervals)), 
+geom_segment(aes(x = -40000, 
                    xend = 0,
                    y = moy_trust_pres, 
-      yend = moy_trust_pres, 
-      linetype = "mean_near"
-    ),
-    color = "darkblue", 
-    size = 1.5
-  ) + 
-  geom_segment(
-    aes(
-      x = 0, 
-      xend = max(abs(data_intervals$mean_dist_border_intervals)), 
+                   yend = moy_trust_pres, linetype = "Close"),
+             inherit.aes = FALSE,
+             color = "navy", size = 1.5, alpha = 0.7, data = data.frame()) + 
+  geom_segment(aes(x = 0, 
+                   xend =40000, 
                    y = moy_trust_loin, 
-      yend = moy_trust_loin, 
-      linetype = "mean_far"
-    ),
-    color = "darkred", 
-    size = 1.5
-  ) +
+                   yend = moy_trust_loin, linetype = "Far"),
+               inherit.aes = FALSE,
+               color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) +
 
-  # Add line type scale
-  scale_linetype_manual(
-    name = NULL, 
-    values = c("mean_near" = "solid", "mean_far" = "solid"),
-    labels = c(expression(bar(y)[far]), expression(bar(y)[close]))
-  ) +
+    # Add annotations in better positions with borders
 
-  # Set coordinate limits
-  coord_cartesian(
-    xlim = c(
-      -max(abs(data_intervals$mean_dist_border_intervals)), 
-      max(abs(data_intervals$mean_dist_border_intervals))
+  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Close to the Capital", 
+           size = 7, fill = "aliceblue", color = "navy", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Far from the Capital", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+
+  # Add legend for mean lines
+  scale_linetype_manual(name = NULL, 
+                        values = c("Far" = "dashed", 
+                                  "Close" = "dashed"),
+                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
+
+  # Set appropriate axis limits
+  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
+                          max(abs(data_intervals$mean_dist_border_intervals))),
+                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
+                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +
+
+  # Format axes
+  scale_x_continuous(labels = function(x) x / 1000,
+                    breaks = seq(-40000, 40000, 10000)) +
+
+  # Add clear labels
+  labs(x = "Distance from the Border (in km)",
+      y = "Political Trust") +
+      #title = "Border Discontinuity in Political Trust",
+      #subtitle = "Comparing areas close to vs. far from the capital") +
+
+  # Polish theme
+  theme_minimal()+
+  theme(
+  text = element_text(family = "Arial"),
+    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)), 
+    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 30)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 30)),
+    axis.text = element_text(size = 11),
+    legend.position = c(0.85, 0.2),
+    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 20),
+    panel.grid.major = element_line(color = "gray90"),
+    panel.grid.minor = element_blank(),
+    plot.margin = margin(t = 20, r = 20, b = 20, l = 20)
   )
-  ) +
 
-  # Add text labels
-  ggtext::geom_richtext(
-    aes(
-      x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
-      y = Inf, 
-      label = "Close to the Capital"
-    ),
-    vjust = 2, 
-    hjust = 0.6, 
-    size = 5, 
-    fill = "white", 
-    color = "black", 
-    fontface = "bold", 
-    label.color = "black", 
-    box.padding = unit(0.5, "lines"), 
-    label.size = 1
-  ) + 
-  ggtext::geom_richtext(
-    aes(
-      x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
-      y = Inf, 
-      label = "Far from the Capital"
-    ),
-    vjust = 2, 
-    hjust = 0.4, 
-    size = 5, 
-    fill = "white", 
-    color = "black", 
-    fontface = "bold", 
-    label.color = "black", 
-    box.padding = unit(0.5, "lines"), 
-    label.size = 1
-  ) +
-
-  # Theme customization
-  theme(
-    plot.title = element_text(size = 20, hjust = 0.5),
-    axis.title = element_text(size = 15),
-    legend.text = element_text(size = 12),
-    legend.position = c(0.85, 0.2),
-    legend.background = element_rect(fill = alpha('white', 1))
-  )
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
 ```

### 2025-03-14 script/r/plots.Rmd
maj discontinuity plot

```{r}
selected_countries <- countries %>% 
 filter(iso_a3 %in% c("BEN", "NER"))

selected_individuals <- individuals %>%
 filter(iso%in% c("BEN", "NER"))

selected_capitals <- capitals %>%
 filter(iso%in% c("BEN", "NER"))

selected_murdock <- murdock_sf%>%
  filter(NAME=="DENDI")

ggplot() +
   geom_sf(data = selected_countries, fill = "white", color = "black") +
geom_sf(data = selected_murdock, fill = "green", color = "darkgreen", size = 1, alpha=0.5) +
 theme_void() + 
geom_point(data = selected_capitals, 
          aes(x = longitude, y = latitude, color = "Capitals"), 
         size = 2, shape = 22, fill = "red", show.legend = FALSE) +

geom_label(aes(x = 2.5, y = 10, label = "Benin"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
     geom_label(aes(x = 4, y = 14.5, label = "Niger"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +

geom_text(aes(x = 2.4, y = 13.75, label = "Niamey"), color = "black", size = 5) +
geom_text(aes(x = 2.2, y = 6.6, label = "Porto-Novo"), color = "black", size = 5) +

  labs(color = NULL) +
   coord_sf(xlim = c(0, 5), ylim = c(6, 18), expand = FALSE)
#ggsave("writing/presentation/bdd_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
```

### 2025-03-14 script/r/draft.Rmd
cleanining

@@
   pull(country)
+```
+
+##Merge internet
+
+```{r}
+gg_stack <- readRDS("data/data_rds/gg_stack.rds")
+ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")
+
+int_stack <- gg_stack %>%
+  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))
+
+saveRDS(int_stack, file="data/data_rds/int_stack.rds")
+
+int_stack <- readRDS("data/data_rds/int_stack.rds")
+
+int_stack%<>%
+  mutate(pop_adm1= coalesce(pop_adm1.x, pop_adm1.y))%>%
+  mutate(pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y))%>%
+  mutate(pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y))
+
+int_stack%<>%
+  select(-ends_with(".x"), -ends_with(".y"))
+
+data_final <- readRDS("data/data_rds/data_final.rds")
+
+data_final %<>%
+  left_join(int_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))
+
+countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+
+data_final%<>%
+mutate(gg_region_pot = case_when(
+    iso %in% countries_adm1 ~ gg_adm1_pot,
+    iso %in%  countries_adm2 ~ gg_adm2_pot, 
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(ggg_region_pot = case_when(
+    iso %in% countries_adm1 ~ ggg_adm1_pot,
+    iso %in%  countries_adm2 ~ ggg_adm2_pot, 
+    TRUE ~ NA_integer_))%>%
+  mutate(cvg_region_pot=ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))
+
+data_final%<>%
+mutate(pop_region = case_when(
+    iso %in% countries_adm1 ~ pop_adm1,
+    iso %in% countries_adm2 ~ pop_adm2, 
+    TRUE ~ NA_integer_
+  ))%>%
+  mutate(pop_region_log=log(pop_region+1))
+
+data_final%<>%
+  group_by(NAME_2) %>%
+  mutate(name2_id = cur_group_id()) %>%
+  ungroup() %>%
+  group_by(NAME_1) %>%
+  mutate(name1_id = cur_group_id())%>%
+  ungroup()%>%
+  mutate(adm1_time = case_when(
+    iso %in% countries_adm1 ~ name1_id * 10000 + round,
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(adm1_time = as.integer(as.factor(adm1_time)))%>%
+mutate(adm2_time = case_when(
+    iso %in% countries_adm2 ~ name2_id * 10000 + round,
+    TRUE ~ NA_integer_
+  ))%>%
+mutate(adm2_time = as.integer(as.factor(adm2_time)))
+
+data_final%<>%
+  mutate(country_round=as.numeric(paste0(round,ccode)))%>%
+  mutate(region_time = case_when(
+    iso %in% countries_adm1 ~ name1_id * 10000 + round, 
+    iso %in% countries_adm2 ~ name2_id * 10000 + round,
+    TRUE ~ NA_integer_
+  ))%>%
+  mutate(region_time = as.integer(as.factor(region_time)))
+
+saveRDS(data_final, file="data/data_rds/data_final.rds")
+write_dta(data_final, "data/data_dta/data_final.dta")
 ```

### 2025-03-14 script/r/rbci_data.Rmd
draft: desert control rds
cleanining

@@
 print(levels, n=40)
+
+cty_adm1 <- levels%>%
+  filter(levels_nb>=1)%>%
+  pull(country)
+
+cty_adm2 <- levels%>%
+  filter(levels_nb>=2)%>%
+  pull(country)
+
+cty_adm3 <- levels%>%
+  filter(levels_nb>=3)%>%
+  pull(country)
+
+cty_adm4 <- levels%>%
+  filter(levels_nb>=4)%>%
+  pull(country)
 ```
@@
 
-#Adm setup
-
-```{r}
-cty_adm1 <- levels%>%
-  filter(levels_nb>=1)%>%
-  pull(country)
-
-cty_adm2 <- levels%>%
-  filter(levels_nb>=2)%>%
-  pull(country)
-
-cty_adm3 <- levels%>%
-  filter(levels_nb>=3)%>%
-  pull(country)
-
-cty_adm4 <- levels%>%
-  filter(levels_nb>=4)%>%
-  pull(country)
-```
-
 #Raster function
@@
 ggg_r5_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
-      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+      stop("error raster matching")
     }
@@
     ggg_r5_adm1 <- rbind(ggg_r5_adm1, regions)
-
 }
@@
 
-saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1_bis.rds")
+saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1.rds")
 ```
@@
 ggg_r5_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r5_adm2 <- rbind(ggg_r5_adm2, regions)
-
 }
@@
 
-saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2_bis.rds")
+saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2.rds")
 ```
@@
 ggg_r5_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r5_adm3 <- rbind(ggg_r5_adm3, regions)
-
 }
@@
 
-saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3_bis.rds")
+saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3.rds")
 ```
@@
 ```{r}
-ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1_bis.rds")
-ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2_bis.rds")
-ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3_bis.rds")
+ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1.rds")
+ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2.rds")
+ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3.rds")
 
@@
 
-saveRDS(ggg_r5, file="data/data_rds/ggg_r5_bis.rds")
+saveRDS(ggg_r5, file="data/data_rds/ggg_r5.rds")
 ```
@@
 ggg_r6_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r6_adm1 <- rbind(ggg_r6_adm1, regions)
-
 }
@@
 
-saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1_bis.rds")
+saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1.rds")
 ```
@@
 ggg_r6_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r6_adm2 <- rbind(ggg_r6_adm2, regions)
-
 }
@@
 
-saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2_bis.rds")
-
+saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2.rds")
 ```
@@
 ggg_r6_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r6_adm3 <- rbind(ggg_r6_adm3, regions)
-
 }
@@
 
-saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3_bis.rds")
+saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3.rds")
 ```
@@
 ```{r}
-ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1_bis.rds")
-ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2_bis.rds")
-ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3_bis.rds")
+ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1.rds")
+ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2.rds")
+ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3.rds")
 
@@
 
-saveRDS(ggg_r6, file="data/data_rds/ggg_r6_bis.rds")
+saveRDS(ggg_r6, file="data/data_rds/ggg_r6.rds")
 ```
@@
 ggg_r7_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r7_adm1 <- rbind(ggg_r7_adm1, regions)
-
 }
@@
 
-saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1_bis.rds")
+saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1.rds")
 ```
@@
 ggg_r7_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r7_adm2 <- rbind(ggg_r7_adm2, regions)
-
 }
@@
 
-saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2_bis.rds")
+saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2.rds")
 ```
@@
 ggg_r7_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r7_adm3 <- rbind(ggg_r7_adm3, regions)
-
 }
@@
 
-saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3_bis.rds")
+saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3.rds")
 ```
@@
 ```{r}
-ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1_bis.rds")
-ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2_bis.rds")
-ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3_bis.rds")
+ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1.rds")
+ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2.rds")
+ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3.rds")
 
@@
 
-saveRDS(ggg_r7, file="data/data_rds/ggg_r7_bis.rds")
+saveRDS(ggg_r7, file="data/data_rds/ggg_r7.rds")
 ```
@@
 ggg_r8_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r8_adm1 <- rbind(ggg_r8_adm1, regions)
-
 }
@@
 
-saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1_bis.rds")
+saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1.rds")
 ```
@@
 ggg_r8_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r8_adm2 <- rbind(ggg_r8_adm2, regions)
-
 }
@@
 
-saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2_bis.rds")
+saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2.rds")
 ```
@@
 ggg_r8_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     ggg_r8_adm3 <- rbind(ggg_r8_adm3, regions)
-
 }
@@
 
-saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3_bis.rds")
+saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3.rds")
 ```
@@
 ```{r}
-ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1_bis.rds")
-ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2_bis.rds")
-ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3_bis.rds")
+ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1.rds")
+ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2.rds")
+ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3.rds")
 
@@
 
-saveRDS(ggg_r8, file="data/data_rds/ggg_r8_bis.rds")
-```
-
-```{r}
-ggg_r5 <- readRDS("data/data_rds/ggg_r5_bis.rds")
-ggg_r6 <- readRDS("data/data_rds/ggg_r6_bis.rds")
-ggg_r7 <- readRDS("data/data_rds/ggg_r7_bis.rds")
-ggg_r8 <- readRDS("data/data_rds/ggg_r8_bis.rds")
+saveRDS(ggg_r8, file="data/data_rds/ggg_r8.rds")
+```
+
+## Merge 3G
+
+```{r}
+ggg_r5 <- readRDS("data/data_rds/ggg_r5.rds")
+ggg_r6 <- readRDS("data/data_rds/ggg_r6.rds")
+ggg_r7 <- readRDS("data/data_rds/ggg_r7.rds")
+ggg_r8 <- readRDS("data/data_rds/ggg_r8.rds")
 
@@
 
-saveRDS(ggg_stack, file="data/data_rds/ggg_stack_bis.rds")
+saveRDS(ggg_stack, file="data/data_rds/ggg_stack.rds")
 ```
@@
 gg_r5_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
-      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+      stop("error raster matching")
     }
@@
     gg_r5_adm1 <- rbind(gg_r5_adm1, regions)
-
 }
@@
 
-saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1_bis.rds")
+saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1.rds")
 ```
@@
 gg_r5_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r5_adm2 <- rbind(gg_r5_adm2, regions)
-
 }
@@
 
-saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2_bis.rds")
+saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2.rds")
 ```
@@
 gg_r5_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 
-saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3_bis.rds")
+saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3.rds")
 ```
@@
 ```{r}
-gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1_bis.rds")
-gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2_bis.rds")
-gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3_bis.rds")
+gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1.rds")
+gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2.rds")
+gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3.rds")
 
@@
 
-saveRDS(gg_r5, file="data/data_rds/gg_r5_bis.rds")
+saveRDS(gg_r5, file="data/data_rds/gg_r5.rds")
 ```
@@
 gg_r6_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r6_adm1 <- rbind(gg_r6_adm1, regions)
-
 }
@@
 
-saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1_bis.rds")
+saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1.rds")
 ```
@@
 gg_r6_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r6_adm2 <- rbind(gg_r6_adm2, regions)
-
 }
@@
 
-saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2_bis.rds")
+saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2.rds")
 ```
@@
 gg_r6_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r6_adm3 <- rbind(gg_r6_adm3, regions)
-
 }
@@
 
-saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3_bis.rds")
+saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3.rds")
 ```
@@
 ```{r}
-gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1_bis.rds")
-gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2_bis.rds")
-gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3_bis.rds")
+gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1.rds")
+gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2.rds")
+gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3.rds")
 
@@
 
-saveRDS(gg_r6, file="data/data_rds/gg_r6_bis.rds")
-
+saveRDS(gg_r6, file="data/data_rds/gg_r6.rds")
 ```
@@
 gg_r7_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 
-saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1_bis.rds")
+saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1.rds")
 ```
@@
 gg_r7_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r7_adm2 <- rbind(gg_r7_adm2, regions)
-
 }
@@
 
-saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2_bis.rds")
+saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2.rds")
 ```
@@
 gg_r7_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 
-saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3_bis.rds")
+saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3.rds")
 ```
@@
 ```{r}
-gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1_bis.rds")
-gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2_bis.rds")
-gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3_bis.rds")
+gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1.rds")
+gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2.rds")
+gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3.rds")
 
@@
 
-saveRDS(gg_r7, file="data/data_rds/gg_r7_bis.rds")
+saveRDS(gg_r7, file="data/data_rds/gg_r7.rds")
 ```
@@
 gg_r8_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 
-saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1_bis.rds")
+saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1.rds")
 ```
@@
 gg_r8_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
     gg_r8_adm2 <- rbind(gg_r8_adm2, regions)
-
 }
@@
 
-saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2_bis.rds")
+saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2.rds")
 ```
@@
 gg_r8_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 
-saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3_bis.rds")
+saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3.rds")
 ```
@@
 ```{r}
-gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1_bis.rds")
-gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2_bis.rds")
-gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3_bis.rds")
+gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1.rds")
+gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2.rds")
+gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3.rds")
 
@@
 
-saveRDS(gg_r8, file="data/data_rds/gg_r8_bis.rds")
-```
-
-```{r}
-gg_r5 <- readRDS("data/data_rds/gg_r5_bis.rds")
-gg_r6 <- readRDS("data/data_rds/gg_r6_bis.rds")
-gg_r7 <- readRDS("data/data_rds/gg_r7_bis.rds")
-gg_r8 <- readRDS("data/data_rds/gg_r8_bis.rds")
+saveRDS(gg_r8, file="data/data_rds/gg_r8.rds")
+```
+
+## Merge 2G
+
+```{r}
+gg_r5 <- readRDS("data/data_rds/gg_r5.rds")
+gg_r6 <- readRDS("data/data_rds/gg_r6.rds")
+gg_r7 <- readRDS("data/data_rds/gg_r7.rds")
+gg_r8 <- readRDS("data/data_rds/gg_r8.rds")
 
@@
 
-saveRDS(gg_stack, file="data/data_rds/gg_stack_bis.rds")
-```
-
-##Merge internet
-
-```{r}
-gg_stack <- readRDS("data/data_rds/gg_stack_bis.rds")
-ggg_stack <- readRDS("data/data_rds/ggg_stack_bis.rds")
-
-int_stack_bis <- gg_stack %>%
+saveRDS(gg_stack, file="data/data_rds/gg_stack.rds")
+```
+
+# Merge Internet
+
+```{r}
+# -----------------------------------------------------------------------------
+# MERGING AND PROCESSING REGIONAL INTERNET DATA
+# -----------------------------------------------------------------------------
+
+# -----------------------------------------------------------------------------
+# 1. LOAD DATA
+# -----------------------------------------------------------------------------
+gg_stack <- readRDS("data/data_rds/gg_stack.rds")
+ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")
+
+# -----------------------------------------------------------------------------
+# 2. MERGE DATASETS
+# -----------------------------------------------------------------------------
+# Merge gg_stack with ggg_stack by region identifiers and round
+int_stack <- gg_stack %>%
   left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))
 
-saveRDS(int_stack_bis, file="data/data_rds/int_stack_bis.rds")
-
-int_stack_bis <- readRDS("data/data_rds/int_stack_bis.rds")
-
-int_stack_bis%<>%
-  mutate(pop_adm1= coalesce(pop_adm1.x, pop_adm1.y))%>%
-  mutate(pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y))%>%
-  mutate(pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y))
-
-int_stack_bis%<>%
+# Save intermediate merged internet dataset
+saveRDS(int_stack, file = "data/data_rds/int_stack.rds")
+
+# -----------------------------------------------------------------------------
+# 3. CLEAN MERGED DATA
+# -----------------------------------------------------------------------------
+# Coalesce population variables from both datasets (take first non-NA value)
+int_stack %<>%
+  mutate(
+    pop_adm1 = coalesce(pop_adm1.x, pop_adm1.y),
+    pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y),
+    pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y)
+  )
+
+# Remove duplicate columns ending with .x and .y
+int_stack %<>%
   select(-ends_with(".x"), -ends_with(".y"))
 
-data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp.rds")
-
-data_final_nlp_bis%<>%
-  select(-c("gg_pop_adm1","gg_adm1","gg_adm1_pot","gg_pop_adm2","gg_adm2","gg_adm2_pot","gg_pop_adm3","gg_adm3","gg_adm3_pot","ggg_pop_adm1","ggg_adm1","ggg_adm1_pot","ggg_pop_adm2","ggg_adm2","ggg_adm2_pot","ggg_pop_adm3","ggg_adm3","ggg_adm3_pot","pop_adm1","pop_adm2","pop_adm3", "gg_region_pot", "ggg_region_pot", "cvg_region_pot", "cvg_region_pot_2"))
-
-data_final_nlp_bis %<>%
-  left_join(int_stack_bis, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))
-
-data_final_nlp_bis%<>%
+# -----------------------------------------------------------------------------
+# 4. MERGE WITH FINAL DATASET
+# -----------------------------------------------------------------------------
+# Load data_final dataset
+data_final <- readRDS("data/data_rds/data_final.rds")
+
+# Merge final dataset with internet stack
+data_final %<>%
+  left_join(int_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))
+
+# -----------------------------------------------------------------------------
+# 5. REGION CLASSIFICATION
+# -----------------------------------------------------------------------------
+# Define country groups by administrative level
+countries_adm1 <- c("GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+
+# -----------------------------------------------------------------------------
+# 6. CREATE REGION POTENTIAL VARIABLES
+# -----------------------------------------------------------------------------
+# Generate region-specific variables based on country classification
+data_final %<>%
+  # Create gg region potential by admin level
   mutate(gg_region_pot = case_when(
-    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ gg_adm1_pot,
-    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ gg_adm2_pot, 
+    iso %in% countries_adm1 ~ gg_adm1_pot,
+    iso %in% countries_adm2 ~ gg_adm2_pot,
     TRUE ~ NA_integer_
-  ))%>%
+  )) %>%
+  # Create ggg region potential by admin level
   mutate(ggg_region_pot = case_when(
-    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ ggg_adm1_pot,
-    iso %in%  c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ ggg_adm2_pot, 
-    TRUE ~ NA_integer_))%>%
-  mutate(cvg_region_pot=ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))
-
-data_final_nlp_bis <- readRDS("data/data_rds/data_final_nlp_bis.rds")
-
-data_final_nlp_bis%<>%
+    iso %in% countries_adm1 ~ ggg_adm1_pot,
+    iso %in% countries_adm2 ~ ggg_adm2_pot,
+    TRUE ~ NA_integer_
+  )) %>%
+  # Create combined coverage variable, prioritizing 3G data
+  mutate(cvg_region_pot = ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))
+
+# -----------------------------------------------------------------------------
+# 7. POPULATION VARIABLES
+# -----------------------------------------------------------------------------
+# Create region-specific population density variables
+data_final %<>%
   mutate(pop_region = case_when(
-    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ pop_adm1,
-    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ pop_adm2, 
+    iso %in% countries_adm1 ~ pop_adm1,
+    iso %in% countries_adm2 ~ pop_adm2,
     TRUE ~ NA_integer_
-  ))%>%
-  mutate(pop_region_log=log(pop_region+1))
-
-data_final_nlp_bis2%<>%
+  )) %>%
+  mutate(pop_region_log = log(pop_region + 1))
+
+# -----------------------------------------------------------------------------
+# 8. CREATE REGION AND TIME IDENTIFIERS
+# -----------------------------------------------------------------------------
+# Generate unique IDs for regions and time periods
+data_final %<>%
+  # Create unique identifiers for administrative regions
   group_by(NAME_2) %>%
@@
   group_by(NAME_1) %>%
-  mutate(name1_id = cur_group_id())%>%
-  ungroup()%>%
+  mutate(name1_id = cur_group_id()) %>%
+  ungroup() %>%
+
+  # Create time-region identifiers for ADM1
   mutate(adm1_time = case_when(
-    iso %in% c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name1_id * 10000 + round,
+    iso %in% countries_adm1 ~ name1_id * 10000 + round,
     TRUE ~ NA_integer_
-  ))%>%
-mutate(adm1_time = as.integer(as.factor(adm1_time)))%>%
+  )) %>%
+  mutate(adm1_time = as.integer(as.factor(adm1_time))) %>%
+
+  # Create time-region identifiers for ADM2
   mutate(adm2_time = case_when(
-    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name2_id * 10000 + round,
+    iso %in% countries_adm2 ~ name2_id * 10000 + round,
     TRUE ~ NA_integer_
-  ))%>%
+  )) %>%
   mutate(adm2_time = as.integer(as.factor(adm2_time)))
 
-  data_final_nlp_bis2%<>%
-  mutate(country_round=as.numeric(paste0(round,ccode)))%>%
+# Create country-round and region-time identifiers
+data_final %<>%
+  mutate(country_round = as.numeric(paste0(round, ccode))) %>%
+  # Create general region-time identifier based on administrative level
   mutate(region_time = case_when(
-    iso %in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name2_id * 10000 + round, 
-    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name1_id * 10000 + round,
+    iso %in% countries_adm1 ~ name1_id * 10000 + round,
+    iso %in% countries_adm2 ~ name2_id * 10000 + round,
     TRUE ~ NA_integer_
-  ))%>%
+  )) %>%
   mutate(region_time = as.integer(as.factor(region_time)))
 
-saveRDS(data_final_nlp_bis, file="data/data_rds/data_final_nlp_bis.rds")
-write_dta(data_final_nlp_bis, "data/data_dta/data.dta")
+# -----------------------------------------------------------------------------
+# 9. SAVE FINAL DATASETS
+# -----------------------------------------------------------------------------
+# Save as R and Stata files
+saveRDS(data_final, file = "data/data_rds/data_final.rds")
+write_dta(data_final, "data/data_dta/data_final.dta")
 ```
@@
 night_r5_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r5_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r5_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r6_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r6_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r6_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r7_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r7_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r7_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r8_adm1 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r8_adm2 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 night_r8_adm3 <- data.frame()
-success_countries <- c()
-failed_countries <- c()
 
@@
 ```{r}
-data_final_int <- readRDS("data/data_rds/data_final_nlp_bis.rds")
+data_final_int <- readRDS("data/data_rds/data_final_nlp.rds")
 night_stack <- readRDS("data/data_rds/night_stack.rds")
@@
     if (!compareRaster(masked, pop_wgs84_resampled)) {
-      stop("Les rasters n'ont pas la même résolution et/ou la même étendue après ajustement.")
+      stop("error raster matching")
     }
@@
 ```{r}
-data_final_nlp_bis <- readRDS("data/data_rds/data_final_int_n_l.rds")
+data_final_nlp <- readRDS("data/data_rds/data_final_int_n_l.rds")
 
@@
 
-data_keep <- subset(data_final_nlp_bis, select = c("id_unique", "latitude", "longitude")) %>%
+data_keep <- subset(data_final_nlp, select = c("id_unique", "latitude", "longitude")) %>%
   filter(!is.na(latitude) & !is.na(longitude))
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c( "area_0_km2", "area_1_km2", "area_2_km2", "area_3_km2"))
 
-data_final_nlp_bis2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
+data_final_nlp2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
   distinct(id_unique, .keep_all = TRUE)
 
-saveRDS(data_final_nlp_bis2, file="data/data_rds/data_final_nlp_bis2.rds")
+saveRDS(data_final_nlp2, file="data/data_rds/data_final_nlp2.rds")
 ```
@@
 ```{r}
-data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")
+data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")
 
 #remove too long variables for stata
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(dist_cap_ncap_quint_mean_norm_all, dist_cap_sndncap_quint_max_norm_all, dist_cap_sndncap_quint_mean_norm_all, dist_cap_sndncap_dec_max_norm_all, dist_cap_sndncap_dec_mean_norm_all))
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c("lis_region", "pop_region", "night_region", "lis_region_pot", "lis_region_log", "pop_region_log", "night_region_log"))
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(lis_region = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(lis_region_pot = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c("pres_adm1", "pres_adm2"))
 
-data_final_nlp_bis2 %<>% left_join(results, by=c("iso", "round"))
-
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>% left_join(results, by=c("iso", "round"))
+
+data_final_nlp2 %<>%
   mutate(pres_adm1=ifelse(NAME_1_pres==NAME_1, 1, 0))
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-geometry)
@@
 #individual variables
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(age = na_if(age, -1) %>% na_if(998) %>% na_if(999))%>%
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
  group_by(id_unique)%>%
@@
 #cluster variables
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(country_round=as.numeric(paste0(round,ccode)))
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(spl=if_else(iso%in%cty_sample, 1, 0))
@@
 
-data_final_nlp_bis2 %<>% left_join(data_color, by="iso")
+data_final_nlp2 %<>% left_join(data_color, by="iso")
 rm(data_color)
@@
 
-data_final_nlp_bis2 %<>% left_join(juriglobe, by="iso")
+data_final_nlp2 %<>% left_join(juriglobe, by="iso")
 
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-geometry)
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c("gdppc", "gdppc_log", "cor_index", "area", "area_log", "pop"))
 
-data_final_nlp_bis2 %<>% left_join(var_cty, by = "iso")
-
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>% left_join(var_cty, by = "iso")
+
+data_final_nlp2 %<>%
 mutate(cor_index = case_when(
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(gdppc = case_when(
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(pop = case_when(
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
 mutate(area = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(cor_2012, cor_2015, cor_2017, cor_2020, gdpcap_2012, gdpcap_2015, gdpcap_2017, gdpcap_2020, pop_2012, pop_2015, pop_2017, pop_2020, area_2012, area_2015, area_2017, area_2020))
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(gdppc_log=log(gdppc+1))%>%
@@
 
-countries <- unique(data_final_nlp_bis2$iso)
+countries <- unique(data_final_nlp2$iso)
 
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c( "med_self_censor", "citiz_self_censor", "fh_med_index", "vdem_med_corrupt", "vdem_polyarchy"))
 
-data_final_nlp_bis2 %<>% left_join(qog, by=c("iso", "round"))
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 %<>% left_join(qog, by=c("iso", "round"))
+
+data_final_nlp2%<>%
   mutate(color_num = as.numeric(factor(color)))
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(gov_num = as.numeric(factor(gov_type)))
@@
 
-data_final_nlp_bis2%<>%select(-sex)
+data_final_nlp2%<>%select(-sex)
 
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   left_join(afro_stack, by="id_unique")
@@
 
-data_final_nlp_bis2%<>%select(-c("rural", "bin_rural"))
+data_final_nlp2%<>%select(-c("rural", "bin_rural"))
 
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c("vote_party", "vote_oppo"))
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w8, by="id_unique")
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w8, by="id_unique")
 
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(vote_party = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(vote_party.y, vote_party.x))
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(vote_party = case_when(
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(vote_party = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
 mutate(vote_party = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c("year_of_election", "date_of_election", "winner"))
@@
 
-data_final_nlp_bis2 %<>% left_join(data_elections_R, by=c("iso","round"))
-
-data_final_nlp_bis2$vote_party <- as.numeric(zap_labels(data_final_nlp_bis2$vote_party))
-
-data_final_nlp_bis2$vote_oppo <- ifelse(data_final_nlp_bis2$winner!=data_final_nlp_bis2$vote_party, 1,0)
+data_final_nlp2 %<>% left_join(data_elections_R, by=c("iso","round"))
+
+data_final_nlp2$vote_party <- as.numeric(zap_labels(data_final_nlp2$vote_party))
+
+data_final_nlp2$vote_oppo <- ifelse(data_final_nlp2$winner!=data_final_nlp2$vote_party, 1,0)
 ```
@@
 
-data_final_nlp_bis2 <- readRDS("data/data_rds/data_final.rds")
+data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")
 
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(growth_country = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(growth_country.y, growth_country.x))
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(growth_country = case_when(
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(growth_country = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
 mutate(growth_country = if_else(growth_country %in% c(1, 2, 3, 4, 5), growth_country, NA_integer_))
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
   mutate(across(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
    group_by(id_unique)%>%
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
 mutate(corr_level = if_else(corr_level %in% c(1, 2, 3, 4, 5), corr_level, NA_integer_))
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
 mutate(corr_parl_a = if_else(corr_parl %in% c(0, 1, 2, 3), corr_parl, NA_integer_))%>%
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   group_by(id_unique)%>%
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(perf_poor = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(perf_poor.y, perf_poor.x))
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(perf_poor = case_when(
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w5, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(perf_poor = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
 mutate(perf_poor = if_else(perf_poor %in% c(1, 2, 3, 4), perf_poor, NA_integer_))
@@
 ```{r}
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_feelnat = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(check_citiz_a = if_else(check_citiz %in% c(1, 2, 3, 4, 5), check_citiz, NA_integer_))%>%
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
   mutate(bin_check_citiz = case_when(
@@
 
-data_final_nlp_bis2 %<>%
+data_final_nlp2 %<>%
   mutate(bin_check_parl = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(assoc_a = if_else(assoc %in% c(0, 1, 2, 3), assoc, NA_integer_))%>%
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(elec_fair_a = if_else(elec_fair %in% c(1, 2, 3, 4), elec_fair, NA_integer_))%>%
@@
 
-data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")
+
+data_final_nlp2%<>%
   mutate(trust_gen_a=if_else(trust_gen%in%c(0,1), trust_gen, NA_integer_))
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(extent_a = if_else(extent %in% c(1, 2, 3, 4), extent, NA_integer_))%>%
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_corr_parl_a = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_corr_pres_a = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_trust_parl_a = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_trust_pres_a = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_pol_trust_2 = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_pol_corr_2 = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   group_by(latitude, longitude)%>%
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(region = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_growth_country = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_internet_news = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_paper_news = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_radio_news = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_tele_news = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_sm_news = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_internet_use = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(bin_disc_pol_a = case_when(
@@
 ```{r}
-data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")
+data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")
 
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w7, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(neig_eth = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   select(-c(neig_eth.y, neig_eth.x))
@@
 
-data_final_nlp_bis2 <- left_join(data_final_nlp_bis2, afro_w6, by="id_unique")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")
+
+data_final_nlp2%<>%
   mutate(neig_eth = case_when(
@@
 
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(neig_eth_a = if_else(neig_eth %in% c(1, 2, 3, 4, 5), neig_eth, NA_integer_))
@@
 ```{r}
-data_final_nlp_bis2%<>%
+data_final_nlp2%<>%
   mutate(dist_cap_10=dist_cap/10,
@@
 ```{r}
-data_final_nlp_bis2 <- readRDS("data/data_rds/data_final_r.rds")
-
-data_final_nlp_bis2%<>%
+data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")
+
+data_final_nlp2%<>%
   group_by(NAME_2, round)%>%
@@
 ```{r}
-table(data_final_nlp_bis2$neig_eth_a)
-hist(data_final_nlp_bis2$neig_eth_a)
+table(data_final_nlp2$neig_eth_a)
+hist(data_final_nlp2$neig_eth_a)
 ```
@@
 ```{r}
-saveRDS(data_final_nlp_bis2, file="data/data_rds/data_final_r.rds")
-
-write_dta(data_final_nlp_bis2, "data/data_dta/data_final_r.dta")
-```
+saveRDS(data_final_nlp2, file="data/data_rds/data_final_r.rds")
+
+write_dta(data_final_nlp2, "data/data_dta/data_final_r.dta")
+```

### 2025-03-14 script/r/discontinuity.Rmd
maj

--- 2025-02-24 script/discontinuity_w8.Rmd
@@
 ```{r}
-# Data manipulation and utility
-library(dplyr)      # Data manipulation
-library(readr)      # Data import/export
-library(magrittr)   # Pipe operator (%>%)
-
-# Statistical analysis and modeling
-library(estimatr)   # Robust regression
-library(car)        # Companion to Applied Regression (e.g., recoding variables)
-
-# Visualization
-library(ggplot2)    # Plotting
-library(texreg)     # Exporting regression results to LaTeX/HTML
-
-# Spatial and geospatial analysis
-library(sf)         # Simple Features for R
-library(geosphere)  # Geospatial functions
-library(rnaturalearth)     # Natural Earth map data
-library(rnaturalearthdata) # Data for rnaturalearth
-
-# Specialized packages
-library(rdrobust)   # Regression discontinuity designs
-library(murdock)    # Specific package, assuming you have a need for it
-
-library(haven)
-
 setwd("~/working_paper/trust/")
 getwd()
+
+library(dplyr)
+library(readr)
+library(magrittr)
+library(ggplot2)
+library(sf)
+library(rnaturalearth)
+library(murdock)
+library(haven)
 ```
@@
 ```{r}
-# Load the Murdock ethnic groups map (1956)
 murdock <- murdock::murdock
-
-# Convert the Murdock map to an 'sf' (Simple Features) object for spatial data manipulation
 murdock_sf <- st_as_sf(murdock)
 
-# Define a set of African countries of interest by specifying their names
 countries <- ne_countries(country = c("Benin","Botswana","Burkina Faso","Cameroon","Ivory Coast",
@@
 
-# Convert the selected countries into an 'sf' object for spatial operations
 countries_sf <- st_as_sf(countries)
 
-# Extract the individual boundaries of the selected African countries
 boundaries <- st_boundary(countries_sf)
@@
 
-ggsave("plots/discontinuity/murdock_map.jpg", width = 10, height = 6, dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_map.jpg", width = 10, height = 6, dpi = 300)
 
-# Create a 50km buffer around the African country borders
 buffer <- st_buffer(boundaries, dist = 25000)
 
-# Plot the Murdock map with the 25km buffers around the African borders
 ggplot() +
-  geom_sf(data = murdock_sf, fill = "transparent", color = "black", size = 1) + # Murdock map in black
-  geom_sf(data = buffer, color = "red", lwd = 1.5) + # 25km buffer around borders in red
-  theme_minimal() +
-  ggtitle("25km Buffer of African Borders and Murdock Ethnic Zones (1956)")
+  geom_sf(data = murdock_sf, aes (color="Murdock"), fill = "transparent", size = 1) + # Murdock map in black
+  geom_sf(data = buffer, aes(color = "boundaries"), lwd = 1) + # 25km buffer around borders in red
+  scale_color_manual(
+    values = c("Murdock" = "black", "boundaries" = "red"),
+    labels = c("25km boundaries", "Historical Ethnic Areas"),
+    name = NULL 
+  ) +
+  theme_minimal(base_size = 15) +
+  theme(
+    panel.grid.major = element_blank(),  
+    panel.grid.minor = element_blank(),  
+    panel.background = element_blank(),   
+    axis.text = element_blank(),         
+    axis.ticks = element_blank(),         
+    axis.title = element_blank(),         
+    legend.key = element_rect(fill = "transparent", color = NA),
+    legend.text = element_text(size = 8),
+    legend.position = c(0.25, 0.35)
+  )
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_map.jpg", width = 10, height = 6, dpi = 300)
 ```
@@
 ```{r}
-# List of countries of interest
 countries <- c("Benin","Botswana","Burkina Faso","Cameroon","Ivory Coast",
@@
 
-# Buffer distances
 buffer_distances <- c(50000, 40000, 30000, 25000, 20000, 15000, 10000)
@@
 }
-
-# List of objects to keep
-objects_to_keep <- c("data_trust_test", "union_list", "murdock_sf", "countries", "countries_sf", "buffer", "buffer_distances")
-
-# Get all objects in the current environment
-
-# Determine which objects to remove
-
-# Remove the unnecessary objects
 
@@
 ggplot() +
-  geom_sf(data = murdock_sf, fill = "transparent", color = "black", size = 1) +
-  geom_sf(data = unions_list[["20000"]], color = "red", lwd=1, fill="transparent") +  # 25km buffer
+  geom_sf(data = murdock_sf, fill = "transparent", aes(color = "Murdock"), size = 1) +
+  geom_sf(data = unions_list[["25000"]], aes(color = "boundaries"), lwd=1, fill="transparent") +
+  scale_color_manual(
+    values = c("Murdock" = "black", "boundaries" = "red"),
+    labels = c("25km boundaries", "Historical Ethnic Areas"),
+    name = NULL 
+  ) +
   theme_minimal(base_size = 15) +
@@
 
-ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)
-
-# List of objects to keep
-objects_to_keep <- c("data_trust_test", "unions_list", "murdock_sf")
-
-# Get all objects in the current environment
-
-# Determine which objects to remove
-
-# Remove the unnecessary objects
+ggsave("buffer_25.jpg", width = 10, height = 6, dpi = 300)
 
@@
 ```{r}
-# Load data
-data_trust_test <- readRDS("data/data_rds/data_final_r.rds")
+data_trust_test <- readRDS("data/data_rds/data_27_02_25.rds")
+data_trust_test%<>%
+  ungroup()
+
 bdd_geo <- read_csv("data/data_raw/bdd_geo_w8.csv")
 
-# Merge and clean data
 data_trust_test %<>%
+  filter(spl==1)%>%
   left_join(bdd_geo, by = "id_unique") %>%
@@
 
-# Convert to spatial data and filter by borders
 border_sample_50_union <- unions_list[["50000"]]
@@
 filtered_data_list <- filter_by_border(data_trust_test_sf, borders)
+
 names(filtered_data_list) <- c("50", "40", "30", "25", "20", "15", "10")
-
-# Remove border polygons
-rm(list = names(borders))
+sapply(filtered_data_list, nrow)
 
@@
 
-# List of objects to keep
-objects_to_keep <- c("df_list", "data_trust_test")
-
-# Get all objects in the current environment
-
-# Determine which objects to remove
-
-# Remove the unnecessary objects
-
 ```
@@
 capitals <- data_trust_test %>%
-  select(caplong, caplat, iso) %>%
+  distinct(caplong, caplat, iso)%>%
   na.omit() %>%
@@
 ggsave("plots/map/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
-
-#selected_countries <- countries %>% 
- # filter(iso_a3 %in% c("BEN", "NER"))
-
-#selected_individuals <- individuals %>%
- # filter(iso%in% c("BEN", "NER"))
-
-#selected_capitals <- capitals %>%
- # filter(iso%in% c("BEN", "NER"))
-
-#test <- murdock_sf%>%
-#  distinct(NAME)
-
-#selected_murdock <- murdock_sf%>%
-#  filter(NAME=="DENDI")
-
-#test <- unions_list[["20000"]]
-
-#test %<>%
- # filter(iso%in%c("BEN", "NER"))
-
-# Create the plot
-#ggplot() +
-  # Base map with country borders
-#    geom_sf(data = selected_countries, fill = "white", color = "black") +
-#  geom_sf(data = selected_murdock, fill = "green", color = "darkgreen", size = 1, alpha=0.5) +
-  # Use theme_void to create a clean background
- # theme_void() + 
-  # Adding capital cities with refined aesthetics
-#  geom_point(data = selected_capitals, 
-   #          aes(x = longitude, y = latitude, color = "Capitals"), 
-  #           size = 2, shape = 22, fill = "red", show.legend = FALSE) +
-
-#geom_label(aes(x = 2.5, y = 10, label = "Benin"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
- #     geom_label(aes(x = 4, y = 14.5, label = "Niger"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
-
-#geom_text(aes(x = 2.4, y = 13.75, label = "Niamey"), color = "black", size = 5) +
-#geom_text(aes(x = 2.2, y = 6.6, label = "Porto-Novo"), color = "black", size = 5) +
-
-#  labs(color = NULL) +
- #   coord_sf(xlim = c(0, 5), ylim = c(6, 18), expand = FALSE)
-
-# Save the plot if needed
-#ggsave("writing/presentation/bdd_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
-
-# List of objects to keep
-objects_to_keep <- c("df_list")
-
-# Get all objects in the current environment
-
-# Determine which objects to remove
-
-# Remove the unnecessary objects
-
 ```
@@
 
-# Apply the function to each data frame in the list with respective thresholds
 df_list <- lapply(names(df_list), function(name) {
@@
 
-# Update the names of the list to match the original names
 names(df_list) <- c("df_50", "df_40", "df_30", "df_25", "df_20", "df_15", "df_10")
@@
 
-# Apply the function to each data frame in the list
 df_list <- lapply(df_list, convert_labelled_to_factors)
 
-# Optionally, update list names if needed
 names(df_list) <- c("df_50", "df_40", "df_30", "df_25", "df_20", "df_15", "df_10")
-
-rm("convert_labelled_to_factors", "process_df")
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_50[list_columns] <- lapply(df_50[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_50, "data/data_dta/df_50.dta")
-
-df_50 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_50 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_50, file="data/data_rds/df_50_2.rds")
-
-write_dta(df_50, "data/data_dta/df_50_2.dta")
-
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_40[list_columns] <- lapply(df_40[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_40, "data/data_dta/df_40.dta")
-
-df_40 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_40 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_40, file="data/data_rds/df_40_2.rds")
-
-write_dta(df_40, "data/data_dta/df_40_2.dta")
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_30[list_columns] <- lapply(df_30[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_30, "data/data_dta/df_30.dta")
-
-df_30 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_30 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_30, file="data/data_rds/df_30_2.rds")
-
-write_dta(df_30, "data/data_dta/df_30_2.dta")
-
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_25[list_columns] <- lapply(df_25[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_25, "data/data_dta/df_25.dta")
-
-df_25 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_25 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_25, file="data/data_rds/df_25_2.rds")
-
-write_dta(df_25, "data/data_dta/df_25_2.dta")
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_20[list_columns] <- lapply(df_20[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_20, "data/data_dta/df_20.dta")
-
-df_20 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_20 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_20, file="data/data_rds/df_20_2.rds")
-
-write_dta(df_20, "data/data_dta/df_20_2.dta")
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_15[list_columns] <- lapply(df_15[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_15, "data/data_dta/df_15.dta")
-
-df_15 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_15 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_15, file="data/data_rds/df_15_2.rds")
-
-write_dta(df_15, "data/data_dta/df_15_2.dta")
 ```
@@
 
-# Handle list columns by converting them to strings (or you could flatten or remove them as needed)
 df_10[list_columns] <- lapply(df_10[list_columns], function(x) sapply(x, toString))
@@
 write_dta(df_10, "data/data_dta/df_10.dta")
-
-df_10 %<>%
-  group_by(murdock_round) %>%
-  filter(n_distinct(iso) >= 2)%>%
-ungroup()
-
-df_10 %<>%
-  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))
-
-saveRDS(df_10, file="data/data_rds/df_10_2.rds")
-
-write_dta(df_10, "data/data_dta/df_10_2.dta")
 ```

### 2025-03-14 script/r/discontinuity_plot.Rmd
maj

@@
             method = "lm", formula = y ~ poly(x, 3), 
-            color = "navy", size = 1.2, se = TRUE,
-            fill="navy",
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill="firebrick",
             alpha=0.1,
@@
             method = "lm", formula = y ~ poly(x, 3), 
-            color = "firebrick", size = 1.2, se = TRUE,
-            fill = "firebrick",
+            color = "darkgreen", size = 1.2, se = TRUE,
+            fill = "darkgreen",
             alpha = 0.1,
@@
              inherit.aes = FALSE,
-             color = "navy", size = 1.5, alpha = 0.7, data = data.frame()) + 
+             color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) + 
   geom_segment(aes(x = 0, 
@@
                inherit.aes = FALSE,
-               color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) +
+               color = "darkgreen", size = 1.5, alpha = 0.7, data = data.frame()) +
 
@@
            label = "Close to the Capital", 
-           size = 7, fill = "aliceblue", color = "navy", fontface = "bold", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
            label.size = 0.5, family = "Arial") +
@@
            label = "Far from the Capital", 
-           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           size = 7, fill = "honeydew", color = "darkgreen", fontface = "bold", 
            label.size = 0.5, family = "Arial") +
@@
   scale_linetype_manual(name = NULL, 
-                        values = c("Far" = "dashed", 
-                                  "Close" = "dashed"),
+                        values = c("Close" = "dashed","Far" = "dashed"),
                         labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
@@
 
-ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity2.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
 ```

### 2025-03-14 script/r/discontinuity_plot.Rmd
maj

@@
   # Add vertical line at border
-  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.8) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +
 
@@
   # Format axes
-  scale_x_continuous(labels = function(x) x / 1000,
+scale_x_continuous(labels = function(x) abs(x) / 1000,
                      breaks = seq(-40000, 40000, 10000)) +  
-
   # Add clear labels
@@
       y = "Political Trust") +
-      #title = "Border Discontinuity in Political Trust",
-      #subtitle = "Comparing areas close to vs. far from the capital") +
 
   # Polish theme
-  theme_minimal()+
+theme_minimal() +
   theme(
@@
     plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
-    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 30)),
-    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 30)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
     axis.text = element_text(size = 11),
+    axis.ticks = element_line(color = "black"),  # Keep the ticks
+    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
+    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
     legend.position = c(0.85, 0.2),
@@
     legend.text = element_text(size = 20),
-    panel.grid.major = element_line(color = "gray90"),
-    panel.grid.minor = element_blank(),
-    plot.margin = margin(t = 20, r = 20, b = 20, l = 20)
+    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
+    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
+    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
+    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
+    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
   )
 
-ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity2.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
 ```

### 2025-03-14 script/r/discontinuity.Rmd
clean and maj

@@
 ggplot() +
-  geom_sf(data = murdock_sf, aes (color="Murdock"), fill = "transparent", size = 1) + # Murdock map in black
-  geom_sf(data = buffer, aes(color = "boundaries"), lwd = 1) + # 25km buffer around borders in red
+  geom_sf(data = murdock_sf, aes (color="Murdock"), fill = "transparent", size = 1) +
+  geom_sf(data = buffer, aes(color = "boundaries"), lwd = 1) +
   scale_color_manual(
@@
 
-ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_map.jpg", width = 10, height = 6, dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries.jpg", width = 10, height = 6, dpi = 300)
 ```
@@
 }
-
 ```
@@
 
-ggsave("buffer_25.jpg", width = 10, height = 6, dpi = 300)
-
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_inter.jpg", width = 10, height = 6, dpi = 300)
 ```
@@
 ```{r}
-data_trust_test <- readRDS("data/data_rds/data_27_02_25.rds")
-data_trust_test%<>%
+data <- readRDS("data/data_rds/data_27_02_25.rds")
+data%<>%
   ungroup()
@@
 
-data_trust_test %<>%
+data %<>%
   filter(spl==1)%>%
@@
 
-data_trust_test_sf <- st_as_sf(data_trust_test, coords = c("longitude", "latitude"), crs = st_crs(border_sample_50_union))
+data_sf <- st_as_sf(data, coords = c("longitude", "latitude"), crs = st_crs(border_sample_50_union))
 
@@
 # Filter data
-filtered_data_list <- filter_by_border(data_trust_test_sf, borders)
+filtered_data_list <- filter_by_border(data_sf, borders)
 
@@
 
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_inter_spl.jpg", width = 10, height = 6, dpi = 300)
 ```
@@
 # Prepare data
-individuals <- data_trust_test %>%
+individuals <- data %>%
   select(longitude, latitude, iso) %>%
@@
 
-capitals <- data_trust_test %>%
+capitals <- data %>%
   distinct(caplong, caplat, iso)%>%
@@
 
-ggsave("plots/map/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/cty_spl.jpg", width = 10, height = 6, dpi = 300)
+```
+
+```{r}
+selected_countries <- countries %>% 
+ filter(iso_a3 %in% c("BEN", "NER"))
+
+selected_capitals <- capitals %>%
+ filter(iso%in% c("BEN", "NER"))
+
+selected_murdock <- murdock_sf%>%
+  filter(NAME=="DENDI")
+
+ggplot() +
+   geom_sf(data = selected_countries, fill = "white", color = "black") +
+geom_sf(data = selected_murdock, fill = "green", color = "darkgreen", size = 1, alpha=0.5) +
+ theme_void() + 
+geom_point(data = selected_capitals, 
+          aes(x = longitude, y = latitude, color = "Capitals"), 
+         size = 2, shape = 22, fill = "red", show.legend = FALSE) +
+
+geom_label(aes(x = 2.5, y = 10, label = "Benin"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
+     geom_label(aes(x = 4, y = 14.5, label = "Niger"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
+
+geom_text(aes(x = 2.4, y = 13.75, label = "Niamey"), color = "black", size = 5) +
+geom_text(aes(x = 2.2, y = 6.6, label = "Porto-Novo"), color = "black", size = 5) +
+
+  labs(color = NULL) +
+   coord_sf(xlim = c(0, 5), ylim = c(6, 18), expand = FALSE)
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/benin_niger.jpg", width = 10, height = 10, dpi = 300)
 ```

### 2025-03-14 script/r/discontinuity_plot.Rmd
add discontinuity plots 20-50km

@@
 
+#50km
+
+```{r}
+df_50 <- read_dta("data/data_dta/df_50.dta")
+
+df_50 <- na.omit(subset(df_50, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))
+
+reg3_50 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv + factor(bin_unfair_eth), clusters = cluster_bdd, data = df_50)
+
+summary(reg3_50)
+
+df_50$ft_values <- fitted(reg3_50)
+```
+
+```{r}
+#Pour les gens près de la capitale (sous la médiane), on rend la distance à la frontière négative (cf. on multiplie par -1)
+df_50$distance_border <- ifelse(df_50$dist_cap_max_norm<median(df_50$dist_cap_max_norm),
+                                       -df_50$distance_border,df_50$distance_border)
+
+#On crée une base avec les gens près et une avec les gens loin
+df_50_pres <- subset(df_50, df_50$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
+df_50_loin <- subset(df_50, df_50$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
+
+#On définit 10 intervalles
+nb_intervals <- 50
+
+#On découpe les deux bases en 10 intervalles
+intervals_dist_border_pres <- cut(df_50_pres$distance_border, breaks = nb_intervals)
+intervals_dist_border_loin <- cut(df_50_loin$distance_border, breaks = nb_intervals)
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base près
+mean_dist_border_intervals_pres <- data.frame(tapply(df_50_pres$distance_border, intervals_dist_border_pres, mean))
+mean_trust_intervals_pres <- data.frame(tapply(df_50_pres$ft_values, intervals_dist_border_pres, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_pres) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_pres) <- "mean_trust_intervals"
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base loin
+mean_dist_border_intervals_loin <- data.frame(tapply(df_50_loin$distance_border, intervals_dist_border_loin, mean))
+mean_trust_intervals_loin <- data.frame(tapply(df_50_loin$ft_values, intervals_dist_border_loin, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_loin) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_loin) <- "mean_trust_intervals"
+
+#On fussionne les bases près et loin
+mean_dist_border_intervals <- rbind(mean_dist_border_intervals_pres,mean_dist_border_intervals_loin)
+mean_trust_intervals <- rbind(mean_trust_intervals_pres,mean_trust_intervals_loin)
+
+data_intervals <- cbind(mean_dist_border_intervals,mean_trust_intervals)
+
+#Les intervalles de confiance pour le trust
+lower_distance_fun <- function(x) {
+  mean_val <- mean(x)
+  conf_int <- t.test(x)$conf.int
+  ic95_ <- abs(conf_int[1] - mean_val)
+  ic95_
+}
+
+#On fait les intervalles de confiance pour chaque intervalle (50 en tout, 10 près + 10 loin)
+mean_trust_intervals_pres_ic <- data.frame(tapply(df_50_pres$ft_values, intervals_dist_border_pres, lower_distance_fun))
+mean_trust_intervals_loin_ic <- data.frame(tapply(df_50_loin$ft_values, intervals_dist_border_loin, lower_distance_fun))
+colnames(mean_trust_intervals_pres_ic) <- "ic_trust"
+colnames(mean_trust_intervals_loin_ic) <- "ic_trust"
+
+#On met toutes les intervalles dans la même base
+mean_trust_intervals_ic <- rbind(mean_trust_intervals_pres_ic,mean_trust_intervals_loin_ic)
+
+data_intervals_ic <- cbind(data_intervals,mean_trust_intervals_ic)
+
+#Les moyenne près/loin pour les lignes sur le graph
+moy_trust_pres <- mean(df_50_pres$ft_values)
+moy_trust_loin <- mean(df_50_loin$ft_values)
+
+```
+
+```{r}
+# Create modified datasets with points at the boundary and extremes
+data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
+data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)
+
+# Find the min and max values in your x range
+x_min <- -50000  # -50 km in your units
+x_max <- 50000   # 50 km in your units
+
+# Find the predicted values at x=0, x_min, and x_max for each curve
+left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
+right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)
+
+y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))
+
+y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))
+
+# Average confidence interval for the added points
+avg_ic_left <- mean(data_left$ic_trust)
+avg_ic_right <- mean(data_right$ic_trust)
+
+# Add points at x=0 and x=x_min to left dataset
+data_left_plus <- rbind(data_left, 
+                        data.frame(
+                          mean_dist_border_intervals = 0,
+                          mean_trust_intervals = y_at_zero_left,
+                          ic_trust = avg_ic_left
+                        ),
+                        data.frame(
+                          mean_dist_border_intervals = x_min,
+                          mean_trust_intervals = y_at_min,
+                          ic_trust = avg_ic_left
+                        ))
+
+# Add points at x=0 and x=x_max to right dataset
+data_right_plus <- rbind(data_right, 
+                         data.frame(
+                           mean_dist_border_intervals = 0,
+                           mean_trust_intervals = y_at_zero_right,
+                           ic_trust = avg_ic_right
+                         ),
+                         data.frame(
+                           mean_dist_border_intervals = x_max,
+                           mean_trust_intervals = y_at_max,
+                           ic_trust = avg_ic_right
+                         ))
+```
+
+```{r}
+ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
+  # Add vertical line at border
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +
+
+  # Left side smooth curve (Close to Capital)
+# Left side smooth curve (Close to Capital)
+geom_smooth(data = data_left_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill="firebrick",
+            alpha=0.1,
+            level = 0.90, show.legend = FALSE) +
+
+# Right side smooth curve (Far from Capital)
+geom_smooth(data = data_right_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "darkgreen", size = 1.2, se = TRUE,
+            fill = "darkgreen",
+            alpha = 0.1,
+            level = 0.90, show.legend = FALSE)+
+
+geom_segment(aes(x = -50000, 
+                   xend = 0,
+                   y = moy_trust_pres, 
+                   yend = moy_trust_pres, linetype = "Close"),
+             inherit.aes = FALSE,
+             color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) + 
+  geom_segment(aes(x = 0, 
+                   xend =50000, 
+                   y = moy_trust_loin, 
+                   yend = moy_trust_loin, linetype = "Far"),
+               inherit.aes = FALSE,
+               color = "darkgreen", size = 1.5, alpha = 0.7, data = data.frame()) +
+
+  # Add annotations in better positions with borders
+
+  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Close to the Capital", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Far from the Capital", 
+           size = 7, fill = "honeydew", color = "darkgreen", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+
+  # Add legend for mean lines
+  scale_linetype_manual(name = NULL, 
+                        values = c("Close" = "dashed","Far" = "dashed"),
+                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
+
+  # Set appropriate axis limits
+  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
+                          max(abs(data_intervals$mean_dist_border_intervals))),
+                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
+                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +
+
+  # Format axes
+scale_x_continuous(labels = function(x) abs(x) / 1000,
+                     breaks = seq(-50000, 50000, 10000)) +  
+  # Add clear labels
+  labs(x = "Distance from the Border (in km)",
+      y = "Political Trust") +
+
+  # Polish theme
+theme_minimal() +
+  theme(
+    text = element_text(family = "Arial"),
+    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)),
+    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
+    axis.text = element_text(size = 11),
+    axis.ticks = element_line(color = "black"),  # Keep the ticks
+    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
+    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
+    legend.position = c(0.85, 0.2),
+    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 20),
+    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
+    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
+    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
+    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
+    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
+  )
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity_50.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+```
+
+```{r}
+# Check sample sizes
+n_far <- nrow(df_50_loin)
+n_close <- nrow(df_50_pres)
+cat("Sample sizes:\nFar from capital:", n_far, "\nClose to capital:", n_close, "\n")
+
+# Check variance in trust values
+var_far <- var(df_50_loin$ft_values)
+var_close <- var(df_50_pres$ft_values)
+cat("\nVariance in trust values:\nFar from capital:", round(var_far, 4), 
+    "\nClose to capital:", round(var_close, 4))
+
+# Check mean number of observations per interval
+mean_obs_per_interval_far <- mean(table(intervals_dist_border_loin))
+mean_obs_per_interval_close <- mean(table(intervals_dist_border_pres))
+cat("\n\nMean observations per interval:\nFar from capital:", 
+    round(mean_obs_per_interval_far, 2),
+    "\nClose to capital:", round(mean_obs_per_interval_close, 2))
+```
+
+#40km
+
 ```{r}
 df_40 <- read_dta("data/data_dta/df_40.dta")
-
-df_40%<>%
-  group_by(id_unique)%>%
-  mutate(mountain_region_tv=mountain_region*tv,
-         desert_region_tv=desert_region*tv) %>%
-  ungroup()
 
@@
 reg3_40 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
-                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv, clusters = cluster_bdd, data = df_40)
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv + factor(bin_unfair_eth), clusters = cluster_bdd, data = df_40)
 
@@
 
-ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity_40.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
 ```
@@
 ```
+
+#30km
+
+```{r}
+df_30 <- read_dta("data/data_dta/df_30.dta")
+
+df_30 <- na.omit(subset(df_30, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))
+
+reg3_30 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv + factor(bin_unfair_eth), clusters = cluster_bdd, data = df_30)
+
+summary(reg3_30)
+
+df_30$ft_values <- fitted(reg3_30)
+```
+
+```{r}
+#Pour les gens près de la capitale (sous la médiane), on rend la distance à la frontière négative (cf. on multiplie par -1)
+df_30$distance_border <- ifelse(df_30$dist_cap_max_norm<median(df_30$dist_cap_max_norm),
+                                       -df_30$distance_border,df_30$distance_border)
+
+#On crée une base avec les gens près et une avec les gens loin
+df_30_pres <- subset(df_30, df_30$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
+df_30_loin <- subset(df_30, df_30$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
+
+#On définit 10 intervalles
+nb_intervals <- 30
+
+#On découpe les deux bases en 10 intervalles
+intervals_dist_border_pres <- cut(df_30_pres$distance_border, breaks = nb_intervals)
+intervals_dist_border_loin <- cut(df_30_loin$distance_border, breaks = nb_intervals)
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base près
+mean_dist_border_intervals_pres <- data.frame(tapply(df_30_pres$distance_border, intervals_dist_border_pres, mean))
+mean_trust_intervals_pres <- data.frame(tapply(df_30_pres$ft_values, intervals_dist_border_pres, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_pres) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_pres) <- "mean_trust_intervals"
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base loin
+mean_dist_border_intervals_loin <- data.frame(tapply(df_30_loin$distance_border, intervals_dist_border_loin, mean))
+mean_trust_intervals_loin <- data.frame(tapply(df_30_loin$ft_values, intervals_dist_border_loin, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_loin) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_loin) <- "mean_trust_intervals"
+
+#On fussionne les bases près et loin
+mean_dist_border_intervals <- rbind(mean_dist_border_intervals_pres,mean_dist_border_intervals_loin)
+mean_trust_intervals <- rbind(mean_trust_intervals_pres,mean_trust_intervals_loin)
+
+data_intervals <- cbind(mean_dist_border_intervals,mean_trust_intervals)
+
+#Les intervalles de confiance pour le trust
+lower_distance_fun <- function(x) {
+  mean_val <- mean(x)
+  conf_int <- t.test(x)$conf.int
+  ic95_ <- abs(conf_int[1] - mean_val)
+  ic95_
+}
+
+#On fait les intervalles de confiance pour chaque intervalle (30 en tout, 10 près + 10 loin)
+mean_trust_intervals_pres_ic <- data.frame(tapply(df_30_pres$ft_values, intervals_dist_border_pres, lower_distance_fun))
+mean_trust_intervals_loin_ic <- data.frame(tapply(df_30_loin$ft_values, intervals_dist_border_loin, lower_distance_fun))
+colnames(mean_trust_intervals_pres_ic) <- "ic_trust"
+colnames(mean_trust_intervals_loin_ic) <- "ic_trust"
+
+#On met toutes les intervalles dans la même base
+mean_trust_intervals_ic <- rbind(mean_trust_intervals_pres_ic,mean_trust_intervals_loin_ic)
+
+data_intervals_ic <- cbind(data_intervals,mean_trust_intervals_ic)
+
+#Les moyenne près/loin pour les lignes sur le graph
+moy_trust_pres <- mean(df_30_pres$ft_values)
+moy_trust_loin <- mean(df_30_loin$ft_values)
+
+```
+
+```{r}
+# Create modified datasets with points at the boundary and extremes
+data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
+data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)
+
+# Find the min and max values in your x range
+x_min <- -30000  # -30 km in your units
+x_max <- 30000   # 30 km in your units
+
+# Find the predicted values at x=0, x_min, and x_max for each curve
+left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
+right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)
+
+y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))
+
+y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))
+
+# Average confidence interval for the added points
+avg_ic_left <- mean(data_left$ic_trust)
+avg_ic_right <- mean(data_right$ic_trust)
+
+# Add points at x=0 and x=x_min to left dataset
+data_left_plus <- rbind(data_left, 
+                        data.frame(
+                          mean_dist_border_intervals = 0,
+                          mean_trust_intervals = y_at_zero_left,
+                          ic_trust = avg_ic_left
+                        ),
+                        data.frame(
+                          mean_dist_border_intervals = x_min,
+                          mean_trust_intervals = y_at_min,
+                          ic_trust = avg_ic_left
+                        ))
+
+# Add points at x=0 and x=x_max to right dataset
+data_right_plus <- rbind(data_right, 
+                         data.frame(
+                           mean_dist_border_intervals = 0,
+                           mean_trust_intervals = y_at_zero_right,
+                           ic_trust = avg_ic_right
+                         ),
+                         data.frame(
+                           mean_dist_border_intervals = x_max,
+                           mean_trust_intervals = y_at_max,
+                           ic_trust = avg_ic_right
+                         ))
+```
+
+```{r}
+ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
+  # Add vertical line at border
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +
+
+  # Left side smooth curve (Close to Capital)
+# Left side smooth curve (Close to Capital)
+geom_smooth(data = data_left_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill="firebrick",
+            alpha=0.1,
+            level = 0.90, show.legend = FALSE) +
+
+# Right side smooth curve (Far from Capital)
+geom_smooth(data = data_right_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "darkgreen", size = 1.2, se = TRUE,
+            fill = "darkgreen",
+            alpha = 0.1,
+            level = 0.90, show.legend = FALSE)+
+
+geom_segment(aes(x = -30000, 
+                   xend = 0,
+                   y = moy_trust_pres, 
+                   yend = moy_trust_pres, linetype = "Close"),
+             inherit.aes = FALSE,
+             color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) + 
+  geom_segment(aes(x = 0, 
+                   xend =30000, 
+                   y = moy_trust_loin, 
+                   yend = moy_trust_loin, linetype = "Far"),
+               inherit.aes = FALSE,
+               color = "darkgreen", size = 1.5, alpha = 0.7, data = data.frame()) +
+
+  # Add annotations in better positions with borders
+
+  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Close to the Capital", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Far from the Capital", 
+           size = 7, fill = "honeydew", color = "darkgreen", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+
+  # Add legend for mean lines
+  scale_linetype_manual(name = NULL, 
+                        values = c("Close" = "dashed","Far" = "dashed"),
+                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
+
+  # Set appropriate axis limits
+  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
+                          max(abs(data_intervals$mean_dist_border_intervals))),
+                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
+                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +
+
+  # Format axes
+scale_x_continuous(labels = function(x) abs(x) / 1000,
+                     breaks = seq(-30000, 30000, 10000)) +  
+  # Add clear labels
+  labs(x = "Distance from the Border (in km)",
+      y = "Political Trust") +
+
+  # Polish theme
+theme_minimal() +
+  theme(
+    text = element_text(family = "Arial"),
+    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)),
+    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
+    axis.text = element_text(size = 11),
+    axis.ticks = element_line(color = "black"),  # Keep the ticks
+    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
+    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
+    legend.position = c(0.85, 0.2),
+    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 20),
+    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
+    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
+    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
+    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
+    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
+  )
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity_30.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+```
+
+```{r}
+# Check sample sizes
+n_far <- nrow(df_30_loin)
+n_close <- nrow(df_30_pres)
+cat("Sample sizes:\nFar from capital:", n_far, "\nClose to capital:", n_close, "\n")
+
+# Check variance in trust values
+var_far <- var(df_30_loin$ft_values)
+var_close <- var(df_30_pres$ft_values)
+cat("\nVariance in trust values:\nFar from capital:", round(var_far, 4), 
+    "\nClose to capital:", round(var_close, 4))
+
+# Check mean number of observations per interval
+mean_obs_per_interval_far <- mean(table(intervals_dist_border_loin))
+mean_obs_per_interval_close <- mean(table(intervals_dist_border_pres))
+cat("\n\nMean observations per interval:\nFar from capital:", 
+    round(mean_obs_per_interval_far, 2),
+    "\nClose to capital:", round(mean_obs_per_interval_close, 2))
+```
+
+#25km
+
+```{r}
+df_25 <- read_dta("data/data_dta/df_25.dta")
+
+df_25 <- na.omit(subset(df_25, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))
+
+reg3_25 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv + factor(bin_unfair_eth), clusters = cluster_bdd, data = df_25)
+
+summary(reg3_25)
+
+df_25$ft_values <- fitted(reg3_25)
+```
+
+```{r}
+#Pour les gens près de la capitale (sous la médiane), on rend la distance à la frontière négative (cf. on multiplie par -1)
+df_25$distance_border <- ifelse(df_25$dist_cap_max_norm<median(df_25$dist_cap_max_norm),
+                                       -df_25$distance_border,df_25$distance_border)
+
+#On crée une base avec les gens près et une avec les gens loin
+df_25_pres <- subset(df_25, df_25$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
+df_25_loin <- subset(df_25, df_25$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
+
+#On définit 10 intervalles
+nb_intervals <- 25
+
+#On découpe les deux bases en 10 intervalles
+intervals_dist_border_pres <- cut(df_25_pres$distance_border, breaks = nb_intervals)
+intervals_dist_border_loin <- cut(df_25_loin$distance_border, breaks = nb_intervals)
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base près
+mean_dist_border_intervals_pres <- data.frame(tapply(df_25_pres$distance_border, intervals_dist_border_pres, mean))
+mean_trust_intervals_pres <- data.frame(tapply(df_25_pres$ft_values, intervals_dist_border_pres, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_pres) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_pres) <- "mean_trust_intervals"
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base loin
+mean_dist_border_intervals_loin <- data.frame(tapply(df_25_loin$distance_border, intervals_dist_border_loin, mean))
+mean_trust_intervals_loin <- data.frame(tapply(df_25_loin$ft_values, intervals_dist_border_loin, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_loin) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_loin) <- "mean_trust_intervals"
+
+#On fussionne les bases près et loin
+mean_dist_border_intervals <- rbind(mean_dist_border_intervals_pres,mean_dist_border_intervals_loin)
+mean_trust_intervals <- rbind(mean_trust_intervals_pres,mean_trust_intervals_loin)
+
+data_intervals <- cbind(mean_dist_border_intervals,mean_trust_intervals)
+
+#Les intervalles de confiance pour le trust
+lower_distance_fun <- function(x) {
+  mean_val <- mean(x)
+  conf_int <- t.test(x)$conf.int
+  ic95_ <- abs(conf_int[1] - mean_val)
+  ic95_
+}
+
+#On fait les intervalles de confiance pour chaque intervalle (25 en tout, 10 près + 10 loin)
+mean_trust_intervals_pres_ic <- data.frame(tapply(df_25_pres$ft_values, intervals_dist_border_pres, lower_distance_fun))
+mean_trust_intervals_loin_ic <- data.frame(tapply(df_25_loin$ft_values, intervals_dist_border_loin, lower_distance_fun))
+colnames(mean_trust_intervals_pres_ic) <- "ic_trust"
+colnames(mean_trust_intervals_loin_ic) <- "ic_trust"
+
+#On met toutes les intervalles dans la même base
+mean_trust_intervals_ic <- rbind(mean_trust_intervals_pres_ic,mean_trust_intervals_loin_ic)
+
+data_intervals_ic <- cbind(data_intervals,mean_trust_intervals_ic)
+
+#Les moyenne près/loin pour les lignes sur le graph
+moy_trust_pres <- mean(df_25_pres$ft_values)
+moy_trust_loin <- mean(df_25_loin$ft_values)
+
+```
+
+```{r}
+# Create modified datasets with points at the boundary and extremes
+data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
+data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)
+
+# Find the min and max values in your x range
+x_min <- -25000  # -25 km in your units
+x_max <- 25000   # 25 km in your units
+
+# Find the predicted values at x=0, x_min, and x_max for each curve
+left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
+right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)
+
+y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))
+
+y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))
+
+# Average confidence interval for the added points
+avg_ic_left <- mean(data_left$ic_trust)
+avg_ic_right <- mean(data_right$ic_trust)
+
+# Add points at x=0 and x=x_min to left dataset
+data_left_plus <- rbind(data_left, 
+                        data.frame(
+                          mean_dist_border_intervals = 0,
+                          mean_trust_intervals = y_at_zero_left,
+                          ic_trust = avg_ic_left
+                        ),
+                        data.frame(
+                          mean_dist_border_intervals = x_min,
+                          mean_trust_intervals = y_at_min,
+                          ic_trust = avg_ic_left
+                        ))
+
+# Add points at x=0 and x=x_max to right dataset
+data_right_plus <- rbind(data_right, 
+                         data.frame(
+                           mean_dist_border_intervals = 0,
+                           mean_trust_intervals = y_at_zero_right,
+                           ic_trust = avg_ic_right
+                         ),
+                         data.frame(
+                           mean_dist_border_intervals = x_max,
+                           mean_trust_intervals = y_at_max,
+                           ic_trust = avg_ic_right
+                         ))
+```
+
+```{r}
+ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
+  # Add vertical line at border
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +
+
+  # Left side smooth curve (Close to Capital)
+# Left side smooth curve (Close to Capital)
+geom_smooth(data = data_left_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill="firebrick",
+            alpha=0.1,
+            level = 0.90, show.legend = FALSE) +
+
+# Right side smooth curve (Far from Capital)
+geom_smooth(data = data_right_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "darkgreen", size = 1.2, se = TRUE,
+            fill = "darkgreen",
+            alpha = 0.1,
+            level = 0.90, show.legend = FALSE)+
+
+geom_segment(aes(x = -25000, 
+                   xend = 0,
+                   y = moy_trust_pres, 
+                   yend = moy_trust_pres, linetype = "Close"),
+             inherit.aes = FALSE,
+             color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) + 
+  geom_segment(aes(x = 0, 
+                   xend =25000, 
+                   y = moy_trust_loin, 
+                   yend = moy_trust_loin, linetype = "Far"),
+               inherit.aes = FALSE,
+               color = "darkgreen", size = 1.5, alpha = 0.7, data = data.frame()) +
+
+  # Add annotations in better positions with borders
+
+  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Close to the Capital", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Far from the Capital", 
+           size = 7, fill = "honeydew", color = "darkgreen", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+
+  # Add legend for mean lines
+  scale_linetype_manual(name = NULL, 
+                        values = c("Close" = "dashed","Far" = "dashed"),
+                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
+
+  # Set appropriate axis limits
+  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
+                          max(abs(data_intervals$mean_dist_border_intervals))),
+                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
+                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +
+
+  # Format axes
+scale_x_continuous(labels = function(x) abs(x) / 1000,
+                     breaks = seq(-25000, 25000, 10000)) +  
+  # Add clear labels
+  labs(x = "Distance from the Border (in km)",
+      y = "Political Trust") +
+
+  # Polish theme
+theme_minimal() +
+  theme(
+    text = element_text(family = "Arial"),
+    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)),
+    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
+    axis.text = element_text(size = 11),
+    axis.ticks = element_line(color = "black"),  # Keep the ticks
+    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
+    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
+    legend.position = c(0.85, 0.2),
+    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 20),
+    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
+    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
+    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
+    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
+    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
+  )
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity_25.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+```
+
+```{r}
+# Check sample sizes
+n_far <- nrow(df_25_loin)
+n_close <- nrow(df_25_pres)
+cat("Sample sizes:\nFar from capital:", n_far, "\nClose to capital:", n_close, "\n")
+
+# Check variance in trust values
+var_far <- var(df_25_loin$ft_values)
+var_close <- var(df_25_pres$ft_values)
+cat("\nVariance in trust values:\nFar from capital:", round(var_far, 4), 
+    "\nClose to capital:", round(var_close, 4))
+
+# Check mean number of observations per interval
+mean_obs_per_interval_far <- mean(table(intervals_dist_border_loin))
+mean_obs_per_interval_close <- mean(table(intervals_dist_border_pres))
+cat("\n\nMean observations per interval:\nFar from capital:", 
+    round(mean_obs_per_interval_far, 2),
+    "\nClose to capital:", round(mean_obs_per_interval_close, 2))
+```
+#20km
+
+```{r}
+df_20 <- read_dta("data/data_dta/df_20.dta")
+
+df_20 <- na.omit(subset(df_20, select = c("pol_trust","dist_cap_max_norm","dist_sndncap_max_norm","age","age_2","sex","educ_sec", "bin_rural","bin_conditions_eco","bin_conditions_country", "bin_emp", "night_region_log","pop_region_log", "area_region_log", "disc_pol_a", "tele_news", "paper_news", "radio_news", "bin_unfair_eth", "pres_adm1", "round", "country_round","murdock_names","cluster_bdd", "distance_border", "distance_border_km", "distance_border_km2", "distance_border_km3", "gdppc_log",  "vdem_polyarchy", "color_num", "cor_index", "area_log", "gov_num", "mountain_region_tv", "desert_region_tv")))
+
+reg3_20 <- lm_robust(pol_trust~dist_cap_max_norm+dist_sndncap_max_norm+age+age_2+factor(sex)+ factor(educ_sec) +factor(bin_rural)+
+                             factor(bin_conditions_eco)+ factor(bin_conditions_country)+ factor(bin_emp)+ disc_pol_a+ tele_news + paper_news + radio_news + night_region_log  + pop_region_log+ area_region_log+gdppc_log+vdem_polyarchy + factor(color_num)+cor_index+area_log+ factor(gov_num) + desert_region_tv + mountain_region_tv + factor(bin_unfair_eth), clusters = cluster_bdd, data = df_20)
+
+summary(reg3_20)
+
+df_20$ft_values <- fitted(reg3_20)
+```
+
+```{r}
+#Pour les gens près de la capitale (sous la médiane), on rend la distance à la frontière négative (cf. on multiplie par -1)
+df_20$distance_border <- ifelse(df_20$dist_cap_max_norm<median(df_20$dist_cap_max_norm),
+                                       -df_20$distance_border,df_20$distance_border)
+
+#On crée une base avec les gens près et une avec les gens loin
+df_20_pres <- subset(df_20, df_20$distance_border<=0)#ici c'est les 50% les plus près, donc la valeur sous 0 (voir ligne précedente)
+df_20_loin <- subset(df_20, df_20$distance_border>=0)#ici c'est les 50% les plus loin, donc la valeur au dessus de 0 (voir ligne précedente)
+
+#On définit 10 intervalles
+nb_intervals <- 20
+
+#On découpe les deux bases en 10 intervalles
+intervals_dist_border_pres <- cut(df_20_pres$distance_border, breaks = nb_intervals)
+intervals_dist_border_loin <- cut(df_20_loin$distance_border, breaks = nb_intervals)
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base près
+mean_dist_border_intervals_pres <- data.frame(tapply(df_20_pres$distance_border, intervals_dist_border_pres, mean))
+mean_trust_intervals_pres <- data.frame(tapply(df_20_pres$ft_values, intervals_dist_border_pres, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_pres) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_pres) <- "mean_trust_intervals"
+
+#On fait la moyenne par intervalle pour la distance à la frontière et le fitted trust pour la base loin
+mean_dist_border_intervals_loin <- data.frame(tapply(df_20_loin$distance_border, intervals_dist_border_loin, mean))
+mean_trust_intervals_loin <- data.frame(tapply(df_20_loin$ft_values, intervals_dist_border_loin, mean))
+
+#On renomme les colonnes
+colnames(mean_dist_border_intervals_loin) <- "mean_dist_border_intervals"
+colnames(mean_trust_intervals_loin) <- "mean_trust_intervals"
+
+#On fussionne les bases près et loin
+mean_dist_border_intervals <- rbind(mean_dist_border_intervals_pres,mean_dist_border_intervals_loin)
+mean_trust_intervals <- rbind(mean_trust_intervals_pres,mean_trust_intervals_loin)
+
+data_intervals <- cbind(mean_dist_border_intervals,mean_trust_intervals)
+
+#Les intervalles de confiance pour le trust
+lower_distance_fun <- function(x) {
+  mean_val <- mean(x)
+  conf_int <- t.test(x)$conf.int
+  ic95_ <- abs(conf_int[1] - mean_val)
+  ic95_
+}
+
+#On fait les intervalles de confiance pour chaque intervalle (20 en tout, 10 près + 10 loin)
+mean_trust_intervals_pres_ic <- data.frame(tapply(df_20_pres$ft_values, intervals_dist_border_pres, lower_distance_fun))
+mean_trust_intervals_loin_ic <- data.frame(tapply(df_20_loin$ft_values, intervals_dist_border_loin, lower_distance_fun))
+colnames(mean_trust_intervals_pres_ic) <- "ic_trust"
+colnames(mean_trust_intervals_loin_ic) <- "ic_trust"
+
+#On met toutes les intervalles dans la même base
+mean_trust_intervals_ic <- rbind(mean_trust_intervals_pres_ic,mean_trust_intervals_loin_ic)
+
+data_intervals_ic <- cbind(data_intervals,mean_trust_intervals_ic)
+
+#Les moyenne près/loin pour les lignes sur le graph
+moy_trust_pres <- mean(df_20_pres$ft_values)
+moy_trust_loin <- mean(df_20_loin$ft_values)
+
+```
+
+```{r}
+# Create modified datasets with points at the boundary and extremes
+data_left <- subset(data_intervals_ic, mean_dist_border_intervals <= 0)
+data_right <- subset(data_intervals_ic, mean_dist_border_intervals >= 0)
+
+# Find the min and max values in your x range
+x_min <- -20000  # -20 km in your units
+x_max <- 20000   # 20 km in your units
+
+# Find the predicted values at x=0, x_min, and x_max for each curve
+left_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_left)
+right_model <- lm(mean_trust_intervals ~ poly(mean_dist_border_intervals, 3), data=data_right)
+
+y_at_zero_left <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_min <- predict(left_model, newdata=data.frame(mean_dist_border_intervals=x_min))
+
+y_at_zero_right <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=0))
+y_at_max <- predict(right_model, newdata=data.frame(mean_dist_border_intervals=x_max))
+
+# Average confidence interval for the added points
+avg_ic_left <- mean(data_left$ic_trust)
+avg_ic_right <- mean(data_right$ic_trust)
+
+# Add points at x=0 and x=x_min to left dataset
+data_left_plus <- rbind(data_left, 
+                        data.frame(
+                          mean_dist_border_intervals = 0,
+                          mean_trust_intervals = y_at_zero_left,
+                          ic_trust = avg_ic_left
+                        ),
+                        data.frame(
+                          mean_dist_border_intervals = x_min,
+                          mean_trust_intervals = y_at_min,
+                          ic_trust = avg_ic_left
+                        ))
+
+# Add points at x=0 and x=x_max to right dataset
+data_right_plus <- rbind(data_right, 
+                         data.frame(
+                           mean_dist_border_intervals = 0,
+                           mean_trust_intervals = y_at_zero_right,
+                           ic_trust = avg_ic_right
+                         ),
+                         data.frame(
+                           mean_dist_border_intervals = x_max,
+                           mean_trust_intervals = y_at_max,
+                           ic_trust = avg_ic_right
+                         ))
+```
+
+```{r}
+ggplot(data_intervals_ic, aes(x = mean_dist_border_intervals, y = mean_trust_intervals)) +
+  # Add vertical line at border
+  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", size = 0.7) +
+
+  # Left side smooth curve (Close to Capital)
+# Left side smooth curve (Close to Capital)
+geom_smooth(data = data_left_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "firebrick", size = 1.2, se = TRUE,
+            fill="firebrick",
+            alpha=0.1,
+            level = 0.90, show.legend = FALSE) +
+
+# Right side smooth curve (Far from Capital)
+geom_smooth(data = data_right_plus,
+            aes(x = mean_dist_border_intervals, y = mean_trust_intervals),
+            method = "lm", formula = y ~ poly(x, 3), 
+            color = "darkgreen", size = 1.2, se = TRUE,
+            fill = "darkgreen",
+            alpha = 0.1,
+            level = 0.90, show.legend = FALSE)+
+
+geom_segment(aes(x = -20000, 
+                   xend = 0,
+                   y = moy_trust_pres, 
+                   yend = moy_trust_pres, linetype = "Close"),
+             inherit.aes = FALSE,
+             color = "firebrick", size = 1.5, alpha = 0.7, data = data.frame()) + 
+  geom_segment(aes(x = 0, 
+                   xend =20000, 
+                   y = moy_trust_loin, 
+                   yend = moy_trust_loin, linetype = "Far"),
+               inherit.aes = FALSE,
+               color = "darkgreen", size = 1.5, alpha = 0.7, data = data.frame()) +
+
+  # Add annotations in better positions with borders
+
+  annotate("label", x = -max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Close to the Capital", 
+           size = 7, fill = "mistyrose", color = "firebrick", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+  annotate("label", x = max(abs(data_intervals$mean_dist_border_intervals)) * 0.5, 
+           y = max(data_intervals_ic$mean_trust_intervals) + 0.05, 
+           label = "Far from the Capital", 
+           size = 7, fill = "honeydew", color = "darkgreen", fontface = "bold", 
+           label.size = 0.5, family = "Arial") +
+
+  # Add legend for mean lines
+  scale_linetype_manual(name = NULL, 
+                        values = c("Close" = "dashed","Far" = "dashed"),
+                        labels = c(expression(bar(y)[far]), expression(bar(y)[close]))) +
+
+  # Set appropriate axis limits
+  coord_cartesian(xlim = c(-max(abs(data_intervals$mean_dist_border_intervals)), 
+                          max(abs(data_intervals$mean_dist_border_intervals))),
+                 ylim = c(min(data_intervals_ic$mean_trust_intervals) - 0.05,
+                         max(data_intervals_ic$mean_trust_intervals) + 0.1)) +
+
+  # Format axes
+scale_x_continuous(labels = function(x) abs(x) / 1000,
+                     breaks = seq(-20000, 20000, 10000)) +  
+  # Add clear labels
+  labs(x = "Distance from the Border (in km)",
+      y = "Political Trust") +
+
+  # Polish theme
+theme_minimal() +
+  theme(
+    text = element_text(family = "Arial"),
+    plot.title = element_text(size = 25, hjust = 0.5, face = "bold", margin = margin(b = 10)),
+    plot.subtitle = element_text(size = 20, hjust = 0.5, margin = margin(b = 20)),
+    axis.title.x = element_text(size = 20, face = "bold", margin = margin(t = 25)),
+    axis.title.y = element_text(size = 20, face = "bold", margin = margin(r = 25)),
+    axis.text = element_text(size = 11),
+    axis.ticks = element_line(color = "black"),  # Keep the ticks
+    axis.ticks.length = unit(5, "pt"),  # Adjust the length of the ticks if needed
+    axis.line = element_line(color = "black"),  # Ensure the axis lines are visible
+    legend.position = c(0.85, 0.2),
+    legend.background = element_rect(fill = alpha('white'), color = "gray80"),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 20),
+    panel.grid.major.x = element_blank(),  # Remove vertical major grid lines
+    panel.grid.minor.x = element_blank(),  # Remove vertical minor grid lines
+    panel.grid.major.y = element_line(color = "gray90"),  # Keep horizontal major grid lines
+    panel.grid.minor.y = element_blank(),  # Remove horizontal minor grid lines
+    plot.margin = margin(t = 20, r = 20, b = 18, l = 18)
+  )
+
+ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/discontinuity_20.jpg", plot = last_plot(), width = 10, height = 6, units = "in", dpi = 300)
+```
+
+```{r}
+# Check sample sizes
+n_far <- nrow(df_20_loin)
+n_close <- nrow(df_20_pres)
+cat("Sample sizes:\nFar from capital:", n_far, "\nClose to capital:", n_close, "\n")
+
+# Check variance in trust values
+var_far <- var(df_20_loin$ft_values)
+var_close <- var(df_20_pres$ft_values)
+cat("\nVariance in trust values:\nFar from capital:", round(var_far, 4), 
+    "\nClose to capital:", round(var_close, 4))
+
+# Check mean number of observations per interval
+mean_obs_per_interval_far <- mean(table(intervals_dist_border_loin))
+mean_obs_per_interval_close <- mean(table(intervals_dist_border_pres))
+cat("\n\nMean observations per interval:\nFar from capital:", 
+    round(mean_obs_per_interval_far, 2),
+    "\nClose to capital:", round(mean_obs_per_interval_close, 2))
+```

### 2025-03-14 script/r/draft.Rmd
maj
rename data file

@@
 
-saveRDS(data_final_r, file="data/data_rds/data_27_02_25.rds")
-
-write_dta(data_final_r, "data/data_dta/data_27_02_25.dta")
-```
+data_final <- readRDS("data/data_rds/data_27_02_25.rds")
+
+data_final%<>%
+  ungroup()
+
+data_final%<>%
+  mutate(desert_region_tv=desert_region*tv,
+         mountain_region_tv=mountain_region*tv)
+
+saveRDS(data_final, file="data/data_rds/data_final.rds")
+
+write_dta(data_final, "data/data_dta/data_final.dta")
+```

### 2025-03-18 script/r/rbci_data.Rmd
maj vdem mean

@@
 ```
+
+```{r}
+#MAJ VDEM
+
+data_final <- readRDS("data/data_rds/data_final.rds")
+
+qog <- read.csv("data/data_raw/qog_std_ts_jan24.csv")
+
+countries <- unique(data_final$iso)
+
+qog%<>%
+  filter(ccodealp %in% countries)
+
+qog%<>%
+  select(year, ccodealp, aii_q55, aii_q56, fhp_mcpp5, vdem_mecorrpt, vdem_polyarchy)%>%
+  rename(iso=ccodealp, fh_med_index=fhp_mcpp5, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)
+
+qog%<>%
+  mutate(round=case_when(between(year, 2011, 2013)~5,
+                         between(year, 2014, 2015)~6,
+                         between(year, 2016, 2018)~7,
+                         between(year, 2019, 2021)~8,
+         TRUE~NA_integer_))
+
+qog%<>%
+  group_by(iso, round)%>%
+  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
+  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
+  ungroup()
+
+qog %<>%
+  filter(!is.na(round)) %>%
+  distinct(iso, round, .keep_all = TRUE) %>%
+  select(iso, round, poly_mean, med_corr_mean)
+
+data_final %<>% left_join(qog, by=c("iso", "round"))
+
+saveRDS(data_final, file="data/data_rds/data_final.rds")
+
+write_dta(data_final, "data/data_dta/data_final.dta")
+```

### 2025-03-18 script/r/rbci_data.Rmd
maj inst: ok pour democ, à creuser pour medias

@@
 write_dta(data_final, "data/data_dta/data_final.dta")
-```
+
+vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")
+
+vdem$v2med
+
+vdem%<>%
+  select(country_text_id, year, v2xedvd_inpt, v2x_polyarchy, v2xedvd_me_cent, v2medstateprint, v2medstatebroad, v2medpolstate, v2medpolnonstate, e_v2x_freexp_altinf_3C, e_v2x_freexp_altinf_4C, e_v2x_freexp_altinf_5C, v2x_freexp, v2xme_altinf, e_polity2)
+
+vdem%<>%
+  filter(country_text_id %in% countries)
+
+vdem%<>%
+  rename(iso=country_text_id)%>%
+    mutate(round=case_when(between(year, 2011, 2013)~5,
+                         between(year, 2014, 2015)~6,
+                         between(year, 2016, 2018)~7,
+                         between(year, 2019, 2021)~8,
+         TRUE~NA_integer_))
+
+vdem %<>%
+  group_by(iso, round) %>%
+  filter(!is.na(round)) %>%
+  mutate(
+    v2xedvd_inpt_mean2 = ifelse(all(is.na(v2xedvd_inpt)), NA_integer_, mean(v2xedvd_inpt, na.rm = TRUE)),
+    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
+    v2xedvd_me_cent_mean2 = ifelse(all(is.na(v2xedvd_me_cent)), NA_integer_, mean(v2xedvd_me_cent, na.rm = TRUE)),
+    v2medstateprint_mean2 = ifelse(all(is.na(v2medstateprint)), NA_integer_, mean(v2medstateprint, na.rm = TRUE)),
+    v2medstatebroad_mean2 = ifelse(all(is.na(v2medstatebroad)), NA_integer_, mean(v2medstatebroad, na.rm = TRUE)),
+    v2medpolstate_mean2 = ifelse(all(is.na(v2medpolstate)), NA_integer_, mean(v2medpolstate, na.rm = TRUE)),
+    v2medpolnonstate_mean2 = ifelse(all(is.na(v2medpolnonstate)), NA_integer_, mean(v2medpolnonstate, na.rm = TRUE)),
+    e_v2x_freexp_altinf_3C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_3C)), NA_integer_, mean(e_v2x_freexp_altinf_3C, na.rm = TRUE)),
+    e_v2x_freexp_altinf_4C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_4C)), NA_integer_, mean(e_v2x_freexp_altinf_4C, na.rm = TRUE)),
+    e_v2x_freexp_altinf_5C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_5C)), NA_integer_, mean(e_v2x_freexp_altinf_5C, na.rm = TRUE)),
+    v2x_freexp_mean2 = ifelse(all(is.na(v2x_freexp)), NA_integer_, mean(v2x_freexp, na.rm = TRUE)),
+    v2xme_altinf_mean2 = ifelse(all(is.na(v2xme_altinf)), NA_integer_, mean(v2xme_altinf, na.rm = TRUE)),
+    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
+  ) %>%
+  ungroup()
+
+vdem%<>%
+  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2)%>%
+    distinct(iso, round, .keep_all = TRUE)
+
+data_final %<>% left_join(vdem, by=c("iso", "round"))
+
+saveRDS(data_final, file="data/data_rds/data_final.rds")
+
+write_dta(data_final, "data/data_dta/data_final.dta")
+```

### 2025-03-19 script/r/rbci_data.Rmd
maj rsf_index

@@
 
-countries <- unique(data_final$iso)
-
-qog%<>%
-  filter(ccodealp %in% countries)
-
-qog%<>%
-  select(year, ccodealp, aii_q55, aii_q56, fhp_mcpp5, vdem_mecorrpt, vdem_polyarchy)%>%
-  rename(iso=ccodealp, fh_med_index=fhp_mcpp5, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)
-
-qog%<>%
-  mutate(round=case_when(between(year, 2011, 2013)~5,
-                         between(year, 2014, 2015)~6,
-                         between(year, 2016, 2018)~7,
-                         between(year, 2019, 2021)~8,
-         TRUE~NA_integer_))
-
-qog%<>%
-  group_by(iso, round)%>%
-  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
-  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
+countries <- data_final %>% filter(spl==1) %>% pull(iso) %>% unique()
+
+qog %<>%
+  select(
+    year,
+    ccodealp,
+    aii_q55,
+    aii_q56,
+    fhp_mcpp5,
+    vdem_mecorrpt,
+    vdem_polyarchy,
+    rsf_pfi1321,
+    rsf_pfi0212,
+    rsf_pfi,
+    rsf_pci
+  ) %>%
+  rename(
+    iso = ccodealp,
+    fh_med_index = fhp_mcpp5,
+    med_self_censor = aii_q55,
+    citiz_self_censor = aii_q56,
+    vdem_med_corrupt = vdem_mecorrpt,
+    rsf_index = rsf_pfi1321
+  )
+
+qog %<>%
+  mutate(round = case_when(
+    year == 2013 ~ 5,
+    between(year, 2014, 2015) ~ 6,
+    between(year, 2016, 2018) ~ 7,
+    between(year, 2019, 2021) ~ 8,
+    TRUE ~ NA_integer_
+  ))
+
+qog %<>%
+  group_by(iso, round) %>%
+  mutate(poly_mean = ifelse(is.na(vdem_polyarchy), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
+  mutate(med_corr_mean = ifelse(is.na(vdem_med_corrupt), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
+  mutate(rsf_index_mean = ifelse(is.na(rsf_index), NA_integer_, mean(rsf_index, na.rm = TRUE))) %>%
   ungroup()
@@
   distinct(iso, round, .keep_all = TRUE) %>%
-  select(iso, round, poly_mean, med_corr_mean)
+  filter(iso %in% countries)%>%
+  mutate(rsf_index_med_all=ifelse(is.na(round), NA_integer_, median(rsf_index_mean, na.rm=TRUE)))
+
+qog %<>%
+  select(iso,
+         round,
+         poly_mean,
+         med_corr_mean,
+         rsf_index_mean,
+         rsf_index_med_all)
 
@@
 vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")
-
-vdem$v2med
 
@@
 vdem%<>%
-  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2)%>%
+  mutate(e_polity2_med_all=ifelse(is.na(round), NA_integer_, median(e_polity2, na.rm=TRUE)))
+
+vdem%<>%
+  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2, e_polity2_med_all)%>%
     distinct(iso, round, .keep_all = TRUE)

### 2025-03-20 script/r/draft.Rmd
maj inst: ok pour democ, à creuser pour medias
Media freedom and democracy indexes

@@
   mutate(desert_region_tv=desert_region*tv,
-         mountain_region_tv=mountain_region*tv)
+         mountain_region_tv=mountain_region*tv,
+         elevation_region_tv=elevation_region*tv)
 
@@
 ```
+
+```{r}
+vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")
+
+vdem%<>%
+  select(country_text_id, year, v2xedvd_inpt, v2x_polyarchy, v2xedvd_me_cent, v2medstateprint, v2medstatebroad, v2medpolstate, v2medpolnonstate, e_v2x_freexp_altinf_3C, e_v2x_freexp_altinf_4C, e_v2x_freexp_altinf_5C, v2x_freexp, v2xme_altinf, e_polity2)
+
+vdem%<>%
+  filter(country_text_id %in% countries)
+
+vdem%<>%
+  rename(iso=country_text_id)%>%
+    mutate(round=case_when(between(year, 2011, 2013)~5,
+                         between(year, 2014, 2015)~6,
+                         between(year, 2016, 2018)~7,
+                         between(year, 2019, 2021)~8,
+         TRUE~NA_integer_))
+
+vdem %<>%
+  group_by(iso, round) %>%
+  filter(!is.na(round)) %>%
+  mutate(
+    v2xedvd_inpt_mean2 = ifelse(all(is.na(v2xedvd_inpt)), NA_integer_, mean(v2xedvd_inpt, na.rm = TRUE)),
+    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
+    v2xedvd_me_cent_mean2 = ifelse(all(is.na(v2xedvd_me_cent)), NA_integer_, mean(v2xedvd_me_cent, na.rm = TRUE)),
+    v2medstateprint_mean2 = ifelse(all(is.na(v2medstateprint)), NA_integer_, mean(v2medstateprint, na.rm = TRUE)),
+    v2medstatebroad_mean2 = ifelse(all(is.na(v2medstatebroad)), NA_integer_, mean(v2medstatebroad, na.rm = TRUE)),
+    v2medpolstate_mean2 = ifelse(all(is.na(v2medpolstate)), NA_integer_, mean(v2medpolstate, na.rm = TRUE)),
+    v2medpolnonstate_mean2 = ifelse(all(is.na(v2medpolnonstate)), NA_integer_, mean(v2medpolnonstate, na.rm = TRUE)),
+    e_v2x_freexp_altinf_3C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_3C)), NA_integer_, mean(e_v2x_freexp_altinf_3C, na.rm = TRUE)),
+    e_v2x_freexp_altinf_4C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_4C)), NA_integer_, mean(e_v2x_freexp_altinf_4C, na.rm = TRUE)),
+    e_v2x_freexp_altinf_5C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_5C)), NA_integer_, mean(e_v2x_freexp_altinf_5C, na.rm = TRUE)),
+    v2x_freexp_mean2 = ifelse(all(is.na(v2x_freexp)), NA_integer_, mean(v2x_freexp, na.rm = TRUE)),
+    v2xme_altinf_mean2 = ifelse(all(is.na(v2xme_altinf)), NA_integer_, mean(v2xme_altinf, na.rm = TRUE)),
+    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
+  ) %>%
+  ungroup()
+
+vdem%<>%
+  mutate(e_polity2_med_all=ifelse(is.na(round), NA_integer_, median(e_polity2, na.rm=TRUE)))
+
+vdem%<>%
+  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2, e_polity2_med_all)%>%
+    distinct(iso, round, .keep_all = TRUE)
+
+data_final %<>% left_join(vdem, by=c("iso", "round"))
+
+```

### 2025-03-20 script/r/rbci_data.Rmd
Media freedom and democracy indexes

--- 2025-03-18 script/r/rbci_data.Rmd
@@
 ```{r}
-#MAJ VDEM
+#Media freedom and democracy indexes
 
@@
 
-countries <- unique(data_final$iso)
-
-qog%<>%
-  filter(ccodealp %in% countries)
-
-qog%<>%
-  select(year, ccodealp, aii_q55, aii_q56, fhp_mcpp5, vdem_mecorrpt, vdem_polyarchy)%>%
-  rename(iso=ccodealp, fh_med_index=fhp_mcpp5, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)
-
-qog%<>%
-  mutate(round=case_when(between(year, 2011, 2013)~5,
-                         between(year, 2014, 2015)~6,
-                         between(year, 2016, 2018)~7,
-                         between(year, 2019, 2021)~8,
-         TRUE~NA_integer_))
-
-qog%<>%
-  group_by(iso, round)%>%
-  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
-  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
+countries <- data_final %>% filter(spl == 1) %>% pull(iso) %>% unique()
+
+qog %<>%
+  select(year, ccodealp, rsf_pfi1321, ) %>%
+  rename(iso = ccodealp, rsf_index = rsf_pfi1321)
+
+qog %<>%
+  mutate(round = case_when(
+    year == 2013 ~ 5,
+    between(year, 2014, 2015) ~ 6,
+    between(year, 2016, 2018) ~ 7,
+    between(year, 2019, 2021) ~ 8,
+    TRUE ~ NA_integer_
+  ))
+
+qog %<>%
+  group_by(iso, round) %>%
+  mutate(rsf_index_mean = ifelse(is.na(rsf_index), NA_integer_, mean(rsf_index, na.rm = TRUE))) %>%
   ungroup()
@@
   distinct(iso, round, .keep_all = TRUE) %>%
-  select(iso, round, poly_mean, med_corr_mean)
-
-data_final %<>% left_join(qog, by=c("iso", "round"))
-
-saveRDS(data_final, file="data/data_rds/data_final.rds")
+  filter(iso %in% countries) %>%
+  mutate(rsf_index_med_all = ifelse(is.na(round), NA_integer_, median(rsf_index_mean, na.rm =
+                                                                        TRUE)))
+qog %<>%
+  select(iso,
+         round,
+         rsf_index_mean)
+
+data_final %<>% left_join(qog, by = c("iso", "round"))
+
+saveRDS(data_final, file = "data/data_rds/data_final.rds")
 
 write_dta(data_final, "data/data_dta/data_final.dta")
-```
+
+vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")
+
+vdem %<>%
+  select(country_text_id, year, v2x_polyarchy, e_polity2)
+
+vdem %<>%
+  filter(country_text_id %in% countries)
+
+vdem %<>%
+  rename(iso = country_text_id) %>%
+  mutate(round = case_when(
+    between(year, 2011, 2013) ~ 5,
+    between(year, 2014, 2015) ~ 6,
+    between(year, 2016, 2018) ~ 7,
+    between(year, 2019, 2021) ~ 8,
+    TRUE ~ NA_integer_
+  ))
+
+vdem %<>%
+  group_by(iso, round) %>%
+  filter(!is.na(round)) %>%
+  mutate(
+    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
+    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
+  ) %>%
+  ungroup()
+
+vdem %<>%
+  select(iso, round, v2x_polyarchy_mean2, e_polity2_mean2) %>%
+  distinct(iso, round, .keep_all = TRUE)
+
+data_final %<>% left_join(vdem, by = c("iso", "round"))
+
+saveRDS(data_final, file = "data/data_rds/data_final.rds")
+
+write_dta(data_final, "data/data_dta/data_final.dta")
+
+```

### 2025-03-20 script/r/draft.Rmd
MAJ path
maj wb_gov

@@
 ```{r}
-setwd("~/working_paper/trust/")
+setwd("~/working_paper/rbci/")
 getwd()
@@
 ```
+
+```{r}
+library(readxl)
+library(tidyr)
+
+data_final <- readRDS("data/data_rds/data_final.rds")
+
+countries <- data_final %>% filter(spl == 1) %>% pull(iso) %>% unique()
+
+wb_gov <- read_excel("data/data_raw/wb_gov/wgidataset.xlsx")
+
+wb_gov %<>%
+  select(code, year, indicator, estimate) %>%
+  mutate(estimate = na_if(estimate, ".."))
+
+wb_gov %<>%
+  pivot_wider(names_from = indicator, values_from = estimate)
+
+wb_gov %<>%
+  rename(
+    ctrl_corr = cc,
+    voice_acc = va,
+    pol_stab = pv,
+    gov_eff = ge,
+    reg_qty = rq,
+    rol = rl,
+    iso = code
+  ) %>%
+  mutate(across(c(
+    ctrl_corr, voice_acc, pol_stab, gov_eff, reg_qty
+  ), as.numeric))
+
+wb_gov %<>%
+  mutate(round = case_when(
+    between(year, 2011, 2013) ~ 5,
+    between(year, 2014, 2015) ~ 6,
+    between(year, 2016, 2018) ~ 7,
+    between(year, 2019, 2021) ~ 8,
+    TRUE ~ NA_integer_
+  ))
+
+wb_gov %<>%
+  group_by(iso, round) %>%
+  filter(!is.na(round)) %>%
+  mutate(
+    ctrl_corr_mean = ifelse(all(is.na(ctrl_corr)), NA_integer_, mean(ctrl_corr, na.rm = TRUE)),
+    voice_acc_mean = ifelse(all(is.na(voice_acc)), NA_integer_, mean(voice_acc, na.rm = TRUE)),
+    pol_stab_mean = ifelse(all(is.na(pol_stab)), NA_integer_, mean(pol_stab, na.rm = TRUE)),
+    gov_eff_mean = ifelse(all(is.na(gov_eff)), NA_integer_, mean(gov_eff, na.rm = TRUE)),
+    reg_qty_mean = ifelse(all(is.na(reg_qty)), NA_integer_, mean(reg_qty, na.rm = TRUE))
+  ) %>%
+  ungroup()
+
+wb_gov %<>%
+  select(
+    iso,
+    round,
+    ctrl_corr_mean,
+    voice_acc_mean,
+    pol_stab_mean,
+    gov_eff_mean,
+    reg_qty_mean
+  ) %>%
+  distinct(iso, round, .keep_all = TRUE)
+
+wb_gov %<>%
+  filter(iso %in% countries)
+```

### 2025-03-20 script/r/draft.Rmd
country heterogeneity

--- 2025-03-20 script/r/draft.Rmd
@@
 ```
+
+```{r}
+library(readxl)
+library(tidyr)
+
+data_final <- readRDS("data/data_rds/data_final.rds")
+
+countries <- data_final %>% pull(iso) %>% unique()
+
+wb_gov <- read_excel("data/data_raw/wb_gov/wgidataset.xlsx")
+
+wb_gov %<>%
+  select(code, year, indicator, estimate) %>%
+  mutate(estimate = na_if(estimate, ".."))
+
+wb_gov %<>%
+  pivot_wider(names_from = indicator, values_from = estimate)
+
+wb_gov %<>%
+  rename(
+    ctrl_corr = cc,
+    voice_acc = va,
+    pol_stab = pv,
+    gov_eff = ge,
+    reg_qty = rq,
+    rol = rl,
+    iso = code
+  ) %>%
+  mutate(across(c(
+    ctrl_corr, voice_acc, pol_stab, gov_eff, reg_qty, rol
+  ), as.numeric))
+
+wb_gov %<>%
+  mutate(round = case_when(
+    between(year, 2011, 2013) ~ 5,
+    between(year, 2014, 2015) ~ 6,
+    between(year, 2016, 2018) ~ 7,
+    between(year, 2019, 2021) ~ 8,
+    TRUE ~ NA_integer_
+  ))
+
+wb_gov %<>%
+  group_by(iso, round) %>%
+  filter(!is.na(round)) %>%
+  mutate(
+    ctrl_corr_mean = ifelse(all(is.na(ctrl_corr)), NA_integer_, mean(ctrl_corr, na.rm = TRUE)),
+    voice_acc_mean = ifelse(all(is.na(voice_acc)), NA_integer_, mean(voice_acc, na.rm = TRUE)),
+    pol_stab_mean = ifelse(all(is.na(pol_stab)), NA_integer_, mean(pol_stab, na.rm = TRUE)),
+    gov_eff_mean = ifelse(all(is.na(gov_eff)), NA_integer_, mean(gov_eff, na.rm = TRUE)),
+    reg_qty_mean = ifelse(all(is.na(reg_qty)), NA_integer_, mean(reg_qty, na.rm = TRUE)),
+    rol_mean = ifelse(all(is.na(rol)), NA_integer_, mean(rol, na.rm = TRUE)),
+  ) %>%
+  ungroup()
+
+wb_gov%<>%
+  mutate(gov_cap = rowMeans(select(., gov_eff_mean, reg_qty_mean), na.rm = TRUE))
+
+wb_gov %<>%
+  select(
+    iso,
+    round,
+    ctrl_corr_mean,
+    voice_acc_mean,
+    pol_stab_mean,
+    gov_eff_mean,
+    reg_qty_mean,
+    rol_mean,
+    gov_cap
+  ) %>%
+  distinct(iso, round, .keep_all = TRUE)
+
+wb_gov %<>%
+  filter(iso %in% countries)
+
+data_final %<>% left_join(wb_gov, by = c("iso", "round"))
+
+saveRDS(data_final, file = "data/data_rds/data_final.rds")
+
+write_dta(data_final, "data/data_dta/data_final.dta")
+
+```
+
+```{r}
+# Load dplyr package
+library(dplyr)
+
+# Assuming your data is in data_final and has columns ctrl_corr_mean and spl
+percentile_below_neg_0_5 <- data_final %>%
+  filter(spl == 1) %>%  # Filter for spl == 1
+  summarise(
+    total_count = n(),  # Total number of observations where spl == 1
+    below_neg_0_5_count = sum(ctrl_corr_mean < -0.5)  # Count values less than -0.5
+  ) %>%
+  mutate(
+    percentile = (below_neg_0_5_count / total_count) * 100  # Calculate the percentage
+  )
+
+# Display the result
+print(percentile_below_neg_0_5)
+
+```

### 2025-04-06 script/r/draft.Rmd
maj gitignore

@@
 ```
+
+```{r}
+df <- readRDS("data/data_rds/data_final.rds")
+
+df %<>%
+  filter(spl==1, round==5)
+
+radius<- 5000
+
+df_sf_buff <- df[, .(longitude, latitude, iso, id_ea)] %>%
+  vect(geom = c("longitude", "latitude"), crs = "EPSG:4326") %>%
+  buffer(width = radius)
+
+if (any(!is.valid(df_sf_buff))) {
+  df_sf_buff <- make_valid(df_sf_buff)
+}
+
+cty_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
+
+cty_buff <- intersect(df_sf_buff, cty_shp)
+
+cty_sf <- st_as_sf(cty_shp)
+cty_buff_sf <- st_as_sf(cty_buff)
+
+ggplot() +
+  geom_sf(
+    data = cty_sf,
+    fill = "lightgray",
+    color = "black",
+    alpha = 0.5
+  ) +
+
+  geom_sf(
+    data = cty_buff_sf,
+    fill = "gold",
+    color = "gold4",
+    alpha = 0.3
+  ) +
+
+  theme_minimal() +
+  labs(title = "Circles 10km radius")
+
+```
+
+```{r}
+rc <- function(x) {
+  ifelse(is.na(x), 0 , 1)
+}
+
+# Define TIFF file path
+tiff_file <- "data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_BEN2G_2012.tif"
+
+# Filter circles based on ISO code
+circles <- df_sf_buff[df_sf_buff$iso == "BEN"]
+
+# Harmonize CRS to WGS84 using terra::project()
+target_crs <- "EPSG:4326"  # WGS84 CRS
+
+# Load and process raster using terra (faster than raster)
+gg <- rast(tiff_file)
+plot(gg)
+gg_wgs84 <- project(gg, target_crs)
+plot(gg_wgs84)
+gg_wgs84_recode <- app(gg_wgs84, fun = rc)
+plot(gg_wgs84_recode)
+
+# Check the extent of circles to ensure it's valid
+circles_extent <- ext(circles)
+
+plot(circles)
+plot(circles_extent)
+# Crop and mask raster to the buffered areas
+gg_wgs84_cropped <- crop(gg_wgs84_recode, circles_extent)
+gg_wgs84_masked <- mask(gg_wgs84_cropped, circles)
+plot(gg_wgs84_cropped)
+plot(gg_wgs84_masked)
+
+global(gg_wgs84_masked, mean, na.rm = TRUE)
+
+circles_cropped <- crop(circles, gg_wgs84_masked)
+
+plot(circles_cropped, add = TRUE, border = "red")
+
+# Extract values from the raster based on the polygons
+gg_values <- terra::extract(gg_wgs84_masked,
+                            circles_cropped,
+                            fun = mean,
+                            na.rm = TRUE)
+
+circles_cropped$gg_mean <- gg_values[, 2]
+```
+
+```{r}
+# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
+adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
+adm2_sf <- st_as_sf(adm2_shp)
+adm2_sf <- st_make_valid(adm2_sf)
+
+df <- readRDS("data/data_rds/data_final.rds")
+
+df_round5 <- df %>% filter(round == 5)
+df_round8 <- df %>% filter(round == 8)
+
+# Get the unique region identifiers in both rounds (intersection)
+common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)
+
+# Filter original data to keep only the regions that appear in both rounds
+df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions) %>% select(-NAME_2)
+
+df_common%<>%filter(round==5)
+
+# Convert to sf object (if not already)
+df_sf <- st_as_sf(df_common, coords = c("longitude", "latitude"), crs = st_crs(adm2_sf))
+
+# Proceed with spatial join or further analysis
+df_adm2_sf <- st_join(df_sf, adm2_sf)
+
+# 5. Aggregate: calculate mean trust by region
+trust_mean <- df_adm2_sf %>%
+  group_by(NAME_2, round) %>%  # replace with actual region ID column
+  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE))
+
+trust_mean_df <- st_drop_geometry(trust_mean)
+
+# 6. Join aggregated data back to region geometries
+regions_map <- adm2_sf %>%
+  left_join(trust_mean_df, by = "NAME_2")  # make sure column name matches
+
+capitals <- df_common %>%
+  distinct(caplong, caplat, iso)%>%
+  na.omit() %>%
+  rename(longitude = caplong, latitude = caplat)
+
+# 7. Plot the map
+ggplot(regions_map) +
+  geom_sf(aes(fill = mean_trust), color = "white") +
+  scale_fill_gradient(
+    low = "red",   # Low values will be red
+    high = "green", # High values will be green
+    na.value = "lightgrey",  # Missing values will be light grey
+    limits = c(0, 3)  # Fix scale between 0 and 3
+
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust - Round 5",
+    fill = "Trust"
+  )+
+   geom_point(data = capitals, 
+             aes(x = longitude, y = latitude), 
+             size = 2, shape = 22, fill = "black", show.legend = FALSE)
+
+# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
+adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
+adm2_sf <- st_as_sf(adm2_shp)
+adm2_sf <- st_make_valid(adm2_sf)
+
+df <- readRDS("data/data_rds/data_final.rds")
+
+df_round5 <- df %>% filter(round == 5)
+df_round8 <- df %>% filter(round == 8)
+
+# Get the unique region identifiers in both rounds (intersection)
+common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)
+
+# Filter original data to keep only the regions that appear in both rounds
+df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions) %>% select(-NAME_2)
+
+df_common%<>%filter(round==8)
+
+# Convert to sf object (if not already)
+df_sf <- st_as_sf(df_common, coords = c("longitude", "latitude"), crs = st_crs(adm2_sf))
+
+# Proceed with spatial join or further analysis
+df_adm2_sf <- st_join(df_sf, adm2_sf)
+
+# 5. Aggregate: calculate mean trust by region
+trust_mean <- df_adm2_sf %>%
+  group_by(NAME_2, round) %>%  # replace with actual region ID column
+  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE))
+
+trust_mean_df <- st_drop_geometry(trust_mean)
+
+# 6. Join aggregated data back to region geometries
+regions_map <- adm2_sf %>%
+  left_join(trust_mean_df, by = "NAME_2")  # make sure column name matches
+
+capitals <- df_common %>%
+  distinct(caplong, caplat, iso)%>%
+  na.omit() %>%
+  rename(longitude = caplong, latitude = caplat)
+
+# 7. Plot the map
+ggplot(regions_map) +
+  geom_sf(aes(fill = mean_trust), color = "white") +
+  scale_fill_gradient(
+    low = "red",   # Low values will be red
+    high = "green", # High values will be green
+    na.value = "lightgrey",  # Missing values will be light grey
+    limits = c(0, 3)  # Fix scale between 0 and 3
+
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust - Round 8",
+    fill = "Trust"
+  )+
+   geom_point(data = capitals, 
+             aes(x = longitude, y = latitude), 
+             size = 2, shape = 22, fill = "black", show.legend = FALSE)
+
+# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
+adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
+adm2_sf <- st_as_sf(adm2_shp)
+adm2_sf <- st_make_valid(adm2_sf)
+
+df <- readRDS("data/data_rds/data_final.rds")
+
+df_round5 <- df %>% filter(round == 5)
+df_round8 <- df %>% filter(round == 8)
+
+# Get the unique region identifiers in both rounds (intersection)
+common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)
+
+# Filter original data to keep only the regions that appear in both rounds
+df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions)
+
+# 3. Aggregate: calculate mean trust by region and round (for both rounds 5 and 8)
+trust_mean_by_round <- df_common %>%
+  group_by(NAME_2, round) %>%
+  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop")
+
+# 4. Spread data: Create a wide format to compare rounds 5 and 8
+trust_mean_wide <- trust_mean_by_round %>%
+  pivot_wider(names_from = round, values_from = mean_trust) %>%
+  rename(mean_trust_5 = `5`, mean_trust_8 = `8`)
+
+# 5. Calculate the variation in trust (difference between round 8 and round 5)
+trust_mean_wide <- trust_mean_wide %>%
+  mutate(variation = mean_trust_8 - mean_trust_5)
+
+# 6. Join the aggregated data back to the region geometries
+regions_map <- adm2_sf %>%
+  left_join(trust_mean_wide, by = "NAME_2")
+
+# 7. Plot the variation map
+ggplot(regions_map) +
+  geom_sf(aes(fill = variation), color = "white") +
+  scale_fill_gradient(
+    low = "red",   # Low values will be red (indicating decrease in trust)
+    high = "green", # High values will be green (indicating increase in trust)
+    na.value = "lightgrey",  # Missing values will be light grey
+    limits = c(-3, 3)  # Fix scale between -3 and 3 for variation
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust (Round 8 - Round 5)",
+    fill = "Delta"
+  ) +
+   geom_point(data = capitals, 
+             aes(x = longitude, y = latitude), 
+             size = 2, shape = 22, fill = "black", show.legend = FALSE)
+
+```
+
+```{r}
+library(terra)
+library(dplyr)
+library(magrittr)
+library(ggplot2)
+library(tidyr)
+library(gt)
+library(rnaturalearth)
+
+# Load survey data
+df <- readRDS("data/data_rds/data_final.rds")
+
+df%<>%
+  filter(spl==1)
+
+# Unique ISO codes in data
+country_codes <- unique(df$iso)
+
+# Path to admin2 shapefiles
+shapefile_path <- "data/data_raw/gadm/"
+
+# Store each country’s region vector
+all_regions_vect <- list()
+
+for (iso in country_codes) {
+  shp_file <- paste0(shapefile_path, "gadm41_", iso, "_2.shp")
+
+  if (!file.exists(shp_file)) {
+    message("⛔ Skipping ", iso, " - shapefile missing.")
+    next
+  }
+
+  message("✅ Processing ", iso)
+
+  # Load shapefile
+  adm2_vect <- vect(shp_file)
+
+  # Filter country data and only include rounds 5 and 8
+  df_country <- df %>% filter(iso == iso, round %in% c(5, 8))
+
+  if (nrow(df_country) == 0) {
+    message("⚠️ No data for rounds 5 or 8 for ", iso)
+    adm2_vect$variation <- NA
+    all_regions_vect[[iso]] <- adm2_vect
+    next
+  }
+
+  df5 <- df_country %>% filter(round == 5)
+  df8 <- df_country %>% filter(round == 8)
+  common_regions <- intersect(df5$NAME_2, df8$NAME_2)
+
+  if (length(common_regions) == 0) {
+    message("⚠️ No common regions for ", iso)
+    adm2_vect$variation <- NA
+    all_regions_vect[[iso]] <- adm2_vect
+    next
+  }
+
+  df_common <- df_country %>% filter(NAME_2 %in% common_regions)
+
+  # Aggregate and calculate mean trust values
+  trust_wide <- df_common %>%
+    group_by(NAME_2, round) %>%
+    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop") %>%
+    pivot_wider(names_from = round, values_from = trust, names_prefix = "R") %>%
+    mutate(variation = R8 - R5)
+
+  # Merge trust data back with spatial data
+  adm2_vect$NAME_2 <- as.character(adm2_vect$NAME_2)
+  joined <- tryCatch({
+    merge(adm2_vect, trust_wide, by = "NAME_2", all.x = TRUE)
+  }, error = function(e) {
+    message("❌ Merge failed for ", iso, ": ", e$message)
+    NULL
+  })
+
+  all_regions_vect[[iso]] <- joined
+}
+
+combined <- Reduce(rbind, all_regions_vect)
+combined_df <- as.data.frame(combined)
+
+capitals <- df %>%
+  filter(round %in% c(5, 8)) %>%
+  distinct(caplong, caplat, iso) %>%
+  na.omit() %>%
+  rename(longitude = caplong, latitude = caplat)
+
+africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
+  st_make_valid()
+
+africa_sf <- st_as_sf(combined)
+
+ggplot() +
+  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
+  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
+  geom_point(data = capitals, aes(x = longitude, y = latitude),
+             shape = 21, size = 2, fill = "black") +
+  scale_fill_gradient2(
+    low = "red", mid = "white", high = "green",
+    midpoint = 0, limits = c(-3, 3),
+    na.value = "lightgrey",
+    name = "Δ Trust\n(R8 - R5)"
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust Change in Parliament (Round 8 - Round 5)",
+    subtitle = "Across African Regions",
+    caption = "Grey = No data"
+  )
+```
+
+```{r}
+# Define which countries use which admin level
+countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+
+# Load required libraries
+library(magrittr)
+library(dplyr)
+library(tidyr)
+library(terra)
+library(sf) # For better spatial data handling
+
+# Load data
+df <- readRDS("data/data_rds/data_final.rds")
+df %<>% filter(spl == 1)
+
+# Unique ISO codes in data
+country_codes <- unique(df$iso)
+
+# Path to admin shapefiles
+shapefile_path <- "data/data_raw/gadm/"
+
+# Store each country's region vector - keeping as sf objects until the end
+all_regions_sf <- list()
+
+for (iso_code in country_codes) {
+  # Skip if not in our specified lists
+  if (!(iso_code %in% c(countries_adm1, countries_adm2))) {
+    message("⛔ Skipping ", iso_code, " - not in specified admin level lists.")
+    next
+  }
+
+  # Determine admin level for this country
+  admin_level <- if(iso_code %in% countries_adm1) 1 else 2
+
+  # Build shapefile path based on admin level
+  shp_file <- paste0(shapefile_path, "gadm41_", iso_code, "_", admin_level, ".shp")
+
+  if (!file.exists(shp_file)) {
+    message("⛔ Skipping ", iso_code, " - shapefile missing at admin level ", admin_level)
+    next
+  }
+
+  message("✅ Processing ", iso_code, " at admin level ", admin_level)
+
+  # Load shapefile with sf for more reliable handling
+  adm_sf <- sf::st_read(shp_file, quiet = TRUE)
+
+  # Get the appropriate region name field based on admin level
+  region_field <- paste0("NAME_", admin_level)
+
+  # Make sure the field exists in the shapefile
+  if(!(region_field %in% names(adm_sf))) {
+    message("⚠️ Field ", region_field, " not found in shapefile for ", iso_code)
+    next
+  }
+
+  # Filter country data and only include rounds 5 and 8
+  df_country <- df %>% filter(iso == iso_code, round %in% c(5, 8))
+
+  if (nrow(df_country) == 0) {
+    message("⚠️ No data for rounds 5 or 8 for ", iso_code)
+    adm_sf$variation <- NA_real_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Ensure we're using the correct region field in the data
+  # Check if fields exist in df_country
+  if(!(region_field %in% names(df_country))) {
+    message("⚠️ Field ", region_field, " not found in data for ", iso_code)
+    adm_sf$variation <- NA_real_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Split by round
+  df5 <- df_country %>% filter(round == 5)
+  df8 <- df_country %>% filter(round == 8)
+
+  # Find common regions between rounds
+  common_regions <- intersect(df5[[region_field]], df8[[region_field]])
+
+  if (length(common_regions) == 0) {
+    message("⚠️ No common regions for ", iso_code)
+    adm_sf$variation <- NA_real_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Filter to common regions
+  df_common <- df_country %>% filter(!!sym(region_field) %in% common_regions)
+
+  # Debug: Print a sample of region names to verify structure
+  message("Sample regions for ", iso_code, ": ", 
+          paste(head(unique(df_common[[region_field]]), 3), collapse=", "))
+
+  # Aggregate and calculate mean trust values
+  trust_wide <- df_common %>%
+    group_by(!!sym(region_field), round) %>%
+    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop") %>%
+    pivot_wider(names_from = round, values_from = trust, names_prefix = "R") %>%
+    mutate(variation = R8 - R5)
+
+  # Debug: Check trust_wide structure
+  message("Trust data structure: ", nrow(trust_wide), " rows with variation calculated")
+
+  # Convert region names to character for reliable joining
+  adm_sf[[region_field]] <- as.character(adm_sf[[region_field]])
+  trust_wide[[region_field]] <- as.character(trust_wide[[region_field]])
+
+  # Left join instead of merge for more reliable behavior
+  joined <- tryCatch({
+    sf::st_join(adm_sf, trust_wide, by = region_field, join = st_equals)
+  }, error = function(e) {
+    # Try a different join method if st_equals fails
+    tryCatch({
+      left_join(adm_sf, trust_wide, by = region_field)
+    }, error = function(e2) {
+      message("❌ Join failed for ", iso_code, ": ", e2$message)
+      message("SHP fields: ", paste(head(names(adm_sf)), collapse=", "))
+      message("Data fields: ", paste(head(names(trust_wide)), collapse=", "))
+      NULL
+    })
+  })
+
+  if(!is.null(joined)) {
+    all_regions_sf[[iso_code]] <- joined
+    # Debug: Check for NAs in variation
+    na_count <- sum(is.na(joined$variation))
+    total_count <- nrow(joined)
+    message("Variation has ", na_count, " NAs out of ", total_count, " regions")
+  }
+}
+
+# Only combine non-NULL elements
+valid_regions <- all_regions_sf[!sapply(all_regions_sf, is.null)]
+
+if(length(valid_regions) > 0) {
+  # Check if we can rbind these objects
+  if(length(valid_regions) > 1) {
+    # Make sure all objects have compatible columns
+    all_cols <- unique(unlist(lapply(valid_regions, names)))
+    for(i in seq_along(valid_regions)) {
+      missing_cols <- setdiff(all_cols, names(valid_regions[[i]]))
+      for(col in missing_cols) {
+        valid_regions[[i]][[col]] <- NA
+      }
+    }
+  }
+
+  # Now bind them safely
+  combined <- do.call(rbind, valid_regions)
+
+  # Convert back to terra format if needed
+  combined_vect <- terra::vect(combined)
+  combined_df <- as.data.frame(combined_vect)
+
+  # Save or continue processing
+} else {
+  message("No valid data to combine")
+}
+
+capitals <- df %>%
+  filter(round %in% c(5, 8)) %>%
+  distinct(caplong, caplat, iso) %>%
+  na.omit() %>%
+  rename(longitude = caplong, latitude = caplat)
+
+africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
+  st_make_valid()
+
+africa_sf <- st_as_sf(combined)
+
+ggplot() +
+  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
+  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
+  geom_point(data = capitals, aes(x = longitude, y = latitude),
+             shape = 21, size = 2, fill = "black") +
+  scale_fill_gradient2(
+    low = "red", mid = "white", high = "green",
+    midpoint = 0, limits = c(-3, 3),
+    na.value = "lightgrey",
+    name = "Δ Trust\n(R8 - R5)"
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust Change in Parliament (Round 8 - Round 5)",
+    subtitle = "Across African Regions",
+    caption = "Grey = No data"
+  )
+```
+
+```{r}
+# Define which countries use which admin level
+countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
+countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")
+
+# Load required libraries
+library(magrittr)
+library(dplyr)
+library(tidyr)
+library(terra)
+library(sf)
+
+# Load data
+df <- readRDS("data/data_rds/data_final.rds")
+df %<>% filter(spl == 1)
+
+# Unique ISO codes in data
+country_codes <- unique(df$iso)
+
+# Path to admin shapefiles
+shapefile_path <- "data/data_raw/gadm/"
+
+# Store each country's region vector
+all_regions_sf <- list()
+
+for (iso_code in country_codes) {
+  # Skip if not in our specified lists
+  if (!(iso_code %in% c(countries_adm1, countries_adm2))) {
+    message("⛔ Skipping ", iso_code, " - not in specified admin level lists.")
+    next
+  }
+
+  # Determine admin level for this country
+  admin_level <- if(iso_code %in% countries_adm1) 1 else 2
+
+  # Build shapefile path based on admin level
+  shp_file <- paste0(shapefile_path, "gadm41_", iso_code, "_", admin_level, ".shp")
+
+  if (!file.exists(shp_file)) {
+    message("⛔ Skipping ", iso_code, " - shapefile missing at admin level ", admin_level)
+    next
+  }
+
+  message("✅ Processing ", iso_code, " at admin level ", admin_level)
+
+  # Load shapefile with sf
+  adm_sf <- sf::st_read(shp_file, quiet = TRUE)
+
+  # Get the appropriate region name field based on admin level
+  region_field <- paste0("NAME_", admin_level)
+
+  # Make sure the field exists in the shapefile
+  if(!(region_field %in% names(adm_sf))) {
+    message("⚠️ Field ", region_field, " not found in shapefile for ", iso_code)
+    next
+  }
+
+  # Filter country data to include rounds 5-8
+  df_country <- df %>% filter(iso == iso_code, round >= 5, round <= 8)
+
+  if (nrow(df_country) == 0) {
+    message("⚠️ No data for rounds 5-8 for ", iso_code)
+    adm_sf$variation <- NA_real_
+    adm_sf$min_round <- NA_integer_
+    adm_sf$max_round <- NA_integer_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Ensure we're using the correct region field in the data
+  if(!(region_field %in% names(df_country))) {
+    message("⚠️ Field ", region_field, " not found in data for ", iso_code)
+    adm_sf$variation <- NA_real_
+    adm_sf$min_round <- NA_integer_
+    adm_sf$max_round <- NA_integer_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Calculate average trust by region and round
+  region_trust <- df_country %>%
+    group_by(!!sym(region_field), round) %>%
+    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop")
+
+  # Find regions with at least 2 rounds of data
+  region_round_counts <- region_trust %>%
+    group_by(!!sym(region_field)) %>%
+    summarise(num_rounds = n(), .groups = "drop")
+
+  regions_with_multiple_rounds <- region_round_counts %>%
+    filter(num_rounds >= 2) %>%
+    pull(!!sym(region_field))
+
+  if (length(regions_with_multiple_rounds) == 0) {
+    message("⚠️ No regions with multiple rounds for ", iso_code)
+    adm_sf$variation <- NA_real_
+    adm_sf$min_round <- NA_integer_
+    adm_sf$max_round <- NA_integer_
+    all_regions_sf[[iso_code]] <- adm_sf
+    next
+  }
+
+  # Filter to regions with multiple rounds
+  region_trust_filtered <- region_trust %>%
+    filter(!!sym(region_field) %in% regions_with_multiple_rounds)
+
+  # For each region, calculate variation between earliest and latest available round
+  variation_data <- region_trust_filtered %>%
+    group_by(!!sym(region_field)) %>%
+    summarise(
+      min_round = min(round),
+      max_round = max(round),
+      earliest_trust = trust[which.min(round)],
+      latest_trust = trust[which.max(round)],
+      variation = latest_trust - earliest_trust,
+      .groups = "drop"
+    )
+
+  # Debug info
+  message("Found ", nrow(variation_data), " regions with variations for ", iso_code)
+
+  # Convert region names to character for reliable joining
+  adm_sf[[region_field]] <- as.character(adm_sf[[region_field]])
+  variation_data[[region_field]] <- as.character(variation_data[[region_field]])
+
+  # Join variation data with shapefile
+  joined <- left_join(adm_sf, variation_data, by = region_field)
+
+  if(!is.null(joined)) {
+    all_regions_sf[[iso_code]] <- joined
+    # Debug: Check for NAs in variation
+    na_count <- sum(is.na(joined$variation))
+    total_count <- nrow(joined)
+    message("Variation has ", na_count, " NAs out of ", total_count, " regions")
+  }
+}
+
+# Only combine non-NULL elements
+valid_regions <- all_regions_sf[!sapply(all_regions_sf, is.null)]
+
+if(length(valid_regions) > 0) {
+  # Ensure column compatibility
+  all_cols <- unique(unlist(lapply(valid_regions, names)))
+  for(i in seq_along(valid_regions)) {
+    missing_cols <- setdiff(all_cols, names(valid_regions[[i]]))
+    for(col in missing_cols) {
+      valid_regions[[i]][[col]] <- NA
+    }
+  }
+
+  # Combine all regions
+  combined <- do.call(rbind, valid_regions)
+
+  # Convert back to terra format if needed
+  combined_vect <- terra::vect(st_cast(combined))
+  combined_df <- as.data.frame(combined_vect)
+
+  # Summary of variations
+  message("Variation summary:")
+  message("Min: ", min(combined$variation, na.rm = TRUE))
+  message("Max: ", max(combined$variation, na.rm = TRUE))
+  message("Mean: ", mean(combined$variation, na.rm = TRUE))
+  message("Median: ", median(combined$variation, na.rm = TRUE))
+  message("NA count: ", sum(is.na(combined$variation)))
+
+  # You can now proceed with further analysis or visualization
+} else {
+  message("No valid data to combine")
+}
+
+capitals <- df %>%
+  filter(round %in% c(5, 8)) %>%
+  distinct(caplong, caplat, iso) %>%
+  na.omit() %>%
+  rename(longitude = caplong, latitude = caplat)
+
+africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
+  st_make_valid()
+
+africa_outline <- st_transform(africa_outline, st_crs(combined))
+
+africa_sf <- st_as_sf(combined)
+
+ggplot() +
+  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
+  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
+    geom_point(data = capitals, aes(x = longitude, y = latitude),
+             shape = 21, size = 2, fill = "black") +
+  scale_fill_gradient2(
+    low = "red", high = "green",
+    midpoint = 0, limits = c(-2, 2),
+    na.value = "lightgrey",
+    name = "Δ Trust\n(R8 - R5)"
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Trust Change in Parliament (Round 8 - Round 5)",
+    subtitle = "Across African Regions",
+    caption = "Grey = No data"
+  )
+```

### 2025-06-29 writing/wp/intro.tex
intro

\documentclass[11pt]{article}
\input{Preamble}

\begin{document}

\title{The Death of Distance: Internet and Political Trust in Africa  \\  }

\author{
\textbf{Illan Barriola} \\ CRED -- Paris-Panthéon-Assas \\
\and 
\textbf{R\'{e}dha Chaba} \\ LEMMA -- Paris-Panthéon-Assas  \\
}

\date{\today}

\maketitle

\newpage

\begin{quotation}
\noindent ``The State stops twelve kilometers from the capital.''

\smallskip

\hfill -- A Central African Republic official, Bierschenk \& Olivier de Sardan, 1997 
\end{quotation}

\section{Introduction}

Democracy requires citizens to both trust and distrust their politicians. Trust to enable governance, distrust to prevent misgovernance.
Yet, this balance is unevenly distributed across space.
In Sub-Saharan Africa, views of politicians and governments differ by region within countries.
People in remote areas tend to support them more than those near capital cities.
A large literature emphasizes the role of information in shaping political opinion.
Information costs increase with distance from state presence and limited media coverage, resulting in shortages of both direct and mediated information.
When information is scarce, citizens might end up trusting politicians in the absence of negative information.\\

Mobile internet is changing traditional information geography in Sub-Saharan Africa. Citizens in remote areas can now access diverse content that used to be concentrated near capitals - including both political information and misinformation.
This technology differs from traditional media by turning citizens from passive consumers into active participants in different information networks.
The impact on views of politicians is likely to be larger in remote areas, where information costs have been highest.\\

This paper examines whether mobile internet use reduces spatial disparities in political trust across Sub-Saharan Africa.
We combine geocoded individual-level data from Afrobarometer rounds 6-8 (2013-2021) across 17 Sub-Saharan countries with digital maps of mobile internet coverage from the Global System for Mobile Communications Association (GSMA).
The geocoded data allows us to measure each respondent's distance from their capital, while the surveys capture political opinions, internet use, and news consumption.\\

We find that internet use shifts opinions in remote areas toward the critical views found near capitals.
Since we cannot disentangle whether citizens consume accurate information or misinformation, we explore institutional heterogeneity and find that the reduction in spatial disparities in political trust is more pronounced in countries where the state controls traditional media, while the effect on corruption perception is stronger where corruption is high.
This supports "liberation technology" arguments that the internet offers alternative information when traditional media are not transparent.
Moreover, we find that the shift is larger for less educated citizens, consistent with the idea that more educated ones may already have access to information.
Further, we find that the shift in opinion of politicians translates into increased demand for accountability mechanisms and greater willingness to vote against the ruling party in the next elections.
Additionally, we provide evidence of the initial difference in political trust by distance from capital, consistent with the existing literature.\\

We estimate how internet use interacts with distance from capital to affect political trust.
Since internet use is potentially endogenous due to political trust and unobserved factors, we develop two distinct instrumental variable strategies.
First, we use population-weighted 3G internet supply at the district level to instrument for internet use, both interacted with distance from capital.
This follows an intention-to-treat design using 3G supply as a measure of potential internet use, only affecting political trust through this channel.
We argue that 3G supply location is determined by economic rather than political factors, particularly in Sub-Saharan Africa where costly internet infrastructure is deployed by profit-focused private companies.
The population weighting and controls for economic development and topographic features help ensure the exogeneity of our instrument.
Second, we explore another framework with a more exogenous instrument using lightning strike patterns to instrument for 3G internet supply, here also both interacted with distance from capital, population-weighted, and at the district level.
This strategy leverages higher internet infrastructure deployment and maintenance costs in lightning-prone areas, while these weather patterns are plausibly exogenous to political opinions.
We then examine heterogeneous effects by re-estimating our specification across subsamples defined by governance and media freedom measures from V-Dem, World Bank, and Reporters Sans Frontières.
Beyond instrumenting for internet use, we also address potential endogeneity concerns with distance from capital itself by exploiting modern national borders that arbitrarily divide historical ethnic homelands.
Our border discontinuity design compares individuals from the same historical ethnic group who live at different distances from their capital city due to national boundaries.
We estimate a specification including institutional controls to address concerns about comparing political opinions across different national contexts.\\

\end{document}

### 2025-06-29 writing/presentation/slides.tex
maj writing

\documentclass[aspectratio=169,xcolor=dvipsnames]{beamer}
\usepackage{graphicx} % Required for inserting images
\pgfdeclareverticalshading[lower.bg,upper.bg]{bmb@transition}{200cm}{%
color(0pt)=(lower.bg); color(2pt)=(lower.bg); color(4pt)=(lower.bg)}

\setbeamersize{text margin left=2em,text margin right=2em}

\setbeamertemplate{footline}{
  \leavevmode%
  \hbox to \paperwidth{%
    \hfill%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \insertframenumber/\inserttotalframenumber%
    \hspace{3em}%  % Adjust this value as needed
  }%
  \vskip2pt%
}
\setbeamertemplate{navigation symbols}{}

\setbeamertemplate{blocks}[rounded][shadow=false]

\setbeamertemplate{enumerate items}[default]
\setbeamertemplate{enumerate subitem}[default]
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{itemize subitem}[circle]

% table of contents (overview) settings
\setbeamertemplate{section in toc}[sections numbered]
\setbeamertemplate{subsection in toc}{%
    \leavevmode
    \leftskip=3.2em
    \rlap{\hskip-2em\inserttocsectionnumber.\inserttocsubsectionnumber}
    \inserttocsubsection\par
}

% frame title customization
\setbeamertemplate{frametitle}{%
    \vspace*{0.5em}
    \bfseries\insertframetitle\par
    \vskip-6pt
    \hrulefill\vspace{-0.1em}
}

% title page customization
\setbeamertemplate{title page}{%
    \vspace{2.5em}
    \begingroup
    \centering
    % ------------------------
    \begin{beamercolorbox}[sep=10pt,center]{title}
        \usebeamerfont{title}\inserttitle\par%
        \ifx\insertsubtitle\@empty%
        \else%
        \vskip 1em%
        {\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}%
        \fi%
    \end{beamercolorbox}%
    \vskip0.5em\par
    % ------------------------
    \begin{beamercolorbox}[sep=8pt,center]{author}
        \usebeamerfont{author}\insertauthor
    \end{beamercolorbox}
    \vskip1em
    % ------------------------
    \begin{beamercolorbox}[sep=8pt,center]{institute}
        \usebeamerfont{institute}\insertinstitute
    \end{beamercolorbox}\vskip0.5em
    % ------------------------
    \begin{beamercolorbox}[sep=8pt,center]{date}
        \usebeamerfont{date}\insertdate
    \end{beamercolorbox}\vskip1em
    % ------------------------
    {\usebeamercolor[fg]{titlegraphic}\inserttitlegraphic\par}
    \endgroup
    \vfill
}

\setbeamerfont{structure}{family=\sffamily,series=\mdseries}

\setbeamerfont{title}{size=\LARGE,series=\bfseries,parent=structure}
\setbeamerfont{subtitle}{size=\normalsize,parent=title}

\setbeamerfont{date}{size=\scriptsize,series=\mdseries,parent=structure}
\setbeamerfont{author}{size=\large,series=\mdseries,parent=structure}
\setbeamerfont{institute}{size=\scriptsize,series=\mdseries,parent=structure}

\setbeamerfont{section in toc}{size=\large,series=\bfseries,parent=structure}
\setbeamerfont{section in head/foot}{size=\tiny,parent=structure}
\setbeamerfont{subsection in toc}{size=\small,series=\mdseries,parent={section in toc}}

\setbeamerfont{frametitle}{size=\Large,series=\bfseries,parent=structure}
\setbeamerfont{framesubtitle}{parent=frametitle,size=\large}

\setbeamerfont{caption}{size=\footnotesize}
\setbeamerfont{item}{parent=structure,series=\mdseries}
\setbeamerfont{block title}{size=\large,series=\mdseries,parent={structure,block body}}

% Custom colors
\definecolor{MutedRed}{rgb}{0.97, 0.92, 0.92}
\definecolor{MutedGreen}{rgb}{0.92, 0.97, 0.92}
\definecolor{MutedBlue}{rgb}{0.92, 0.92, 0.97}
\definecolor{MutedBlack}{rgb}{0.95, 0.95, 0.95}

\definecolor{MediumRed}{rgb}{0.925, 0.345, 0.345}
\definecolor{MediumGreen}{rgb}{0.37, 0.7, 0.66}
\definecolor{MediumBlue}{rgb}{0.015, 0.315, 0.45}
\definecolor{MediumBlack}{rgb}{0.219, 0.259, 0.349}

\definecolor{DarkBlue}{rgb}{0.05, 0.15, 0.35}

% Set beamer color themes
\usecolortheme[named=DarkBlue]{structure}

% Customize block colors
\setbeamercolor{titlelike}{parent=structure}
\setbeamercolor{block title}{fg=white,bg=MediumBlue}
\setbeamercolor{block body}{fg=black,bg=MutedBlue}
\setbeamercolor{block title example}{fg=white,bg=MediumGreen}
\setbeamercolor{block body example}{fg=black,bg=MutedGreen}
\setbeamercolor{block title alerted}{fg=white,bg=MediumRed}
\setbeamercolor{block body alerted}{fg=black,bg=MutedRed}

% Environment for frames without page number
\newenvironment{hidepagenumberframe}
  {\setbeamertemplate{footline}{}\begin{frame}}
  {\end{frame}\setbeamertemplate{footline}[frame number]}

\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, fit, backgrounds, calc, shapes.geometric, decorations.pathmorphing}

\setbeamertemplate{caption}[numbered]

\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amssymb}

\vspace{1.5em}

\begin{document}

\title{The Death of Distance: Internet and Political Trust in Africa}

\author[Illan Barriola, Rédha Chaba]{Illan Barriola\inst{1} \and Rédha Chaba\inst{2}}

\institute{
	\inst{1} CRED, Paris Panthéon Assas University, Paris, France
	\and
	\inst{2} LEMMA, Paris Panthéon Assas University, Paris, France
}
\date{June 26, 2025}

\begin{hidepagenumberframe}
    \titlepage
\end{hidepagenumberframe}

\addtocounter{framenumber}{-1}

\begin{frame}{Motivation}
\begin{itemize}
    \item Democracy requires citizens to both trust and distrust their politicians
    \vfill
    \begin{itemize}
        \item Trust to enable governance
        \vfill
        \item Distrust to prevent misgovernance
    \end{itemize}
    \vfill
\item In Sub-Saharan Africa: views of politicians and governments differ by region within countries
\vfill
    $\rightarrow$ People in remote areas tend to support them more than those near capital cities \textcolor{gray}{\textit{(Provenzano, 2024; Brinkerhoff et al., 2018)}}
\end{itemize}
\end{frame}

\begin{frame}{Greater support in remote regions}
\begin{itemize}
        \item State capacity diminishes in remote regions \textcolor{gray}{\textit{(Müller-Crepon, 2021; McKay et al., 2023)}}
        \vfill
    \begin{itemize}
        \item “\textit{The State stops twelve kilometers from the capital.}” (Bierschenk \& Olivier de \\
        \hspace{0.005em} Sardan, 1997)\\
        \vfill    
        $\rightarrow$ Citizens relate more to national institutions near capitals; remote areas maintain \\
        \hspace{1.1em} local/traditional focus \textcolor{gray}{\textit{(Herbst, 2000)}}\\
        \vfill
    \end{itemize}
\item Clientelist networks \textcolor{gray}{\textit{(Henn, 2023; Adida et al., 2020)}}
        \vfill
        \begin{itemize}
            \item More prevalent in remote regions where ethnic ties are stronger\\
            \vfill
        \end{itemize}
\item \textcolor[RGB]{220, 10, 10}{\textbf{Information gradient}} \textcolor{gray}{\textit{(Bhandari et al. 2023; Gottlieb, 2016)}}
\end{itemize}
\end{frame}

\begin{frame}{Information gradient}
\begin{itemize}
\item Information costs increase with distance from state presence and limited media coverage\\
\vfill
$\rightarrow$ Shortages of both direct and mediated information
\vfill
\item When information is scarce, citizens might end up trusting politicians in the absence of negative information
\end{itemize}
\end{frame}

\begin{frame}{Internet access}
\begin{itemize}
\item Mobile internet is changing traditional information geography in Sub-Saharan Africa
\vfill
\item Citizens in remote areas can now access diverse content that used to be concentrated near capitals
\vfill\begin{itemize}
    \vfill
    \item Including both political information
and misinformation
\end{itemize}
\vfill
\item Differs from traditional media by turning citizens from passive
consumers into active participants in different information networks
\vfill
\item \textcolor[RGB]{220, 10, 10}{\textbf{The impact on views of politicians is likely
to be larger in remote areas, where information costs have been highest}}
\end{itemize}
\end{frame}

\begin{frame}{Narrow spatial differences in political trust}
    \vspace{2em}
\centering    \begin{tikzpicture}
        \tikzset{
          node distance=5mm and 0mm,
          boite/.style={
            draw,align=center,
            font=\footnotesize\bfseries,text=black,
          },
          boite coins ronds/.style={boite,rounded corners=3pt},
          boite circulaire/.style={boite,circle},
          fleche/.style={
            line cap=round,-latex,line width=0.25mm,
          },
          grosse fleche/.style={fleche,line width=1mm},
          }
        \node[boite coins ronds, fill=white, below left=1cm] (a) {Close to the capital\\
        \vspace{0.01cm}\\
        \textcolor[RGB]{220, 10, 10}{- Political Trust}\\
        \textcolor[RGB]{220, 10, 10}{+ Perception of Corruption}};
        \node[boite coins ronds, fill=white, below right=1cm] (b) {Far from the capital\\
        \vspace{0.01cm}\\
        \textcolor{gray}{+ Political Trust}\\
        \textcolor{gray}{- Perception of Corruption}};
\node[boite coins ronds, fill=white, minimum width=7cm] (c) at (0,-3.5) {Internet use};
        \node[boite coins ronds,fill=white, below = 2cm of a] (d) {Close to the capital\\
        \vspace{0.01cm}\\
        \textcolor[RGB]{220, 10, 10}{- Political Trust}\\
        \textcolor[RGB]{220, 10, 10}{+ Perception of Corruption}};
        \node[boite coins ronds, fill=white, below=2cm of b] (e) {Far from the capital\\
        \vspace{0.01cm}\\
        \textcolor[RGB]{220, 10, 10}{- Political Trust}\\
        \textcolor[RGB]{220, 10, 10}{+ Perception of Corruption}};

        \begin{scope}[on background layer]
            \draw (a.south) -- ++(0,-1);
            \draw (b.south) -- ++(0,-1);
    \draw[->] (c.north -| a.south) -- (d.north -| a.south);
        \draw[->] (c.north -| b.south) -- (e.north -| b.south);
\node[font=\huge\bfseries] at ($(d.east)!0.5!(e.west)$) {\textcolor[RGB]{220, 10, 10}{=}};

        \end{scope}
      \end{tikzpicture}
\end{frame}

\begin{frame}{Related literature}
    \begin{itemize}
        \item Geography of trust\\
        \vfill
        \begin{itemize}
            \item McKay et al., 2019; Brinkerhoff et al. 2018; Yeandle, 2025\\
        \vfill
        \end{itemize}
        \item Internet and political behaviour\\
        \vfill
        \begin{itemize}
            \item Guriev et al. 2021; Cariolle et al. 2024; Manacorda and Tesei, 2020\\
        \vfill
        \end{itemize}
        \item Political economy of the capital city\\
        \vfill
        \begin{itemize}
            \item Provenzano, 2024; Michalopoulos and Papaioannou, 2014; Campante and Do, 2014\\
        \vfill
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Data}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}
    \item \textbf{Afrobarometer geocoded surveys}\\
    17 countries - Rounds 6-8 (2013-2021)
    \vspace{0.5em}
    \begin{itemize}
        \item Geolocated public opinion, media consumption, socio-demographics
        \vspace{0.5em}
        \item Distance calculations from capital cities
        \vspace{0.5em}
    \end{itemize}
    \vspace{0.5em}
    \item \textbf{GSMA internet coverage data}
    \vspace{0.5em}
    \begin{itemize}
        \item 3G coverage at 1×1-km resolution
     \vspace{0.5em}
        \item Aggregated to district level, weighted by population density
      \vspace{0.5em}
    \end{itemize}

\end{itemize}

\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/cty_spl.jpg}
    \caption{Country Sample and Capital Cities}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Internet and political trust}
\begin{equation}
    \fontsize{10}{11}\selectfont
    Trust_{irct} = \beta_{1} Dist_{irc} + \beta_{2} \textcolor[RGB]{220, 10, 10}{\textbf{Int\_use}_{rct}} + \beta_{3} \textcolor[RGB]{220, 10, 10}{\textbf{Dist} \times \textbf{Int\_use}_{irct}} + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{rt}
    \end{equation}
\vfill
\hspace{1em}
where\\
\vfill
    {\fontsize{10}{11}\selectfont
\begin{flushleft}
 \hspace{2.5em}
    - $Trust_{irct}$: average trust in president and parliament\\
    \vfill
\hspace{2.5em}
    - $Dist_{irc}$: normalized distance from the capital \textcolor{gray}{\textit{(Michalopoulos and Papaioannou, 2014)}}\\
    \vfill
 \hspace{2.5em}
   - \textcolor[RGB]{220, 10, 10}{\textbf{Int\_use}$_{rct}$:} district average of internet use\\
    \vfill
 \hspace{2.5em}
   - $X^{'}_{ir}$:
- Individual: socio-demographics, distances from largest non-capital city and roads, \\
\hspace{5.7em} traditional media consumption\\
\vfill
\hspace{5em}
- District: economic development, population density, area, terrain ruggedness, 2G \\
\hspace{5.7em} coverage president's birthplace\\    \vfill
\hspace{2.5em}
    - $\mu_{ct}$: country $\times$ time fixed effects\\ \vfill
\hspace{2.5em}
    - $\varepsilon_{rt}$: SE clustered at the region $\times$ time level

\end{flushleft}
    }
\end{frame}

\begin{frame}{Internet and political trust}
    \vfill
\begin{itemize}
    \item \textcolor[RGB]{220, 10, 10}{\textbf{Identification concerns:}} Reverse causality and unobserved factors
    \vfill
    \item \textcolor[rgb]{0.0,0.6,0.0}{\textbf{Instrumental variable:}} District average of 3G internet coverage weighted by population density \textcolor{gray}{(Guriev et al., 2021; Cariolle and Carroll, 2024)}\\
    \vfill
\end{itemize}

    \center

    \begin{tikzpicture}[
    node distance=3cm,
    every node/.style={draw, rounded corners, text width=2.5cm, text centered, minimum height=1cm},
    arrow/.style={->, thick},
    red arrow/.style={->, thick, black},
    blue arrow/.style={->, thick, black},
    dashed arrow/.style={->, thick, dashed, gray}]

\node[fill={rgb,255:red,216;green,236;blue,212}] (instrument) at (0,2) {3G Coverage};
\node[fill=red!20] (treatment) at (4.5,2) {Internet Use};
\node[fill={rgb,255:red,214;green,226;blue,247}] (outcome) at (9,2) {Political Trust};
\node[fill=gray!20] (confounder) at (4.5,-1) {Unobserved Factors};

\draw[blue arrow] (instrument) -- (treatment);
\draw[red arrow] (treatment) -- (outcome);
\draw[dashed arrow] (confounder) -- (treatment);
\draw[dashed arrow] (confounder.north) -- ([yshift=-3pt]outcome.south);

\end{tikzpicture}

\end{frame}

    \begin{frame}{Internet and political trust}
        \begin{itemize}
\item 
3G supply location is determined by economic rather than political factors
\vfill
\begin{itemize}
    \item 
Particularly in Sub-Saharan Africa where costly internet infrastructure is mainly deployed by profit-focused private companies
\end{itemize}
\vfill
\item Population weighting and controls for economic development and topographic features help ensure the exogeneity of our instrument
\vfill
\item \textcolor{gray}{Robustness: We explore another framework using lightning strike patterns to instrument for 3G internet supply}
\end{itemize}
\end{frame}

    \begin{frame}{Internet and political trust}
    \centering \textbf{First-stage}
\vspace{0.5em}
    \begin{equation}
    \fontsize{10}{11}\selectfont
    \textcolor[RGB]{220, 10, 10}{\textbf{Int\_use}_{rct}} = \beta_{1} Dist_{irc} + \beta_{2} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{3G\_coverage}_{rct}} + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{rt}
    \end{equation}
\\
\begin{equation}
    \fontsize{10}{11}\selectfont
    \textcolor[RGB]{220, 10, 10}{\textbf{Dist} \times \textbf{Int\_use}_{irct}} = \beta_{1} Dist_{irc} + \beta_{2} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{Dist} \times \textbf{3G\_coverage}_{irct}} + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{rt}
    \end{equation}
\\
    \centering \textbf{Second-stage}
    \vspace{0.5em}
    \begin{equation}
    \fontsize{10}{11}\selectfont
    Trust_{irct} = \beta_{1} Dist_{irc} + \beta_{2}^{2S} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{Int\_use}_{rct}} + \beta_{3}^{2S} \textcolor[rgb]{0.0,0.6,0.0}{\textbf{Dist} \times \textbf{Int\_use}_{irct}} + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{rt}
    \end{equation}

\end{frame}

\begin{frame}{Internet mitigates the distance effect}

\begin{figure}
    \includegraphics[scale=0.09]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/pol_trust_iv_10p.jpg}
    \caption{Marginal effect of distance from the capital as a function of internet use}
\end{figure}

\end{frame}

\begin{frame}{Internet mitigates the distance effect}
    \begin{table}[H]
    \centering
    \resizebox{10.5cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-5}
        \cmidrule(r){6-6}
        & \multicolumn{1}{c}{{Pol. trust}} & \multicolumn{1}{c}{{Dist. $\times$ Int. use}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Int. use}} & \multicolumn{1}{c}{{Pol. trust}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){5-5}    
        \cmidrule(r){6-6}    
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital&      0.514***&&&&       0.513***\\
\smallskip
&       (0.06)  &&&&      (0.09)   \\
Distance from the capital $\times$ Internet use&    -0.423***&&&&      -0.628***         \\
\smallskip
&       (0.09)   &&&&      (0.16)  \\
Internet use&     0.081*&&&&      -0.306        \\
\smallskip
        &     (0.05)   &&&&        (0.19)           \\

Distance from the capital city $\times$ 3G coverage&&0.733***  && -0.048\\
        \smallskip&& (0.06) &&  (0.10) \\
3G coverage &&-0.086***&&0.330***  \\
\medskip&& (0.02) && (0.05)\\

     \midrule
     SW \emph{F} - Distance $\times$ 3G coverage &-&-& 258.6 &-&-\\
     \smallskip
    SW \emph{F} - 3G coverage &-&-& 50.65 &-&-\\
    \smallskip
    Country X Round FE       & \checkmark & \checkmark&- & \checkmark & \checkmark \\
    Individual \& district controls  & \checkmark & \checkmark & - &  \checkmark & \checkmark\\
    \smallskip
    Observations       &       66,574    &66,574 & &       66,574 & 66,574  \\
    Adjusted-R$^2$    &       0.178     &-&-&-&-  \\
                          \bottomrule
    \multicolumn{6}{p{18cm}}{}
\end{tabular}}
    \caption{Effect of internet use on political trust by distance}

    \end{table}

\end{frame}

\begin{frame}{Internet mitigates the distance effect}
    \begin{itemize}
        \item Internet use shifts opinions in remote areas towards the critical views found near
capitals
\vfill
        \item We cannot disentangle whether citizens consume accurate information or misinformation\\
        \vfill
        $\rightarrow$ We explore institutional heterogeneity: traditional media freedom and corruption indexes
    \end{itemize}
\end{frame}

\begin{frame}{More pronounced where the state controls traditional media}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/rsf_iv_10p.jpg}
    \caption{Political Trust - Media Freedom}
\end{figure}
\end{frame}

\begin{frame}{Where there is corruption}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/pol_corr_gici_iv_10p.jpg}
    \caption{Political Corruption - Corruption Index}
\end{figure}
\end{frame}

\begin{frame}{Country heterogeneity}

\begin{table}[H]
    \centering
    \resizebox{10cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
        & \multicolumn{2}{c}{{Pol. Trust}} & \multicolumn{2}{c}{{Pol. Corr}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{2}{c}{{Media}} & \multicolumn{2}{c}{{Corruption}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}} & \multicolumn{1}{c}{{Low}} & \multicolumn{1}{c}{{High}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){4-4}
        \cmidrule(r){5-5}
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital        &      0.455***&       0.722***&           -0.533***&      -0.775***\\
\smallskip
&     (0.13)   &      (0.18)   &      (0.11)   &      (0.09)  \\
Distance from the capital $\times$ Int. use&      -0.250   &      -0.826***&         0.700** &       1.032***\\
\smallskip            &       (0.25)   &      (0.24)  &      (0.32)   &      (0.27)   \\

Internet use &       -0.262   &       0.047   &           -0.286   &      -0.687** \\
\medskip            &      (0.29)   &      (0.35)     &        (0.41)   &      (0.30)   \\

     \midrule
    Country X Round FE       & \checkmark & \checkmark & \checkmark & \checkmark \\
    Individual \& district controls   & \checkmark & \checkmark & \checkmark & \checkmark \\
    Geographic controls  & \checkmark & \checkmark & \checkmark & \checkmark  \\
    \smallskip
    Observations        &       31,210   &       35,364   &       17,745   &       44,633  \\
                          \bottomrule
    \multicolumn{5}{p{14cm}}{}
\end{tabular}}
    \caption{Media freedom and corruption level}
    \end{table}

\end{frame}

\begin{frame}{When education is low}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/educ_iv_10p.jpg}
    \caption{Political Trust - Education Level}
\end{figure}
\end{frame}

\begin{frame}{Individual heterogeneity}

        \begin{table}[H]
    \centering
    \resizebox{12cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{2}{c}{{Education}} & \multicolumn{3}{c}{{Age}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-6}
        & \multicolumn{1}{c}{{High}} & \multicolumn{1}{c}{{Low}} & \multicolumn{1}{c}{{18-25}} & \multicolumn{1}{c}{{26-40}} & \multicolumn{1}{c}{{41+}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){4-4}
        \cmidrule(r){5-5}
        \cmidrule(r){6-6}

        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}}\\

        \midrule

Distance from the capital        &      0.402** &       0.594***&       0.801***&       0.495***&       0.387***\\
\smallskip
            &     (0.16)   &      (0.11)               &     (0.13)   &      (0.12)   &      (0.12)   \\

Distance from the capital $\times$ Int. use&      -0.348*  &      -0.788***&      -0.916***&      -0.526***&      -0.501** \\
\smallskip            &     (0.21)   &      (0.21)              &     (0.19)   &      (0.18)   &      (0.21)   \\
Internet use &       -0.341   &      -0.167  &        0.019   &      -0.379   &      -0.473** \\
\medskip            &       (0.23)   &      (0.20)  &       (0.22)   &      (0.23)   &      (0.24)   \\

     \midrule
    Country X Round FE       & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    Individual \& district controls   & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark\\
    Geographic controls  & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark\\
    \smallskip
    Observations        &         20,428   &       46,146  &       17,519   &       27,607   &       21,614   \\
                          \bottomrule
    \multicolumn{5}{p{13cm}}{}
\end{tabular}}
    \caption{Political Trust - Individual Heterogeneity}

    \end{table}

\end{frame}

\begin{frame}{Other political outcomes}

        \begin{table}[H]
    \centering
    \resizebox{12cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{1}{c}{{Perf. Econ.}} & \multicolumn{1}{c}{{Account. Citizens}} & \multicolumn{1}{c}{{Account. Parl.}} & \multicolumn{1}{c}{{Vote Oppo.}}\\
        \cmidrule(r){2-2}
        \cmidrule(r){3-3}
        \cmidrule(r){4-4}
        \cmidrule(r){5-5}
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\

        \midrule

Distance from the capital         &       0.339***&      -0.099** &      -0.098** &       0.184** \\
\smallskip
            &      (0.10)   &      (0.04)   &      (0.04)   &      (0.07)   \\

Distance from the capital $\times$ Int. use&      -0.222** &       0.110** &       0.108** &      -0.178** \\
\smallskip
 &      (0.10)   &      (0.05)   &      (0.04)   &      (0.08)   \\
Internet use&       0.148   &      -0.037   &      -0.037   &      -0.063   \\
\medskip                        &      (0.11)   &      (0.05)   &      (0.05)   &      (0.08)   \\

     \midrule
    Country X Round FE       & \checkmark & \checkmark & \checkmark & \checkmark\\
    Individual \& district controls   & \checkmark & \checkmark & \checkmark & \checkmark\\
    Geographic controls  & \checkmark & \checkmark & \checkmark & \checkmark\\
    \smallskip
    Observations        &       65,364   &       66,612   &       65,728   &       45,329   \\
                          \bottomrule
    \multicolumn{5}{p{13cm}}{}
\end{tabular}}
    \caption{Other political outcomes}

    \end{table}

\end{frame}

\begin{frame}{Robustness}
\begin{itemize}
    \item Distance measures: km, log(km), mean normalization, excluding closest/furthest observations
    \vfill
    \item Geographical IV: Lightning strikes
    \vfill
    \item Leave-one-out regressions: Estimated coefficient and AR Weak IV test
\end{itemize}

\end{frame}

\begin{frame}{Conclusion}
    \begin{enumerate}
        \item \textcolor[RGB]{220, 10, 10}{\textbf{Internet use shifts opinions in remote areas}} towards the critical views found near capitals
        \vfill
        \item The reduction in spatial disparities in political trust is more pronounced in countries with \textcolor[RGB]{220, 10, 10}{\textbf{high corruption and where the state controls traditional media}}\\
        \vfill
        $\rightarrow$ Supports "liberation technology" arguments that the internet offers alternative information when traditional media are not transparent
        \vfill
        \item These attitude changes translate into \textcolor[RGB]{220, 10, 10}{\textbf{increased government accountability demands}} and opposition voting
    \end{enumerate}
\end{frame}

\begin{frame}{Next steps}
    \begin{itemize}
        \item Language: traditional media could be in a language that's difficult to access, while the internet can provide content in local languages
        \vfill
        \item Differences in internet news/use/social media news
        \vfill
        \item Positive/Negative events heterogeneity
        \vfill
        \item Submarine cables instrument
        \vfill
        \item Staggered DiD specification
        \vfill
        \item 0.5 $\times$ 0.5° grid focus
        \vfill
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{center}
        \Large Thank you!\\
        \vspace{1em}
        \textcolor{DarkBlue}{Illan.Barriola@assas-universite.fr}\\
        \vspace{1em}
        \textcolor{DarkBlue}{Redha.Chaba@assas-universite.fr}
    \end{center}
\end{frame}

\begin{frame}[noframenumbering]{Distance and political trust}
\begin{equation}
    \fontsize{10}{11}\selectfont
    Trust_{irct} = \beta_{1} Dist_{irc} + \Gamma X^{'}_{ir} + \mu_{ct}+ \varepsilon_{rt}
    \end{equation}
\vfill
\hspace{1em}
where\\
\vfill
    {\fontsize{9}{12}\selectfont
\begin{flushleft}
\hspace{2.5em}
    - $Trust_{irct}$: average trust in president and parliament\\
    \vfill
\hspace{2.5em}
    - $Dist_{irc}$: normalized distance from the capital \textcolor{gray}{\textit{(Michalopoulos and Papaioannou, 2014)}}\\
    \vfill
 \hspace{2.5em}
   - $X^{'}_{ir}$: individual and district controls\\ \vfill
 \hspace{5em}
- Individual: socio-demographics, distances from largest non-capital city and roads, traditional\\
 \hspace{10.3em}
 media consumption\\
\hspace{5em}
- District: economic development, population density, area, president's birthplace\\    \vfill
\hspace{2.5em}
    - $\mu_{ct}$: country $\times$ time fixed effects\\ \vfill
\hspace{2.5em}
    - $\varepsilon_{rt}$: SE clustered at the region $\times$ time level
\end{flushleft}
    }
\end{frame}

\begin{frame}[noframenumbering]{Distance and political trust}
    \begin{columns}
    \begin{column}{0.5\textwidth}
        \begin{figure}
    \centering
    \includegraphics[width=0.825\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_map.jpg}
    \caption{Ethnic Areas and National Boundaries}
\end{figure}
    \end{column}

    \begin{column}{0.5\textwidth}
        \begin{figure}
    \centering
    \includegraphics[width=0.385\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/benin_niger.jpg}
    \caption{Example: Dendi Ethnic Group}
\end{figure}

    \end{column}

\end{columns}
\end{frame}

\begin{frame}[noframenumbering]{Distance and political trust}
    \centering \textcolor[rgb]{0.0,0.6,0.0}{\textbf{Identification assumptions}}\vfill
    \setbeamertemplate{enumerate items}[default]
    \begin{enumerate}
        \item Two individuals living in the same historical ethnic group share similar characteristics, with distance from capital as the key differentiating factor \\ \vfill
        \textcolor{gray}{\textit{Michalopoulos and Papaioannou, 2014; Provenzano, 2024; McCauley and Posner, 2015}} \\ \vfill
        \begin{equation}
    Trust_{irct}=\beta_{1}Dist_{irc}+\Gamma X^{'}_{ir}+ \mu_{ct} + \textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\varepsilon_{ict}
    \end{equation}\vfill
        \item Cross-border variation in trust reflects distance effects rather than institutional differences between countries

\begin{equation}
    Trust_{irct}=\beta_{1}Dist_{irc}+\Gamma X^{'}_{ir}+ \textcolor[rgb]{0.0,0.6,0.0}{\theta Z^{'}_{ct}} + \textcolor[rgb]{0.0,0.6,0.0}{\mathbf{\nu_{e}}}+\textcolor[rgb]{0.0,0.6,0.0}{\lambda_{t}}+\varepsilon_{ict}
    \end{equation}

    \end{enumerate}
\end{frame}

\begin{frame}[noframenumbering]{Distance increases political trust}

\begin{figure}
    \includegraphics[scale=0.15]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/df_25_fe.jpg}
    \caption{Border discontinuity - \textit{Based on regression estimates from (2) of Table 1}}
\end{figure}

\end{frame}

\begin{frame}[noframenumbering]{Distance increases political trust}

    \begin{table}[H]
    \centering
    \resizebox{10cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c}
    \\
    \toprule
    \toprule
    & \multicolumn{1}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample (25km)}} \\
        \cmidrule(r){2-2}
        \cmidrule(r){3-4}
        & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{(3)}}\\
        \midrule

Distance from the capital   &       0.311***&       0.547** &       0.845***\\
\medskip
            &      (0.04)   &      (0.22)   &      (0.21)   \\

     \midrule
    Country X Round FE       & \checkmark & \checkmark & $\times$\\
    Country controls       & $\times$ & $\times$ & \checkmark\\
    Individual \& district controls   & \checkmark & \checkmark & \checkmark \\
    \smallskip
    Observations        &       66,574   &        5,494   &        5,494   \\
    Adjusted-R$^2$           &         0.176   &       0.168   &       0.139   \\
                          \bottomrule
    \multicolumn{4}{p{11cm}}{}
\end{tabular}}
    \caption{Effect of distance from the capital on political trust}
\end{table}

\end{frame}

\begin{frame}[noframenumbering]{Political corruption}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/pol_corr_iv_10p.jpg}
    \caption{Political corruption perception}
\end{figure}
\end{frame}

\begin{frame}[noframenumbering]{Political corruption perception}

        \begin{table}[H]
    \centering
    \resizebox{7cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c}
    \\
    \toprule
    \toprule
    & \multicolumn{1}{c}{{Pol. Corr}}\\
        \cmidrule(r){2-2}
        & \multicolumn{1}{c}{{(1)}}\\

        \midrule

Distance from the capital        &            -0.377***\\
\smallskip
            &      (0.07)   \\

Distance from the capital $\times$ Int. use &        0.522***\\
\smallskip
            &      (0.12)   \\

Internet use &       -0.154    \\
\medskip
            &      (0.16)   \\

     \midrule
    Country X Round FE       & \checkmark\\
    Individual \& district controls   & \checkmark\\
    Geographic controls  & \checkmark\\
    \smallskip
    Observations        &       62,378 \\
                          \bottomrule
    \multicolumn{2}{p{8cm}}{}
\end{tabular}}
    \caption{Political corruption perception}

    \end{table}

\end{frame}

\begin{frame}[noframenumbering]{Economic performance}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/perf_eco_iv_10p.jpg}
    \caption{Economic performance}
\end{figure}
\end{frame}

\begin{frame}[noframenumbering]{Accoutability towards citizens}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/check_citiz_iv_10p.jpg}
    \caption{Accoutability towards citizens}
\end{figure}
\end{frame}

\begin{frame}[noframenumbering]{Accoutability towards parliament}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/check_parl_iv_10p.jpg}
    \caption{Accoutability towards parliament}
\end{figure}
\end{frame}

\begin{frame}[noframenumbering]{Willingness to vote for the ruling party}
        \begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/marginal_effect/int_use_adm/vote_oppo_min_iv_10p.jpg}
    \caption{Willingness to vote for the ruling party}
\end{figure}
\end{frame}

\end{document}
